### 2016-08-08 AnalysisNote.tex
Initial commit

\documentclass[a4paper,12pt,twoside]{article}
        \usepackage{graphicx,type1cm,eso-pic,color}
        \usepackage{hyperref}
        \usepackage{longtable}
        \usepackage{amsmath,amssymb} 
        \usepackage[latin1]{inputenc}
        \usepackage[OT1]{fontenc}
        \usepackage{setspace}
        \usepackage{epigraph}

\hypersetup{
     backref=true,    %permet d'ajouter des liens dans...
     pagebackref=true,%...les bibliographies
     hyperindex=true, %...les index.
     colorlinks=true, %colorise les liens
     breaklinks=true, %permet le retour à la ligne dans les liens trop longs
     urlcolor= blue, %couleur des hyperliens
     linkcolor= black, %couleur des liens internes
     bookmarks=true, %créé des signets pour Acrobat
     bookmarksopen=true,            %si les signets Acrobat sont créés,
                                    %les afficher complètement.
     pdftitle={Hadronization Analysis Note (EG2)}, %informations apparaissant dans
     pdfauthor={Raphael Dupre},     %dans les informations du document
     pdfsubject={Physics}          %sous Acrobat.
}

\setlength{\hoffset}{-18pt}  	
\setlength{\oddsidemargin}{20pt} 	% Marge gauche sur pages impaires
\setlength{\evensidemargin}{20pt} 	% Marge gauche sur pages paires
\setlength{\marginparwidth}{54pt} 	% Largeur de note dans la marge
\setlength{\textwidth}{440pt} 		% Largeur de la zone de texte (17cm)
\setlength{\voffset}{18pt}	        % Bon pour DOS
\setlength{\marginparsep}{7pt} 	 	% Séparation de la marge
\setlength{\topmargin}{0pt} 	        % Pas de marge en haut
\setlength{\headheight}{13pt} 		% Haut de page
\setlength{\headsep}{0pt}              % Entre le haut de page et le texte
\setlength{\footskip}{27pt} 	        % Bas de page + séparation
\setlength{\textheight}{600pt} 	 	% Hauteur de la zone de texte (25cm)

\newcommand{\xbp}{$x_{Bj}$}
\newcommand{\xb}{$x_{Bj}~$}
\newcommand{\ptp}{$p_\perp^2$}
\newcommand{\pt}{$p_\perp^2~$}
\newcommand{\dptp}{$\Delta \langle p_\perp^2 \rangle$}
\newcommand{\dpt}{$\Delta \langle p_\perp^2 \rangle ~$}

\makeatother

\title{Study of the hadronization of $\pi^-$}

\author{Rapha\"el \textsc{Dupr\'e}, 
Lamiaa \textsc{El Fassi}\thanks{also {\it Rutgers University}} , 
Kawtar \textsc{Hafidi} ... \\ 
{\it Physics Division, Argonne National Laboratory,} \\
{\it Argonne, Illinois 60439, USA} }

\date{\today}

\begin{document}

\maketitle

%doublespacing
%onehalfspacing
%\linenumbers
\renewcommand{\baselinestretch}{1.10}

\begin{abstract}
Hadronization is the process by which energetic quarks transform into 
colorless hadrons. The process is non-perturbative, therefore, only 
qualitative understanding can be achieved, and using phenomenological models 
is necessary. It is believed that hadronization has two distinct phases: 
the quark propagation phase, where the quark emit gluons until it neutralizes 
its color by forming a pre-hadron and the hadron formation phase, where the 
pre-hadron evolves into a hadron. Those process are respectively characterized 
by the production time and the formation time. By comparing hadron production 
on different nuclei, one can measure variables with different sensitivities 
to the hadronization phases, the two principal variables are: the transverse 
momentum broadening, that is believed to be tightly connected to quark energy 
loss and the multiplicity ratio, which is a measure of the hadron attenuation 
in the medium.

The goals of the experiment E-02-104 are to study both quark propagation
and hadronization dynamic using various nuclear target.
In this analysis we focus on two particles, the negative pion and the proton.
Our goals are to constrain the theoritical models and extract the production
time using precise multidimensional analysis of $\pi^+$ and $\pi^-$ to enlight possible
new physical processes with a precise analysis of proton production in nuclei.

\end{abstract}

\newpage

\tableofcontents

\newpage

\include{intro}

\include{chap5}

\include{chap6}

\bibliography{hadro}
\bibliographystyle{plain}

\end{document}

### 2016-08-08 chap5.tex
Initial commit

\section{Data Analysis}
\label{chap:analysis}

\subsection{Introduction}

This chapter treats of the analysis of the data taken in CLAS for the 
experiments E-02-104 \cite{Brooks:2002aa} and E-02-110 \cite{Hafidi:2002aa}.
The code name for the run is {\it eg2}, it was composed of three phases 
labeled {\it a}, {\it b} and {\it c}. The analysis is performed on the data 
collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
which the beam energy was 5.014 GeV\footnote{The other phases gave a small 
amount of data at a beam energy of 4 GeV.}.

As the two experiments, running simultaneously, aimed at comparing deuterium 
with heavier nuclei, it was decided to use a double target system 
\cite{Hakobyan:2008zz}. The first target is filled with liquid deuterium and 
the second is a solid target. The latter can be made of carbon, aluminum, 
iron, tin or lead and changed remotely (the system is shown in figure 
\ref{fig:phototarget}). The two targets are separated by only 4~cm in order to reduce
the acceptance differences between them. The 
advantage to have the two targets in the beam line simultaneously
is that several systematic effects related to the beam 
and detector properties will cancel in the nuclear ratio.

\begin{figure}[htbp]
\centering
\includegraphics[width=7cm] {chap5-fig/PhTar.jpg} 
\caption {Picture of the target system of the {\it eg2} run. The cryogenic target is 
in the back, enveloped in aluminum foils. The solid targets are held by mechanical arms
allowing to change targets remotely, in the picture the top arm is in the beam line.}
\label{fig:phototarget}
\end{figure}

The analysis of the experiment E-02-110, focusing on the study of color 
transparency effects, has been approved recently \cite{ElFassi:2008}. As this 
analysis went through a careful review by the CLAS collaboration, we use
similar analysis methods when possible. In particular, the electron selection 
presented here is very similar to theirs; the main difference being a new 
target determination method.

In the section \ref{sec:pid}, we identify the following particles e$^-$, 
$\pi^-$ and $\pi^+$ using a series of cuts on the various 
detector outputs. For pions, we use the signal in the drift chambers (DC) and 
in the scintillator counters (SC), for which we require a positive status (global and DC) 
from the reconstruction code. For electron identification, we use signals from 
all detector parts DC, Cherenkov Counters (CC), SC and Electromagnetic 
Calorimeter (EC).

Once particles are identified, we can extract the observables (multiplicity 
ratio and transverse momentum broadening). The method is presented in the 
section \ref{sec:obs}, however these need several corrections presented in the 
section \ref{sec:corrections}. The 
two main corrections are the acceptance of the detector and the radiative 
effects, both are evaluated using Monte-Carlo generator. The evaluation of 
the systematic errors is presented in the section \ref{sec:TotSys}.
The analysis' final results are presented and discussed in the next chapter.

\subsection{Particle Identification}
\label{sec:pid}

\subsubsection{Electron Identification}

First, we apply a fiducial cut on the EC to remove the electrons detected on 
the edge of the calorimeter ($U_{EC}>40$~cm, $V_{EC}<360$~cm and 
$W_{EC}<395$~cm in the calorimeter's coordinates). These are problematic hits 
because the generated electromagnetic shower might be partly outside the 
detector, leading to a wrong measurement of the energy deposited.

To reject pions, we apply cuts on the energy deposited
in the EC using the measurements in the inner ($E_{in}$) and the 
outer part ($E_{out})$ of the calorimeter:

\begin{equation}
\label{einout}
\mu  \left[1-\frac{0.3}{\sqrt{a}}\right] - \frac{E_{in}}{p} \leq 
\frac{E_{out}}{p} \leq 
\mu  \left[1+\frac{0.3}{\sqrt{b}}\right] - \frac{E_{in}}{p},
\end{equation}

where $\mu = 0.271$ is the mean of the fraction of the energy deposited in the 
calorimeter by electrons, the $a$ parameter is set at 0.5 and the parameter 
$b$ is a function of momentum given in table \ref{tab:ecoutin-par}. The 
adjustment of $b$ is motivated by the non-linear dependence of the energy 
deposited as a function of the particle's momentum (see figure \ref{eleEC}). As pions are 
minimum ionizing particles, they are expected to lose a constant energy in 
the inner part of the calorimeter (around 30~MeV), regardless of their 
momentum. Therefore, by requesting more than 60~MeV to be deposited, we 
efficiently cut the pion contamination (see figure~\ref{eleECi}).

\begin{table}[tbp]
  \centering
  \begin{tabular}{@{} cc @{}}
    \hline
    Momentum bin (GeV/c)& Parameter b \\ 
    \hline
    0.5 - 0.7 & 0.85 \\
    0.7 - 0.9 & 0.8  \\
    0.9 - 1.1 & 0.85 \\
    1.1 - 1.3 & 1.05 \\
    1.3 - 1.5 & 1.1  \\
    1.5 - 1.7 & 1.35 \\
    1.7 - 1.9 & 1.35 \\
    1.9 - 2.1 & 1.45 \\
    2.1 - 2.3 & 1.35 \\
    2.3 - 2.5 & 1.35 \\
    2.5 - 2.7 & 1.35 \\
    2.7 - 2.9 & 1.3  \\
    2.9 - 3.1 & 1.35 \\
    3.1 - 3.3 & 1.35 \\
    3.3 - 3.5 & 1.5  \\
    3.5 - 3.7 & 1.6  \\
    3.7 - 3.9 & 1.8  \\
    3.9 - 4.1 & 1.8  \\
    4.1 - 4.3 & 1.8  \\
    4.3 - 4.5 & 1.8  \\
    \hline
  \end{tabular}
  \caption{Values of the parameter $b$ used in equation \ref{einout} for 
           different momentum ranges.}
  \label{tab:ecoutin-par}
\end{table}

\begin{figure}[p]
\centering
\includegraphics[width=14cm] {chap5-fig/fig02.jpg} 
\caption {Energy deposited in the inner part of the EC ($E_{in})$) as a function of the 
energy deposited in the outer part ($E_{out})$), both divided by the momentum of the 
particle. Each panel is for a different momentum range, the red lines 
illustrate the cuts from equation \ref{einout}.}
\label{eleEC}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=9cm] {chap5-fig/fig03.png} 
\caption {Energy deposited in the inner part of the EC as a function of the 
energy in the outer part. The red line illustrates the cut applied for 
electron selection.}
\label{eleECi}
\end{figure}

In the CC, the mean number of photo-electrons\footnote{Photo-electrons are 
electrons produced in the front window of the Photo-Multiplier Tube (PMT) by 
single photons.} from a high energy electron is expected to be around 10.
However, hadrons can generate noise due to $\delta$ electrons produced in 
the materials of the detector. This signal is expected around 
one photo-electron, to remove it, we keep only tracks with more than 
2.5~photo-electrons (figure \ref{delta}).

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/fig04.png} 
\caption {Number of photo-electrons ($\times 10$) per tracks, the red line 
shows the cut to remove pion contamination.}
\label{delta}
\end{figure}

To select electrons, we also require that the particles are negatively charged, 
according to the bending direction of the tracks in the drift chamber.
Positively charged particles are identified as positrons. In the rest of the 
analysis we use events with only one electron and no positron to avoid any 
confusion between the scattered electron and electrons from hadronic decays or 
photon conversion to $e^+e^-$ pair, which often lead to the production of a
positron.

\subsubsection{$\pi^-$ Identification}
\label{PiId}

To identify negatively charged pions, we select negative tracks, which are not 
identified as electron. Pions are detected in the angular range from $\sim$10 to 
$\sim$140 degrees using the DC and SC only.

The identification consists mostly of a time of flight (TOF) test. We define 
$\Delta \beta = \beta_{measured} - {p \over \sqrt{p^2 + m_\pi^2}}$ and request 
$\Delta \beta$ to be zero within $\pm 0.03$. Figure \ref{PionTOF} illustrates 
the effect of this cut. We notice that there is not much negative kaons or 
anti-protons. Therefore, the contamination from these should be small (see 
section \ref{SysId} for more detailed analysis).

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/fig05.png} 
\caption {$\Delta \beta$ as a 
function of momentum (GeV/c). Only negative particles are plotted. The red 
lines are the cuts applied to select negative pions.}
\label{PionTOF}
\end{figure}

In principle, pion identification could be improved using the Cherenkov counter 
for momentum higher than 2.5~GeV/c. But, the low efficiency observed (figure 
\ref{PionCC}), especially at momentum close to the threshold ($\sim$25\% at 
2.5~GeV/c and $\sim$50\% at 3~GeV/c), makes its use less compelling. 
Moreover, as only a very small amount of $K^-$ and no $\bar p$ are present on 
the figure \ref{PionTOF}, we decided not to use the CC for pion identification.

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/fig06.png} 
\caption {Histograms of momentum (GeV/c) for $\pi^-$. In black are all 
identified $\pi^-$, in red pions that also fire in the Cherenkov counter and 
in blue those that fire in the Cherenkov counter with more than 
1 photo-electrons.}
\label{PionCC}
\end{figure}

\subsubsection{$\pi^+$ Identification}

The identification of positively charged pions is similar to that of negative 
pions. However, the time of flight plot is significantly more busy (figure 
\ref{PipTOF}), showing significant contamination from $K^+$ and protons at 
high momentum. As the CC is not efficient enough for hadron separation, the 
numerous kaons and protons should be removed by a tighter TOF cut:

\begin{subequations}\label{TOF-Pip}
\begin{align}
    p_\pi &\leq 3.375 \text{ GeV/c : }
  & \Delta \beta &> \max\left(-0.03,{p \over\sqrt{p^2+0.4^2}}\right), \\ 
    p_\pi &> 3.375    \text{ GeV/c : }
  & \Delta \beta &> \max\left(-0.02,{p \over\sqrt{p^2+0.7^2}}\right).
\end{align}
\end{subequations}

These cuts permit to minimize the kaon contamination, below 2.5~GeV/c, and the 
proton contamination for all momentum. The kaon contribution cannot be avoided, however 
it should remain a small contribution ($\sim$ 3\% according to simulation) 
with only a small effect on the final results (see section \ref{SysId} 
for details). Because protons could lead to even more contamination than kaons, 
a stricter cut is used at high momentum. This cut is also justified by 
HERMES data \cite{Airapetian:2007vu}, which show a very 
different behavior of the protons compared to the other hadrons (see chapter \ref{chap:data}).

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/pip_data.png} 
\caption {$\Delta \beta$ as a 
function of momentum (GeV/c). Only positive particles are shown, the red 
lines are the cuts applied to select positive pions. The blue lines indicate 
theoretical positions for other particle masses, are plotted from top to 
bottom the lines for positrons, muons, kaons and protons.}
\label{PipTOF}
\end{figure}

\subsubsection{Target Determination}

To differentiate the two targets and remove the background, we need to 
determine the origin of the particles. It appears that the different sectors 
are shifted in $z$ (figure \ref{vertex}), because of a small misalignment of 
the beam with the detector. To correct this problem, we apply the modification shown in table 
\ref{tab:vertex} for the vertex determination. Those values were determined by 
fitting the solid target position viewed by each sector.

\begin{table}[p]
  \centering
  \begin{tabular}{@{} cc @{}}
    \hline
    Sector & Shift (cm) \\ 
    \hline
    1 & + 0.1 \\ 
    2 & - 0.4 \\ 
    3 & - 0.6 \\ 
    4 & - 0.1 \\ 
    5 & + 0.4 \\ 
    6 & + 0.6 \\ 
    \hline
  \end{tabular}
  \caption{Values used to correct the vertex information for all sectors}
  \label{tab:vertex}
\end{table}

The position of the targets may also vary from one run to another, but 
this does not happen too often. Indeed, except for aluminum, the targets remain in 
the same position within one or two millimeters. The positions, in CLAS 
coordinates, are given in table \ref{tab:targets}.

\begin{table}[p]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    Target & Carbon & Al (1) & Al (2) & Iron   & Tin    & Lead   \\ 
    \hline \hline
    Liquid & -30.1  & n/a    & n/a    & -30.2  & -30.1  & -30.1  \\ 
    Solid  & -24.7  & -25.0  & -23.8  & -24.9  & -23.8  & -24.9  \\
    \hline
  \end{tabular}
  \caption{Measured mean vertex position of targets, relative to the center of 
           CLAS (in cm). (Aluminum data are separated in two sets because the 
           target position appears to have changed at some point.)}
  \label{tab:targets}
\end{table}

\begin{figure}[p]
\centering
\includegraphics[width=10cm] {chap5-fig/Vertex_el_data.png}
\caption {In each sector, the reconstructed vertex of electrons along the beam
direction relatively to the center of CLAS. The red lines show the cuts 
to select the targets.}
\label{vertex}
\end{figure}

The detected electrons are associated with the solid target if their vertex 
position is at less than 1.5~cm ($\sim$3~$\sigma$) from the value of table 
\ref{tab:targets}. For the liquid target, the cut is larger, 2 cm, in order to 
account for the size of the target (see figure \ref{vertex}). The vertex of 
the pions is checked against the electron one and we request that 
$| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/Vertex_pi_data.png}
\caption {Distance along the beam axis between the electrons and pions 
vertexes. $\pi^+$ are plotted in the top panel and the $\pi^-$ in the bottom.
The red lines show the cuts applied to select pions.}
\label{fig:dvzpi}
\end{figure}

\subsubsection{Data Quality}

To check the quality of the runs\footnote{Runs correspond roughly to two hours
of data, they can be smaller in case of problem.}, we look at the ratio of the number of 
scattered electrons, between the liquid and solid targets. If the beam is 
hitting other materials than the targets or if the detector is not working 
properly this ratio can be off and indicates a problematic run. The figure 
\ref{DataQ} shows the values obtained; we fit the 
mean value for all runs of each target and eliminate runs away by more than 
5$\sigma$. We note that the ratios are coherent with target thicknesses given 
in \cite{Hakobyan:2008zz} except for carbon. Because of this, the density of 
the carbon target was remeasured recently and found to be coherent with the 
data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.

\begin{figure}[tbp]
\centering
\includegraphics[width=15cm] {chap5-fig/TargetElRatio.png}
\caption {Ratio of the number of electrons scattered by the targets (solid over deuterium) 
for each run.}
\label{DataQ}
\end{figure}

\subsection{Extraction of Multiplicity Ratio and $\Delta$P$_\perp^2$}
\label{sec:obs}

Since we are interested in deep inelastic scattering, we use the following 
cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut $y < 0.85$ to 
reduce the impact of radiative effects, which will be discussed in more details in 
the section \ref{RadCor}.

\subsubsection{Method}
\label{RatioCalc}

Once the identification is done, the calculation of the observables is 
straight forward and the statistical errors are calculated with this expression

\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = \sqrt{ 1 /N_A^h + 1/ N_A^e +1/N_D^h + 1/N_D^e}
\end{equation}
and
\begin{equation}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_A / N_A^h
 + \left ({\langle P_\perp^4 \rangle - \langle P_\perp^2 \rangle ^2}\right )_D / N_D^h.
\end{equation}

The implementation of acceptance and radiative corrections is done through weights
given to each particles depending on its kinematic. The multiplicity ratio becomes

\begin{equation}
R_A^h (Q^2,\nu,z_h,P_\perp^2) = {{\sum \omega_A^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_A^e (Q^2,\nu)} 
                       \over {\sum \omega_D^h (Q^2,\nu,z_h,P_\perp^2) / \sum \omega_D^e (Q^2,\nu)}},
\end{equation}
with $\omega$ the weights and all the sums running over all measured particles.
The expression for the transverse momentum broadening remains
\begin{equation}
\Delta \langle P_\perp^2 \rangle = \langle P_\perp^2 \rangle_A - \langle P_\perp^2 \rangle_D,
\end{equation}
but with
\begin{equation}
\langle P_\perp^2 \rangle = {\sum P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
\end{equation}

This expressions leads to new expressions for the statistical error uncertainties:

\begin{equation}
{\delta \left ( R_A^h \right ) \over R_A^h} = 
      \sqrt{ \left ( {\sum {\omega^h_A}^2 \over \left (\sum \omega^h_A \right )^2} \right ) 
           + \left ( {\sum {\omega^e_A}^2 \over \left (\sum \omega^e_A \right )^2} \right ) 
           + \left ( {\sum {\omega^h_D}^2 \over \left (\sum \omega^h_D \right )^2} \right ) 
           + \left ( {\sum {\omega^e_D}^2 \over \left (\sum \omega^e_D \right )^2} \right ) }
\end{equation}
 and 
\begin{equation}
\begin{split}
\left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
 + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
\end{split}
\end{equation}

\subsubsection{Preliminary Results}
\label{prelim}

We present in figure \ref{fig:prelim} few preliminary results, before the application of any correction, with the goal to 
provide a first idea on data quality. The preliminary results will also be used to 
illustrate the effects of the corrections discussed below.

\begin{figure}[htb]
\centering
\includegraphics[width=7.4cm] {chap5-fig/a_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/a_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/a_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/a_PvNu.png} 
\caption {Results for multiplicity ratios (top) and transverse momentum 
broadening (bottom) without correction.}
\label{fig:prelim}
\end{figure}

\subsection{Corrections}
\label{sec:corrections}

\subsubsection{Acceptance Correction}
\label{sec:accept}

The acceptance correction consists of applying weights to the events in 
experimental data to correct for the inefficient parts of the detectors.
Incidentally, it also corrects for small other issues of detection,
such as misidentification and scattering on detectors materials. The quality 
of the correction depends on the ability of the simulation to reproduce the 
experiment, the statistics accumulated and the size of interfering effects, such 
as bin migration.

\paragraph{Simulation}
\label{sec:simul}

To correct for acceptance effects, we simulated a total of a 100 million events 
per target ($^2$H, C, Fe and Pb) using the PYTHIA \cite{Sjostrand:2006za} 
event generator slightly modified to include Fermi motion effects. The 
generated events are processed by the CLAS software (GSIM, GPP and user\_ana) 
to simulate the detector and the reconstruction process similarly to the one for experimental data.

Then the simulated data are processed in a similar way than the experimental data by 
applying the cuts described in the section \ref{sec:pid}. Overall the 
simulation reproduces quite well the detectors responses, yet two issues might 
affect us and have to be understood. First, the efficiency of the CC is overestimated in the simulation. 
On the electron side the signal is a little stronger in the simulation (11 
photo-electrons) compared to experimental data (8 photo-electrons), but this 
feature should not affect us too much, because we are cutting only the tail of the 
distribution in both cases. For pion identification, as mentioned in section \ref{PiId},
we do not use the CC because of its unexpectedly low efficiency 
We observe, in the simulation, a much better detector response than in experiment 
(figure \ref{simPionCC} compared to figure \ref{PionCC}), this result also advocates against the use of the CC in the 
particle identification. Indeed, the poor reproduction of the experimental signal would introduce a bias in our acceptance correction. 
Second, in figure \ref{vertex} the cuts on vertex are shifted from one sector 
to another, since the simulation have perfect alignment of beam with CLAS this 
feature is not present in the simulated data. Therefore, we do not apply the 
shift from the table \ref{tab:vertex} to the simulation; results are shown in 
figure~\ref{simvertex}.

\begin{figure}[tpb]
\centering
\includegraphics[width=9cm] {chap5-fig/fig06simul.png} 
\caption {Histograms of momentum (GeV/c) of $\pi^-$ for {\bf simulated data}.
In black are all identified $\pi^-$, in red pions that also fire in the 
Cherenkov counter and in blue those that fire in the Cherenkov counter with 
more than one photo-electron.}
\label{simPionCC}
\end{figure}

\begin{figure}[tpb]
\centering
\includegraphics[width=9cm] {chap5-fig/Vertex_el_sim.png}
\caption {Reconstructed vertex position, along the beam direction, with values 
relative to CLAS center, for electrons from {\bf simulated data} and each 
sector. The red lines show the cuts used to select the targets.}
\label{simvertex}
\end{figure}

The kinematic distributions from the simulation are compared to the 
experimental ones. This is important for the acceptance correction, to see 
whether or not, we can integrate over these variables for the correction.
Comparisons between simulation and experiment are shown in figures 
\ref{fig:compNuQ2} to \ref{fig:compPhih}. The agreement is reasonable, but not 
perfect. The differences are due to the PYTHIA simulation, which is not including some 
physical effects, such as radiative and diffractive processes.

\begin{figure}[tbp]
\centering
\includegraphics[width=12cm] {chap5-fig/El_compar.png}
\caption {Comparisons, for $Q^2$ (GeV$^2$/c$^2$) and $\nu$ (GeV), of the distributions
from simulated (red crosses) and experimental (histogram) data using deuterium target.}
\label{fig:compNuQ2}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=12cm] {chap5-fig/z_compar.png}
\caption {Comparisons, for $z$ of charged pions, of the distributions
from simulated (red crosses) and experimental (histogram) data using deuterium target.}
\label{fig:compZ}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=12cm] {chap5-fig/pts_compar.png}
\caption {Comparisons, for \pt (GeV$^2$/c$^2$) of charged pions, of the distributions
from simulated (red crosses) and experimental (histogram) data using deuterium target.}
\label{fig:compPts}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=12cm] {chap5-fig/phih_compar.png}
\caption {Comparisons, for $\phi_h$ of charged pions, of the distributions
from simulated (red crosses) and experimental (histogram) data using deuterium target.}
\label{fig:compPhih}
\end{figure}

\paragraph{Correction of the Data}

The acceptance is defined as the ratio of reconstructed events over generated ones,

\begin{equation}
\label{eq:acc}
\text{Acc} = {N_{rec} \over N_{gen}}.
\end{equation}

The data is corrected using weights defined as $\omega = 1/\text{Acc}$. The 
$\omega$ coefficient are calculated in many bins, in order to be independent of 
the imperfections of the event generator. However, an excess of bin could results into a strong 
bin migration\footnote{Fraction of events not reconstructed in the bin they 
were produced in.}, which might introduce a bias if it becomes a large effect.

We use a 4-dimensional binning to divide the large phase space available to 
the two particles in the measured final state. To evaluate the systematic error 
associated to the correction, we use two different binning, which are 
presented in the table \ref{tab:AcceptBinning}. The total number of bins is 
constrained by the amount of data generated and has to be maintained 
reasonably low in order to keep a good statistical precision and reasonable 
bin migration.

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{} cc @{}}
    \hline
    Variable & Number of bins \\ 
    \hline
    $\nu$    & 5 \\
    $x_{Bj}$ & 5 \\
    $p_h$    & 7 \\
    $t$      & 7 \\
    \hline
    Total    & 1225 \\
    \hline
  \end{tabular}
  \begin{tabular}{@{} c @{}}
  ~~~~~~\\
  ~~~~~~\\
  \end{tabular}
  \begin{tabular}{@{} cc @{}}
    \hline
    Variable & Number of bins \\ 
    \hline
    $Q^2$    & 5 \\
    $\nu$    & 5 \\
    $z_h$    & 7 \\
    $t$      & 7 \\
    \hline
    Total    & 1225 \\
    \hline
  \end{tabular}
  \caption{Variables and their associated number of bins used for the 
   multi-dimensional binning of the acceptance correction. The left panel 
   shows the variables used for the correction and the right panel the 
   variables used for the evaluation of the systematic error.}
  \label{tab:AcceptBinning}
\end{table}

The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
the simulation using equation \ref{eq:acc}, however, it appears that these should not be used directly.
Three factors are sources of problematic bins:
\begin{itemize}
 \item too large weight values, i.e. very small acceptance;
 \item very few events reconstructed, leading to large statistical errors;
 \item many events that were generated in another bin (bin migration).
\end{itemize}
To remove these bins we apply the following cuts:
\begin{equation} \label{eq:AccL1}
\left ({\delta \omega \over \omega}\right ) ^2 \times {R_c \over \omega} < 2,
\end{equation}
and
\begin{equation} \label{eq:AccL2}
N_{rec} > 4,
\end{equation}
with $\delta \omega / \omega$ the relative error on the weight and $R_c$ the 
proportion of events in the bin initially generated in another bin. Figure 
\ref{fig:AccCoef} shows the distributions of $\omega$, after the cuts. Around 
900 bins remain for both targets, but we notice that weights are much larger 
for $\pi^-$, indicating a larger correction, compared to $\pi^+$. In order to 
maximize the acceptance and reduce the sensitivity to the cuts applied on the 
weights, which are arbitrary, the bin weights are corrected. We apply a 
reweighting by calculating a new acceptance in a two dimensional binning:
\begin{equation}
\text{Acc}_2(\nu,p_h) = {\sum_{rec} \omega (\nu,x_{Bj},p_h,t)\over N_{gen}(\nu,p_h)}.
\end{equation}
with $\omega$ either the previously calculated weights or one for the 
excluded bins.
One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
\ref{eq:AccL2} is to keep the reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
percents level.

\begin{figure}[tbp]
\centering
\includegraphics[width=14cm] {chap5-fig/pawpipdeut.png}
\caption {Acceptance weights for pions in deuterium (not reweighted).}
\label{fig:AccCoef}
\end{figure}

The electron acceptance, necessary in order to correct the number of electrons 
in the multiplicity ratios, is done with the same method than in the 
semi-inclusive case, but only using the two first dimensions ($\nu$ 
and $Q^2$). It is also interesting to note that no reweighting is necessary 
for electrons as all non-empty bins pass the cuts \ref{eq:AccL1} and 
\ref{eq:AccL2}.

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
\caption {Preliminary results are compared with results corrected for 
acceptance, for multiplicity ratios (top) and transverse momentum broadening 
(bottom). Only statistical errors are shown.}
\label{fig:AcceptPlots}
\end{figure}

Figure \ref{fig:AcceptPlots}, where only statistical errors are 
represented, shows the new results after applying the acceptance correction.
The acceptance effects appear to be of $\sim 10$\% for multiplicity ratios and 
$\sim 30$\% for transverse momentum broadening. This is a surprisingly 
significant correction for the few centimeters between the two targets. The 
$\pi^-$s are more affected because of CLAS' magnetic field. Indeed, the low \pt
$\pi^-$s have very low acceptance, this makes the errors 
on \dpt very large and the related results difficult to exploit. Finally, because 
of some difference in position between the solid targets (table 
\ref{tab:targets}), some extra simulation is needed in order to exploit 
correctly the aluminum and tin results. Therefore, these two targets should not be considered for 
the final results.

\subsubsection{Coulomb Correction}
\label{CCor}

The large charge of the nuclear targets create an electric field that should 
be accounted for at our energies. This nuclear electric field accelerate or 
decelerate the incoming and outgoing charged particles, it also has non 
trivial effects such as focussing effects at lower energies. Aste {\it et 
al.}~\cite{Aste:2005wc} have shown that an effective momentum approximation is 
reliable for larger momentums ($Q^2>.5$ GeV$^2$). Being clearly beyond this 
limit and the Coulomb correction being relatively small in our kinematic, we 
decide to use such an approximation. Following the prescription from Aste 
{\it et al.} we use an effective potential $\bar V= 0.8 V_0$, that they found 
best suited when using such approximation. $V_0$ being the electrostatic 
potential in the center of the nuclei, {\it i.e.}: $V_0= -3 \alpha_{EM} Z / 
(2 R)$. Values for $V_0$ and $\bar V$ used in this analysis are given in 
table~\ref{tab:Coulomb}. Coulomb corrections are applied on electrons, and
both charged pions before to calculate the kinematic variables.

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{} ccc @{}}
    \hline
Nucleus & $V_0$ (MeV)  &  $\bar V$ (MeV) \\ \hline
$^2$H  & -1  &     -1 \\
C   &  -4 &      -3 \\
Al  &  -7 &      -6 \\
Fe  & -11 &    -9 \\
Sn  & -17 &   -14 \\
Pb  & -23 &   -19 \\
    \hline
  \end{tabular}
  \caption{Values for $V_0$ and $\bar V$ used for Coulomb correction of charged particles.}
  \label{tab:Coulomb}
\end{table}

\subsubsection{Radiative Correction}
\label{RadCor}

Despite its lower magnitude, compared to the strong force, the 
electromagnetic force might have a non negligible impact on our results. The 
reason is that even a moderate energy photon 
emission can modify significantly the measured kinematic variables.
To correct this effect, several simulation codes exist \cite{Akushevich:2001yp}, 
however, none permit to treat directly semi-inclusive DIS on nuclei. In order 
to make the correction, a dedicated Monte-Carlo simulation, based on existing 
codes, was developed.

\paragraph{Simulation}

The inclusive radiative effects are generated using the RADGEN software 
\cite{Akushevich:1998ft}, which includes the Feynman diagrams shown in 
figure~\ref{fig:FDRadCorr}. This code evaluates directly the correction 
factors ($\delta = \sigma_{obs} / \sigma_{Born}$) to apply for inclusive 
measurements. As RADGEN is also a Monte-Carlo generator of photon emissions, 
it can be used to modify the virtual photon kinematic before the 
hadron production in any DIS generator. This allows to evaluate the radiative 
effects on semi-inclusive measurements by implementing RADGEN inside a full 
Monte-Carlo event generator.

\begin{figure}[htbp]
\centering
\includegraphics[width=12cm] {chap5-fig/RadDiag.png}
\caption {Diagrams taken into account in RADGEN \cite{Akushevich:1998ft}. The 
diagrams b) to e) contribute to the first order calculation of the radiative 
effects on Born cross section (diagram a)).}
\label{fig:FDRadCorr}
\end{figure}

The Monte-Carlo simulation we use is the GENIE software 
\cite{Andreopoulos:2009rq}, which describes well electron-nuclei scattering. 
Indeed, GENIE includes quasi-elastic scattering\footnote{Elastic 
scattering on a single nucleon of a nuclei.}, which is the main channel contributing 
to the radiative events in the DIS region \cite{Akushevich:2007jc}. The GENIE 
software includes also hadron cascades in the nuclei, which lead to the 
possibility to generate pions in quasi-elastic events. This is an important 
feature because the quasi-elastic cannot contribute directly to semi-inclusive 
measurements.

\paragraph{Correction of the Data}

We generate 100 million events per target, with and without radiative effects.
The RADGEN software gives direct indication for the inclusive correction and 
the comparison between the two data sets allows to extract factors for 
semi-inclusive correction.

The correction factors for inclusive ratio (figure \ref{fig:RadCorrFac}) are 
relatively small (couple of percents maximum) except at low \xb and high $\nu$. Semi-inclusive factors are 
shown in figure \ref{fig:RadCorrFacSIDIS} as a function of $z$ and \ptp. However 
the statistical error on these is large, the problem being that only a small 
fraction of the events involved photon radiation.

\begin{figure}[htbp]
\centering
\includegraphics[width=9cm] {chap5-fig/ElecRadWei_Lead.png}
\caption {Ratios of the radiative correction factors $\delta_\text{Pb}/
\delta_{^2\text{H}}$ as a function of \xb in various $\nu$ bins.}
\label{fig:RadCorrFac}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=9cm] {chap5-fig/RadGenFactors.png}
\caption {Ratios of the radiative correction factors $\delta_\text{Pb}/
\delta_{^2\text{H}}$ as a function of $z$ and \ptp.}
\label{fig:RadCorrFacSIDIS}
\end{figure}

The radiative correction appears to be limited in amplitude in most of the 
kinematic, so we decided not to apply it before further studies. Improvement can 
be easily obtained by generating more statistics, in order to analyze the 
semi-inclusive effects in more depth. Also radiative effects from the target thickness 
are ignored in the current setup; these need to be evaluated and, eventually, 
corrected as well.

\subsubsection{Isospin Correction}

The important excess of neutron in heavy nuclei leads to a modification of the 
$\pi$ multiplicity per DIS events. Using Hall~C results 
\cite{Asaturyan:2011mq}, shown in figure \ref{fig:IsoSpin}, we evaluate 
correction factors for this effect. Our simple estimation is solely based on 
proton and neutron numbers; the results for $\pi^+$s are shown in 
table~\ref{tab:isospin}. The effect on $\pi^-$ is found to be coherent with zero,
therefore no correction is applied for them. 
We attribute errors of 10\% of the effect for the isospin correction, this is chosen 
relatively to the precision of the Hall~C measurement.

\begin{figure}[tbp]
\centering
\includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
\caption {Ratios of deuteron over proton for $\pi^+$s and $\pi^-$s 
as a function of \xb at $z=0.55$ \cite{Asaturyan:2011mq}.}
\label{fig:IsoSpin}
\end{figure}

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{} cc @{}}
    \hline
    Target & Isospin  \\ 
           & correction \\ 
    \hline
    C & 0 \\
    Al & 1.5\%\\
    Fe &  3\% \\
    Sn &  8\%\\
    Pb &  10\% \\
    \hline
  \end{tabular}
  \caption{Isospin correction applied to the $\pi^+$ multiplicity ratios for different targets.}
  \label{tab:isospin}
\end{table}

It is important to note that we correct isospin effects only for rates, thus 
we correct only the multiplicity ratios. Transverse momentum broadening could, in 
principle, also be affected, however, the results from \cite{Asaturyan:2011mq} 
show no isospin effect in \ptp. This gives good confidence that \dpt is not 
affected by isospin effects.

We finally note that the $A$ dependencies of the multiplicity ratios of the 
charged pions are similar after the isospin correction\footnote{Within 
normalization errors presented in section \ref{sec:TotSys}} (figure 
\ref{fig:IsoPlot}). Considering previous measurements and existing models, 
this result was expected and confirm the need for this correction to be applied.

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm] {chap5-fig/c_RvA.png}
\caption {Multiplicity ratios as a function of $A^{1/3}$ 
with only isospin correction applied.}
\label{fig:IsoPlot}
\end{figure}

\subsection{Systematic Uncertainties}
\label{sec:TotSys}

In this section are summarized the systematic errors that we identified. The 
systematic point to point errors are calculated bin by bin for each results.
They are caused by uncertainties on the acceptance and on the identification of 
particles. The normalization errors are attributed globally. They are due to 
acceptance effects, target misidentifications and isospin correction.

\subsubsection{Quality of the Detection}
\label{SysId}

The simulation of the CLAS detector, using GSIM package, is used 
to evaluate the systematic errors linked with:

  - experimental resolution of kinematic variables,

  - particle misidentification,

  - particle re-scattering in the detector,

  - particle energy loss.\\

To evaluate those errors, we compare the reconstructed particles with the 
generated ones. Each reconstructed particle is associated with its generated parent using the
similarity in momentum and angle.
Distributions of $\Delta p$, $\Delta \theta$ and $\Delta \phi$ are defined as 
$\Delta x = {\sum_n |x_{gen} - x_{rec}| \over n}$. They give the precision with which we measure 
these variables. Using the same simulation than for the acceptance, we find 
${\delta p \over p } = 0.03$, $\delta \theta = 3$ mrad and 
$\delta \phi = 10$~mrad. These are broader than announced in \cite{Mecking:2003zu} 
but still reasonable. Then associated systematic errors can be easily 
evaluated for other variables: $\delta Q^2 \sim 0.013$ GeV$^2$/c$^2$, $\delta z \sim 
0.4 \%$, $\delta P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$ and so on\footnote{These were 
evaluated for typical kinematics, the results can be significantly larger at 
extreme kinematics (large \pt or Q$^2$).}. These are negligible because they are 
several times smaller than our usual bin sizes (see figures in section 
\ref{prelim}).

We also evaluate particle misidentification and particles originating from 
scattering in the detector or the coils. Only tails of distributions can lead to high 
contamination by misidentification, the most problematic being the tail of the 
\pt distribution. This effect is due to the low probability to produce high 
\pt events, therefore the contribution from accidental is relatively 
increased. We use the following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which 
only removes a very little amount of data ($\sim 1$ $\pi$ in 30000). The 
misidentification of electrons is found to be of the order of 1 in a 1000 and 
does not contribute significantly to the uncertainty. For pions, the main 
contamination comes from kaons above 2~GeV/c ($\sim$3\% of $\pi^+$ and 
$\sim$0.5\% of $\pi^-$). Incidentally, protons also contaminates $\pi^+$ at 
high momentum (up to few \%). The uncertainty related to 
misidentification is taken into account for the point to point systematic error 
evaluation, other effects are found to be negligible.

\subsubsection{Target Reconstruction}

Because of reconstruction errors or scattering on the detector materials, it 
is possible to associate a particle with the wrong target. To estimate this 
effect, we look, in the experimental data, at the number of events 
reconstructed upstream and downstream of the targets, where nothing should be
detected. We define two test regions (see figure \ref{fig:targetleak}) to evaluate
the contamination. The region 1 is upstream and chosen to be of the same size as the window used for solid 
target selection. We use it to evaluate contamination from the liquid target to the solid one. The region 2
is downstream and of the size of the window for the liquid target selection and allows to evaluate the solid target leak into the liquid one
The distance between detection and test regions is identical to the 
distance between the two detection regions.

We find
that the number of electrons in the test regions 1 and 2 represent 1 and 2\%, 
respectively, of the total number of events. In the case of semi-inclusive measurement, where we request
2 particles in the final state, the number drops drastically and is of the order of
0.01\%. In conclusion, only the number of electron is significantly affected by this problem
leading to a normalization error of 1\% for all multiplicity ratios.

\begin{figure}[tbp]
\centering
\includegraphics[width=9cm] {chap5-fig/Vertex.png}
\caption {Distribution of the vertex positions along z (cm), i.e. along the 
beam line. In red are shown the cuts used to evaluate the leak from one target to 
another.}
\label{fig:targetleak}
\end{figure}

\subsubsection{Acceptance}

We apply two different acceptance corrections to the data using two different binnings 
(table \ref{tab:AcceptBinning}). The differences between them give us a good 
indication on the systematic error associated with the method. Using a sample 
of results from iron, we find the systematic presented in the table 
\ref{tab:SysAcc}. We note the significantly larger errors for $\pi^-$, which 
was expected because of the smaller acceptance and the larger weights. More 
significant are the large errors on the \dpt measurements, this is mainly due to 
the nature of the observable; as a difference \dpt enhances relative errors 
significantly. As was seen in figure~\ref{fig:AcceptPlots}, error bars are much 
larger for corrected \dpt indicating an important statistical 
sensitivity introduced by the weighting. The errors on \dpt are of the same 
order, or smaller, as the differences observed between the two sets. This is 
an indication that the uncertainties reported in table \ref{tab:SysAcc} are already 
taken into account in the statistical error.

\begin{table}[htbp]
  \centering
\renewcommand{\arraystretch}{1.3}
  \begin{tabular}{|c|c|c|}
    \hline
    Variable & Normalization & Point to point \\ 
             & errors        & errors         \\ 
    \hline
    $R^{\pi^+}_A$  & 1.2\% & 1.5\%  \\
    $R^{\pi^-}_A$  & 2.5\% & 2.6\%   \\
    $\langle \Delta P_\perp^2 \rangle^{\pi^+}_A$ & 5\% & 11\% \\
    $\langle \Delta P_\perp^2 \rangle^{\pi^-}_A$ & 5\% & 21\% \\
    \hline
  \end{tabular}
  \caption{Relative errors on observables between the two weighting 
  described in the text.}
  \label{tab:SysAcc}
\end{table}

\subsubsection{Normalization Error}

The normalization errors -- i.e. independent of kinematic variables -- are due to acceptance effects, target identification 
and isospin correction. They are summarized in the table \ref{tab:sysid}.

\begin{table}[htbp]
  \centering
\renewcommand{\arraystretch}{1.3}
  \begin{tabular}{|c|cc|cc|}
    \hline
              & $R_A^{\pi^+}$  & $R_A^{\pi^-}$ & \dptp$^{\pi^+}$ &  \dptp$^{\pi^-}$\\ 
    \hline
    Acceptance & 1.2\% & 2.5\% & 5\% & 5\% \\
    Target id. & 1\% & 1\% & 1\% & 1\% \\
    Isospin (Pb)& 1\% & 1\% & 1\% & 1\% \\
    Total      & 1.9\% & 2.9\% & 5.2\% & 5.2\% \\
    \hline
  \end{tabular}
  \caption{Normalization uncertainties.}
  \label{tab:sysid}
\end{table}

### 2016-08-08 chap6.tex
Initial commit

\section{Results and Discussions}
\label{chap:results}

The results presented in this chapter are corrected for acceptance effects, 
but not for radiative ones. We use the following DIS selection cuts: 
$Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$. In order to ensure that 
factorization applies, we select $0.4$~$<$~$z$~$<$~$0.7$\footnote{This cut is not 
applied for plots as a function of $z$.}, this choice is based on experimental results from 
\cite{Asaturyan:2011mq}. Moreover, this cut also ensures that we measure the leading 
hadron and that we avoid the high $z$ region, which might be contaminated by 
the diffractive $\rho^0$ decay products. Finally, the cut $x_F > 0$ select the 
current fragmentation region.

\subsection{Multiplicity Ratio}

\subsubsection{$A$ Dependence}
\label{sec:resA}

\begin{figure}[p]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_RvA.png} 
\caption {$A^{1/3}$ dependence of the multiplicity ratio. Normalization 
uncertainties are not shown.}
\label{fig:RA}
\end{figure}

The figure \ref{fig:RA} presents our result for the $A^{1/3}$ dependence of 
the multiplicity ratio. One can see a 5\% normalization difference between
pions. However, this difference is not significant as it represents only 1.5 
standard deviation of our normalization uncertainty (see table~\ref{tab:sysid}).

The attenuation, presented in the figure \ref{fig:RA}, is not linear as 
a function of $A^{1/3}$ nor $A^{2/3}$. HERMES data has already showed some indication 
of this feature \cite{Airapetian:2007vu,Airapetian:2009jy}, but here, the nonlinearity, 
which has important implication on models, is clear. Indeed, it seems difficult 
to conciliate the prehadron absorption models with this result. Prehadrons 
are expected to have their cross section increasing with time and, therefore, 
distance. On the parton energy loss side, the BDMPS calculation gives a parton energy loss proportional to 
$L^2 \propto A^{2/3}$ also in contradiction with this result. However, 
this statement does not hold at low energy and might also be 
modified if the production time occurs inside the nuclei.

\subsubsection{Cronin Effect}

\begin{figure}[p]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_RvPt.png} 
\includegraphics[width=7.4cm] {chap6-fig/F_RvPt_PbC.png} 
\caption {Multiplicity ratios as a function of \pt (GeV$^2$/c$^2$) for charged pions. Left panel is 
the usual observable, right panel shows multiplicity ratio of lead normalized to carbon.
Normalization uncertainties are not shown.}
\label{fig:RPt}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_RvPtinZ.png} 
\includegraphics[width=7.4cm] {chap6-fig/F_RvPtinNu.png} 
\caption {Multiplicity ratios as a function of \pt (GeV$^2$/c$^2$) and $z$ (left) 
or $\nu$ (GeV) (right) for positive pions. Normalization uncertainties are not shown.}
\label{fig:RPtMulti}
\end{figure}

The Cronin effect is characterized by a large increase of the multiplicity 
ratio at high \pt ($\sim$1~GeV$^2$/c$^2$), but it is a controversial 
measurement in hadronization studies. Indeed, whereas SLAC measurements 
\cite{Osborne:1978ai} did not show such an effect, HERMES 
\cite{Airapetian:2007vu} measured a significant increase of the multiplicity 
ratio with \ptp. Our result (figure \ref{fig:RPt} (left)), integrated over 
all other variables, shows a pattern similar to the HERMES measurement. 
However, there is potential contributions from the target fragmentation (see 
chapter~\ref{chap:data}) and the Fermi motion (see chapter \ref{chap:pyqm}).

Fermi motion effects can be significantly reduced by modifying 
our usual observables. Indeed, using carbon for normalization, instead of deuterium, 
cancels most of the effects of Fermi motion. Moreover, acceptance 
effects (section~\ref{sec:accept}) are mostly canceled as well in such a ratio, 
reducing various systematic errors (including most of the normalization error). 
The figure \ref{fig:RPt} (right) represents the multiplicity ratio based on carbon. We 
observe an attenuation, at low \ptp, similar to the usual multiplicity ratio 
of iron. This can be understood from the radius of the nuclei $R_{Pb}-R_{C} 
\sim R_{Fe}$. Nevertheless, the observed enhancement with \pt is much more modest than in 
iron. At first sight the difference can be attributed to Fermi motion, which 
might affect the measurement based on deuterium. The target fragmentation 
effects might also lead to similar observation and more evidence are 
needed to confirm our interpretation.

In the figure \ref{fig:RPtMulti}, the multi-dimensionally binned multiplicity 
ratio are presented. HERMES found an important dependence of the Cronin effect 
with $z$ \cite{Airapetian:2007vu,Airapetian:2011jp} that we interpreted as a 
sign of an important target fragmentation contribution. The present result 
(figure~\ref{fig:RPtMulti} (left)) does not show this behavior, but it can be 
explained by our stricter cut on $z$ ($z>0.4$ whereas HERMES uses $z>0.2$), which 
leads to a smaller target fragmentation contamination. The second result, 
binned in \pt and $\nu$ (figure \ref{fig:RPtMulti} (right)), shows an important 
dependence of the Cronin effect with $\nu$. However, HERMES results did not 
reveal any similar $\nu$ variation. This is an evidence of the importance of 
the Fermi motion effect in our measurement. Indeed, in the 
chapter~\ref{chap:pyqm}, it was shown that the impact of Fermi motion gets 
smaller at higher energy.

The result for the lead to carbon multiplicity ratio, figure \ref{fig:RPt} 
(right), has another interesting feature: the $\pi^+$s have a stronger Cronin 
effect. However, the signification of this observation is not clear. This could be 
a contribution from target fragmentation, as we might expect more positive 
particles than negative ones coming from the nuclei.
This could also come from other sources such as isospin effect or factorization breaking at high 
\ptp, but no test of these features exists in this kinematical range\footnote{
\cite{Asaturyan:2011mq} covers only \pt$<0.2$ GeV$^2$/c$^2$.}. Last, it could 
be linked to the hadron rank and reflect some hadronization properties. Indeed, 
as we probe mostly valence quark at our energies, $\pi^+$s are more likely to 
be leading hadron compared to $\pi^-$s.

In conclusion, our results indicate that the HERMES results were affected by target 
fragmentation and that our results are affected by Fermi motion. These effects can 
be easily controlled by selecting carefully our observables and kinematic coverage.

\subsubsection{$\nu$ Dependence}

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_RvNu.png} 
\includegraphics[width=7.4cm] {chap6-fig/F_RvNu_PbC.png} 
\caption{Multiplicity ratios as a function of $\nu$ (GeV). Left panel is the usual 
observable, right panel shows multiplicity ratio of lead normalized to carbon. 
Normalization uncertainties are not shown.}
\label{fig:RNu}
\end{figure}

The HERMES collaboration clearly observed a rise of the multiplicity ratio 
between $\nu$ of 4 and 22~GeV. However, at first sight, in our results (figure 
\ref{fig:RNu} (left)), no dependence is observed, except for a 
slight increase in lead. The results on Fermi motion together 
with the figure \ref{fig:RNu} (right) permit to reach a coherent explanation. The 
Fermi motion seems to cancel the hadronization effect almost completely and the
systematic uncertainties linked with acceptance might wash out what remains of the effect. The 
multiplicity ratio based on carbon, however, offers a very neat slope consistent 
with what was observed on a much larger range by HERMES.

We also notice here that both pions give similar results in the figure 
\ref{fig:RNu} (right). This confirms our previous remark that the difference 
observed in the multiplicity ratio based on deuterium might come from the 
normalization uncertainty caused by the acceptance correction. Therefore, there is no 
clear difference between the charged pions for the integrated multiplicity 
ratios.

\subsubsection{$z$ Dependence}

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_RvZ.png} 
\includegraphics[width=7.4cm] {chap6-fig/F_RvZ_PbC.png} 
\caption {Multiplicity ratios as a function of $z$. Left panel is the usual
observable, right panel shows multiplicity ratio of lead normalized to carbon. 
Normalization uncertainties are not shown.}
\label{fig:Rz}
\end{figure}

The multiplicity ratio was observed to decrease with $z$ in HERMES data, 
whereas this feature was not as significant in other experiments. Indeed the 
nature of this behavior is questionable, the target fragmentation also reduce 
with $z$ and can mimic the effect. In figure \ref{fig:Rz} (left), as in 
HERMES, we see a clear slope even at values higher than 0.4, where target fragmentation
effects are expected to be small. However, the ratio lead to carbon (figure 
\ref{fig:Rz} (right)) shows a much flatter behavior in the region of interest 
(0.4 to 0.7). This is coherent with what we showed in chapter \ref{chap:pyqm}, i.e. the expected $z$ slope 
is enhanced by Fermi motion effects. Therefore, the situation seems to be 
similar to the Cronin effect one, where HERMES observation was enhanced by 
target fragmentation. The measurement using the carbon as basis is, therefore, 
more useful to isolate effects from the hadronization, but low $z$ behavior 
remains driven by the target region. Another strange feature of the data is 
the behavior at high $z$ (figure \ref{fig:Rz} (right)), where the two pions 
behave differently. However, we lack of solid theoretical grounds in this 
region to interpret this result.

\subsubsection{$Q^2$ Dependence}

The behavior of hadronization as a function of $Q^2$ is an important issue, that 
has direct implications on our understanding of nuclear matter properties in 
QCD. HERMES results, which covers $1<Q^2<10$~GeV$^2$/c$^2$, give a hint for an 
increase of the multiplicity ratio with $Q^2$. Our result, in figure 
\ref{fig:RQ2}, does not allow to reach the same conclusion and indicates no 
significant dependence as a function of $Q^2$.

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_RvQ2.png} 
\caption {Multiplicity ratios as a function of $Q^2$ (GeV$^2$/c$^2$). 
Normalization uncertainties are not shown.}
\label{fig:RQ2}
\end{figure}

We can use our large statistics to get more information. As 
a dependence in $\nu$ is expected for the multiplicity ratio, it might be helpful to use a tight 
$\nu$ bin to plot the $Q^2$ dependence (figure \ref{fig:RQ2Detailed} (left)), 
and remove any coupling between the two variables.
We could also expect some effects from the Fermi motion, 
therefore, we show in figure \ref{fig:RQ2Detailed} (right) the multiplicity ratio of lead to 
carbon as a function of $Q^2$. The two results of figure \ref{fig:RQ2Detailed} 
show a slight increase with $Q^2$, but as for HERMES, no evidence is 
reached on this question. Our leverage on $Q^2$ appears to be too modest
to make a clear measurement. Future programs to explore this question are 
discussed in chapter~\ref{chap:future}.

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_RvQ2inNu.png} 
\includegraphics[width=7.4cm] {chap6-fig/F_RvQ2_PbC.png} 
\caption {Multiplicity ratios as a function of $Q^2$ (GeV$^2$/c$^2$). In the left panel,
the multiplicity ratio in a tight $\nu$ bin ($3.25 < \nu < 3.75$ GeV). In the right 
panel, the multiplicity ratio of lead normalized to carbon. Normalization 
uncertainties are not shown.}
\label{fig:RQ2Detailed}
\end{figure}

\subsection{Transverse Momentum Broadening}

\subsubsection{$A$ Dependence}

The $A$ dependence of the transverse momentum broadening, presented in 
figure~\ref{fig:PA}, is an important result. The large statistics coupled with the 
large coverage in $A$ available to the CLAS experiment give precise indication on \dpt 
as a function of $A^{1/3}$. Compared to HERMES \cite{Airapetian:2009jy}, we
find smaller \dptp. This is coherent with theory, which predicts larger effects
at larger energies. However, calculations of parton energy loss from BDMPS 
\cite{Baier:1996sk} show that \pt should depend on the nucleus radii
(see chapter \ref{chap:theory}). However, this feature does not appear in our 
result. Of course, because of the low energy of the CLAS experiment, one might 
discuss the possibility to make a direct comparison with BDMPS calculations. Nonetheless, 
this result shows an unexpected pattern that remains to be explained. One 
possibility is that, as proposed for the multiplicity ratio as a function of 
$A^{1/3}$, the production time occurs inside the nuclei. In this case, the 
colored parton would not interact with the whole nuclei and therefore changing 
its size would lead to limited effect.

\begin{figure}[tbp]
\centering
\includegraphics[width=8.2cm] {chap6-fig/F_PvA.png} 
\caption {$A$ dependence of \dptp. Points are slightly offset for readability, normalization uncertainties are not shown.}
\label{fig:PA}
\end{figure}

\subsubsection{$z$ Dependence}

The $z$ dependence of \dpt has some importance for parton energy loss
models, because it is linked to the assumptions needed to extrapolate the hadronic \pt
to the partonic one. Moreover, usually, in parton energy loss models, \dpt
goes to zero at the highest $z$. Our results (figure \ref{fig:PZ}) do
not show such a pattern. However, our previous results showed the importance of 
Fermi motion in our kinematics, which is expected to enhance \dpt at very high
$z$. This is confirmed by the flattening observed for the carbon based \dptp, but
the distribution is not clearly going down either at high $z$. This might be due to the size of the 
error bars and the potential contamination from diffractive $\rho^0$ production, both 
preventing us from any definitive statement on this feature of the data.

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_PvZ.png} 
\includegraphics[width=7.4cm] {chap6-fig/F_PvZ_PbC.png} 
\caption {\dpt as a function of $z$. Left panel is the usual
observable, right panel shows multiplicity ratio of lead normalized to carbon. Normalization uncertainties are not shown.}
\label{fig:PZ}
\end{figure}

\subsubsection{$Q^2$ Dependence}

Finally, the $Q^2$ dependence of \dpt is an important result for the BDMPS based 
calculation from \cite{Domdey:2008aq}. They expect a raise of \dpt with $Q^2$,
which is not observed in the figure \ref{fig:PQ2}. Using
binning in $\nu$ and carbon based \dpt (figure \ref{fig:PQ2-detailed}) gives a similar
result. In conclusion, within error bars, no effect is observed for \dpt as a function of $Q^2$.
However, as theoretical input is missing, it is not clear if we have the resolution to observe
the effect expected within BDMPS based models.

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_PvQ2.png} 
\caption {\dpt for iron as a function of $Q^2$ (GeV$^2$/c$^2$) 
with usual cuts. Normalization uncertainties are not shown.}
\label{fig:PQ2}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap6-fig/F_PvQ2inNu.png} 
\includegraphics[width=7.4cm] {chap6-fig/F_PvQ2_PbC.png} 
\caption {\dpt as a function of $Q^2$ (GeV$^2$/c$^2$). Left panel is the usual
observable in a tight $\nu$ bin ($3.25 < \nu < 3.75$~GeV). Right panel shows \dpt 
of lead relative to carbon. Normalization uncertainties are not shown.}
\label{fig:PQ2-detailed}
\end{figure}

### 2016-08-08 intro.tex
Initial commit

\section{Introduction}
\label{physics}

The fragmentation process by which parton fragment into hadrons is 
experimentally well studied and fragmentation functions fitted from 
data are measured on a large kinematic and for numerous particles
\cite{AKK}.
Nevertheless, the hadron formation is a non perturbative process and can not 
be theoritically described, only a global picture 
(see figure \ref{fig:hadro}) can be drawn for
energies above the resonance region. In deep inelastic scattering the
virtual photon interact with a quark which propagate quasi-free emitting
gluons during the 
so-called production time. After neutralizing its color the quark become 
a pre-hadron which will eventualy form a hadron after the formation time.
On nuclear target the process of hadronization occurs, at least partly, in 
nuclear matter, then one can extract the production time using the different 
behaviour of quarks and colorless pre-hadrons in medium. The measurement of
pions is especially suited to lead that kind of analysis because they are easy
to detect and abundant in deep inelastic scattering.

\begin{figure}[htbp]
\centering
\includegraphics[width=10cm] {fig/hadro.png} 
\caption {Sketch of the hadronization process.}
\label{fig:hadro}
\end{figure}

The hadronization in nuclear matter is a key process in QCD also
because it leads to a major theoritical uncertainty in numerous measurements.
In heavy ion collisions, the measured hadrons are produced in hot and evolving 
medium, the models describing those collisions can be tested in deep inelatic scattering 
where the size of the medium is stable and known. Quantitative
understanding of the hadronization in nuclei is also of interest for
neutrino experiment which often use nuclei to maximize their cross section.
The hadronization can give important information about the 
nuclei through quark energy loss, for exemple \cite{Arleo:2003yf} link 
energy loss with gluon density and \cite{Kopeliovich:2010aa} link the $\Delta \langle
P_T^2 \rangle$ with the saturation scale. Other models \cite{Gallmeister:2007an}
can give information about how the pre-hadron evolve into hadron but are based
on very different assomptions, therefore it is very important to discriminate between
models.

In order to constrain the existing models we extract our results
using multi-dimensional binning. Another way to constrain the models will be
the observation of baryon hadronization (here protons), which behaviour is
not understood yet. 
The importance of the EG2 data then come from its high statistics which permit, 
this multi-dimensional measurement of both pions and protons on a 
large kinematic range.

We present in section \ref{sec:theo} the different familly of models describing
hadronization in nuclear matter then in section \ref{sec:exp} we make a rapid
overview of the published data on the topic. For more detailed information we 
refer the reader to the review from Accardi {\it et al.} \cite{Accardi:2009qv}.

\subsection{Kinetic Variables and Observables}

In this analysis we use the following semi-inclusive DIS variables:
\begin{itemize}
 \item $\nu = E_i - E_f$ with $E_i$ the beam energy and $E_f$ the scattered electron energy,
 \item $Q^2 = 4 E_i E_f \sin ^2(\theta_e / 2)$ with $\theta_e$ the scattered electron angle with the beam line,
 \item $x_{Bj} = {{Q^2} \over {2 M_n \nu}}$ with $M_n$ the nucleon mass,
 \item $W^2 = M_n^2 - Q^2 + 2 M_n \nu$
 \item $z_h = E_h / \nu$
 \item $P_T^2$ which is transverse momentum according to the virtual photon
 \item $\phi_h$ the angle between the electronic plan (contain initial and scattered electrons) and the hadronic plan (contain virtual photon and hadron)
 \item add xf
\end{itemize}

We define the multiplicity ratio as:
\begin{equation}
R_A^h (Q^2,\nu,z_h,P_T^2) = {{N_A^h (Q^2,\nu,z_h,P_T^2) / N_A^e (Q^2,\nu)} 
                       \over {N_D^h (Q^2,\nu,z_h,P_T^2) / N_D^e (Q^2,\nu)}}
\end{equation}
with $N^e_t$ the number of electron measured from a target t and $N_t^h$ the number
of semi-inclusive hadrons h (detection of both an electron and a hadron) from the
target~t. The multiplicity ratio represents the attenuation of the hadron h in a 
nuclear target~A.
\newline

We define the transverse momentum broadening as:
\begin{equation}
\Delta \langle P_T^2 \rangle = \langle P_T^2 \rangle_A - \langle P_T^2 \rangle_D
\end{equation}
with $\langle P_T^2 \rangle_t$ the mean transverse momentum measured in a target t.

Finally a less used observable to carachterise the momentum broadening is the ratio
of mean transverse momentum:

\begin{equation}
\langle P_T^2 \rangle_A / \langle P_T^2 \rangle_D
\end{equation}

\subsection{Theoretical Efforts}
\label{sec:theo}

The different models explaining the data can be separated in three families,
some assume that the quark loose energy in the medium and that either, hadronization occurs
outside the medium or the hadronic interaction is 
negligible, others consider the quark energy loss negligible and consider
only the hadron and pre-hadron absorption and finally some models consider both
interactions. We will give an example of each case to illustrate, for more
detailed information we refer again to \cite{Accardi:2009qv} which is more exaustive and
mention few other models used for RHIC experiments.

In \cite{Wang:2002ri}, E.~Wang and X.-N.~Wang, describe HERMES data using only energy 
loss from the parton, the suppression observed is then due to the fact that a 
lower energy quark will fragment into a lower number of hadrons and a lower 
z. That kind of model is used in both RHIC and nDIS and permit a commom 
interpretation of hadron suppression in nuclear matter. Lot of different
calculations of the energy loss exist, the main parameter for those is $\hat q$
(GeV$^2$ fm$^{-1}$) which is the transverse momentum per unit of length of a quark after propagating
in nuclear matter, this value is related to the $P_T$ 
broadening observables. The two main difficulties for the quark energy loss
models are to have coherent picture of both multiplicity ratios and $P_T$ 
broadening because usually the $\hat q$ needed to reproduce multiplicity ratio
is bigger than the one necessary to describe transverse momentum broadening.

The GiBUU model \cite{Gallmeister:2007an} is a transport model based on Boltzmann equation
using hadronic and pre-hadronic interaction in the nuclear matter, with no
quark energy loss involved. This model reproduce very well most of the hadrons, 
surprisingly, it does not reproduce protons
data from HERMES correctly, it is surprising in the sense that the proton
case should be well handle by this kind of models. Another problem 
is that the $\Delta \langle P_T^2 \rangle$ variable is not yet described by 
hadron absorption models.

B.Z.~Kopeliovich \cite{Kopeliovich:2008uy} describe the process neglegting neither quark 
energy loss or hadron absorption, using transverse momentum and
multiplicity ratios to differenciate the effects. In that case the transverse 
momentum broadening is linked to quark energy loss and the multiplicity ratio
suppression is explained by hadron absorption in medium.

To conclude it is important to point out that no consensus is reached on which 
mecanisms are dominant and it is important to perform precise measurment with
the right observables to solve this problem.

\subsection{Previous Mesurements}
\label{sec:exp}

Hadron multiplicity ratios in nuclei were measured in numerous lepton 
facilities: L.S.~Osborne {\it et al.} \cite{Osborne:1978ai} at SLAC,
L.~Hand {\it et al.} \cite{Hand:1978tx} and the E665 collaboration \cite{Adams:1994ri} at FNAL
and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN. Those 
measurements revealed the general picture; we observe a sizeable suppression when
looking at hadron production in nuclei, this suppression is lower at higher
$\nu$ and lower z, it can even inverse and increase at very low z.

The figures \ref{fig:her1}, \ref{fig:her2} and \ref{fig:her3} shows a sample of 
more recent data from HERMES collaboration \cite{Airapetian:2007vu}, numerous 
hadrons are studied individually and new variables linked with transverse 
momentum are used on top of the usual multiplicity ratio.

\begin{figure}[htbp]
\centering
\includegraphics[width=14cm] {fig/Hermes/pi0hermes.png} 
\caption {Multiplicity ratio of $\pi^0$ in function of various kinetic 
variables from HERMES collaboration \cite{Airapetian:2003mi}}
\label{fig:her1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=14cm] {fig/Hermes/hermes1.png} 
\caption {Multiplicity ratio of $\pi^+$, K$^+$, protons and anti-protons in 
function of various kinetic variables from HERMES collaboration \cite{Airapetian:2007vu}}
\label{fig:her2}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=7cm] {fig/Hermes/pthermes.png} 
\caption {Transverse momentum broadening for various particles
from HERMES collaboration \cite{Airapetian:2009jy}}
\label{fig:her3}
\end{figure}

The HERMES data, because of their precision,
permit to have an insight into new features. One can cite the behavior of K$^+$
which have less attenuation than pions (see figure \ref{fig:her1}) but more 
$\Delta \langle P_T^2 \rangle$, it is difficult to reproduce this in 
models where only one stage of hadronization is taken into account to 
explain all effects.
Also the different behaviour of protons compare to anti-protons
(see figure \ref{fig:her1}) is interesting
and need precise analysis even most of the theoritical models do not treat 
baryon hadronization yet.

### 2016-08-08 chap6-fig/SomeSrc/18_Qdep_DePts_Q2.C

@@ -1,0 +1,76 @@
+{
+//=========Macro generated from canvas: Plot18/#DeltaP_{T}^{2} in function of Q^{2}
+//=========  (Tue Sep  6 21:54:48 2011) by ROOT version5.28/00d
+   TCanvas *Plot18 = new TCanvas("Plot18", "#DeltaP_{T}^{2} in function of Q^{2}",204,49,600,500);
+   Plot18->Range(0,0,1,1);
+   Plot18->SetFillColor(0);
+   Plot18->SetBorderMode(0);
+   Plot18->SetBorderSize(2);
+   Plot18->SetFrameBorderMode(0);
+   
+   TH2D *Can90 = new TH2D("Can90","#DeltaP_{T}^{2} in function of Q^{2}",100,1,3.5,100,0,0.05);
+   Can90->SetStats(0);
+   Can90->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   Can90->GetXaxis()->CenterTitle(true);
+   Can90->Draw("");
+   
+   gre = new TGraphErrors(10);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,1.145147,0.01417336);
+   gre->SetPointError(0,0,0.0007432174);
+   gre->SetPoint(1,1.432998,0.01516447);
+   gre->SetPointError(1,0,0.000802094);
+   gre->SetPoint(2,1.736606,0.01459879);
+   gre->SetPointError(2,0,0.0007797307);
+   gre->SetPoint(3,2.035761,0.01638586);
+   gre->SetPointError(3,0,0.0008819226);
+   gre->SetPoint(4,2.33631,0.01605178);
+   gre->SetPointError(4,0,0.0008710169);
+   gre->SetPoint(5,2.641345,0.01322938);
+   gre->SetPointError(5,0,0.0007185465);
+   gre->SetPoint(6,2.932933,0.01471728);
+   gre->SetPointError(6,0,0.0008016168);
+   gre->SetPoint(7,3.229178,0.01230394);
+   gre->SetPointError(7,0,0.000675704);
+   gre->SetPoint(8,3.52591,0.01465997);
+   gre->SetPointError(8,0,0.0008149437);
+   gre->SetPoint(9,3.802196,0.01018128);
+   gre->SetPointError(9,0,0.0005782321);
+   gre->Draw("z");
+   
[…]

### 2016-08-08 chap6-fig/SomeSrc/19_zdep_DePts_Zz.C

@@ -1,0 +1,196 @@
+{
+//=========Macro generated from canvas: Plot19/#DeltaP_{T}^{2} in function of z
+//=========  (Tue Sep  6 21:54:49 2011) by ROOT version5.28/00d
+   TCanvas *Plot19 = new TCanvas("Plot19", "#DeltaP_{T}^{2} in function of z",204,49,600,500);
+   Plot19->Range(0,0,1,1);
+   Plot19->SetFillColor(0);
+   Plot19->SetBorderMode(0);
+   Plot19->SetBorderSize(2);
+   Plot19->SetFrameBorderMode(0);
+   
+   TH2D *Can91 = new TH2D("Can91","#DeltaP_{T}^{2} in function of z",100,0,1,100,0,0.05);
+   Can91->SetStats(0);
+   Can91->GetXaxis()->SetTitle("z");
+   Can91->GetXaxis()->CenterTitle(true);
+   Can91->Draw("");
+   
+   gre = new TGraphErrors(10);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,0.09108739,-0.0004988631);
+   gre->SetPointError(0,0,-4.800299e-05);
+   gre->SetPoint(1,0.1569883,-0.0009950626);
+   gre->SetPointError(1,0,-9.574974e-05);
+   gre->SetPoint(2,0.24744,0.00216998);
+   gre->SetPointError(2,0,0.0002088077);
+   gre->SetPoint(3,0.3468615,0.006540157);
+   gre->SetPointError(3,0,0.0006293584);
+   gre->SetPoint(4,0.4466872,0.01509296);
+   gre->SetPointError(4,0,0.001457809);
+   gre->SetPoint(5,0.546303,0.02349188);
+   gre->SetPointError(5,0,0.002287525);
+   gre->SetPoint(6,0.6478302,0.02533919);
+   gre->SetPointError(6,0,0.002479855);
+   gre->SetPoint(7,0.7489944,0.02737295);
+   gre->SetPointError(7,0,0.002683366);
+   gre->SetPoint(8,0.8451953,0.02465121);
+   gre->SetPointError(8,0,0.002416646);
+   gre->SetPoint(9,0.9469178,0.04018737);
+   gre->SetPointError(9,0,0.003941493);
+   gre->Draw("z");
+   
[…]

### 2016-08-08 chap6-fig/SomeSrc/27_Qnbi_DePts_Q2.C

@@ -1,0 +1,194 @@
+{
+//=========Macro generated from canvas: Plot27/#DeltaP_{T}^{2} in function of Q^{2} in a #nu bin
+//=========  (Tue Sep  6 21:54:50 2011) by ROOT version5.28/00d
+   TCanvas *Plot27 = new TCanvas("Plot27", "#DeltaP_{T}^{2} in function of Q^{2} in a #nu bin",204,49,600,500);
+   Plot27->Range(0,0,1,1);
+   Plot27->SetFillColor(0);
+   Plot27->SetBorderMode(0);
+   Plot27->SetBorderSize(2);
+   Plot27->SetFrameBorderMode(0);
+   
+   TH2D *Can99 = new TH2D("Can99","#DeltaP_{T}^{2} in function of Q^{2} in a #nu bin",100,1,3.5,100,0,0.05);
+   Can99->SetStats(0);
+   Can99->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   Can99->GetXaxis()->CenterTitle(true);
+   Can99->Draw("");
+   
+   gre = new TGraphErrors(10);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,1.1406,0.02518127);
+   gre->SetPointError(0,0,0.0003192421);
+   gre->SetPoint(1,1.437328,0.02610357);
+   gre->SetPointError(1,0,0.0003758764);
+   gre->SetPoint(2,1.736467,0.02380804);
+   gre->SetPointError(2,0,0.0003740736);
+   gre->SetPoint(3,2.038695,0.02168911);
+   gre->SetPointError(3,0,0.0003637805);
+   gre->SetPoint(4,2.340773,0.02462797);
+   gre->SetPointError(4,0,0.0004366961);
+   gre->SetPoint(5,2.638487,0.01781863);
+   gre->SetPointError(5,0,0.00032903);
+   gre->SetPoint(6,2.935701,0.01470831);
+   gre->SetPointError(6,0,0.0002810217);
+   gre->SetPoint(7,3.227992,0.01635381);
+   gre->SetPointError(7,0,0.0003499124);
+   gre->SetPoint(8,3.523806,0.01213842);
+   gre->SetPointError(8,0,0.0003012748);
+   gre->SetPoint(9,3.771982,0.02197004);
[…]

### 2016-08-08 chap6-fig/SomeSrc/34_Ndep_DePts_Nu.C

@@ -1,0 +1,71 @@
+{
+//=========Macro generated from canvas: Plot34/#DeltaP_{T}^{2} in function of #nu
+//=========  (Tue Sep  6 21:54:50 2011) by ROOT version5.28/00d
+   TCanvas *Plot34 = new TCanvas("Plot34", "#DeltaP_{T}^{2} in function of #nu (Pb/C)",204,49,600,500);
+   Plot34->Range(0,0,1,1);
+   Plot34->SetFillColor(0);
+   Plot34->SetBorderMode(0);
+   Plot34->SetBorderSize(2);
+   Plot34->SetFrameBorderMode(0);
+   
+   TH2D *Can106 = new TH2D("Can106","#DeltaP_{T}^{2} in function of #nu",100,2.25,4.25,100,0,0.05);
+   Can106->SetStats(0);
+   Can106->GetXaxis()->SetTitle("#nu (GeV)");
+   Can106->GetXaxis()->CenterTitle(true);
+   Can106->Draw("");
+   
+   gre = new TGraphErrors(10);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,2.375859,0.003348286);
+   gre->SetPointError(0,0,2.631464e-05);
+   gre->SetPoint(1,2.557998,0.005685322);
+   gre->SetPointError(1,0,3.403397e-05);
+   gre->SetPoint(2,2.75467,0.009775429);
+   gre->SetPointError(2,0,7.658079e-05);
+   gre->SetPoint(3,2.945351,0.009417139);
+   gre->SetPointError(3,0,8.934772e-05);
+   gre->SetPoint(4,3.15153,0.01026019);
+   gre->SetPointError(4,0,0.0001206908);
+   gre->SetPoint(5,3.348671,0.01140175);
+   gre->SetPointError(5,0,0.0001524563);
+   gre->SetPoint(6,3.55054,0.01385551);
+   gre->SetPointError(6,0,0.0002112915);
+   gre->SetPoint(7,3.749285,0.0164821);
+   gre->SetPointError(7,0,0.0002757341);
+   gre->SetPoint(8,3.950376,0.01618296);
+   gre->SetPointError(8,0,0.0002927697);
+   gre->SetPoint(9,4.146619,0.01549412);
+   gre->SetPointError(9,0,0.0003000872);
+   gre->Draw("z");
+   
[…]

### 2016-08-08 chap6-fig/SomeSrc/35_Qdep_DePts_Q2.C

@@ -1,0 +1,71 @@
+{
+//=========Macro generated from canvas: Plot35/#DeltaP_{T}^{2} in function of Q^{2}
+//=========  (Tue Sep  6 21:54:50 2011) by ROOT version5.28/00d
+   TCanvas *Plot35 = new TCanvas("Plot35", "#DeltaP_{T}^{2} in function of Q^{2}",204,49,600,500);
+   Plot35->Range(0,0,1,1);
+   Plot35->SetFillColor(0);
+   Plot35->SetBorderMode(0);
+   Plot35->SetBorderSize(2);
+   Plot35->SetFrameBorderMode(0);
+   
+   TH2D *Can107 = new TH2D("Can107","#DeltaP_{T}^{2} in function of Q^{2} (Pb/C)",100,1,3.5,100,0,0.05);
+   Can107->SetStats(0);
+   Can107->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   Can107->GetXaxis()->CenterTitle(true);
+   Can107->Draw("");
+   
+   gre = new TGraphErrors(10);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,1.1469,0.01288373);
+   gre->SetPointError(0,0,0.000139524);
+   gre->SetPoint(1,1.433126,0.01279101);
+   gre->SetPointError(1,0,0.0001628511);
+   gre->SetPoint(2,1.736309,0.01153183);
+   gre->SetPointError(2,0,0.0001712212);
+   gre->SetPoint(3,2.035953,0.01233677);
+   gre->SetPointError(3,0,0.0002025859);
+   gre->SetPoint(4,2.336202,0.01285533);
+   gre->SetPointError(4,0,0.0002317548);
+   gre->SetPoint(5,2.640238,0.01613859);
+   gre->SetPointError(5,0,0.0003008523);
+   gre->SetPoint(6,2.933009,0.01062012);
+   gre->SetPointError(6,0,0.0002083349);
+   gre->SetPoint(7,3.228389,0.01581968);
+   gre->SetPointError(7,0,0.0003442193);
+   gre->SetPoint(8,3.525126,0.009783665);
+   gre->SetPointError(8,0,0.0002357498);
+   gre->SetPoint(9,3.808178,-0.01045033);
+   gre->SetPointError(9,0,-0.0003226118);
+   gre->Draw("z");
+   
[…]

### 2016-08-08 chap6-fig/SomeSrc/36_zdep_DePts_Zz.C

@@ -1,0 +1,72 @@
+{
+//=========Macro generated from canvas: Plot36/#DeltaP_{T}^{2} in function of z
+//=========  (Tue Sep  6 21:54:51 2011) by ROOT version5.28/00d
+   TCanvas *Plot36 = new TCanvas("Plot36", "#DeltaP_{T}^{2} in function of z",204,49,600,500);
+   Plot36->Range(0,0,1,1);
+   Plot36->SetFillColor(0);
+   Plot36->SetBorderMode(0);
+   Plot36->SetBorderSize(2);
+   Plot36->SetFrameBorderMode(0);
+   
+   TH2D *Can108 = new TH2D("Can108","#DeltaP_{T}^{2} in function of z (Pb/C)",100,0,1,100,0,0.05);
+   Can108->SetStats(0);
+   Can108->GetXaxis()->SetTitle("z");
+   Can108->GetXaxis()->CenterTitle(true);
+   Can108->Draw("");
+   
+   gre = new TGraphErrors(10);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,0.09093677,-0.0001601485);
+   gre->SetPointError(0,0,-3.469524e-08);
+   gre->SetPoint(1,0.1560351,-0.0004970079);
+   gre->SetPointError(1,0,-1.234737e-07);
+   gre->SetPoint(2,0.2471762,0.0009751046);
+   gre->SetPointError(2,0,4.866866e-07);
+   gre->SetPoint(3,0.3465305,0.004093999);
+   gre->SetPointError(3,0,4.465929e-06);
+   gre->SetPoint(4,0.4463604,0.01007902);
+   gre->SetPointError(4,0,8.586379e-05);
+   gre->SetPoint(5,0.5461572,0.01486604);
+   gre->SetPointError(5,0,0.0002257607);
+   gre->SetPoint(6,0.6473591,0.01606426);
+   gre->SetPointError(6,0,0.0002923881);
+   gre->SetPoint(7,0.747917,0.01182961);
+   gre->SetPointError(7,0,0.0002275783);
+   gre->SetPoint(8,0.8456777,0.006341035);
+   gre->SetPointError(8,0,0.0001237255);
+   gre->SetPoint(9,0.941401,0.01992575);
+   gre->SetPointError(9,0,0.0003949237);
+   gre->Draw("z");
+   
+   
[…]

### 2016-08-08 chap6-fig/SomeSrc/74_Adep_DePts_A13.C

@@ -1,0 +1,119 @@
+{
+//=========Macro generated from canvas: Plot68/#DeltaP_{T}^{2} in function of A
+//=========  (Tue Sep  6 21:54:54 2011) by ROOT version5.28/00d
+   TCanvas *Plot68 = new TCanvas("Plot68", "#DeltaP_{T}^{2} in function of A",204,49,600,500);
+   Plot68->Range(0,0,1,1);
+   Plot68->SetFillColor(0);
+   Plot68->SetBorderMode(0);
+   Plot68->SetBorderSize(2);
+   Plot68->SetFrameBorderMode(0);
+   
+   TH2D *Can140 = new TH2D("Can140","#DeltaP_{T}^{2} in function of A",100,2,6.5,100,0,0.01);
+   Can140->SetStats(0);
+   Can140->GetXaxis()->SetTitle("A^{1/3}");
+   Can140->GetXaxis()->CenterTitle(true);
+   Can140->Draw("");
+   
+   TGraphErrors *gre = new TGraphErrors(5);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,2.27,0.002435207);
+   gre->SetPointError(0,0,5.627494e-06);
+   gre->SetPoint(1,3,-1.003894665);
+   gre->SetPointError(1,0,1.279648e-05);
+   gre->SetPoint(2,3.81,0.003885922);
+   gre->SetPointError(2,0,7.100679e-06);
+   gre->SetPoint(3,4.93,-1.004067569);
+   gre->SetPointError(3,0,3.448317e-05);
+   gre->SetPoint(4,5.89,0.004390894);
+   gre->SetPointError(4,0,1.16601e-05);
+   gre->Draw("z");
+   
+   gre = new TGraphErrors(5);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,2.31,0.001560869);
+   gre->SetPointError(0,0,1.488616e-05);
+   gre->SetPoint(1,3,-1.004059956);
+   gre->SetPointError(1,-1,3.868138e-05);
+   gre->SetPoint(2,3.85,0.004425123);
+   gre->SetPointError(2,0,4.202184e-05);
+   gre->SetPoint(3,4.93,-1.005633675);
+   gre->SetPointError(3,-1,5.445841e-05);
[…]

### 2016-08-08 chap6-fig/SomeSrc/76_Qdep_DePts_Q2.C

@@ -1,0 +1,135 @@
+{
+//=========Macro generated from canvas: Plot70/#DeltaP_{T}^{2} in function of Q^{2}
+//=========  (Tue Sep  6 21:54:55 2011) by ROOT version5.28/00d
+   TCanvas *Plot70 = new TCanvas("Plot70", "#DeltaP_{T}^{2} in function of Q^{2}",204,49,600,500);
+   Plot70->Range(0,0,1,1);
+   Plot70->SetFillColor(0);
+   Plot70->SetBorderMode(0);
+   Plot70->SetBorderSize(2);
+   Plot70->SetFrameBorderMode(0);
+   
+   TH2D *Can142 = new TH2D("Can142","#DeltaP_{T}^{2} in function of Q^{2} (#pi^{+} at HERMES kine)",100,1,4,100,0,0.015);
+   Can142->SetStats(0);
+   Can142->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   Can142->GetXaxis()->CenterTitle(true);
+   Can142->Draw("");
+   
+   gre = new TGraphErrors(10);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetPoint(0,1.143957,0.003233615);
+   gre->SetPointError(0,0,2.473937e-05);
+   gre->SetPoint(1,1.433418,0.005569031);
+   gre->SetPointError(1,0,5.250027e-05);
+   gre->SetPoint(2,1.73578,0.004906317);
+   gre->SetPointError(2,0,5.345957e-05);
+   gre->SetPoint(3,2.036504,0.00536328);
+   gre->SetPointError(3,0,6.313194e-05);
+   gre->SetPoint(4,2.336353,0.005894907);
+   gre->SetPointError(4,0,7.370661e-05);
+   gre->SetPoint(5,2.640944,0.004719257);
+   gre->SetPointError(5,0,5.817705e-05);
+   gre->SetPoint(6,2.932344,0.0061784);
+   gre->SetPointError(6,0,7.717599e-05);
+   gre->SetPoint(7,3.228429,0.005439379);
+   gre->SetPointError(7,0,7.203062e-05);
+   gre->SetPoint(8,3.523581,0.007341272);
+   gre->SetPointError(8,0,0.0001060131);
+   gre->SetPoint(9,3.799023,-0.0005670077);
+   gre->SetPointError(9,0,-9.221503e-06);
[…]

### 2016-09-21 AnalysisNote.tex
Author update

@@
 
-\title{Study of the hadronization of $\pi^-$}
+\title{Study of the hadronization of charged pions}
 
-\author{Rapha\"el \textsc{Dupr\'e}, 
-Lamiaa \textsc{El Fassi}\thanks{also {\it Rutgers University}} , 
-Kawtar \textsc{Hafidi} ... \\ 
+\author{
+  Rapha\"el \textsc{Dupr\'e} \\ 
+  {\it Institut de Physique Nucl\'eaire, Orsay, France} \\
+  Lamiaa \textsc{El Fassi} \\ 
+  {\it Mississippi State University, Mississippi State,} \\ 
+  {\it Mississippi 39762, USA} \\
+  Kawtar \textsc{Hafidi} \\ 
   {\it Physics Division, Argonne National Laboratory,} \\ 
-{\it Argonne, Illinois 60439, USA} }
+  {\it Argonne, Illinois 60439, USA} 
+}
 

### 2016-09-27 AnalysisNote.tex
Edit on the part 1

@@
 qualitative understanding can be achieved, and using phenomenological models 
-is necessary. It is believed that hadronization has two distinct phases: 
-the quark propagation phase, where the quark emit gluons until it neutralizes 
-its color by forming a pre-hadron and the hadron formation phase, where the 
-pre-hadron evolves into a hadron. Those process are respectively characterized 
-by the production time and the formation time. By comparing hadron production 
+is necessary. By comparing hadron production 
 on different nuclei, one can measure variables with different sensitivities 
@@
 and hadronization dynamic using various nuclear target.
-In this analysis we focus on two particles, the negative pion and the proton.
-Our goals are to constrain the theoritical models and extract the production
-time using precise multidimensional analysis of $\pi^+$ and $\pi^-$ to enlight possible
-new physical processes with a precise analysis of proton production in nuclei.
+In this analysis we focus on two particles, the positive and negative pions
+to constrain theoritical models using precise multidimensional analysis.
 
@@
 \bibliography{hadro}
-\bibliographystyle{plain}
+\bibliographystyle{ieeetr}
 

### 2016-09-27 intro.tex
Edit on the part 1

@@
 
-The fragmentation process by which parton fragment into hadrons is 
+The hadronization process by which parton fragment into hadrons is 
 experimentally well studied and fragmentation functions fitted from 
-data are measured on a large kinematic and for numerous particles
-\cite{AKK}.
+data are measured on a large kinematic range~\cite{Albino:2008fy}.
 Nevertheless, the hadron formation is a non perturbative process and can not 
@@
 In order to constrain the existing models we extract our results
-using multi-dimensional binning. Another way to constrain the models will be
-the observation of baryon hadronization (here protons), which behaviour is
-not understood yet. 
-The importance of the EG2 data then come from its high statistics which permit, 
-this multi-dimensional measurement of both pions and protons on a 
+using tight multi-dimensional binning. 
+The importance of the EG2 data comes from its high statistics which permit, 
+this multi-dimensional measurement of both pions on a 
 large kinematic range.
@@
  \item $\phi_h$ the angle between the electronic plan (contain initial and scattered electrons) and the hadronic plan (contain virtual photon and hadron)
- \item add xf
+ \item $x_F = P_L/P_L^{max}$ the fraction of longitudinal momentum carried by the hadron calculated in respect to the virtual photon direction in the laboratory frame.
 \end{itemize}
+%TODO Add t
 
@@
 \end{equation}
-with $N^e_t$ the number of electron measured from a target t and $N_t^h$ the number
-of semi-inclusive hadrons h (detection of both an electron and a hadron) from the
-target~t. The multiplicity ratio represents the attenuation of the hadron h in a 
-nuclear target~A.
+with $N^e_A$ the number of electron measured from a target $A$ and $N_A^h$ the number
+of semi-inclusive hadrons $h$ (detection of both an electron and a hadron) from the
+target~$A$. The multiplicity ratio represents the attenuation of the hadron $h$ in a 
+nuclear target~$A$.
 \newline
@@
 \end{equation}
-with $\langle P_T^2 \rangle_t$ the mean transverse momentum measured in a target t.
-
-Finally a less used observable to carachterise the momentum broadening is the ratio
-of mean transverse momentum:
-
-\begin{equation}
-\langle P_T^2 \rangle_A / \langle P_T^2 \rangle_D
-\end{equation}
+with $\langle P_T^2 \rangle_A$ the mean transverse momentum measured in a target $A$.
 
@@
 lower energy quark will fragment into a lower number of hadrons and a lower 
-z. That kind of model is used in both RHIC and nDIS and permit a commom 
+$z$. That kind of model is used in both RHIC and nDIS and permit a commom 
 interpretation of hadron suppression in nuclear matter. Lot of different
 calculations of the energy loss exist, the main parameter for those is $\hat q$
-(GeV$^2$ fm$^{-1}$) which is the transverse momentum per unit of length of a quark after propagating
+(GeV$^2$ fm$^{-1}$) which is the transverse momentum per unit of length of a 
+quark after propagating
 in nuclear matter, this value is related to the $P_T$ 
-broadening observables. The two main difficulties for the quark energy loss
-models are to have coherent picture of both multiplicity ratios and $P_T$ 
-broadening because usually the $\hat q$ needed to reproduce multiplicity ratio
-is bigger than the one necessary to describe transverse momentum broadening.
+broadening observables. The main difficulty for the quark energy loss
+models is to have coherent description of both multiplicity ratios and $P_T$ 
+broadening. Recent models find a $\hat q$ to reproduce multiplicity ratio
+which is bigger than the one necessary to describe transverse momentum broadening.
+% TODO Add a ref
 
@@
 quark energy loss involved. This model reproduce very well most of the hadrons, 
-surprisingly, it does not reproduce protons
-data from HERMES correctly, it is surprising in the sense that the proton
-case should be well handle by this kind of models. Another problem 
-is that the $\Delta \langle P_T^2 \rangle$ variable is not yet described by 
-hadron absorption models.
+however the $\Delta \langle P_T^2 \rangle$ variable is not described at all by 
+this hadron absorption models.
 
@@
 To conclude it is important to point out that no consensus is reached on which 
-mecanisms are dominant and it is important to perform precise measurment with
+mecanisms are dominant. It is therefore important to perform precise measurements with
 the right observables to solve this problem.
@@
 and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN. Those 
-measurements revealed the general picture; we observe a sizeable suppression when
+measurements revealed the general features of hadronization
+in nuclei: we observe a sizeable suppression when
 looking at hadron production in nuclei, this suppression is lower at higher
-$\nu$ and lower z, it can even inverse and increase at very low z.
+$\nu$ and lower $z$, it can even inverse and be an increased yield at very low $z$.
 
 The figures \ref{fig:her1}, \ref{fig:her2} and \ref{fig:her3} shows a sample of 
-more recent data from HERMES collaboration \cite{Airapetian:2007vu}, numerous 
+the most recent data from HERMES collaboration \cite{Airapetian:2007vu}, numerous 
 hadrons are studied individually and new variables linked with transverse 
@@
 \includegraphics[width=14cm] {fig/Hermes/pi0hermes.png} 
-\caption {Multiplicity ratio of $\pi^0$ in function of various kinetic 
+\caption {Multiplicity ratio of $\pi^0$ as a function of various kinetic 
 variables from HERMES collaboration \cite{Airapetian:2003mi}}
@@
 \includegraphics[width=14cm] {fig/Hermes/hermes1.png} 
-\caption {Multiplicity ratio of $\pi^+$, K$^+$, protons and anti-protons in 
+\caption {Multiplicity ratio of $\pi^+$, K$^+$, protons and anti-protons as a 
 function of various kinetic variables from HERMES collaboration \cite{Airapetian:2007vu}}

### 2016-10-06 chap5.tex
Corrections of chapter 5

@@
 collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
-which the beam energy was 5.014 GeV\footnote{The other phases gave a small 
-amount of data at a beam energy of 4 GeV.}.
+which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small 
+amounts of data at a beam energy of 4~GeV that we decided not to use for this analysis.}.
 
@@
 The analysis of the experiment E-02-110, focusing on the study of color 
-transparency effects, has been approved recently \cite{ElFassi:2008}. As this 
+transparency effects, has been approved and published~\cite{ElFassi:2008}. As this 
 analysis went through a careful review by the CLAS collaboration, we use
-similar analysis methods when possible. In particular, the electron selection 
+similar analysis methods as much as possible. In particular, the electron selection 
 presented here is very similar to theirs; the main difference being a new 
-target determination method.
+target determination method. The pion identification methods are however tightened
+in this analysis as we have less constraints on the kinematics to exclude possible
+contaminations.
 
@@
 confusion between the scattered electron and electrons from hadronic decays or 
-photon conversion to $e^+e^-$ pair, which often lead to the production of a
-positron.
+photon conversion.
 
@@
 HERMES data \cite{Airapetian:2007vu}, which show a very 
-different behavior of the protons compared to the other hadrons (see chapter \ref{chap:data}).
+different behavior of the protons compared to the other hadrons.
 
@@
   \caption{Measured mean vertex position of targets, relative to the center of 
-           CLAS (in cm). (Aluminum data are separated in two sets because the 
-           target position appears to have changed at some point.)}
+           CLAS (in cm). We note that aluminum data are separated in two sets because the 
+           target position has brutally changed, moreover
+           during these runs the deuterium target was empty.}
   \label{tab:targets}
@@
 Since we are interested in deep inelastic scattering, we use the following 
-cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut $y < 0.85$ to 
-reduce the impact of radiative effects, which will be discussed in more details in 
-the section \ref{RadCor}.
+cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut $y < 0.85$ 
+which corresponds to low energy electrons. These are removed beacause they are
+significantly affected by radiative effects and at the limit of our trigger 
+threshold.
 
@@
 Once the identification is done, the calculation of the observables is 
-straight forward and the statistical errors are calculated with this expression
-
+straight forward with statistical errors given by:
 \begin{equation}
@@
 
-The implementation of acceptance and radiative corrections is done through weights
-given to each particles depending on its kinematic. The multiplicity ratio becomes
-
+However, the implementation of acceptance and radiative corrections is done through weights
+given to each events depending on their kinematics. The multiplicity ratio then becomes
 \begin{equation}
@@
 \begin{equation}
-\langle P_\perp^2 \rangle = {\sum P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
+\langle P_\perp^2 \rangle = {\sum \left ( P_\perp^2 \times \omega (Q^2,\nu,z_h,P_\perp^2) \right ) \over \sum \omega (Q^2,\nu,z_h,P_\perp^2)}.
 \end{equation}
 
-This expressions leads to new expressions for the statistical error uncertainties:
-
+This expressions leads to new expressions for the statistical error uncertainties taking weights into account: 
 \begin{equation}
@@
 
-We present in figure \ref{fig:prelim} few preliminary results, before the application of any correction, with the goal to 
-provide a first idea on data quality. The preliminary results will also be used to 
+We present in figure \ref{fig:prelim} few preliminary results, before the application 
+of any correction, to 
+provide a first idea on data quality. These preliminary results will also be used to 
 illustrate the effects of the corrections discussed below.
@@
 generated events are processed by the CLAS software (GSIM, GPP and user\_ana) 
-to simulate the detector and the reconstruction process similarly to the one for experimental data.
+to simulate the detector and the reconstruction process similarly to the one for 
+experimental data.
+% TODO GPP factors
 
@@
 simulation reproduces quite well the detectors responses, yet two issues might 
-affect us and have to be understood. First, the efficiency of the CC is overestimated in the simulation. 
+affect us and have to be understood. First, the efficiency of the CC is 
+overestimated in the simulation. 
 On the electron side the signal is a little stronger in the simulation (11 
@@
 feature should not affect us too much, because we are cutting only the tail of the 
-distribution in both cases. For pion identification, as mentioned in section \ref{PiId},
-we do not use the CC because of its unexpectedly low efficiency 
-We observe, in the simulation, a much better detector response than in experiment 
-(figure \ref{simPionCC} compared to figure \ref{PionCC}), this result also advocates against the use of the CC in the 
-particle identification. Indeed, the poor reproduction of the experimental signal would introduce a bias in our acceptance correction. 
+distribution in both cases. 
+%For pion identification, as mentioned in section \ref{PiId},
+%we do not use the CC because of its low efficiency.
+%We observe, in the simulation, a much better detector response than in experiment 
+%(figure \ref{simPionCC} compared to figure \ref{PionCC}), this result also 
+%advocates against the use of the CC in the 
+%particle identification. Indeed, the poor reproduction of the experimental 
+%signal would introduce a bias in our acceptance correction. 
 Second, in figure \ref{vertex} the cuts on vertex are shifted from one sector 
@@
 
-\begin{figure}[tpb]
-\centering
-\includegraphics[width=9cm] {chap5-fig/fig06simul.png} 
-\caption {Histograms of momentum (GeV/c) of $\pi^-$ for {\bf simulated data}.
-In black are all identified $\pi^-$, in red pions that also fire in the 
-Cherenkov counter and in blue those that fire in the Cherenkov counter with 
-more than one photo-electron.}
-\label{simPionCC}
-\end{figure}
+%\begin{figure}[tpb]
+%\centering
+%\includegraphics[width=9cm] {chap5-fig/fig06simul.png} 
+%\caption {Histograms of momentum (GeV/c) of $\pi^-$ for {\bf simulated data}.
+%In black are all identified $\pi^-$, in red pions that also fire in the 
+%Cherenkov counter and in blue those that fire in the Cherenkov counter with 
+%more than one photo-electron.}
+%\label{simPionCC}
+%\end{figure}
 
@@
  \item very few events reconstructed, leading to large statistical errors;
- \item many events that were generated in another bin (bin migration).
+ \item large fraction of events originaly generated in another bin (bin migration).
 \end{itemize}
@@
 \begin{equation} \label{eq:AccL1}
-\left ({\delta \omega \over \omega}\right ) ^2 \times {R_c \over \omega} < 2,
+\left ({\delta \omega \over \omega}\right ) ^2 \times R_c \times \omega < 2,
 \end{equation}
@@
 \end{equation}
-with $\omega$ either the previously calculated weights or one for the 
-excluded bins.
+with $\omega$ the previously calculated weights or one for the 
+bins excluded by the cuts.
 One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
-\ref{eq:AccL2} is to keep the reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
+\ref{eq:AccL2}is to keep the reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
 percents level.
@@
 significant correction for the few centimeters between the two targets. The 
-$\pi^-$s are more affected because of CLAS' magnetic field. Indeed, the low \pt
-$\pi^-$s have very low acceptance, this makes the errors 
-on \dpt very large and the related results difficult to exploit. Finally, because 
-of some difference in position between the solid targets (table 
-\ref{tab:targets}), some extra simulation is needed in order to exploit 
-correctly the aluminum and tin results. Therefore, these two targets should not be considered for 
-the final results.
+$\pi^-$s appears to be more affected. This is due to the inbending magnetic 
+field. Indeed, the low \pt $\pi^-$s have very low acceptance, leading to large 
+correction factors. The large spread in weights makes the errors 
+on \dpt very large and the related results difficult to exploit. 
+On the bright side, after the correction, the transverse momentum
+broadening of both pions now match.
 
@@
 
-The radiative correction appears to be limited in amplitude in most of the 
-kinematic, so we decided not to apply it before further studies. Improvement can 
-be easily obtained by generating more statistics, in order to analyze the 
-semi-inclusive effects in more depth. Also radiative effects from the target thickness 
-are ignored in the current setup; these need to be evaluated and, eventually, 
-corrected as well.
+The semi-inclusive part of the radiative correction appears to be limited 
+in amplitude in most of the 
+kinematic, except for high $z$ and \ptp. So, we decided not to apply this 
+correction before further studies.
+
+{\color{red} We found a better way to implement the radiative correction,
+that is not limited by the Monte-Carlo technique. We will implement it in
+the second version of the note as we do not want to delay the review process for
+this correction that we already found to be small. Sorry about that.}
 
@@
 
-The important excess of neutron in heavy nuclei leads to a modification of the 
+The important excess of neutrons in heavy nuclei leads to a modification of the 
 $\pi$ multiplicity per DIS events. Using Hall~C results 
@@
 We attribute errors of 10\% of the effect for the isospin correction, this is chosen 
-relatively to the precision of the Hall~C measurement.
+relatively to the precision of the Hall~C measurement and the fact that they do not 
+cover as much phase space as we do.
 
@@
 We finally note that the $A$ dependencies of the multiplicity ratios of the 
-charged pions are similar after the isospin correction\footnote{Within 
+charged pions are parallel after the isospin correction\footnote{Within 
 normalization errors presented in section \ref{sec:TotSys}} (figure 
@@
 0.4 \%$, $\delta P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$ and so on\footnote{These were 
-evaluated for typical kinematics, the results can be significantly larger at 
+evaluated for typical kinematics, the results can be larger at 
 extreme kinematics (large \pt or Q$^2$).}. These are negligible because they are 
@@
 contamination comes from kaons above 2~GeV/c ($\sim$3\% of $\pi^+$ and 
-$\sim$0.5\% of $\pi^-$). Incidentally, protons also contaminates $\pi^+$ at 
-high momentum (up to few \%). The uncertainty related to 
-misidentification is taken into account for the point to point systematic error 
-evaluation, other effects are found to be negligible.
+$\sim$0.5\% of $\pi^-$). Protons also contaminates $\pi^+$ at 
+high momentum (up to few \%). 
+%TODO Justify the pt cut with a figure?
+
+In conclusion, the uncertainty related to misidentification 
+is taken into account at the level of 100\% of the contamination in the point 
+to point systematic errors, other effects are found to be negligible.
 
@@
 target selection. We use it to evaluate contamination from the liquid target to the solid one. The region 2
-is downstream and of the size of the window for the liquid target selection and allows to evaluate the solid target leak into the liquid one
+is downstream and of the size of the window for the liquid target selection 
+and allows to evaluate the solid target leak into the liquid one.
 The distance between detection and test regions is identical to the 
@@
 
-We apply two different acceptance corrections to the data using two different binnings 
+We tested several different acceptance corrections to the data using finally 
+two different binnings 
 (table \ref{tab:AcceptBinning}). The differences between them give us a good 
-indication on the systematic error associated with the method. Using a sample 
-of results from iron, we find the systematic presented in the table 
+indication on the systematic error associated with the method. Using our
+results on iron, we find the systematic presented in the table 
 \ref{tab:SysAcc}. We note the significantly larger errors for $\pi^-$, which 
@@
 order, or smaller, as the differences observed between the two sets. This is 
-an indication that the uncertainties reported in table \ref{tab:SysAcc} are already 
-taken into account in the statistical error.
+an indication that the uncertainties reported in table \ref{tab:SysAcc} are 
+similar in nature with the statistical error, in the sense that they originate
+from the large variation between the weights from event to event. For this
+reason, we decide not to include this error in order to double count it.
 
@@
 
-\subsubsection{Normalization Error}
+\subsubsection{Total Error}
 
-The normalization errors -- i.e. independent of kinematic variables -- are due to acceptance effects, target identification 
-and isospin correction. They are summarized in the table \ref{tab:sysid}.
+The point to point errors include the contributions from detection 
+contamination and acceptance effects. The normalization errors 
+-- i.e.~independent of kinematic variables -- are due to acceptance effects, 
+target identification and isospin correction. They are summarized in the 
+table~\ref{tab:sysid}.
 

### 2016-10-07 chap6.tex
Updated the result part.

@@
 
-The results presented in this chapter are corrected for acceptance effects, 
-but not for radiative ones. We use the following DIS selection cuts: 
+The results presented in this chapter are a selection of the observables 
+that we want to use in a first publication, eventually a long paper would
+include all results as function of all variables. We use the following DIS selection cuts: 
 $Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$. In order to ensure that 
@@
 hadron and that we avoid the high $z$ region, which might be contaminated by 
-the diffractive $\rho^0$ decay products. Finally, the cut $x_F > 0$ select the 
-current fragmentation region.
+the decay products of the diffractive production of $\rho^0$. Finally, the cut 
+$x_F > 0$ select the forward fragmentation region.
 
@@
 all other variables, shows a pattern similar to the HERMES measurement. 
-However, there is potential contributions from the target fragmentation (see 
-chapter~\ref{chap:data}) and the Fermi motion (see chapter \ref{chap:pyqm}).
+However, there is potential contributions from the target fragmentation and 
+the Fermi motion.
 
@@
 effects (section~\ref{sec:accept}) are mostly canceled as well in such a ratio, 
-reducing various systematic errors (including most of the normalization error). 
+reducing the associated systematic errors (including most of the normalization error). 
 The figure \ref{fig:RPt} (right) represents the multiplicity ratio based on carbon. We 
@@
 iron. At first sight the difference can be attributed to Fermi motion, which 
-might affect the measurement based on deuterium. The target fragmentation 
-effects might also lead to similar observation and more evidence are 
-needed to confirm our interpretation.
+might affect the measurement based on deuterium.
 
@@
 ratio are presented. HERMES found an important dependence of the Cronin effect 
-with $z$ \cite{Airapetian:2007vu,Airapetian:2011jp} that we interpreted as a 
+with $z$ \cite{Airapetian:2007vu,Airapetian:2011jp} that can be interpreted as a 
 sign of an important target fragmentation contribution. The present result 
@@
 reveal any similar $\nu$ variation. This is an evidence of the importance of 
-the Fermi motion effect in our measurement. Indeed, in the 
-chapter~\ref{chap:pyqm}, it was shown that the impact of Fermi motion gets 
-smaller at higher energy.
+the Fermi motion effect in our measurement.
 
@@
 fragmentation and that our results are affected by Fermi motion. These effects can 
-be easily controlled by selecting carefully our observables and kinematic coverage.
+be easily controlled by selecting carefully our observables. In this regard, the
+Pb/C ratio seems to give cleaner results than Fe/D.
 
@@
 \ref{fig:RNu} (left)), no dependence is observed, except for a 
-slight increase in lead. The results on Fermi motion together 
-with the figure \ref{fig:RNu} (right) permit to reach a coherent explanation. The 
-Fermi motion seems to cancel the hadronization effect almost completely and the
+slight increase in lead.
+However, Fermi motion could cancel the hadronization effect almost completely and the
 systematic uncertainties linked with acceptance might wash out what remains of the effect. The 
-multiplicity ratio based on carbon, however, offers a very neat slope consistent 
+multiplicity ratio based on carbon, however, offers a cleaner result with a slope consistent 
 with what was observed on a much larger range by HERMES.
@@
 observed in the multiplicity ratio based on deuterium might come from the 
-normalization uncertainty caused by the acceptance correction. Therefore, there is no 
+normalization uncertainty caused by the acceptance correction. There is no 
 clear difference between the charged pions for the integrated multiplicity 
-ratios.
+ratios as a function of $\nu$.
 
@@
 \ref{fig:Rz} (right)) shows a much flatter behavior in the region of interest 
-(0.4 to 0.7). This is coherent with what we showed in chapter \ref{chap:pyqm}, i.e. the expected $z$ slope 
-is enhanced by Fermi motion effects. Therefore, the situation seems to be 
+(0.4 to 0.7). Therefore, the situation seems to be 
 similar to the Cronin effect one, where HERMES observation was enhanced by 
@@
 reached on this question. Our leverage on $Q^2$ appears to be too modest
-to make a clear measurement. Future programs to explore this question are 
-discussed in chapter~\ref{chap:future}.
+to make a clear measurement.
 
@@
 at larger energies. However, calculations of parton energy loss from BDMPS 
-\cite{Baier:1996sk} show that \pt should depend on the nucleus radii
-(see chapter \ref{chap:theory}). However, this feature does not appear in our 
+\cite{Baier:1996sk} show that \pt should depend on the nucleus radii. However, 
+this feature does not appear in our 
 result. Of course, because of the low energy of the CLAS experiment, one might 
@@
 $A^{1/3}$, the production time occurs inside the nuclei. In this case, the 
-colored parton would not interact with the whole nuclei and therefore changing 
-its size would lead to limited effect.
+colored parton would not interact with the whole nuclei and limit the nuclear 
+effect.
 
@@
 \label{fig:PA}
-\end{figure}
-
-\subsubsection{$z$ Dependence}
-
-The $z$ dependence of \dpt has some importance for parton energy loss
-models, because it is linked to the assumptions needed to extrapolate the hadronic \pt
-to the partonic one. Moreover, usually, in parton energy loss models, \dpt
-goes to zero at the highest $z$. Our results (figure \ref{fig:PZ}) do
-not show such a pattern. However, our previous results showed the importance of 
-Fermi motion in our kinematics, which is expected to enhance \dpt at very high
-$z$. This is confirmed by the flattening observed for the carbon based \dptp, but
-the distribution is not clearly going down either at high $z$. This might be due to the size of the 
-error bars and the potential contamination from diffractive $\rho^0$ production, both 
-preventing us from any definitive statement on this feature of the data.
-
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=7.4cm] {chap6-fig/F_PvZ.png} 
-\includegraphics[width=7.4cm] {chap6-fig/F_PvZ_PbC.png} 
-\caption {\dpt as a function of $z$. Left panel is the usual
-observable, right panel shows multiplicity ratio of lead normalized to carbon. Normalization uncertainties are not shown.}
-\label{fig:PZ}
 \end{figure}

### 2016-10-11 AnalysisNote.tex
Corrections from Lamiaa

@@
 The goals of the experiment E-02-104 are to study both quark propagation
-and hadronization dynamic using various nuclear target.
+and hadronization dynamics using various nuclear target.
 In this analysis we focus on two particles, the positive and negative pions
-to constrain theoritical models using precise multidimensional analysis.
+to constrain theoritical models using a precise multidimensional analysis.
 

### 2016-10-11 chap5.tex
Small fix
Corrections from Lamiaa

@@
 
-This chapter treats of the analysis of the data taken in CLAS for the 
+This chapter treats the analysis of CLAS data taken for both 
 experiments E-02-104 \cite{Brooks:2002aa} and E-02-110 \cite{Hafidi:2002aa}.
-The code name for the run is {\it eg2}, it was composed of three phases 
+The run period, named {\it eg2}, was composed of three phases 
 labeled {\it a}, {\it b} and {\it c}. The analysis is performed on the data 
@@
 which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small 
-amounts of data at a beam energy of 4~GeV that we decided not to use for this analysis.}.
+amounts of data at beam energies of 4 and 4.7~GeV, Thus, we decided not to use them 
+for this analysis.}.
 
@@
 with heavier nuclei, it was decided to use a double target system 
-\cite{Hakobyan:2008zz}. The first target is filled with liquid deuterium and 
-the second is a solid target. The latter can be made of carbon, aluminum, 
-iron, tin or lead and changed remotely (the system is shown in figure 
-\ref{fig:phototarget}). The two targets are separated by only 4~cm in order to reduce
+\cite{Hakobyan:2008zz}. The first target was filled with liquid deuterium and 
+the second was a solid target. The latter was made of either carbon, aluminum, 
+iron, tin or lead and was changed remotely (the system is shown in figure 
+\ref{fig:phototarget}). The two targets were separated by only 4~cm in order to reduce
 the acceptance differences between them. The 
-advantage to have the two targets in the beam line simultaneously
+advantage of having two targets simulataneously in the beam line
 is that several systematic effects related to the beam 
@@
 \caption {Picture of the target system of the {\it eg2} run. The cryogenic target is 
-in the back, enveloped in aluminum foils. The solid targets are held by mechanical arms
-allowing to change targets remotely, in the picture the top arm is in the beam line.}
+in the back, wrapped with aluminum foils. The solid targets are held by mechanical arms
+that were remotely controled. In the picture, the top solid target is in the beam line.}
 \label{fig:phototarget}
@@
 Once particles are identified, we can extract the observables (multiplicity 
-ratio and transverse momentum broadening). The method is presented in the 
-section \ref{sec:obs}, however these need several corrections presented in the 
-section \ref{sec:corrections}. The 
-two main corrections are the acceptance of the detector and the radiative 
-effects, both are evaluated using Monte-Carlo generator. The evaluation of 
+ratios and transverse momentum broadening). The method is presented in the 
+section \ref{sec:obs}, the corrections to these observables are presented in the 
+section \ref{sec:corrections}. The evaluation of 
 the systematic errors is presented in the section \ref{sec:TotSys}.
-The analysis' final results are presented and discussed in the next chapter.
+Finally, the analysis' final results are presented and discussed in the next chapter.
 
@@
   \caption{Values of the parameter $b$ used in equation \ref{einout} for 
-           different momentum ranges.}
+           different momentum ranges~\cite{ElFassi:2008}.}
   \label{tab:ecoutin-par}
@@
 \includegraphics[width=14cm] {chap5-fig/fig02.jpg} 
-\caption {Energy deposited in the inner part of the EC ($E_{in})$) as a function of the 
-energy deposited in the outer part ($E_{out})$), both divided by the momentum of the 
+\caption {Energy deposited in the inner part of the EC ($E_{in}$) as a function of the 
+energy deposited in the outer part ($E_{out}$), both divided by the momentum of the 
 particle. Each panel is for a different momentum range, the red lines 
@@
 However, hadrons can generate noise due to $\delta$ electrons produced in 
-the materials of the detector. This signal is expected around 
-one photo-electron, to remove it, we keep only tracks with more than 
+the materials of the detector. This signal is expected to be around 
+one to two photo-electrons, hence to remove it we keep only tracks with more than 
 2.5~photo-electrons (figure \ref{delta}).
@@
 To select electrons, we also require that the particles are negatively charged, 
-according to the bending direction of the tracks in the drift chamber.
-Positively charged particles are identified as positrons. In the rest of the 
-analysis we use events with only one electron and no positron to avoid any 
-confusion between the scattered electron and electrons from hadronic decays or 
-photon conversion.
+which is determined based on the bending direction of the track in the drift chamber.
+Positively charged particles verifying electrons' cuts are identified as 
+positrons. In the rest of the 
+analysis we use only events with a single electron and no positron to avoid any 
+confusion between the scattered electron and electrons originating from hadronic decays or 
+a photon conversion.
 
@@
 The identification consists mostly of a time of flight (TOF) test. We define 
+the relativistic particles' velocity difference as
 $\Delta \beta = \beta_{measured} - {p \over \sqrt{p^2 + m_\pi^2}}$ and request 
@@
 Moreover, as only a very small amount of $K^-$ and no $\bar p$ are present on 
-the figure \ref{PionTOF}, we decided not to use the CC for pion identification.
+the figure \ref{PionTOF}, we decided to not use the CC for the pion identification.
 
@@
 pions. However, the time of flight plot is significantly more busy (figure 
-\ref{PipTOF}), showing significant contamination from $K^+$ and protons at 
+\ref{PipTOF}), showing a significant contamination from $K^+$ and protons at 
 high momentum. As the CC is not efficient enough for hadron separation, the 
@@
 lines are the cuts applied to select positive pions. The blue lines indicate 
-theoretical positions for other particle masses, are plotted from top to 
+the theoretical positions for other particles, we plotted from top to 
 bottom the lines for positrons, muons, kaons and protons.}
@@
 The detected electrons are associated with the solid target if their vertex 
-position is at less than 1.5~cm ($\sim$3~$\sigma$) from the value of table 
+position is less than 1.5~cm ($\sim$3~$\sigma$) from the value of table 
 \ref{tab:targets}. For the liquid target, the cut is larger, 2 cm, in order to 
@@
 To check the quality of the runs\footnote{Runs correspond roughly to two hours
-of data, they can be smaller in case of problem.}, we look at the ratio of the number of 
+of data, they can be smaller in case of problems.}, we looked at the ratio of the number of 
 scattered electrons, between the liquid and solid targets. If the beam is 
@@
 Since we are interested in deep inelastic scattering, we use the following 
-cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut $y < 0.85$ 
-which corresponds to low energy electrons. These are removed beacause they are
-significantly affected by radiative effects and at the limit of our trigger 
+cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut on the 
+fraction of energy transferred $y = \nu/E_{beam} < 0.85$.
+This corresponds to removing the low energy electrons because they are
+significantly affected by radiative effects and sat the limit of our trigger 
 threshold.
@@
 \end{equation}
-with $\omega$ the weights and all the sums running over all measured particles.
-The expression for the transverse momentum broadening remains
+with $\omega$ the weight associated with the event and the sums running over all measured 
+particles. The expression for the transverse momentum broadening remains
 \begin{equation}
@@
 
-This expressions leads to new expressions for the statistical error uncertainties taking weights into account: 
+Thus, new expressions are also needed for the statistical error uncertainties: 
 \begin{equation}
@@
 
-We present in figure \ref{fig:prelim} few preliminary results, before the application 
-of any correction, to 
-provide a first idea on data quality. These preliminary results will also be used to 
+To provide a first idea on data quality, we present in figure~\ref{fig:prelim} 
+few preliminary results, before the application 
+of any corrections. These preliminary results will also be used to 
 illustrate the effects of the corrections discussed below.
@@
 
-The acceptance correction consists of applying weights to the events in 
-experimental data to correct for the inefficient parts of the detectors.
+The acceptance correction consists of applying weights to the experimental data
+events by events to correct for detection inefficiencies of the detectors.
 Incidentally, it also corrects for small other issues of detection,
@@
 experiment, the statistics accumulated and the size of interfering effects, such 
-as bin migration.
+as bin migration. For this correction, we applied the method from the 
+approved and published analysis from the same eg2 data~\cite{ElFassi:2008}.
 
@@
 distribution in both cases. 
-%For pion identification, as mentioned in section \ref{PiId},
-%we do not use the CC because of its low efficiency.
-%We observe, in the simulation, a much better detector response than in experiment 
-%(figure \ref{simPionCC} compared to figure \ref{PionCC}), this result also 
-%advocates against the use of the CC in the 
-%particle identification. Indeed, the poor reproduction of the experimental 
-%signal would introduce a bias in our acceptance correction. 
-Second, in figure \ref{vertex} the cuts on vertex are shifted from one sector 
-to another, since the simulation have perfect alignment of beam with CLAS this 
-feature is not present in the simulated data. Therefore, we do not apply the 
-shift from the table \ref{tab:vertex} to the simulation; results are shown in 
-figure~\ref{simvertex}.
-
-%\begin{figure}[tpb]
-%\centering
-%\includegraphics[width=9cm] {chap5-fig/fig06simul.png} 
-%\caption {Histograms of momentum (GeV/c) of $\pi^-$ for {\bf simulated data}.
-%In black are all identified $\pi^-$, in red pions that also fire in the 
-%Cherenkov counter and in blue those that fire in the Cherenkov counter with 
-%more than one photo-electron.}
-%\label{simPionCC}
-%\end{figure}
+Second, since the simulation has a perfect alignment of the beam with CLAS the 
+vertex cuts do not need to be shifted from one sector to another. Therefore, 
+we do not apply the shift from the table \ref{tab:vertex} to the simulation; 
+the resulting cuts are shown in figure~\ref{simvertex}.
 
@@
 experimental ones. This is important for the acceptance correction, to see 
-whether or not, we can integrate over these variables for the correction.
-Comparisons between simulation and experiment are shown in figures 
+whether or not, we can integrate over these variables in this correction.
+Comparisons between simulated and experimental data are shown in figures 
 \ref{fig:compNuQ2} to \ref{fig:compPhih}. The agreement is reasonable, but not 
@@
 
-The data is corrected using weights defined as $\omega = 1/\text{Acc}$. The 
+The experimental data are corrected using weights defined as $\omega = 1/\text{Acc}$. The 
 $\omega$ coefficient are calculated in many bins, in order to be independent of 
@@
 
-We use a 4-dimensional binning to divide the large phase space available to 
-the two particles in the measured final state. To evaluate the systematic error 
-associated to the correction, we use two different binning, which are 
-presented in the table \ref{tab:AcceptBinning}. The total number of bins is 
-constrained by the amount of data generated and has to be maintained 
-reasonably low in order to keep a good statistical precision and reasonable 
+We used a 4-dimensional binning to divide the large phase space available to 
+our two particle final state. To evaluate the systematic error 
+associated to this correction, we uses the two different binning
+presented in table~\ref{tab:AcceptBinning}. The total number of bins is 
+constrained by the amount of data generated and must be maintained 
+reasonably low in order to keep a good statistical precision and manageable 
 bin migration.
@@
  \item very few events reconstructed, leading to large statistical errors;
- \item large fraction of events originaly generated in another bin (bin migration).
+ \item large fraction of events originally generated in an other bin (bin migration).
 \end{itemize}
@@
 \end{equation}
-with $\delta \omega / \omega$ the relative error on the weight and $R_c$ the 
-proportion of events in the bin initially generated in another bin. Figure 
+$\delta \omega / \omega$ is the relative error on the weight and $R_c$ the 
+proportion of reconstructed events initially generated in another bin. Figure 
 \ref{fig:AccCoef} shows the distributions of $\omega$, after the cuts. Around 
@@
 \end{equation}
-with $\omega$ the previously calculated weights or one for the 
-bins excluded by the cuts.
+$\omega$ is the previously calculated weights or $1$ when the 
+bin was excluded by the cuts.
 One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
-\ref{eq:AccL2}is to keep the reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
+\ref{eq:AccL2} is to keep reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
 percents level.
@@
 
-The electron acceptance, necessary in order to correct the number of electrons 
-in the multiplicity ratios, is done with the same method than in the 
+The electron acceptance, which is necessary in order to correct the number of electrons 
+in the multiplicity ratios, is done following the same method as in the 
 semi-inclusive case, but only using the two first dimensions ($\nu$ 
-and $Q^2$). It is also interesting to note that no reweighting is necessary 
+and $Q^2$). However, reweighting is not used 
 for electrons as all non-empty bins pass the cuts \ref{eq:AccL1} and 
@@
 \includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
-\caption {Preliminary results are compared with results corrected for 
-acceptance, for multiplicity ratios (top) and transverse momentum broadening 
+\caption {Preliminary results are compared with acceptance corrected ones, 
+for multiplicity ratios (top) and transverse momentum broadening 
 (bottom). Only statistical errors are shown.}
@@
 represented, shows the new results after applying the acceptance correction.
-The acceptance effects appear to be of $\sim 10$\% for multiplicity ratios and 
-$\sim 30$\% for transverse momentum broadening. This is a surprisingly 
-significant correction for the few centimeters between the two targets. The 
-$\pi^-$s appears to be more affected. This is due to the inbending magnetic 
+The acceptance correction effects appear to be of the order of $10$\% for 
+multiplicity ratios and 
+$30$\% for transverse momentum broadening. This is a surprisingly 
+significant correction in regard to the few centimeters between the two targets. 
+The reason for such a large correction is that the small shift in $z$ position changes 
+slightly the minimum angle of the detector in the region where most hadron production 
+is concentrated, {\it i.e.} at low \pt close to the beam line. The 
+$\pi^-$s appears to be more affected, which is due to the inbending magnetic 
 field. Indeed, the low \pt $\pi^-$s have very low acceptance, leading to large 
@@
 on \dpt very large and the related results difficult to exploit. 
-On the bright side, after the correction, the transverse momentum
-broadening of both pions now match.
+Looking at the results themselves after the correction, we notice that now 
+the transverse momentum broadening of both pions match, which is consistent 
+with HERMES results.
 

### 2016-10-11 intro.tex
Corrections from Lamiaa

@@
 energies above the resonance region. In deep inelastic scattering the
-virtual photon interact with a quark which propagate quasi-free emitting
+virtual photon interact with a quark which propagates quasi-free emitting
 gluons during the 
-so-called production time. After neutralizing its color the quark become 
+so-called production time. After neutralizing its color, the quark becomes 
 a pre-hadron which will eventualy form a hadron after the formation time.
-On nuclear target the process of hadronization occurs, at least partly, in 
+On nuclear target the process of hadronization occurs, at least partialy, in 
 nuclear matter, then one can extract the production time using the different 
@@
 
-The hadronization in nuclear matter is a key process in QCD also
-because it leads to a major theoritical uncertainty in numerous measurements.
-In heavy ion collisions, the measured hadrons are produced in hot and evolving 
+The hadronization in nuclear matter is a key process in QCD 
+because it leads to major theoritical uncertainties in numerous measurements.
+In Relativistic Heavy Ion Collisions (RHIC), the 
+measured hadrons are produced in hot and evolving 
 medium, the models describing those collisions can be tested in deep inelatic scattering 
@@
 understanding of the hadronization in nuclei is also of interest for
-neutrino experiment which often use nuclei to maximize their cross section.
+neutrino experiments which often use nuclei to maximize their cross sections.
 The hadronization can give important information about the 
@@
 P_T^2 \rangle$ with the saturation scale. Other models \cite{Gallmeister:2007an}
-can give information about how the pre-hadron evolve into hadron but are based
+can give information about how the pre-hadron evolves into hadron but are based
 on very different assomptions, therefore it is very important to discriminate between
@@
 In order to constrain the existing models we extract our results
-using tight multi-dimensional binning. 
+using a tight multi-dimensional binning. 
 The importance of the EG2 data comes from its high statistics which permit, 
@@
 
-\subsection{Kinetic Variables and Observables}
+\subsection{Kinematic Variables and Observables}
 
-In this analysis we use the following semi-inclusive DIS variables:
+In this analysis we use the following semi-inclusive Deep Inelastic Scattering (DIS) variables:
 \begin{itemize}
- \item $\nu = E_i - E_f$ with $E_i$ the beam energy and $E_f$ the scattered electron energy,
- \item $Q^2 = 4 E_i E_f \sin ^2(\theta_e / 2)$ with $\theta_e$ the scattered electron angle with the beam line,
- \item $x_{Bj} = {{Q^2} \over {2 M_n \nu}}$ with $M_n$ the nucleon mass,
- \item $W^2 = M_n^2 - Q^2 + 2 M_n \nu$
- \item $z_h = E_h / \nu$
- \item $P_T^2$ which is transverse momentum according to the virtual photon
- \item $\phi_h$ the angle between the electronic plan (contain initial and scattered electrons) and the hadronic plan (contain virtual photon and hadron)
- \item $x_F = P_L/P_L^{max}$ the fraction of longitudinal momentum carried by the hadron calculated in respect to the virtual photon direction in the laboratory frame.
+ \item $\nu = E_i - E_f$ is the energy transfered by the lepton probe in the laboratory frame, $E_i$ is the beam energy and $E_f$ is the scattered electron energy,
+ \item $Q^2 = 4 E_i E_f \sin ^2(\theta_e / 2)$ is the 4-momentum transfered and $\theta_e$ is the scattered electron angle,
+ \item $x_{Bj} = {{Q^2} \over {2 M_n \nu}}$ is the fraction of the proton momentum carried by the struck quark and $M_n$ is the nucleon mass,
+ \item $W^2 = M_n^2 - Q^2 + 2 M_n \nu$ is the mass squared of the hadronic system produced,
+ \item $z_h = E_h / \nu$ is the fraction of energy available carried by the measured hadron and $E_h$ is the hadron energy,
+ \item $P_T^2$ is the transverse momentum with regard to the virtual photon,
+ \item $\phi_h$ is the angle between the leptonic plan (containing the initial and scattered electrons) and the hadronic plan (containing the virtual photon and hadron),
+ \item $x_F = P_L/P_L^{max}$ is the longitudinal momentum fraction carried by the hadron calculated in respect to the virtual photon direction in the laboratory frame.
 \end{itemize}
@@
 R_A^h (Q^2,\nu,z_h,P_T^2) = {{N_A^h (Q^2,\nu,z_h,P_T^2) / N_A^e (Q^2,\nu)} 
-                       \over {N_D^h (Q^2,\nu,z_h,P_T^2) / N_D^e (Q^2,\nu)}}
+                       \over {N_D^h (Q^2,\nu,z_h,P_T^2) / N_D^e (Q^2,\nu)}},
 \end{equation}
-with $N^e_A$ the number of electron measured from a target $A$ and $N_A^h$ the number
-of semi-inclusive hadrons $h$ (detection of both an electron and a hadron) from the
+$N^e_A$ is the number of electrons measured from a target $A$ and $N_A^h$ is the number
+of semi-inclusive hadrons $h$ (detection of both an electron and a hadron is required) from the
 target~$A$. The multiplicity ratio represents the attenuation of the hadron $h$ in a 
@@
 \begin{equation}
-\Delta \langle P_T^2 \rangle = \langle P_T^2 \rangle_A - \langle P_T^2 \rangle_D
+\Delta \langle P_T^2 \rangle = \langle P_T^2 \rangle_A - \langle P_T^2 \rangle_D,
 \end{equation}
-with $\langle P_T^2 \rangle_A$ the mean transverse momentum measured in a target $A$.
+$\langle P_T^2 \rangle_A$ is the mean transverse momentum measured in a target $A$.
 
@@
 The different models explaining the data can be separated in three families,
-some assume that the quark loose energy in the medium and that either, hadronization occurs
+some assume that the quark looses energy in the medium and that either, hadronization occurs
 outside the medium or the hadronic interaction is 
-negligible, others consider the quark energy loss negligible and consider
-only the hadron and pre-hadron absorption and finally some models consider both
-interactions. We will give an example of each case to illustrate, for more
-detailed information we refer again to \cite{Accardi:2009qv} which is more exaustive and
-mention few other models used for RHIC experiments.
+negligible, others neglect the quark energy loss and consider
+only the hadron and pre-hadron absorption, and finally some models consider both
+interactions. We will give an example of each case to illustrate. For more
+detailed information, we refer again to~\cite{Accardi:2009qv}, which is more exaustive and
+highlights also models used for RHIC experiments.
 
-In \cite{Wang:2002ri}, E.~Wang and X.-N.~Wang, describe HERMES data using only energy 
+In \cite{Wang:2002ri}, E.~Wang and X.-N.~Wang, describe HERMES data using only 
+the energy 
 loss from the parton, the suppression observed is then due to the fact that a 
 lower energy quark will fragment into a lower number of hadrons and a lower 
-$z$. That kind of model is used in both RHIC and nDIS and permit a commom 
+$z$. That kind of model is used in both RHIC and nuclear DIS and permit a commom 
 interpretation of hadron suppression in nuclear matter. Lot of different
@@
 (GeV$^2$ fm$^{-1}$) which is the transverse momentum per unit of length of a 
-quark after propagating
-in nuclear matter, this value is related to the $P_T$ 
-broadening observables. The main difficulty for the quark energy loss
-models is to have coherent description of both multiplicity ratios and $P_T$ 
-broadening. Recent models find a $\hat q$ to reproduce multiplicity ratio
-which is bigger than the one necessary to describe transverse momentum broadening.
+quark after propagating in the nuclear matter. Its value is related to the $P_T$ 
+broadening observable. The main difficulty for quark energy loss
+models is the lack of a coherent description for both multiplicity ratios and $P_T$ 
+broadening. Recent models used a $\hat q$ to reproduce multiplicity ratio
+which is to large to describe the transverse momentum broadening.
 % TODO Add a ref
 
-The GiBUU model \cite{Gallmeister:2007an} is a transport model based on Boltzmann equation
-using hadronic and pre-hadronic interaction in the nuclear matter, with no
-quark energy loss involved. This model reproduce very well most of the hadrons, 
+The GiBUU model \cite{Gallmeister:2007an} is a transport model based on the 
+Boltzmann equation
+using hadronic and pre-hadronic interactions in the nuclear matter, with no
+quark energy loss involved. This model reproduces very well most of hadrons'
+multiplicity ratios, 
 however the $\Delta \langle P_T^2 \rangle$ variable is not described at all by 
-this hadron absorption models.
+these hadron absorption models.
 
-B.Z.~Kopeliovich \cite{Kopeliovich:2008uy} describe the process neglegting neither quark 
-energy loss or hadron absorption, using transverse momentum and
-multiplicity ratios to differenciate the effects. In that case the transverse 
-momentum broadening is linked to quark energy loss and the multiplicity ratio
-suppression is explained by hadron absorption in medium.
+B.Z.~Kopeliovich \cite{Kopeliovich:2008uy} described the process by neglegting 
+neither the quark 
+energy loss nor the hadron absorption, and by using transverse momentum and
+multiplicity ratios to differenciate their effects. In that case the transverse 
+momentum broadening is linked to the quark energy loss and the multiplicity ratio
+suppression is explained by the hadron absorption in the nuclear medium.
 
@@
 L.~Hand {\it et al.} \cite{Hand:1978tx} and the E665 collaboration \cite{Adams:1994ri} at FNAL
-and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN. Those 
-measurements revealed the general features of hadronization
-in nuclei: we observe a sizeable suppression when
-looking at hadron production in nuclei, this suppression is lower at higher
-$\nu$ and lower $z$, it can even inverse and be an increased yield at very low $z$.
+and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN. These 
+measurements revealed the general features of the hadronization mechanism
+in nuclei: we observe a suppression hadron production in heavier nuclei.
+This suppression appears to be reduced at higher $\nu$ and lower $z$, and it 
+can even inverse and become an increased yield at very low $z$.
 
-The figures \ref{fig:her1}, \ref{fig:her2} and \ref{fig:her3} shows a sample of 
-the most recent data from HERMES collaboration \cite{Airapetian:2007vu}, numerous 
-hadrons are studied individually and new variables linked with transverse 
-momentum are used on top of the usual multiplicity ratio.
+The figures \ref{fig:her1}, \ref{fig:her2} and \ref{fig:her3} show a sample of 
+the most recent data from the HERMES collaboration~\cite{Airapetian:2007vu}, 
+where numerous 
+hadrons were studied individually and new variables linked with transverse 
+momentum were used in addition of the usual multiplicity ratio.
 
@@
 The HERMES data, because of their precision,
-permit to have an insight into new features. One can cite the behavior of K$^+$
+permit to have an insight into new features. One can cite the behavior of K$^+$s
 which have less attenuation than pions (see figure \ref{fig:her1}) but more 
-$\Delta \langle P_T^2 \rangle$, it is difficult to reproduce this in 
+$\Delta \langle P_T^2 \rangle$. It is difficult to reproduce this in 
 models where only one stage of hadronization is taken into account to 
 explain all effects.
-Also the different behaviour of protons compare to anti-protons
-(see figure \ref{fig:her1}) is interesting
-and need precise analysis even most of the theoritical models do not treat 
+Also the different behavior of protons compare to anti-protons
+(see figure \ref{fig:her2}) is interesting
+and need a precise analysis since most of the theoretical models do not treat 
 baryon hadronization yet.

### 2016-10-13 AnalysisNote.tex
Add Will to the authors

@@
      pdftitle={Hadronization Analysis Note (EG2)}, %informations apparaissant dans
-     pdfauthor={Raphael Dupre},     %dans les informations du document
-     pdfsubject={Physics}          %sous Acrobat.
+     pdfauthor={Raphael Dupre et al.},     %dans les informations du document
+     pdfsubject={Nuclear Physics}          %sous Acrobat.
 }
@@
   {\it Physics Division, Argonne National Laboratory,} \\ 
-  {\it Argonne, Illinois 60439, USA} 
+  {\it Argonne, Illinois 60439, USA} \\
+  William \textsc{Brooks} \\
+  {\it Universidad T\'ecnica Federico Santa Mar\'ia,} \\ 
+  {\it Valpara\'iso, Chile} 
 }

### 2016-10-20 AnalysisNote.tex
Changes from Lamiaa

@@
 \begin{abstract}
-Hadronization is the process by which energetic quarks transform into 
-colorless hadrons. The process is non-perturbative, therefore, only 
-qualitative understanding can be achieved, and using phenomenological models 
-is necessary. By comparing hadron production 
-on different nuclei, one can measure variables with different sensitivities 
-to the hadronization phases, the two principal variables are: the transverse 
-momentum broadening, that is believed to be tightly connected to quark energy 
-loss and the multiplicity ratio, which is a measure of the hadron attenuation 
-in the medium.
+Hadronization is the process by which energetic quarks transform into colorless hadrons.
+The process is non-perturbative, therefore, only a qualitative understanding based on phenomenological models can be achieved.
+By comparing hadron production on different nuclei, one can measure the most sensitive variables to the hadronization phases, the transverse momentum broadening, that is believed to be tightly connected to the quark energy loss, and the multiplicity ratio, which is a measure of the hadron attenuation in the nuclear medium.
 
-The goals of the experiment E-02-104 are to study both quark propagation
-and hadronization dynamics using various nuclear target.
-In this analysis we focus on two particles, the positive and negative pions
-to constrain theoritical models using a precise multidimensional analysis.
+The goal of the experiment E-02-104 was the study of the quark propagation and hadronization dynamics using various nuclear targets.
+In this note, we focus on the production of two charged particles, positive and negative pions, to constrain theoretical models using a precise multidimensional analysis.
 

### 2016-10-20 chap5.tex
Changes from Lamiaa

@@
 collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
-which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small 
-amounts of data at beam energies of 4 and 4.7~GeV, Thus, we decided not to use them 
-for this analysis.}.
+which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small amounts of data at beam energies of 4 and 4.7~GeV. Thus, we decided to not use them in this analysis.}.
 
-As the two experiments, running simultaneously, aimed at comparing deuterium 
-with heavier nuclei, it was decided to use a double target system 
-\cite{Hakobyan:2008zz}. The first target was filled with liquid deuterium and 
-the second was a solid target. The latter was made of either carbon, aluminum, 
-iron, tin or lead and was changed remotely (the system is shown in figure 
-\ref{fig:phototarget}). The two targets were separated by only 4~cm in order to reduce
-the acceptance differences between them. The 
-advantage of having two targets simulataneously in the beam line
-is that several systematic effects related to the beam 
-and detector properties will cancel in the nuclear ratio.
+As the two married experiments aimed at comparing deuterium with heavy nuclei, it was decided to use a double target system~\cite{Hakobyan:2008zz}.
+The first target was filled with a liquid deuterium, and the second was a solid target.
+The latter was made of either carbon, aluminum, iron, tin or lead, and was changed remotely (see figure~\ref{fig:phototarget}).
+The two targets were separated by only 4~cm in order to minimize the difference on CLAS acceptance between them.
+The advantage of having two targets mounted simultaneously on the beam line is that several systematic effects related to the beam and detector's properties will cancel in the nuclear ratio.
 
@@
 \includegraphics[width=7cm] {chap5-fig/PhTar.jpg} 
-\caption {Picture of the target system of the {\it eg2} run. The cryogenic target is 
-in the back, wrapped with aluminum foils. The solid targets are held by mechanical arms
-that were remotely controled. In the picture, the top solid target is in the beam line.}
+\caption {Picture of the {\it eg2} target system. The cryogenic target is 
+in the back wrapped with aluminum foils, while solid targets are held by mechanical arms that were controlled remotely. In the picture, the top solid target is in the beam line.}
 \label{fig:phototarget}
@@
 transparency effects, has been approved and published~\cite{ElFassi:2008}. As this 
-analysis went through a careful review by the CLAS collaboration, we use
-similar analysis methods as much as possible. In particular, the electron selection 
+analysis went through a careful review by the CLAS collaboration, we have adapted similar analysis methods as much as possible. In particular, the electron selection 
 presented here is very similar to theirs; the main difference being a new 
-target determination method. The pion identification methods are however tightened
-in this analysis as we have less constraints on the kinematics to exclude possible
-contaminations.
+target determination method. The pion identification cuts are, however, tightened
+in this analysis as we have less constraints on the kinematics to exclude any possible pions' contamination.
 
-In the section \ref{sec:pid}, we identify the following particles e$^-$, 
-$\pi^-$ and $\pi^+$ using a series of cuts on the various 
-detector outputs. For pions, we use the signal in the drift chambers (DC) and 
-in the scintillator counters (SC), for which we require a positive status (global and DC) 
-from the reconstruction code. For electron identification, we use signals from 
-all detector parts DC, Cherenkov Counters (CC), SC and Electromagnetic 
+In the section \ref{sec:pid}, we identify the following particles, e$^-$, 
+$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs.
+For pions, we require a positive status of drift chambers (DC) and scintillator counters (SC) local signals, in addition to the global status reconstructed with the time-based tracking correction.
+For electron identification, we use good signals from
+all detectors, DC, Cherenkov Counters (CC), SC and the Electromagnetic 
 Calorimeter (EC).
 
-Once particles are identified, we can extract the observables (multiplicity 
-ratios and transverse momentum broadening). The method is presented in the 
-section \ref{sec:obs}, the corrections to these observables are presented in the 
-section \ref{sec:corrections}. The evaluation of 
-the systematic errors is presented in the section \ref{sec:TotSys}.
-Finally, the analysis' final results are presented and discussed in the next chapter.
+Once all particles are identified, we extract our two observables, multiplicity 
+ratios and the transverse momentum broadening.
+Their derivation method is presented in the section \ref{sec:obs}, while a list of our corrections is summarized in the section \ref{sec:corrections}.
+The budget of our systematical uncertainties is detailed in the section \ref{sec:TotSys}, and the final analysis results are presented and discussed in the next chapter.
 
@@
 
-First, we apply a fiducial cut on the EC to remove the electrons detected on 
-the edge of the calorimeter ($U_{EC}>40$~cm, $V_{EC}<360$~cm and 
-$W_{EC}<395$~cm in the calorimeter's coordinates). These are problematic hits 
-because the generated electromagnetic shower might be partly outside the 
-detector, leading to a wrong measurement of the energy deposited.
+First, we apply a fiducial cut on the EC local coordinates to remove electrons detected close to the calorimeter's edges ($U_{EC}>40$~cm, $V_{EC}<360$~cm and 
+$W_{EC}<395$~cm). These hits are problematic because part of the electromagnetic shower might be generated outside of the detector. That leads to a wrong measurement of the energy deposited.
 
-To reject pions, we apply cuts on the energy deposited
-in the EC using the measurements in the inner ($E_{in}$) and the 
-outer part ($E_{out})$ of the calorimeter:
+To reject pions, we apply a momentum-dependent cut of the energy deposited in the inner ($E_{in}$) and the outer parts ($E_{out})$ of the calorimeter as,
 
@@
 
-where $\mu = 0.271$ is the mean of the fraction of the energy deposited in the 
-calorimeter by electrons, the $a$ parameter is set at 0.5 and the parameter 
-$b$ is a function of momentum given in table \ref{tab:ecoutin-par}. The 
-adjustment of $b$ is motivated by the non-linear dependence of the energy 
-deposited as a function of the particle's momentum (see figure \ref{eleEC}). As pions are 
-minimum ionizing particles, they are expected to lose a constant energy in 
+where $\mu = 0.271$ is the mean of the total energy fraction deposited in the 
+calorimeter, the parameter $a$ is set to 0.5, and the parameter 
+$b$ varies with momenta, as shown in table \ref{tab:ecoutin-par}. The derivation of $b$ was motivated by the non-linear momentum dependence of the energy 
+deposited on both EC regions (see figure \ref{eleEC}). As pions are 
+minimum ionizing particles, they are expected to loose a constant energy in 
 the inner part of the calorimeter (around 30~MeV), regardless of their 
-momentum. Therefore, by requesting more than 60~MeV to be deposited, we 
+momenta. Therefore, by requesting more than 60~MeV to be deposited, we 
 efficiently cut the pion contamination (see figure~\ref{eleECi}).
@@
 \includegraphics[width=14cm] {chap5-fig/fig02.jpg} 
-\caption {Energy deposited in the inner part of the EC ($E_{in}$) as a function of the 
-energy deposited in the outer part ($E_{out}$), both divided by the momentum of the 
-particle. Each panel is for a different momentum range, the red lines 
+\caption {Energy deposited in the inner part of the EC ($E_{in}$) as a function of the energy deposited in its outer part ($E_{out}$) normalized by tracks' momenta.
+Each panel is for a different momentum range, and the drawn red lines
 illustrate the cuts from equation \ref{einout}.}
@@
 \caption {Energy deposited in the inner part of the EC as a function of the 
-energy in the outer part. The red line illustrates the cut applied for 
-electron selection.}
+energy deposited in its outer part. The red line illustrates the applied cut.}
 \label{eleECi}
@@
 In the CC, the mean number of photo-electrons\footnote{Photo-electrons are 
-electrons produced in the front window of the Photo-Multiplier Tube (PMT) by 
-single photons.} from a high energy electron is expected to be around 10.
+electrons produced in the front window of the Photo-Multiplier Tube (PMT) by a single photon.} from a high energy electron is expected to be around 10.
 However, hadrons can generate noise due to $\delta$ electrons produced in 
 the materials of the detector. This signal is expected to be around 
-one to two photo-electrons, hence to remove it we keep only tracks with more than 
-2.5~photo-electrons (figure \ref{delta}).
+one to two photo-electrons. Hence, to get rid of $\delta$-electrons, we kept only tracks with more than 2.5~photo-electrons, as depicted in figure \ref{delta}.
 
@@
 \includegraphics[width=8cm] {chap5-fig/fig04.png} 
-\caption {Number of photo-electrons ($\times 10$) per tracks, the red line 
-shows the cut to remove pion contamination.}
+\caption {Number of photo-electrons ($\times 10$) per tracks. The red line 
+shows the applied cut to remove any low-energy pions' contamination.}
 \label{delta}
@@
 
-To select electrons, we also require that the particles are negatively charged, 
-which is determined based on the bending direction of the track in the drift chamber.
+To select electrons, we also require that particles are negatively charged\footnote{In the CLAS reconstruction software, the electric charge is determined based on the tracks' bending direction in drift chambers.}.
 Positively charged particles verifying electrons' cuts are identified as 
-positrons. In the rest of the 
-analysis we use only events with a single electron and no positron to avoid any 
-confusion between the scattered electron and electrons originating from hadronic decays or 
-a photon conversion.
+positrons.
+In the rest of this analysis, we used only events with a single electron and no positron to avoid any confusion between the scattered electron and electrons originating from hadronic decays or a photon conversion.
 
@@
 
-To identify negatively charged pions, we select negative tracks, which are not 
-identified as electron. Pions are detected in the angular range from $\sim$10 to 
-$\sim$140 degrees using the DC and SC only.
+To identify negatively charged pions, we select negative tracks which didn't verify electrons' identification cuts.
+Pions are detected in the angular range from $\sim$10 to $\sim$140 degrees using only DC and SC signals.
 
-The identification consists mostly of a time of flight (TOF) test. We define 
+This identification consists mostly of a time of flight (TOF) test. We define 
 the relativistic particles' velocity difference as
-$\Delta \beta = \beta_{measured} - {p \over \sqrt{p^2 + m_\pi^2}}$ and request 
-$\Delta \beta$ to be zero within $\pm 0.03$. Figure \ref{PionTOF} illustrates 
-the effect of this cut. We notice that there is not much negative kaons or 
-anti-protons. Therefore, the contamination from these should be small (see 
-section \ref{SysId} for more detailed analysis).
+$\Delta \beta = \beta_{measured} - {p \over \sqrt{p^2 + m_\pi^2}}$, which is required to be zero within $\pm 0.03$.
+Figure \ref{PionTOF} illustrates the effect of this cut.
+As we noticed there are not much negative kaons or anti-protons, we concluded that their contamination must be small (see section~\ref{SysId} for more detailed study).
 
@@
 \includegraphics[width=8cm] {chap5-fig/fig05.png} 
-\caption {$\Delta \beta$ as a 
-function of momentum (GeV/c). Only negative particles are plotted. The red 
-lines are the cuts applied to select negative pions.}
+\caption {$\Delta \beta$ of negatively charged particles as a function of momentum (GeV/c). The red lines shows the applied cuts to select negative pions.}
 \label{PionTOF}
@@
 
-In principle, pion identification could be improved using the Cherenkov counter 
-for momentum higher than 2.5~GeV/c. But, the low efficiency observed (figure 
-\ref{PionCC}), especially at momentum close to the threshold ($\sim$25\% at 
-2.5~GeV/c and $\sim$50\% at 3~GeV/c), makes its use less compelling. 
-Moreover, as only a very small amount of $K^-$ and no $\bar p$ are present on 
-the figure \ref{PionTOF}, we decided to not use the CC for the pion identification.
+In principle, a pion identification could be improved using the Cherenkov counter 
+for momenta higher than 2.5~GeV/c. But, the observed low CC efficiency (see figure 
+\ref{PionCC}) especially at momenta close to the CC threshold ($\sim$25\% at 
+2.5~GeV/c and $\sim$50\% at 3~GeV/c) makes its use less compelling. 
+Moreover, as only a very small amount of $K^-$s and no ${\bar p}s$ are present on figure \ref{PionTOF}, we decided to not use CC on this pions' identification.
 
@@
 \includegraphics[width=8cm] {chap5-fig/fig06.png} 
-\caption {Histograms of momentum (GeV/c) for $\pi^-$. In black are all 
-identified $\pi^-$, in red pions that also fire in the Cherenkov counter and 
-in blue those that fire in the Cherenkov counter with more than 
-1 photo-electrons.}
+\caption {Histograms of momentum (GeV/c) for $\pi^-$s.
+The black, red, and blue distributions are, respectively, for all identified $\pi^-$s, pions that fire Cherenkov counters, and pions that fire CC with more than one photo-electron.}
 \label{PionCC}
@@
 The identification of positively charged pions is similar to that of negative 
-pions. However, the time of flight plot is significantly more busy (figure 
-\ref{PipTOF}), showing a significant contamination from $K^+$ and protons at 
-high momentum. As the CC is not efficient enough for hadron separation, the 
-numerous kaons and protons should be removed by a tighter TOF cut:
+pions. However, the time of flight plot is significantly more busy (see figure 
+\ref{PipTOF}), indicating a significant contamination from $K^+$s and protons at a
+higher momentum. As the CC is not efficient enough for a hadron separation, the 
+numerous kaons and protons should be removed by the following tighter TOF cuts:
 
@@
 These cuts permit to minimize the kaon contamination, below 2.5~GeV/c, and the 
-proton contamination for all momentum. The kaon contribution cannot be avoided, however 
-it should remain a small contribution ($\sim$ 3\% according to simulation) 
-with only a small effect on the final results (see section \ref{SysId} 
-for details). Because protons could lead to even more contamination than kaons, 
-a stricter cut is used at high momentum. This cut is also justified by 
-HERMES data \cite{Airapetian:2007vu}, which show a very 
-different behavior of the protons compared to the other hadrons.
+proton contamination for all momenta. The kaon contribution cannot be avoided, however, it should remain small ($\sim$ 3\% according to simulation) 
+with only a small effect on our final results (see section \ref{SysId} 
+for more details). Because protons could lead to even more contamination than kaons, 
+a stricter cut is used at a high momentum. This cut is also justified by 
+HERMES data \cite{Airapetian:2007vu}, which showed a very different behavior of protons compared to other hadrons.
 
@@
 \includegraphics[width=8cm] {chap5-fig/pip_data.png} 
-\caption {$\Delta \beta$ as a 
-function of momentum (GeV/c). Only positive particles are shown, the red 
-lines are the cuts applied to select positive pions. The blue lines indicate 
-the theoretical positions for other particles, we plotted from top to 
-bottom the lines for positrons, muons, kaons and protons.}
+\caption {$\Delta \beta$ of positively charged particles as a function of momentum (GeV/c).
+The red lines shows the applied cuts to select positive pions.
+The blue lines indicate other particles' theoretical positions, and present from top to
+bottom positrons, muons, kaons and protons.}
 \label{PipTOF}
@@
 
-To differentiate the two targets and remove the background, we need to 
-determine the origin of the particles. It appears that the different sectors 
-are shifted in $z$ (figure \ref{vertex}), because of a small misalignment of 
-the beam with the detector. To correct this problem, we apply the modification shown in table 
-\ref{tab:vertex} for the vertex determination. Those values were determined by 
-fitting the solid target position viewed by each sector.
+To differentiate between the two targets and remove the background, we need to 
+determine the origin of our final-state particles.
+As illustrated in figure~\ref{vertex}, the small misalignment of the beam with the CLAS detector led to an artificial shift on different sectors' z-vertex positions.
+To correct from this effect, we added the shift shown in table~\ref{tab:vertex} when determining each particle's vertex position.
+Those values were obtained from the fit of the solid target distribution on each sector.
 
@@
   \end{tabular}
-  \caption{Values used to correct the vertex information for all sectors}
+  \caption{Values used to correct the vertex position on each sector}
   \label{tab:vertex}
@@
 
-The position of the targets may also vary from one run to another, but 
-this does not happen too often. Indeed, except for aluminum, the targets remain in 
-the same position within one or two millimeters. The positions, in CLAS 
-coordinates, are given in table \ref{tab:targets}.
+The position of our targets could also vary from a run to another, but this did not happen too often in this experiment.
+Indeed, except for aluminum, other targets remained in the same position within one or two millimeters.
+All targets' positions, in CLAS coordinates, are given in table \ref{tab:targets}.
 
@@
   \end{tabular}
-  \caption{Measured mean vertex position of targets, relative to the center of 
-           CLAS (in cm). We note that aluminum data are separated in two sets because the 
-           target position has brutally changed, moreover
-           during these runs the deuterium target was empty.}
+  \caption{The measured mean vertex position of our nuclear targets relative to the center of CLAS (in cm).
+Must note that aluminum data are separated in two sets because this target's position has brutally changed.
+Moreover, during these runs the deuterium target was empty.}
   \label{tab:targets}
@@
 \includegraphics[width=10cm] {chap5-fig/Vertex_el_data.png}
-\caption {In each sector, the reconstructed vertex of electrons along the beam
-direction relatively to the center of CLAS. The red lines show the cuts 
-to select the targets.}
+\caption {Sector-by-sector electrons' vertex distributions.
+The latter are reconstructed along the beam direction and relative to the center of CLAS located at 0~cm.
+The red lines show the applied cuts to select the two targets.}
 \label{vertex}
@@
 The detected electrons are associated with the solid target if their vertex 
-position is less than 1.5~cm ($\sim$3~$\sigma$) from the value of table 
-\ref{tab:targets}. For the liquid target, the cut is larger, 2 cm, in order to 
-account for the size of the target (see figure \ref{vertex}). The vertex of 
-the pions is checked against the electron one and we request that 
-$| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).
+position is less than 1.5~cm ($\sim$3~$\sigma$) from the values shown on table 
+\ref{tab:targets}.
+For the liquid target, the cut is a bit larger, 2 cm, in order to count for the cryogenic target's size (see figure \ref{vertex}).
+The pions' vertex was checked against the electron one and was imposed to satisfy this additional condition $| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).
 
@@
 \includegraphics[width=8cm] {chap5-fig/Vertex_pi_data.png}
-\caption {Distance along the beam axis between the electrons and pions 
-vertexes. $\pi^+$ are plotted in the top panel and the $\pi^-$ in the bottom.
-The red lines show the cuts applied to select pions.}
+\caption {The difference between electrons and pions z-vertex positions.
+$\pi^+$s and $\pi^-$ are plotted, respectively, in the top and bottom panels.
+The red lines show the applied cuts to select both pions.}
 \label{fig:dvzpi}
@@
 
-To check the quality of the runs\footnote{Runs correspond roughly to two hours
-of data, they can be smaller in case of problems.}, we looked at the ratio of the number of 
-scattered electrons, between the liquid and solid targets. If the beam is 
-hitting other materials than the targets or if the detector is not working 
-properly this ratio can be off and indicates a problematic run. The figure 
-\ref{DataQ} shows the values obtained; we fit the 
-mean value for all runs of each target and eliminate runs away by more than 
-5$\sigma$. We note that the ratios are coherent with target thicknesses given 
-in \cite{Hakobyan:2008zz} except for carbon. Because of this, the density of 
-the carbon target was remeasured recently and found to be coherent with the 
-data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.
+To check the quality of the runs\footnote{Runs were formed roughly from two hours
+of data, but they were much smaller in case of problems.}, we monitored the ratio of scattered electrons yields obtained from solid and liquid targets.
+In case of the beam hitting other materials in the beam-line or any detector is not working
+properly, this ratio will be off and indicates problematic runs. A figure 
+\ref{DataQ} shows electrons yields' ratios for different nuclear target; we fitted these ratios to extract the mean value for each target, then we discarded runs that were 5~$\sigma$ away from the appropriate mean.
+Must note that these ratios were consistent with our target's thicknesses given in \cite{Hakobyan:2008zz} except for a carbon target.
+For that reason, the density of the latter was recently remeasured, and its new value was finally matching our data\footnote{i.e.
+(1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.
 
@@
 \includegraphics[width=15cm] {chap5-fig/TargetElRatio.png}
-\caption {Ratio of the number of electrons scattered by the targets (solid over deuterium) 
-for each run.}
+\caption {Ratio of scattered electrons yields (solid over deuterium) for each run.}
 \label{DataQ}
@@
 Since we are interested in deep inelastic scattering, we use the following 
-cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV. We also apply a cut on the 
-fraction of energy transferred $y = \nu/E_{beam} < 0.85$.
-This corresponds to removing the low energy electrons because they are
-significantly affected by radiative effects and sat the limit of our trigger 
-threshold.
+cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV.
+We also apply a cut on the energy transferred fraction, $y = \nu/E_{beam} < 0.85$.
+This cut aims to remove the low energy electrons that are significantly affected by radiative effects and sat at the limit of our trigger threshold.
 
@@
 
-Once the identification is done, the calculation of the observables is 
-straight forward with statistical errors given by:
+Once the identification is done, the calculation of our two observables and their statistical uncertainties is straightforward. The latter are given by:
 \begin{equation}
@@
 
-However, the implementation of acceptance and radiative corrections is done through weights
-given to each events depending on their kinematics. The multiplicity ratio then becomes
+However, the implementation of acceptance and radiative corrections is done through some given weights to each event based on its kinematics. The multiplicity ratio then becomes
 \begin{equation}
@@
 \end{equation}
-with $\omega$ the weight associated with the event and the sums running over all measured 
-particles. The expression for the transverse momentum broadening remains
+where $\omega$ is the weight associated with the event, and the sums run over all measured particles. The expression of the transverse momentum broadening remains as
 \begin{equation}
@@
 
-Thus, new expressions are also needed for the statistical error uncertainties: 
+Thus, new expressions of the weighted statistical uncertainties are: 
 \begin{equation}
@@
 
-To provide a first idea on data quality, we present in figure~\ref{fig:prelim} 
-few preliminary results, before the application 
-of any corrections. These preliminary results will also be used to 
-illustrate the effects of the corrections discussed below.
+To provide some insight into the quality of our data, we present in figure~\ref{fig:prelim} few preliminary results before the application of any corrections.
+These preliminary results will be used also to illustrate the effects of the corrections discussed below.
 
@@
 \includegraphics[width=7.4cm] {chap5-fig/a_PvNu.png} 
-\caption {Results for multiplicity ratios (top) and transverse momentum 
-broadening (bottom) without correction.}
+\caption {Results for multiplicity ratios (top) and the transverse momentum 
+broadening (bottom) before applying any corrections.}
 \label{fig:prelim}
@@
 The acceptance correction consists of applying weights to the experimental data
-events by events to correct for detection inefficiencies of the detectors.
-Incidentally, it also corrects for small other issues of detection,
-such as misidentification and scattering on detectors materials. The quality 
+event by event to correct for any detection inefficiencies of used detectors.
+Incidentally, it also corrects for other small detection issues, such as misidentification and re-scattering on detectors' materials. The quality 
 of the correction depends on the ability of the simulation to reproduce the 
-experiment, the statistics accumulated and the size of interfering effects, such 
-as bin migration. For this correction, we applied the method from the 
+experiment, the accumulated statistics, and the size of interfering effects, such 
+as the bin migration. For this correction, we applied the method from the 
 approved and published analysis from the same eg2 data~\cite{ElFassi:2008}.
@@
 
-To correct for acceptance effects, we simulated a total of a 100 million events 
+To correct for acceptance effects, we simulated a total of 100 million events 
 per target ($^2$H, C, Fe and Pb) using the PYTHIA \cite{Sjostrand:2006za} 
-event generator slightly modified to include Fermi motion effects. The 
-generated events are processed by the CLAS software (GSIM, GPP and user\_ana) 
-to simulate the detector and the reconstruction process similarly to the one for 
-experimental data.
+event generator that was slightly modified to include Fermi motion effects. The 
+generated events are processed by CLAS softwares (GSIM, GPP and user\_ana) 
+to simulate the detector and the reconstruction process similarly to the experimental data.
 % TODO GPP factors
@@
 affect us and have to be understood. First, the efficiency of the CC is 
-overestimated in the simulation. 
-On the electron side the signal is a little stronger in the simulation (11 
+overestimated in the simulation. On the electron side the signal is a little stronger in the simulation (11 
 photo-electrons) compared to experimental data (8 photo-electrons), but this 
@@
 distribution in both cases.
-Second, since the simulation has a perfect alignment of the beam with CLAS the 
-vertex cuts do not need to be shifted from one sector to another. Therefore, 
-we do not apply the shift from the table \ref{tab:vertex} to the simulation; 
-the resulting cuts are shown in figure~\ref{simvertex}.
+Second, since in the simulation the beam is perfectly aligned with CLAS, the vertex cuts do not need to be shifted from one sector to an other.
+Therefore, we do not apply the shift from table \ref{tab:vertex} to the simulated data; the resulting cuts are shown in figure~\ref{simvertex}.
 
@@
 \includegraphics[width=9cm] {chap5-fig/Vertex_el_sim.png}
-\caption {Reconstructed vertex position, along the beam direction, with values 
-relative to CLAS center, for electrons from {\bf simulated data} and each 
-sector. The red lines show the cuts used to select the targets.}
+\caption {Sector by sector electrons' vertex distributions from the {\bf simulated data}.
+The latter are reconstructed along the beam direction, and relative to the CLAS center.
+The red lines show the used cuts to select both targets.}
 \label{simvertex}
@@
 
-The kinematic distributions from the simulation are compared to the 
+The kinematical distributions from the simulation are compared to the 
 experimental ones. This is important for the acceptance correction, to see 
-whether or not, we can integrate over these variables in this correction.
+whether or not, we can integrate over any variables in this correction.
 Comparisons between simulated and experimental data are shown in figures 
@@
 
-The acceptance is defined as the ratio of reconstructed events over generated ones,
+The acceptance correction coefficients are defined as the ratio of reconstructed and generated events,
 
@@
 
-The experimental data are corrected using weights defined as $\omega = 1/\text{Acc}$. The 
-$\omega$ coefficient are calculated in many bins, in order to be independent of 
-the imperfections of the event generator. However, an excess of bin could results into a strong 
-bin migration\footnote{Fraction of events not reconstructed in the bin they 
-were produced in.}, which might introduce a bias if it becomes a large effect.
+Experimental data were corrected using the weights defined as $\omega = 1/\text{Acc}$.
+These coefficients are calculated in many bins, in order to be independent of the imperfections of our event generator.
+However, an excess of bins could lead to a strong bin migration\footnote{Fraction of events not reconstructed in the bin they were produced in.}, which might introduce a bias in case it becomes quite large.
 
-We used a 4-dimensional binning to divide the large phase space available to 
-our two particle final state. To evaluate the systematic error 
-associated to this correction, we uses the two different binning
-presented in table~\ref{tab:AcceptBinning}. The total number of bins is 
-constrained by the amount of data generated and must be maintained 
-reasonably low in order to keep a good statistical precision and manageable 
-bin migration.
+We used a 4-dimensional binning to divide the large phase space of our two particles' final state.
+However, to evaluate the associated systematic errors with this correction, we used the two different binning presented in table~\ref{tab:AcceptBinning}.
+The total number of bins is constrained by the amount of generated data, and must be maintained reasonably low in order to keep a good statistical precision and a manageable bin migration.
 
@@
   \end{tabular}
-  \caption{Variables and their associated number of bins used for the 
-   multi-dimensional binning of the acceptance correction. The left panel 
-   shows the variables used for the correction and the right panel the 
-   variables used for the evaluation of the systematic error.}
+  \caption{Variables and their associated number of bins used on the 
+   multi-dimensional binning of our acceptance correction. The left panel 
+   shows the variables used on this correction, and the right panel contains the 
+   variables used on the evaluation of the related systematic uncertainties.}
   \label{tab:AcceptBinning}
@@
 The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
-the simulation using equation \ref{eq:acc}, however, it appears that these should not be used directly.
-Three factors are sources of problematic bins:
+the simulation using equation \ref{eq:acc}. However, it turned out that these coefficients should not be applied to data before resolving the issue of the problematic bins that have either
 \begin{itemize}
- \item too large weight values, i.e. very small acceptance;
- \item very few events reconstructed, leading to large statistical errors;
- \item large fraction of events originally generated in an other bin (bin migration).
+ \item too large weight values, i.e., very small acceptance, or
+ \item very few reconstructed events leading to large statistical errors, or
+ \item a large fraction of events originally generated in an other bin (bin migration issue).
 \end{itemize}
-To remove these bins we apply the following cuts:
+To eliminate these bins we apply the following cuts:
 \begin{equation} \label{eq:AccL1}
@@
 \end{equation}
-$\delta \omega / \omega$ is the relative error on the weight and $R_c$ the 
-proportion of reconstructed events initially generated in another bin. Figure 
-\ref{fig:AccCoef} shows the distributions of $\omega$, after the cuts. Around 
-900 bins remain for both targets, but we notice that weights are much larger 
-for $\pi^-$, indicating a larger correction, compared to $\pi^+$. In order to 
-maximize the acceptance and reduce the sensitivity to the cuts applied on the 
-weights, which are arbitrary, the bin weights are corrected. We apply a 
-reweighting by calculating a new acceptance in a two dimensional binning:
+where $\delta \omega / \omega$ is the relative error on the weight, and $R_c$ is the 
+proportion of reconstructed events initially generated in an other kinematical bin.
+Figure \ref{fig:AccCoef} shows $\omega$ distributions after applying these cuts.
+Around 900 bins remain for both targets, but we noticed that these weights are much larger for $\pi^-$ compared to $\pi^+$, as an indication of a larger correction for the inbent particles.
+In order to maximize the acceptance and reduce the sensitivity to our arbitrary weights' cuts, we corrected the data with an additional two dimensional reweighting factor as:
 \begin{equation}
@@
 \end{equation}
-$\omega$ is the previously calculated weights or $1$ when the 
-bin was excluded by the cuts.
-One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
-\ref{eq:AccL2} is to keep reweighting factors $\omega_2 = 1/\text{Acc}_2$ at a few 
-percents level.
+where $\omega$ is the previously calculated weight of either one remaining bin or a bin that was excluded by the cuts. One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
+\ref{eq:AccL2} is to keep reweighting factors, $\omega_2 = 1/\text{Acc}_2$, at the level of a few percents.
 
@@
 \includegraphics[width=14cm] {chap5-fig/pawpipdeut.png}
-\caption {Acceptance weights for pions in deuterium (not reweighted).}
+\caption {The extracted acceptance correction weights for pions on a deuterium target (not re-weighted).}
 \label{fig:AccCoef}
@@
 
-The electron acceptance, which is necessary in order to correct the number of electrons 
-in the multiplicity ratios, is done following the same method as in the 
-semi-inclusive case, but only using the two first dimensions ($\nu$ 
-and $Q^2$). However, reweighting is not used 
-for electrons as all non-empty bins pass the cuts \ref{eq:AccL1} and 
-\ref{eq:AccL2}.
+In order to correct the number of electrons in multiplicity ratios, we followed the semi-inclusive acceptance correction method by using only the two first dimensions ($\nu$ and $Q^2$).
+However, the reweighting was not used for electrons as all non-empty bins pass the two cuts, \ref{eq:AccL1} and \ref{eq:AccL2}.
 
@@
 \includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
-\caption {Preliminary results are compared with acceptance corrected ones, 
+\caption {Preliminary results are compared with the acceptance corrected ones, 
 for multiplicity ratios (top) and transverse momentum broadening 
@@
 represented, shows the new results after applying the acceptance correction.
-The acceptance correction effects appear to be of the order of $10$\% for 
-multiplicity ratios and 
-$30$\% for transverse momentum broadening. This is a surprisingly 
-significant correction in regard to the few centimeters between the two targets. 
-The reason for such a large correction is that the small shift in $z$ position changes 
-slightly the minimum angle of the detector in the region where most hadron production 
-is concentrated, {\it i.e.} at low \pt close to the beam line. The 
-$\pi^-$s appears to be more affected, which is due to the inbending magnetic 
-field. Indeed, the low \pt $\pi^-$s have very low acceptance, leading to large 
-correction factors. The large spread in weights makes the errors 
-on \dpt very large and the related results difficult to exploit. 
-Looking at the results themselves after the correction, we notice that now 
-the transverse momentum broadening of both pions match, which is consistent 
+The acceptance correction effects appear to be in the order of $10$\% for 
+multiplicity ratios and $30$\% for the transverse momentum broadening.
+This is a surprisingly significant correction with regard to a few centimeters separating the two targets.
+The reason for such a large correction is that the small shift in the $z$-vertex position changes slightly the minimum angle of the detector in the region where most hadron production is concentrated, {\it i.e.} at low \pt close to the beam line.
+The $\pi^-$s were more affected due to the inbending magnetic field.
+Indeed, the low \pt $\pi^-$s had very low acceptance which led to large correction factors.
+The large spread in weights makes the errors on \dpt very large, and the related results difficult to exploit.
+However, our transverse momentum broadening results of both pions matched each other after this correction, which is consistent
 with HERMES results.
@@
 
-The large charge of the nuclear targets create an electric field that should 
-be accounted for at our energies. This nuclear electric field accelerate or 
-decelerate the incoming and outgoing charged particles, it also has non 
-trivial effects such as focussing effects at lower energies. Aste {\it et 
-al.}~\cite{Aste:2005wc} have shown that an effective momentum approximation is 
-reliable for larger momentums ($Q^2>.5$ GeV$^2$). Being clearly beyond this 
-limit and the Coulomb correction being relatively small in our kinematic, we 
-decide to use such an approximation. Following the prescription from Aste 
-{\it et al.} we use an effective potential $\bar V= 0.8 V_0$, that they found 
-best suited when using such approximation. $V_0$ being the electrostatic 
-potential in the center of the nuclei, {\it i.e.}: $V_0= -3 \alpha_{EM} Z / 
-(2 R)$. Values for $V_0$ and $\bar V$ used in this analysis are given in 
-table~\ref{tab:Coulomb}. Coulomb corrections are applied on electrons, and
-both charged pions before to calculate the kinematic variables.
+The large electric charge of our nuclear targets create an electric field that should be taken into account at our energies.
+Besides the fact that the nuclear electric field accelerates or decelerates the incoming and outgoing charged particles, it has some non trivial effects such as the focusing of low energy particles.
+Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb effects could be corrected for by using an effective momentum approximation at large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$).
+As our kinematics coverage is beyond this limit, we decided to use this approximation on the coulomb correction of our data-sets.
+According to Aste {\it et al.}, the best effective potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the electrostatic potential at the center of nuclei.
+The latter is evaluated as $V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure constant, Z is the proton number, and R is the radius of nuclei.
+Table 5 contains the used values of $V_0$ and $\bar V$ on different nuclear target's analysis.
+We must note that this Coulomb correction has been applied to both electrons and charged pions before calculating any kinematical variables.
 
@@
   \end{tabular}
-  \caption{Values for $V_0$ and $\bar V$ used for Coulomb correction of charged particles.}
+  \caption{The $V_0$ and $\bar V$ values used on Coulomb corrections for different charged particles.}
   \label{tab:Coulomb}
@@
 
-Despite its lower magnitude, compared to the strong force, the 
-electromagnetic force might have a non negligible impact on our results. The 
-reason is that even a moderate energy photon 
-emission can modify significantly the measured kinematic variables.
-To correct this effect, several simulation codes exist \cite{Akushevich:2001yp}, 
-however, none permit to treat directly semi-inclusive DIS on nuclei. In order 
-to make the correction, a dedicated Monte-Carlo simulation, based on existing 
-codes, was developed.
+Despite its lower magnitude compared to the strong force, the 
+electromagnetic force may have a non negligible impact on our results. The 
+reason is that even a moderate energy photon emission can modify significantly the measured kinematical variables.
+To correct this effect, several simulation codes exist \cite{Akushevich:2001yp}, however, none of them treat directly the SIDIS production on nuclei.
+For that reason, a dedicated Monte-Carlo simulation based on existing codes was developed.
 
@@
 
-The inclusive radiative effects are generated using the RADGEN software 
-\cite{Akushevich:1998ft}, which includes the Feynman diagrams shown in 
-figure~\ref{fig:FDRadCorr}. This code evaluates directly the correction 
-factors ($\delta = \sigma_{obs} / \sigma_{Born}$) to apply for inclusive 
-measurements. As RADGEN is also a Monte-Carlo generator of photon emissions, 
-it can be used to modify the virtual photon kinematic before the 
-hadron production in any DIS generator. This allows to evaluate the radiative 
-effects on semi-inclusive measurements by implementing RADGEN inside a full 
+The inclusive radiative effects are generated using the RADGEN code 
+\cite{Akushevich:1998ft}, which includes Feynman diagrams shown in 
+figure~\ref{fig:FDRadCorr}. Using this code one can evaluate the correction 
+factors for inclusive measurements as $\delta = \sigma_{obs} / \sigma_{Born}$, where $\sigma_{obs}$ is the measured inclusive cross section, and $\sigma_{Born}$ is the Born cross section.
+As RADGEN is also a Monte-Carlo generator for photon emissions, it could be used to modify the virtual photon kinematics before the
+hadron production in any DIS generator. This allows the evaluation of the radiative 
+effects on semi-inclusive measurements by implementing RADGEN inside the main 
 Monte-Carlo event generator.
 
-\begin{figure}[htbp]
+\begin{figure}[htp]
 \centering
@@
 
-The Monte-Carlo simulation we use is the GENIE software 
-\cite{Andreopoulos:2009rq}, which describes well electron-nuclei scattering. 
-Indeed, GENIE includes quasi-elastic scattering\footnote{Elastic 
-scattering on a single nucleon of a nuclei.}, which is the main channel contributing 
-to the radiative events in the DIS region \cite{Akushevich:2007jc}. The GENIE 
-software includes also hadron cascades in the nuclei, which lead to the 
-possibility to generate pions in quasi-elastic events. This is an important 
-feature because the quasi-elastic cannot contribute directly to semi-inclusive 
-measurements.
+The Monte-Carlo simulation was done using the event generator, GENIE~\cite{Andreopoulos:2009rq}, that describes well electron-nucleus interactions.
+Indeed, GENIE contains the quasi-elastic scattering\footnote{Elastic
+scattering off a single nucleon on nuclei.}, which is considered as the main channel generating radiative events in the DIS region \cite{Akushevich:2007jc}.
+This generator includes also hadronic cascades in nuclei, at which pions might be generated in quasi-elastic events.
+This is an important feature because the quasi-elastic production can not contribute directly to semi-inclusive measurements.
 
@@
 
-We generate 100 million events per target, with and without radiative effects.
-The RADGEN software gives direct indication for the inclusive correction and 
-the comparison between the two data sets allows to extract factors for 
-semi-inclusive correction.
+We generated 100 million events with and without radiative effects for each target.
+The RADGEN code gave us the magnitude of inclusive correction coefficients, however, the comparison between the two data sets allows the extraction of semi-inclusive correction factors.
 
-The correction factors for inclusive ratio (figure \ref{fig:RadCorrFac}) are 
-relatively small (couple of percents maximum) except at low \xb and high $\nu$. Semi-inclusive factors are 
-shown in figure \ref{fig:RadCorrFacSIDIS} as a function of $z$ and \ptp. However 
-the statistical error on these is large, the problem being that only a small 
-fraction of the events involved photon radiation.
+The ratio of inclusive correction factors, as depicted in figure \ref{fig:RadCorrFac}, is relatively small (couple of percents at most) except for low \xb and high $\nu$.
+Similarly for the semi-inclusive factors' ratio shown in figure \ref{fig:RadCorrFacSIDIS} as a function of $z$ and \ptp.
+However, the associated statistical errors are quite large because only a small fraction of the events involved a photon radiation.
 
@@
 \includegraphics[width=9cm] {chap5-fig/ElecRadWei_Lead.png}
-\caption {Ratios of the radiative correction factors $\delta_\text{Pb}/
-\delta_{^2\text{H}}$ as a function of \xb in various $\nu$ bins.}
+\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
+\delta_{^2\text{H}}$, as a function of \xb in various $\nu$ bins.}
 \label{fig:RadCorrFac}
@@
 \includegraphics[width=9cm] {chap5-fig/RadGenFactors.png}
-\caption {Ratios of the radiative correction factors $\delta_\text{Pb}/
-\delta_{^2\text{H}}$ as a function of $z$ and \ptp.}
+\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
+\delta_{^2\text{H}}$, as a function of $z$ (top) and \ptp (bottom).}
 \label{fig:RadCorrFacSIDIS}
@@
 
-The semi-inclusive part of the radiative correction appears to be limited 
-in amplitude in most of the 
-kinematic, except for high $z$ and \ptp. So, we decided not to apply this 
-correction before further studies.
+The semi-inclusive part of the radiative correction turned out to be limited 
+in amplitude for the most kinematics, except for high $z$ and \ptp. Thus, we decided to not apply this correction before further studies.
 
 {\color{red} We found a better way to implement the radiative correction,
-that is not limited by the Monte-Carlo technique. We will implement it in
-the second version of the note as we do not want to delay the review process for
-this correction that we already found to be small. Sorry about that.}
+that is not limited by the used MC technique. We will implement it in
+the second version of the note as we do not want to delay the review process because this correction that we already found to be small. Sorry about that.}
 
@@
 
-The important excess of neutrons in heavy nuclei leads to a modification of the 
-$\pi$ multiplicity per DIS events. Using Hall~C results 
-\cite{Asaturyan:2011mq}, shown in figure \ref{fig:IsoSpin}, we evaluate 
-correction factors for this effect. Our simple estimation is solely based on 
-proton and neutron numbers; the results for $\pi^+$s are shown in 
-table~\ref{tab:isospin}. The effect on $\pi^-$ is found to be coherent with zero,
-therefore no correction is applied for them. 
-We attribute errors of 10\% of the effect for the isospin correction, this is chosen 
-relatively to the precision of the Hall~C measurement and the fact that they do not 
-cover as much phase space as we do.
+The important excess of neutrons in heavy nuclei leads to a modification of both $\pi$ multiplicities on DIS events. Using Hall~C results 
+\cite{Asaturyan:2011mq}, shown in figure \ref{fig:IsoSpin}, we evaluated the correction factors for this effect. Our simple estimation is solely based on 
+proton and neutron numbers that gave $\pi^+$s results shown in table~\ref{tab:isospin}.
+As the effect on $\pi^-$s was found to be consistent with zero, no correction was applied to their multiplicity ratios.
+We attribute a 10\% normalization error to the effect of the isospin correction on our results.
+It is relatively chosen based on the precision of the Hall~C measurement, and the limited phase space coverage of Hall-C data compared to ours.
 
@@
 \includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
-\caption {Ratios of deuteron over proton for $\pi^+$s and $\pi^-$s 
+\caption {Ratios of deuteron over proton for $\pi^+$s (top) and $\pi^-$s (bottom)
 as a function of \xb at $z=0.55$ \cite{Asaturyan:2011mq}.}
@@
   \end{tabular}
-  \caption{Isospin correction applied to the $\pi^+$ multiplicity ratios for different targets.}
+  \caption{Isospin correction applied to $\pi^+$ multiplicity ratios for different targets.}
   \label{tab:isospin}
@@
 
-It is important to note that we correct isospin effects only for rates, thus 
-we correct only the multiplicity ratios. Transverse momentum broadening could, in 
-principle, also be affected, however, the results from \cite{Asaturyan:2011mq} 
-show no isospin effect in \ptp. This gives good confidence that \dpt is not 
-affected by isospin effects.
+It is important to mention that the isospin correction is applied only to rates, which means applied only to $\pi^+$s multiplicity ratios.
+The transverse momentum broadening could, in principle, be affected, however, the results from \cite{Asaturyan:2011mq} showed no isospin effects in \ptp.
+Therefore, we are confident that our \dpt results should not be sensitive to any isospin effects.
 
-We finally note that the $A$ dependencies of the multiplicity ratios of the 
-charged pions are parallel after the isospin correction\footnote{Within 
-normalization errors presented in section \ref{sec:TotSys}} (figure 
+We finally note that the $A$ dependence of multiplicity ratios of both charged pions became parallel after the isospin correction\footnote{Within 
+normalization errors presented in section \ref{sec:TotSys}} (see figure 
 \ref{fig:IsoPlot}). Considering previous measurements and existing models, 
-this result was expected and confirm the need for this correction to be applied.
+this result was expected and demonstrated the importance of this correction.
 
@@
 \caption {Multiplicity ratios as a function of $A^{1/3}$ 
-with only isospin correction applied.}
+with only the isospin correction applied.}
 \label{fig:IsoPlot}
@@
 
-In this section are summarized the systematic errors that we identified. The 
-systematic point to point errors are calculated bin by bin for each results.
-They are caused by uncertainties on the acceptance and on the identification of 
-particles. The normalization errors are attributed globally. They are due to 
-acceptance effects, target misidentifications and isospin correction.
+In this section, we are presenting details of our two types of systematic uncertainties.
+The point-to-point systematic errors, that vary with kinematical variables, were calculated bin by bin for each result.
+They are caused by uncertainties on the particles' identification cuts and the CLAS acceptance.
+The normalization errors are attributed globally since they don't depend on kinematics.
+They are due to acceptance effects, target's misidentification, and the isospin correction.
 
@@
 
-The simulation of the CLAS detector, using GSIM package, is used 
-to evaluate the systematic errors linked with:
+The simulation of the CLAS detector, using the GSIM package, is used 
+to evaluate the systematic errors correlated with:
 
-  - experimental resolution of kinematic variables,
+  - experimental resolution of kinematical variables,
 
-  - particle misidentification,
+  - particles' misidentification,
 
-  - particle re-scattering in the detector,
+  - particles' re-scattering in different detectors,
 
-  - particle energy loss.\\
+  - particles' energy loss.\\
 
-To evaluate those errors, we compare the reconstructed particles with the 
-generated ones. Each reconstructed particle is associated with its generated parent using the
-similarity in momentum and angle.
-Distributions of $\Delta p$, $\Delta \theta$ and $\Delta \phi$ are defined as 
-$\Delta x = {\sum_n |x_{gen} - x_{rec}| \over n}$. They give the precision with which we measure 
-these variables. Using the same simulation than for the acceptance, we find 
-${\delta p \over p } = 0.03$, $\delta \theta = 3$ mrad and 
-$\delta \phi = 10$~mrad. These are broader than announced in \cite{Mecking:2003zu} 
-but still reasonable. Then associated systematic errors can be easily 
-evaluated for other variables: $\delta Q^2 \sim 0.013$ GeV$^2$/c$^2$, $\delta z \sim 
-0.4 \%$, $\delta P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$ and so on\footnote{These were 
-evaluated for typical kinematics, the results can be larger at 
-extreme kinematics (large \pt or Q$^2$).}. These are negligible because they are 
-several times smaller than our usual bin sizes (see figures in section 
-\ref{prelim}).
+To evaluate those errors, we are comparing the kinematics of reconstructed particles with the generated ones.
+Each reconstructed particle is associated with its generated parent if both particles have a similar momentum and angle coverage.
+However, the precision of the measured kinematical distribution $\Delta p$, $\Delta \theta$ and $\Delta \phi$ were determined as $\Delta x = {\sum_n |x_{gen} - x_{rec}| \over n}$, where $n$ is the kinematical bin number.
+Using the same simulation as for the acceptance, we found ${\delta p \over p } = 0.03$, $\delta \theta = 3$ mrad and $\delta \phi = 10$~mrad.
+Nevertheless of being much larger than the nominal CLAS resolutions published in \cite{Mecking:2003zu}, they are still reasonable for our measurement.
+Although, we evaluated the systematic errors associated with other variables\footnote{These values were evaluated for a typical kinematics range.
+However, the results can be much larger at extreme kinematics (large \pt or Q$^2$).}, such as $\delta Q^2 \sim 0.013$ GeV$^2$/c$^2$, $\delta z \sim 0.4 \%$, and $\delta P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$.
+These errors are overall negligible since they are several times smaller than our usual bin sizes (see figures in a section \ref{prelim}).
 
-We also evaluate particle misidentification and particles originating from 
-scattering in the detector or the coils. Only tails of distributions can lead to high 
-contamination by misidentification, the most problematic being the tail of the 
-\pt distribution. This effect is due to the low probability to produce high 
-\pt events, therefore the contribution from accidental is relatively 
-increased. We use the following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which 
-only removes a very little amount of data ($\sim 1$ $\pi$ in 30000). The 
-misidentification of electrons is found to be of the order of 1 in a 1000 and 
-does not contribute significantly to the uncertainty. For pions, the main 
-contamination comes from kaons above 2~GeV/c ($\sim$3\% of $\pi^+$ and 
-$\sim$0.5\% of $\pi^-$). Protons also contaminates $\pi^+$ at 
-high momentum (up to few \%). 
+We also evaluated the particles' misidentification and the re-scattering effect in different detectors or coils. The misidentification usually leads to a high 
+contamination on the kinematical distributions tails, which is manifested most in our case on the tail of the \pt distribution.
+This effect is due to a low probability to produce high \pt events, therefore the contribution from the accidental background is relatively increased.
+As a consequence, we used the following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which basically discarded only a very little amount of data (about one $\pi$ from 30000 pions).
+The misidentification of electrons was found to be too small in the order of $1\,e^-$ each 1000 events, hence does not contribute significantly to this uncertainty.
+For pions, the main contamination comes from kaons with momenta above 2~GeV/c ($\sim$ 3\% for $\pi^+$s and $\sim$ 0.5\% for $\pi^-$s).
+Protons also contaminates a $\pi^+$ sample at high momenta (up to a few \%).
 %TODO Justify the pt cut with a figure?
 
-In conclusion, the uncertainty related to misidentification 
-is taken into account at the level of 100\% of the contamination in the point 
-to point systematic errors, other effects are found to be negligible.
+In conclusion, the uncertainty related to particles' misidentification is taken into account in the point-to-point systematic errors by assuming a 100\% contamination level.
+Other effects were found negligible.
 
@@
 
-Because of reconstruction errors or scattering on the detector materials, it 
+Because of some reconstruction errors or a re-scattering on detectors' materials, it 
 is possible to associate a particle with the wrong target. To estimate this 
-effect, we look, in the experimental data, at the number of events 
-reconstructed upstream and downstream of the targets, where nothing should be
-detected. We define two test regions (see figure \ref{fig:targetleak}) to evaluate
-the contamination. The region 1 is upstream and chosen to be of the same size as the window used for solid 
-target selection. We use it to evaluate contamination from the liquid target to the solid one. The region 2
-is downstream and of the size of the window for the liquid target selection 
-and allows to evaluate the solid target leak into the liquid one.
+effect, we looked, in the experimental data, at the number of reconstructed events upstream and downstream our targets, where nothing should be detected.
+Thus, we defined two test regions (see figure \ref{fig:targetleak}) to evaluate a targets' contamination.
+The upstream region, named as a test region 1, was given the size of the solid target's selection cut to evaluate the contamination from the liquid target.
+However, the downstream region, named as a test region 2, covered the same size of the liquid target's selection cut to estimate the leak from the solid target.
 The distance between detection and test regions is identical to the
-distance between the two detection regions.
+distance between the two targets' detection regions.
 
-We find
-that the number of electrons in the test regions 1 and 2 represent 1 and 2\%, 
-respectively, of the total number of events. In the case of semi-inclusive measurement, where we request
-2 particles in the final state, the number drops drastically and is of the order of
-0.01\%. In conclusion, only the number of electron is significantly affected by this problem
-leading to a normalization error of 1\% for all multiplicity ratios.
+We found that the number of electrons in the test region 1 and 2 represents, 
+respectively, 1 and 2\% of the total number of events.
+However, in the case of semi-inclusive measurements, where we request two particles in the final state, this number drastically dropped, and became in the order of 0.01\%.
+In conclusion, only the number of electrons is significantly affected by a target's contamination issue, which leads to a normalization error of 1\% in all multiplicity ratios.
 
@@
 \includegraphics[width=9cm] {chap5-fig/Vertex.png}
-\caption {Distribution of the vertex positions along z (cm), i.e. along the 
+\caption {Vertex distribution along a z direction (in cm), i.e. along the 
 beam line. In red are shown the cuts used to evaluate the leak from one target to 
@@
 
-We tested several different acceptance corrections to the data using finally 
-two different binnings 
-(table \ref{tab:AcceptBinning}). The differences between them give us a good 
-indication on the systematic error associated with the method. Using our
-results on iron, we find the systematic presented in the table 
-\ref{tab:SysAcc}. We note the significantly larger errors for $\pi^-$, which 
-was expected because of the smaller acceptance and the larger weights. More 
-significant are the large errors on the \dpt measurements, this is mainly due to 
-the nature of the observable; as a difference \dpt enhances relative errors 
-significantly. As was seen in figure~\ref{fig:AcceptPlots}, error bars are much 
-larger for corrected \dpt indicating an important statistical 
-sensitivity introduced by the weighting. The errors on \dpt are of the same 
-order, or smaller, as the differences observed between the two sets. This is 
-an indication that the uncertainties reported in table \ref{tab:SysAcc} are 
-similar in nature with the statistical error, in the sense that they originate
-from the large variation between the weights from event to event. For this
-reason, we decide not to include this error in order to double count it.
+After testing several different acceptance correction methods, we finally converged with the one using the two different binning presented on a table \ref{tab:AcceptBinning}.
+The difference between these methods gave us an idea about the systematic error associated with this correction.
+Using our results on iron, we found the relative uncertainties presented in a table~\ref{tab:SysAcc}.
+We noticed the significantly large errors for $\pi^-$s, which were expected, due to their low acceptance and larger weights.
+Although, systematical errors are considerably large on \dpt measurements.
+This is mainly due to the nature of the \dpt observable; as a difference, it would indeed enhance relative errors significantly.
+As it was shown in figure~\ref{fig:AcceptPlots}, error bars became much larger for the corrected \dpt from the acceptance effect.
+This fact indicated an important statistical sensitivity introduced by our weighting methods.
+The errors on \dpt are of the same order, or smaller, than the differences observed between the two weighted data-sets.
+This is an indication that the uncertainties reported in table \ref{tab:SysAcc} are, in nature, similar to the statistical errors, in the sense that both originate from the large variation between event-by-event weights.
+For this reason, we decided to do not include this error in our systematic budget to avoid double counting this effect.
 
@@
   \end{tabular}
-  \caption{Relative errors on observables between the two weighting 
-  described in the text.}
+  \caption{Relative errors on pions' observables using the two weighting methods described in the text.}
   \label{tab:SysAcc}
@@
 
-\subsubsection{Total Error}
+\subsubsection{Total Systematic Budget}
 
-The point to point errors include the contributions from detection 
-contamination and acceptance effects. The normalization errors 
--- i.e.~independent of kinematic variables -- are due to acceptance effects, 
-target identification and isospin correction. They are summarized in the 
-table~\ref{tab:sysid}.
+The point-to-point errors include contributions from a detection contamination and acceptance effects.
+However, the normalization errors, which are independent of kinematical variables and due to acceptance effects, a target's misidentification and the isospin correction, are summarized in a table~\ref{tab:sysid}.
 
@@
   \end{tabular}
-  \caption{Normalization uncertainties.}
+  \caption{Total normalization uncertainties for both charged pions.}
   \label{tab:sysid}

### 2016-10-20 chap6.tex
Changes from Lamiaa

@@
 The results presented in this chapter are a selection of the observables 
-that we want to use in a first publication, eventually a long paper would
-include all results as function of all variables. We use the following DIS selection cuts: 
-$Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$. In order to ensure that 
-factorization applies, we select $0.4$~$<$~$z$~$<$~$0.7$\footnote{This cut is not 
-applied for plots as a function of $z$.}, this choice is based on experimental results from 
-\cite{Asaturyan:2011mq}. Moreover, this cut also ensures that we measure the leading 
-hadron and that we avoid the high $z$ region, which might be contaminated by 
-the decay products of the diffractive production of $\rho^0$. Finally, the cut 
-$x_F > 0$ select the forward fragmentation region.
+that we want to use in the first publication, eventually a long paper will
+include results as function of all variables. All results were extracted with the following DIS selection cuts: 
+$Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$.
+To ensure that a factorization holds, we are selecting events with $0.4$~$<$~$z$~$<$~$0.7$~\footnote{This cut is not applied for plots with results as a function of $z$.} based on the previously published results from \cite{Asaturyan:2011mq}.
+Moreover, this cut also ensures that we are measuring the leading hadron, and avoiding the high $z$ region, which might be contaminated by
+the decay products of the diffractive production of $\rho^0$. Finally, we are applying a cut on $x_F > 0$ to select the forward fragmentation region.
 
@@
 
-The figure \ref{fig:RA} presents our result for the $A^{1/3}$ dependence of 
-the multiplicity ratio. One can see a 5\% normalization difference between
-pions. However, this difference is not significant as it represents only 1.5 
+Figure \ref{fig:RA} contains our results for the $A^{1/3}$ dependence of 
+the multiplicity ratio. One can see a 5\% normalization difference between both pions. However, this difference is not significant as it represents only 1.5 
 standard deviation of our normalization uncertainty (see table~\ref{tab:sysid}).
 
-The attenuation, presented in the figure \ref{fig:RA}, is not linear as 
-a function of $A^{1/3}$ nor $A^{2/3}$. HERMES data has already showed some indication 
-of this feature \cite{Airapetian:2007vu,Airapetian:2009jy}, but here, the nonlinearity, 
-which has important implication on models, is clear. Indeed, it seems difficult 
-to conciliate the prehadron absorption models with this result. Prehadrons 
-are expected to have their cross section increasing with time and, therefore, 
-distance. On the parton energy loss side, the BDMPS calculation gives a parton energy loss proportional to 
-$L^2 \propto A^{2/3}$ also in contradiction with this result. However, 
-this statement does not hold at low energy and might also be 
+The attenuation, presented in the figure \ref{fig:RA}, is not linear neither for $A^{1/3}$ nor $A^{2/3}$. The HERMES data have already showed some indication 
+of this feature~\cite{Airapetian:2007vu,Airapetian:2009jy}, but here, the non-linearity, which has important implication on models, is clear.
+Indeed, it seems difficult to conciliate the prehadron absorption models with this result.
+Prehadrons
+are expected to have their cross sections increasing with time and, therefore, 
+distance.
+On the parton energy loss side, the BDMPS calculation gives a parton energy loss proportional to $L^2 \propto A^{2/3}$, which is in contradiction with this result.
+However, this statement does not hold at low energy, and might be
 modified if the production time occurs inside the nuclei.
@@
 \includegraphics[width=7.4cm] {chap6-fig/F_RvPt_PbC.png} 
-\caption {Multiplicity ratios as a function of \pt (GeV$^2$/c$^2$) for charged pions. Left panel is 
-the usual observable, right panel shows multiplicity ratio of lead normalized to carbon.
+\caption {Multiplicity ratios as a function of \pt (GeV$^2$/c$^2$) for both charged pions.
+Left: The usual multiplicity ratio results.
+Right: Lead results normalized to carbon.
 Normalization uncertainties are not shown.}
@@
 \includegraphics[width=7.4cm] {chap6-fig/F_RvPtinNu.png} 
-\caption {Multiplicity ratios as a function of \pt (GeV$^2$/c$^2$) and $z$ (left) 
-or $\nu$ (GeV) (right) for positive pions. Normalization uncertainties are not shown.}
+\caption {Positive pions multiplicity ratios as a function of \pt (GeV$^2$/c$^2$) for different $z$ bins (left), and different $\nu$ (GeV) bins (right). Normalization uncertainties are not shown.}
 \label{fig:RPtMulti}
@@
 The Cronin effect is characterized by a large increase of the multiplicity 
-ratio at high \pt ($\sim$1~GeV$^2$/c$^2$), but it is a controversial 
-measurement in hadronization studies. Indeed, whereas SLAC measurements 
-\cite{Osborne:1978ai} did not show such an effect, HERMES 
-\cite{Airapetian:2007vu} measured a significant increase of the multiplicity 
+ratio at high \pt ($\sim$1~GeV$^2$/c$^2$), which is a controversial result in hadronization studies. Indeed, whereas SLAC measurements 
+\cite{Osborne:1978ai} did not show such an effect, HERMES \cite{Airapetian:2007vu} measured a significant increase of the multiplicity 
 ratio with \ptp. Our result (figure \ref{fig:RPt} (left)), integrated over 
-all other variables, shows a pattern similar to the HERMES measurement. 
-However, there is potential contributions from the target fragmentation and 
+all other variables, showed a pattern similar to the HERMES measurement. 
+However, there are some potential contributions from the target fragmentation and 
 the Fermi motion.
 
-Fermi motion effects can be significantly reduced by modifying 
-our usual observables. Indeed, using carbon for normalization, instead of deuterium, 
-cancels most of the effects of Fermi motion. Moreover, acceptance 
-effects (section~\ref{sec:accept}) are mostly canceled as well in such a ratio, 
-reducing the associated systematic errors (including most of the normalization error). 
-The figure \ref{fig:RPt} (right) represents the multiplicity ratio based on carbon. We 
-observe an attenuation, at low \ptp, similar to the usual multiplicity ratio 
-of iron. This can be understood from the radius of the nuclei $R_{Pb}-R_{C} 
-\sim R_{Fe}$. Nevertheless, the observed enhancement with \pt is much more modest than in 
-iron. At first sight the difference can be attributed to Fermi motion, which 
-might affect the measurement based on deuterium.
+Fermi motion effects can be significantly reduced by modifying our regular observables.
+Indeed, using carbon for normalization, instead of deuterium, most effects of Fermi motion cancel out.
+Moreover, acceptance effects (section~\ref{sec:accept}) will also be mostly canceled in such a ratio, leading to a reduction of their systematic errors dominated mainly by the normalization error.
+The normalized lead multiplicity ratio to carbon is presented on figure \ref{fig:RPt} (right).
+There is an attenuation, at low \ptp, similar to the usual multiplicity ratio of iron.
+This can be understood based on the difference of both nuclei radii, $R_{Pb}-R_{C} \sim R_{Fe}$.
+Nevertheless, the observed enhancement with \pt is much more modest than in iron.
+At first sight the difference can be attributed to Fermi motion, which might affect the normalized measurement with deuterium compared to carbon.
 
-In the figure \ref{fig:RPtMulti}, the multi-dimensionally binned multiplicity 
-ratio are presented. HERMES found an important dependence of the Cronin effect 
-with $z$ \cite{Airapetian:2007vu,Airapetian:2011jp} that can be interpreted as a 
-sign of an important target fragmentation contribution. The present result 
-(figure~\ref{fig:RPtMulti} (left)) does not show this behavior, but it can be 
-explained by our stricter cut on $z$ ($z>0.4$ whereas HERMES uses $z>0.2$), which 
-leads to a smaller target fragmentation contamination. The second result, 
-binned in \pt and $\nu$ (figure \ref{fig:RPtMulti} (right)), shows an important 
-dependence of the Cronin effect with $\nu$. However, HERMES results did not 
-reveal any similar $\nu$ variation. This is an evidence of the importance of 
+In figure \ref{fig:RPtMulti}, the multi-dimensional multiplicity ratio results are presented.
+HERMES found an important $z$ dependence of the Cronin effect \cite{Airapetian:2007vu,Airapetian:2011jp}.
+That can be treated as a sign of an essential contribution from a target fragmentation.
+The present result
+(figure~\ref{fig:RPtMulti} (left)) does not show this behavior, which could be due to our strict cut on $z$ ($z>0.4$ whereas HERMES used $z>0.2$) that leads to a smaller target fragmentation contamination.
+The second result, binned in \pt and $\nu$ (figure \ref{fig:RPtMulti} (right)), showed an important
+$\nu$ dependence of the Cronin effect. However, HERMES results did not exhibit such a $\nu$ behavior. This is a clear evidence of the importance of 
 the Fermi motion effect in our measurement.
 
-The result for the lead to carbon multiplicity ratio, figure \ref{fig:RPt} 
+The result of the lead to carbon multiplicity ratio, figure \ref{fig:RPt} 
 (right), has another interesting feature: the $\pi^+$s have a stronger Cronin 
@@
 a contribution from target fragmentation, as we might expect more positive 
-particles than negative ones coming from the nuclei.
-This could also come from other sources such as isospin effect or factorization breaking at high 
-\ptp, but no test of these features exists in this kinematical range\footnote{
-\cite{Asaturyan:2011mq} covers only \pt$<0.2$ GeV$^2$/c$^2$.}. Last, it could 
-be linked to the hadron rank and reflect some hadronization properties. Indeed, 
-as we probe mostly valence quark at our energies, $\pi^+$s are more likely to 
-be leading hadron compared to $\pi^-$s.
+particles would originate from nuclei than negative ones. This could also come from other sources such as the isospin effect or a factorization breaking at high 
+\ptp.
+However, no test of these features exists in our kinematical range\footnote{Results of \cite{Asaturyan:2011mq} covered only \pt$<0.2$ GeV$^2$/c$^2$.}.
+Last but not least, it could be correlated with the hadronic rank and reflect some hadronization properties.
+Indeed, as we probe mostly valence quarks at our energies, $\pi^+$s are more likely to be the leading hadrons compared to $\pi^-$s.
 
-In conclusion, our results indicate that the HERMES results were affected by target 
-fragmentation and that our results are affected by Fermi motion. These effects can 
-be easily controlled by selecting carefully our observables. In this regard, the
-Pb/C ratio seems to give cleaner results than Fe/D.
+In conclusion, our results indicate that the HERMES results were affected by a target fragmentation and that our results are affected by the Fermi motion.
+These effects can be easily controlled by a careful selection of our observables.
+In this regard, the Pb/C ratio seems to give cleaner results than Fe/D.
 
@@
 \includegraphics[width=7.4cm] {chap6-fig/F_RvNu_PbC.png} 
-\caption{Multiplicity ratios as a function of $\nu$ (GeV). Left panel is the usual 
-observable, right panel shows multiplicity ratio of lead normalized to carbon. 
+\caption{Multiplicity ratios as a function of $\nu$ (GeV) for both charged pions.
+Left: The usual multiplicity ratio results.
+Right: Lead results normalized to carbon.
 Normalization uncertainties are not shown.}
@@
 
-The HERMES collaboration clearly observed a rise of the multiplicity ratio 
-between $\nu$ of 4 and 22~GeV. However, at first sight, in our results (figure 
-\ref{fig:RNu} (left)), no dependence is observed, except for a 
-slight increase in lead.
-However, Fermi motion could cancel the hadronization effect almost completely and the
-systematic uncertainties linked with acceptance might wash out what remains of the effect. The 
-multiplicity ratio based on carbon, however, offers a cleaner result with a slope consistent 
-with what was observed on a much larger range by HERMES.
+The HERMES collaboration clearly observed a rise of the multiplicity ratio with $\nu$ from 4 till 22~GeV.
+However, at first sight to our results (figure \ref{fig:RNu} (left)), no dependence is observed, besides a slight increase in lead.
+However, the Fermi motion could cancel most of this hadronization effect, and what left will be washed out with the acceptance correction systematic uncertainty.
+The normalized multiplicity ratio to carbon, however, offers a cleaner result with a slope consistent with what was observed on a much larger range of HERMES data.
 
-We also notice here that both pions give similar results in the figure 
+We must note the similar behavior of both pions results in a figure 
 \ref{fig:RNu} (right). This confirms our previous remark that the difference 
-observed in the multiplicity ratio based on deuterium might come from the 
-normalization uncertainty caused by the acceptance correction. There is no 
-clear difference between the charged pions for the integrated multiplicity 
+observed in the regular multiplicity ratio might originate from the 
+normalization uncertainty caused by the acceptance correction. Also, there is no 
+clear difference between both charged pions on the integrated multiplicity 
 ratios as a function of $\nu$.
@@
 \includegraphics[width=7.4cm] {chap6-fig/F_RvZ_PbC.png} 
-\caption {Multiplicity ratios as a function of $z$. Left panel is the usual
-observable, right panel shows multiplicity ratio of lead normalized to carbon. 
+\caption {Multiplicity ratios as a function of $z$ for both charged pions. Left: The usual multiplicity ratio results. Right: Lead results normalized to carbon. 
 Normalization uncertainties are not shown.}
@@
 The multiplicity ratio was observed to decrease with $z$ in HERMES data, 
-whereas this feature was not as significant in other experiments. Indeed the 
-nature of this behavior is questionable, the target fragmentation also reduce 
-with $z$ and can mimic the effect. In figure \ref{fig:Rz} (left), as in 
-HERMES, we see a clear slope even at values higher than 0.4, where target fragmentation
-effects are expected to be small. However, the ratio lead to carbon (figure 
-\ref{fig:Rz} (right)) shows a much flatter behavior in the region of interest 
-(0.4 to 0.7). Therefore, the situation seems to be 
-similar to the Cronin effect one, where HERMES observation was enhanced by 
-target fragmentation. The measurement using the carbon as basis is, therefore, 
-more useful to isolate effects from the hadronization, but low $z$ behavior 
-remains driven by the target region. Another strange feature of the data is 
-the behavior at high $z$ (figure \ref{fig:Rz} (right)), where the two pions 
-behave differently. However, we lack of solid theoretical grounds in this 
-region to interpret this result.
+whereas this behavior was not significant in other experiments. Indeed the 
+nature of this behavior is questionable as the target fragmentation also get reduced 
+with $z$, hence can mimic the signal.
+In figure \ref{fig:Rz} (left), as for HERMES results, we see a clear slope even at values higher than 0.4, where target fragmentation effects are expected to be small.
+However, the lead to carbon ratio (figure \ref{fig:Rz} (right)) shows a much flatter behavior in the region of interest (from 0.4 to 0.7).
+Therefore, this situation seems similar to the Cronin effect, where HERMES observation was enhanced by a target fragmentation.
+The measurement using the carbon as a basis is, therefore, more useful on isolating effects from the hadronization.
+However, the low $z$ behavior remains driven by the target fragmentation region.
+Another strange feature of the data is the behavior at higher $z$ (figure \ref{fig:Rz} (right)), where the two pions behave differently.
+However, there is a lack of solid theoretical grounds in this region to interpret this result.
 
@@
 has direct implications on our understanding of nuclear matter properties in 
-QCD. HERMES results, which covers $1<Q^2<10$~GeV$^2$/c$^2$, give a hint for an 
+QCD. HERMES results, which covered $1<Q^2<10$~GeV$^2$/c$^2$, gave a hint of an 
 increase of the multiplicity ratio with $Q^2$. Our result, in figure 
-\ref{fig:RQ2}, does not allow to reach the same conclusion and indicates no 
-significant dependence as a function of $Q^2$.
+\ref{fig:RQ2}, did not indicate any significant $Q^2$ dependence, hence no conclusions can be made from our measurement.
 
@@
 
-We can use our large statistics to get more information. As 
-a dependence in $\nu$ is expected for the multiplicity ratio, it might be helpful to use a tight 
-$\nu$ bin to plot the $Q^2$ dependence (figure \ref{fig:RQ2Detailed} (left)), 
-and remove any coupling between the two variables.
-We could also expect some effects from the Fermi motion, 
-therefore, we show in figure \ref{fig:RQ2Detailed} (right) the multiplicity ratio of lead to 
-carbon as a function of $Q^2$. The two results of figure \ref{fig:RQ2Detailed} 
-show a slight increase with $Q^2$, but as for HERMES, no evidence is 
-reached on this question. Our leverage on $Q^2$ appears to be too modest
-to make a clear measurement.
+We can use our large statistics to extract more information by handling the results differently.
+As a $\nu$ dependence is expected for the multiplicity ratio, it might be helpful to use a tighter $\nu$ bin to plot the $Q^2$ dependence (figure \ref{fig:RQ2Detailed} (left)), thus remove any coupling between the two variables.
+As some Fermi motion effects would persist, it is more convenient to show the $Q^2$ dependence of the normalized multiplicity ratio of lead to carbon, see figure \ref{fig:RQ2Detailed} (right).
+The two results of figure \ref{fig:RQ2Detailed}
+showed a slight increase with $Q^2$, but as for HERMES, no evidence is 
+reached on this context. Our leverage on $Q^2$ appears to be too modest to make a clear measurement.
 
@@
 \includegraphics[width=7.4cm] {chap6-fig/F_RvQ2_PbC.png} 
-\caption {Multiplicity ratios as a function of $Q^2$ (GeV$^2$/c$^2$). In the left panel,
-the multiplicity ratio in a tight $\nu$ bin ($3.25 < \nu < 3.75$ GeV). In the right 
-panel, the multiplicity ratio of lead normalized to carbon. Normalization 
-uncertainties are not shown.}
+\caption {Multiplicity ratios as a function of $Q^2$ (GeV$^2$/c$^2$) for both charged pions.
+Left: The multiplicity ratio for a tighter $\nu$ bin ($3.25 < \nu < 3.75$ GeV).
+Right: The normalized multiplicity ratio of lead to carbon.
+Normalization uncertainties are not shown.}
 \label{fig:RQ2Detailed}
@@
 The $A$ dependence of the transverse momentum broadening, presented in 
-figure~\ref{fig:PA}, is an important result. The large statistics coupled with the 
-large coverage in $A$ available to the CLAS experiment give precise indication on \dpt 
-as a function of $A^{1/3}$. Compared to HERMES \cite{Airapetian:2009jy}, we
-find smaller \dptp. This is coherent with theory, which predicts larger effects
-at larger energies. However, calculations of parton energy loss from BDMPS 
-\cite{Baier:1996sk} show that \pt should depend on the nucleus radii. However, 
-this feature does not appear in our 
-result. Of course, because of the low energy of the CLAS experiment, one might 
-discuss the possibility to make a direct comparison with BDMPS calculations. Nonetheless, 
-this result shows an unexpected pattern that remains to be explained. One 
-possibility is that, as proposed for the multiplicity ratio as a function of 
-$A^{1/3}$, the production time occurs inside the nuclei. In this case, the 
-colored parton would not interact with the whole nuclei and limit the nuclear 
-effect.
+figure~\ref{fig:PA}, is a crucial result.
+The combination of our large statistics with a wide $A$ coverage gave an outright indication of $A^{1/3}$ dependence of \dpt.
+This \dptp~ effect is found much smaller compared to HERMES measurment\cite{Airapetian:2009jy}, which is consistent with theoretical models predicting larger effects at larger energies.
+However, calculations of the parton energy loss from BDMPS \cite{Baier:1996sk} correlated \pt with the nuclei radii.
+A feature that is not enhanced in our result.
+Although, by looking to the low energy of our CLAS experiment, one might argue the validity of a direct comparison with BDMPS calculations.
+Nonetheless, this result shows an unexpected pattern that remains to be explained.
+One interpretation might favor the occurrence of the production time inside nuclei, as we proposed for the $A^{1/3}$ dependence of multiplicity ratios.
+In this case, the colored parton would not interact with the whole nuclei which limit the nuclear effect.
 
@@
 \includegraphics[width=8.2cm] {chap6-fig/F_PvA.png} 
-\caption {$A$ dependence of \dptp. Points are slightly offset for readability, normalization uncertainties are not shown.}
+\caption {$A$ dependence of \dptp. Points are slightly shifted for a readability. Normalization uncertainties are not shown.}
 \label{fig:PA}
@@
 Finally, the $Q^2$ dependence of \dpt is an important result for the BDMPS based 
-calculation from \cite{Domdey:2008aq}. They expect a raise of \dpt with $Q^2$,
-which is not observed in the figure \ref{fig:PQ2}. Using
-binning in $\nu$ and carbon based \dpt (figure \ref{fig:PQ2-detailed}) gives a similar
-result. In conclusion, within error bars, no effect is observed for \dpt as a function of $Q^2$.
-However, as theoretical input is missing, it is not clear if we have the resolution to observe
-the effect expected within BDMPS based models.
+calculation from \cite{Domdey:2008aq}.
+They have expected a raise of \dpt with $Q^2$, which is not observed in a figure \ref{fig:PQ2}.
+Even a tighter $\nu$ bin and a carbon normalization (see figure \ref{fig:PQ2-detailed}) gave a similar result.
+In conclusion, within error bars, no effect is observed for \dpt as a function of $Q^2$.
+However, as a theoretical input is missing, it is not clear if we have the needed resolution to observe the effect expected within BDMPS based models.
 
@@
 \includegraphics[width=7.4cm] {chap6-fig/F_PvQ2.png} 
-\caption {\dpt for iron as a function of $Q^2$ (GeV$^2$/c$^2$) 
-with usual cuts. Normalization uncertainties are not shown.}
+\caption {Iron \dpt as a function of $Q^2$ (GeV$^2$/c$^2$) after applying the regular DIS cuts. Normalization uncertainties are not shown.}
 \label{fig:PQ2}
@@
 \includegraphics[width=7.4cm] {chap6-fig/F_PvQ2_PbC.png} 
-\caption {\dpt as a function of $Q^2$ (GeV$^2$/c$^2$). Left panel is the usual
-observable in a tight $\nu$ bin ($3.25 < \nu < 3.75$~GeV). Right panel shows \dpt 
+\caption {Positive pions \dpt as a function of $Q^2$ (GeV$^2$/c$^2$). Left: The usual observable for a tighter $\nu$ bin ($3.25 < \nu < 3.75$~GeV). Right: \dpt 
 of lead relative to carbon. Normalization uncertainties are not shown.}

### 2016-10-20 intro.tex
Changes from Lamiaa

--- 2016-09-27 intro.tex
@@
 
-The hadronization process by which parton fragment into hadrons is 
-experimentally well studied and fragmentation functions fitted from 
-data are measured on a large kinematic range~\cite{Albino:2008fy}.
-Nevertheless, the hadron formation is a non perturbative process and can not 
-be theoritically described, only a global picture 
-(see figure \ref{fig:hadro}) can be drawn for
-energies above the resonance region. In deep inelastic scattering the
-virtual photon interact with a quark which propagate quasi-free emitting
-gluons during the 
-so-called production time. After neutralizing its color the quark become 
-a pre-hadron which will eventualy form a hadron after the formation time.
-On nuclear target the process of hadronization occurs, at least partly, in 
-nuclear matter, then one can extract the production time using the different 
-behaviour of quarks and colorless pre-hadrons in medium. The measurement of
-pions is especially suited to lead that kind of analysis because they are easy
-to detect and abundant in deep inelastic scattering.
+The hadronization process by which partons fragment into hadrons is 
+experimentally well studied, and the associated fragmentation functions are extracted from the fit of experimental data over a wide range of kinematics~\cite{Albino:2008fy}.
+Nevertheless, the hadron formation is a non perturbative process, which can not be described theoretically, but only via a systematic study of the whole hadronization mechanism (see figure \ref{fig:hadro}) for energies above the resonance region.
+In Deep Inelastic Scattering (DIS), the virtual photon interacts with a quark which propagates quasi-free emitting gluons during the so-called production time.
+After neutralizing its color, the quark becomes a pre-hadron that eventually evolves to a full hadron after the formation time.
+The advantage of using nuclear targets is that the hadronization process occurs, at least partially, inside the nuclear matter, which allows the extraction of hadronization time-scales by comparing different behavior of quarks and colorless pre-hadrons in the medium.
+The measurement of pions production is especially suited for this analysis because they are easy to detect and abundant in the nuclear deep inelastic scattering (nDIS).
 
@@
 
-The hadronization in nuclear matter is a key process in QCD also
-because it leads to a major theoritical uncertainty in numerous measurements.
-In heavy ion collisions, the measured hadrons are produced in hot and evolving 
-medium, the models describing those collisions can be tested in deep inelatic scattering 
-where the size of the medium is stable and known. Quantitative
-understanding of the hadronization in nuclei is also of interest for
-neutrino experiment which often use nuclei to maximize their cross section.
-The hadronization can give important information about the 
-nuclei through quark energy loss, for exemple \cite{Arleo:2003yf} link 
-energy loss with gluon density and \cite{Kopeliovich:2010aa} link the $\Delta \langle
-P_T^2 \rangle$ with the saturation scale. Other models \cite{Gallmeister:2007an}
-can give information about how the pre-hadron evolve into hadron but are based
-on very different assomptions, therefore it is very important to discriminate between
-models.
+The hadronization in nuclear matter is a key process of the Quantum Chromo-Dynamics theory (QCD) because it leads to major theoretical uncertainties in numerous measurements.
+As the nuclear medium is hot and evolving in Relativistic Heavy Ion Collisions (RHIC), DIS experiments at JLab energies are well suited to test different theoretical models, including the RHIC's ones, because the size of cold nuclei is stable and known.
+A quantitative understanding of the hadronization process in nuclei is also an interesting theme for neutrino experiments that often use nuclei to maximize their cross sections.
+The hadronization can give an important information about nuclei through the quark energy loss, for example, Arleo's model~\cite{Arleo:2003yf} correlates the quark energy loss with a gluon density, and Kopeliovich et al.'s model~\cite{Kopeliovich:2010aa} correlates the $\Delta \langle P_T^2 \rangle$ with the saturation scale.
+Other models \cite{Gallmeister:2007an} utilize different assumptions to describe the pre-hadron evolution into a full hadron.
+Therefore, high precision measurements are very important to discriminate between different models.
 
-In order to constrain the existing models we extract our results
-using tight multi-dimensional binning. 
-The importance of the EG2 data comes from its high statistics which permit, 
-this multi-dimensional measurement of both pions on a 
-large kinematic range.
+In order to constrain the existing models we extracted our results using a tight multi-dimensional binning.
+That was viable due to the high statistics of our EG2 data, which allowed the study of both pions production over a wide kinematic range.
 
-We present in section \ref{sec:theo} the different familly of models describing
-hadronization in nuclear matter then in section \ref{sec:exp} we make a rapid
-overview of the published data on the topic. For more detailed information we 
-refer the reader to the review from Accardi {\it et al.} \cite{Accardi:2009qv}.
+We present in section \ref{sec:theo} a highlight of different models' families describing the hadronization process in hot and cold nuclear matter, then in section \ref{sec:exp} we make a rapid overview of published results.
+For more detailed information, we refer the readers to the review of Accardi {\it et al.} \cite{Accardi:2009qv}.
 
-\subsection{Kinetic Variables and Observables}
+\subsection{Kinematic Variables and Observables}
 
-In this analysis we use the following semi-inclusive DIS variables:
+In this analysis we use the following Semi-Inclusive Deep Inelastic Scattering (SIDIS) variables:
 \begin{itemize}
- \item $\nu = E_i - E_f$ with $E_i$ the beam energy and $E_f$ the scattered electron energy,
- \item $Q^2 = 4 E_i E_f \sin ^2(\theta_e / 2)$ with $\theta_e$ the scattered electron angle with the beam line,
- \item $x_{Bj} = {{Q^2} \over {2 M_n \nu}}$ with $M_n$ the nucleon mass,
- \item $W^2 = M_n^2 - Q^2 + 2 M_n \nu$
- \item $z_h = E_h / \nu$
- \item $P_T^2$ which is transverse momentum according to the virtual photon
- \item $\phi_h$ the angle between the electronic plan (contain initial and scattered electrons) and the hadronic plan (contain virtual photon and hadron)
- \item $x_F = P_L/P_L^{max}$ the fraction of longitudinal momentum carried by the hadron calculated in respect to the virtual photon direction in the laboratory frame.
+ \item $\nu = E_i - E_f$ is the energy transferred by the lepton probe in the laboratory frame, where $E_i$ is the beam energy and $E_f$ is the scattered electron energy,
+ \item $Q^2 = 4 E_i E_f \sin ^2(\theta_e / 2)$ is the 4-momentum transferred, with $\theta_e$ is the polar angle of a scattered electron,
+ \item $x_{Bj} = {{Q^2} \over {2 M_n \nu}}$ is the proton momentum fraction carried by the struck quark, with $M_n$ is the nucleon mass,
+ \item $W^2 = M_n^2 - Q^2 + 2 M_n \nu$ is the mass squared of the hadronic final state,
+ \item $z_h = E_h / \nu$ is the virtual photon energy fraction carried by the measured hadron, with $E_h$ is the hadron energy,
+ \item $P_T^2$ is the hadron transverse momentum measured with regard to the virtual photon direction,
+ \item $\phi_h$ is the angle between the leptonic plane (containing initial and scattered electrons) and the hadronic plane (containing the virtual photon and a measured hadron),
+ \item $x_F = P_L/P_L^{max}$ is the longitudinal momentum fraction carried by the hadron, and calculated with respect to the virtual photon direction in the laboratory frame.
 \end{itemize}
@@
 R_A^h (Q^2,\nu,z_h,P_T^2) = {{N_A^h (Q^2,\nu,z_h,P_T^2) / N_A^e (Q^2,\nu)} 
-                       \over {N_D^h (Q^2,\nu,z_h,P_T^2) / N_D^e (Q^2,\nu)}}
+                       \over {N_D^h (Q^2,\nu,z_h,P_T^2) / N_D^e (Q^2,\nu)}},
 \end{equation}
-with $N^e_A$ the number of electron measured from a target $A$ and $N_A^h$ the number
-of semi-inclusive hadrons $h$ (detection of both an electron and a hadron) from the
-target~$A$. The multiplicity ratio represents the attenuation of the hadron $h$ in a 
-nuclear target~$A$.
+$N^e_A$ and $N_A^h$ are the number of electrons and semi-inclusive hadrons $h$ measured simultaneously on a target $A$.
+The multiplicity ratio represents the attenuation of the hadron $h$ in a nuclear target~$A$.
 \newline
@@
 \begin{equation}
-\Delta \langle P_T^2 \rangle = \langle P_T^2 \rangle_A - \langle P_T^2 \rangle_D
+\Delta \langle P_T^2 \rangle = \langle P_T^2 \rangle_A - \langle P_T^2 \rangle_D,
 \end{equation}
-with $\langle P_T^2 \rangle_A$ the mean transverse momentum measured in a target $A$.
+where $\langle P_T^2 \rangle_A$ is the mean transverse momentum measured on a target $A$.
 
@@
 
-The different models explaining the data can be separated in three families,
-some assume that the quark loose energy in the medium and that either, hadronization occurs
-outside the medium or the hadronic interaction is 
-negligible, others consider the quark energy loss negligible and consider
-only the hadron and pre-hadron absorption and finally some models consider both
-interactions. We will give an example of each case to illustrate, for more
-detailed information we refer again to \cite{Accardi:2009qv} which is more exaustive and
-mention few other models used for RHIC experiments.
+The different models explaining the data can be separated in three families;
+some assume that the quark looses energy in the medium and that either the hadronization occurs outside the medium or the hadronic interaction is 
+negligible, others neglect the quark energy loss and consider
+only the hadron and pre-hadron absorption, and the third category considers both
+interactions.
+For illustration, we will give an example of each case, but for more detailed information, we refer the readers again to our reference~\cite{Accardi:2009qv}, which is more exhaustive and highlights also models describing RHIC's experiments.
 
-In \cite{Wang:2002ri}, E.~Wang and X.-N.~Wang, describe HERMES data using only energy 
-loss from the parton, the suppression observed is then due to the fact that a 
-lower energy quark will fragment into a lower number of hadrons and a lower 
-$z$. That kind of model is used in both RHIC and nDIS and permit a commom 
-interpretation of hadron suppression in nuclear matter. Lot of different
-calculations of the energy loss exist, the main parameter for those is $\hat q$
-(GeV$^2$ fm$^{-1}$) which is the transverse momentum per unit of length of a 
-quark after propagating
-in nuclear matter, this value is related to the $P_T$ 
-broadening observables. The main difficulty for the quark energy loss
-models is to have coherent description of both multiplicity ratios and $P_T$ 
-broadening. Recent models find a $\hat q$ to reproduce multiplicity ratio
-which is bigger than the one necessary to describe transverse momentum broadening.
+In \cite{Wang:2002ri}, E.~Wang and X.-N.~Wang, described HERMES data using only 
+the parton energy loss, hence the observed suppression is due to the fact that a lower energy quark fragments into a low number of hadrons at a very low $z$.
+This kind of models is suitable for both RHIC and nDIS experiments since it permits a common interpretation of hadron suppression in the nuclear matter.
+Moreover, various calculations have described the parton energy loss in the nuclear medium using the $\hat q$ (GeV$^2$ fm$^{-1}$) parameter, that is defined as the quark transverse momentum normalized by its propagation path length.
+In these models, $\hat q$ is mainly related to the $P_T$ broadening observable.
+The main difficulty of quark energy loss models is the lack of a coherent description for both multiplicity ratios and $P_T$ broadening behaviors.
+Recent models used a $\hat q$ to reproduce multiplicity ratio, which is too large to describe the transverse momentum broadening.
 % TODO Add a ref
 
-The GiBUU model \cite{Gallmeister:2007an} is a transport model based on Boltzmann equation
-using hadronic and pre-hadronic interaction in the nuclear matter, with no
-quark energy loss involved. This model reproduce very well most of the hadrons, 
-however the $\Delta \langle P_T^2 \rangle$ variable is not described at all by 
-this hadron absorption models.
+The other transport model, GiBUU~\cite{Gallmeister:2007an}, is based on the 
+Boltzmann equation that employs hadronic and pre-hadronic interactions in the nuclear matter without involving any quark energy loss.
+This model reproduces very well most of hadrons' multiplicity ratios, however, it failed to describe the transverse momentum broadening.
+%$\Delta \langle P_T^2 \rangle$ variable is not described at all by
 
-B.Z.~Kopeliovich \cite{Kopeliovich:2008uy} describe the process neglegting neither quark 
-energy loss or hadron absorption, using transverse momentum and
-multiplicity ratios to differenciate the effects. In that case the transverse 
-momentum broadening is linked to quark energy loss and the multiplicity ratio
-suppression is explained by hadron absorption in medium.
+Furthermore, B.Z.~Kopeliovich et al.
+\cite{Kopeliovich:2008uy} described the process by neither neglecting the quark energy loss nor the hadron absorption, but used both $\Delta \langle P_T^2 \rangle$ and $R_A^h$ observables to differentiate between these effects.
+In that case, the transverse momentum broadening is correlated with the quark energy loss, and the suppression of multiplicity ratios is explained by the hadron absorption in the nuclear medium.
 
 To conclude it is important to point out that no consensus is reached on which 
-mecanisms are dominant. It is therefore important to perform precise measurements with
-the right observables to solve this problem.
+mechanisms are dominant. It is, therefore, important to perform precise measurements with the appropriate observables to disentangle these effects.
 
@@
 facilities: L.S.~Osborne {\it et al.} \cite{Osborne:1978ai} at SLAC,
-L.~Hand {\it et al.} \cite{Hand:1978tx} and the E665 collaboration \cite{Adams:1994ri} at FNAL
-and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN. Those 
-measurements revealed the general features of hadronization
-in nuclei: we observe a sizeable suppression when
-looking at hadron production in nuclei, this suppression is lower at higher
-$\nu$ and lower $z$, it can even inverse and be an increased yield at very low $z$.
+L.~Hand {\it et al.} \cite{Hand:1978tx}, the E665 collaboration \cite{Adams:1994ri} at FNAL, and the European Muon Collaboration \cite{Arvidson:1984fz,Ashman:1991cx} at CERN.
+These measurements revealed the main features of the hadronization mechanism
+in nuclei by showing a suppression of hadrons' production in heavy nuclei.
+This suppression appears to be reduced at higher $\nu$ and lower $z$, and it 
+can even inverse sign and become an increased yield at very low $z$.
 
-The figures \ref{fig:her1}, \ref{fig:her2} and \ref{fig:her3} shows a sample of 
-the most recent data from HERMES collaboration \cite{Airapetian:2007vu}, numerous 
-hadrons are studied individually and new variables linked with transverse 
-momentum are used on top of the usual multiplicity ratio.
+Figures \ref{fig:her1}, \ref{fig:her2} and \ref{fig:her3} show a sample of 
+the most recent HERMES data~\cite{Airapetian:2007vu}, where numerous hadrons were individually studied, and new variables linked with the transverse momentum were used in addition to the usual multiplicity ratio.
 
@@
 \includegraphics[width=14cm] {fig/Hermes/pi0hermes.png} 
-\caption {Multiplicity ratio of $\pi^0$ as a function of various kinetic 
-variables from HERMES collaboration \cite{Airapetian:2003mi}}
+\caption {Multiplicity ratios of $\pi^0$ as a function of various kinematical variables from the HERMES collaboration \cite{Airapetian:2003mi}}
 \label{fig:her1}
@@
 \includegraphics[width=14cm] {fig/Hermes/hermes1.png} 
-\caption {Multiplicity ratio of $\pi^+$, K$^+$, protons and anti-protons as a 
-function of various kinetic variables from HERMES collaboration \cite{Airapetian:2007vu}}
+\caption {Multiplicity ratios of $\pi^+$, K$^+$, protons and anti-protons as a 
+function of various kinematical variables from the HERMES collaboration \cite{Airapetian:2007vu}}
 \label{fig:her2}
@@
 \includegraphics[width=7cm] {fig/Hermes/pthermes.png} 
-\caption {Transverse momentum broadening for various particles
-from HERMES collaboration \cite{Airapetian:2009jy}}
+\caption {Transverse momentum broadening for various particles from the HERMES collaboration \cite{Airapetian:2009jy}}
 \label{fig:her3}
@@
 
-The HERMES data, because of their precision,
-permit to have an insight into new features. One can cite the behavior of K$^+$
-which have less attenuation than pions (see figure \ref{fig:her1}) but more 
-$\Delta \langle P_T^2 \rangle$, it is difficult to reproduce this in 
-models where only one stage of hadronization is taken into account to 
-explain all effects.
-Also the different behaviour of protons compare to anti-protons
-(see figure \ref{fig:her1}) is interesting
-and need precise analysis even most of the theoritical models do not treat 
-baryon hadronization yet.
+The good precision of HERMES data shed light on new hadronization features, such as the behavior of K$^+$s, which have less attenuation than pions (see figure \ref{fig:her1}) but an excess on $\Delta \langle P_T^2 \rangle$.
+Must note that it is difficult to reproduce this behavior on models where only one hadronization stage is taken into account to explain all effects.
+Likewise, the different behavior of protons compared to anti-protons (see figure \ref{fig:her2}) is interesting and needs more precise analyses to unravel it since most of the existing models do not treat yet the baryons' hadronization.

### 2016-12-20 1-Answers-Review.tex
Add review questions and answer doc

\documentclass[12pt]{article}                                            
\usepackage {epsfig}
\textwidth  16.0cm
\textheight 21.5cm
\topmargin -1.0 cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\pagestyle{plain}
\headheight 0.3cm 
\usepackage[dvipsnames]{color}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{Myred}{named}{Red}
\pagestyle{plain}
\begin{titlepage}
\begin{flushright}
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~{\today}
\end{flushright}
\vskip 3.cm
\centerline{\bf \color{Myred}{M. Wood (chair), S. Manly, and A. Kim} }
\vskip 0.5cm
\centerline{\bf \LARGE \color{Myred}{Analysis Review of the :} }
\vskip 1.cm
\centerline{\bf \Large ``Study of the Hadronization}
\vskip 0.5cm
\centerline{\bf \Large of Charged Pions”''}
\vskip 0.5cm
\centerline {\bf  by R. Dupre et al.}
\vskip .5cm
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{titlepage}
\setcounter{page}{2}

The committee has reviewed the analysis note and has a number of comments that should be 
addressed.  It has been a long time since the data were taken, and it is an interesting study, so 
we encourage the authors to move forward with the improvements in order to bring it to 
publication.

This report is organized in 3 sections: lager issues to resolve, questions from the reviewers, and 
typographical corrections.  There may be some repetition between the 3 sections.  The notation 
is P\# for page \#.

\section{Larger Issues }
1.
Ownership of the pi+ channel.  This was brought up in an email from the committee chair 
(M. Wood).  Before this analysis can move on to round 2 of the review, the ownership issue 
has to be resolved.  The NPWG chair (also M. Wood) has left it up to the eg2 group to 
resolve it.

2.
The particle ID and cuts seem to be well understood.  The acceptance correction and 
radiative corrections need to be developed.  There is confusion about how the acceptance 
corrections were done (see Section 2 below).  The radiative corrections are incomplete as 
reported in the note.  Both corrections need to be well-understood before the committee can 
approve of the analysis.

3.
In the next version, line numbers need to be added to the document for easier reference.

\section{Reviewers’ Questions/Comments}
1.
P3, para 2- The discussion about the importance of this to neutrino experiments misses the 
main point.  In neutrino experiments, it is true that nuclei other than hydrogen are used to 
increase the event rate and to avoid explosions.  That means that nuclear effects come into 
play.  Fermi motion and final state interactions and correlations cause confusion in the 
extraction of the signal and reconstruction of the energy of the incoming neutrino.  This 
leads to less precise determination of the oscillation parameters.  The modeling of nuclear 
effects is necessary to understand and correct for these effects.  Pion production 
measurements like this provide ways to tune the models and look at the A dependence.  The 
A dependence is very important in part because in the long baseline experiments sometimes 
the near detector and far detectors are made of different materials.  In DUNE, for example, 
the far detector will be a liquid argon TPC.  It is not yet clear that a liquid argon TPC will 
work well as a near detector in such an intense neutrino beam.  Clearly you don’t want to 
say all this on page 3 of the paper.  But I think an additional sentence is warranted.

2.
P10 footnote: "single photon" could be confusing in this context, since the mean number of 
10 is from multiple optical photons (produced from a single electron).

3.
P13 - The number 0.03 - is it from the fit results of previous analysis note you mentioned in 
the first chapter? Or is it eyeball fit? If former you could add 1D histogram with fit results 
plotted to Figure 9?

4.
P16 - similarly, 1D fits for positive pion $\Delta\beta$?

5.
P16 - You state that the target position could vary from run to run, but “did not happen too 
often”.  Can you quantify this?

6.
P17, Fig 12 - what solid target is shown?  Are the shifts the same for electrons and pions?

7.
P18, Start of section 2.2.5 - I’m not sure I understand the logic in this.  If you have a drift 
chamber problem, it will be manifest in both the solid and liquid target data and the ratio of 
these should be relatively stable.  Why do you not determine run quality by looking at the 
event rate per coulomb of beam current?  For this quantity, a change in the detector 
operation will show up.

8.
P19, FIg. 14- Hard to tell how much data was discarded.  Maybe give a table of means and 
sigmas for each target or show the cuts on the figure are horizontal lines.

9.
P19 - If you use "c" constant in dimensions of Q2, then use it for W as well.

10.
P19, Sec. 2.3 - Show plots of Q$^2$, W and y with the cuts.

11.
P19, eq. 7 - Is it really just the sum of weights or are they the counts multiplied by the 
weights?

12.
P23, I’d be very worried about the MC modeling acceptance on falling edges like that at the 
right of the top right plot.

13.
P25, I find this discussion quite confusing.   At top you talk about two binnings.  It’s not just 
binning that is changing, right?  You are using different variables.  Then you talk about the 
extracted weight, but that weight is defined with only one of those sets of variables.  You 
also do it for the other set?  Then you an arbitrary weight cut to take care of the problems 
listed in the middle of the page?  Why not just increase the size of the bins in regions where 
you have too few events or large bin migration?  I don’t see how the procedure you use 
does not lead to holes in your data somehow.  And I don’t really understand what you are 
doing with the second weighting factor.  How is this not doing a double correction for 
acceptance, i.e., a double counting?  This whole section needs to be reworked.  I am fairly 
certain that I don’t really understand what you are doing but it leaves me worried that 
something is amiss.  Anyway, that’s not where you want readers to be.

14.
P26, bottom, if you have regions with very low acceptance, should they be cut out?

15.
P26 - "consistent with HERMES results" - could you add HERMES points to the plot with 
your data points to show what you mean as consistent?

16.
P27 fig.22-
 It's unclear to which point the error bar is associated. I think the common 
practice is to slightly shift markers horizontally.

17.
P27, Fig. 22 - the right column of plots is not the same as those in Fig. 15.  Why change the 
variables?

18.
P28 - What is Coulolmb Correction applied to? Momentum of charged particles? Could you 
plot effect of this correction on particles? Is it really big enough to be visible within our 
resolutions ?

19.
P30 - 
fig.24 is missing X axis label. You also may consider 2D histogram for better display.

20.
P31 - I don’t understand the isospin correction.  It does smooth out the data in Fig. 27; 
however, I am missing the physics motivation.  Why does it matter if the quark came from a 
proton or a neutron?  I think you just clarify the explanation.

21.
P33, Sec. 2.5.1 - list the negligible effects.

22.
P34, Fig. 28 - why is the resolution poorer than in Fig. 12?

23.
P34, why do you have a 1\% normalization error in all the multiplicity ratios when you say just 
above that for this particular sample with two particles in the final state the events in the test 
regions dropped to 0.01?  Doesn’t that mean the target contamination normalization error is 
smaller than 1\%?

24.
P34, with this technique of comparing results using the two different sets of variables (you 
call it two binnings, but I think that is sort of misleading), you are using the same events.  
Does this not mean you have a statistical contribution to this systematic error?  You say you 
noticed larger systematic errors for the pi- events due to lower acceptance and bigger 
weights.  Might it also be lower statistics and so you have statistical fluctuations contributing 
to the systematic error?  If so, you are sort of double-counting the statistical error and 
inflating the systematic error more than it should be.

25.
P35 - It would clarify the discussion with a summary or table of the point-to-point systematic 
errors.

26.
P35 -
 add plots with systematic uncertainty bands on it to demonstrate bin-by-bin values.

27.
P35, end of top paragraph, you say you don’t include the acceptance systematic, but it looks 
to me like it is included in Table 8?  What am I missing?

28.
P36, top paragraph, “that a factorization holds” means what??  Should explain.

29.
P36 top of section 3.1.1, 5% versus 5% looks more like 1 sigma rather than the 1.5 sigma 
you say in the text.

30.
P36, second paragraph of section 3.1.1, “... might be modified if the production time occurs 
inside the nucleus.”  I think I know what you mean but the language makes no sense.  You 
mean if the formation takes place inside the nucleus, right?

31.
P42, top, “... that is seen in our result.”  Where do I see what you are discussing in the top 
two lines of this page.  I could not find whatever it is.  What should I be looking at?

\section{Typographical Corrections}

Abstract L2, “... non-perturbative; therefore, only...”

P3, para 2:  “... models, including ones relevant for RHIC, because the size of the cold nuclei 
used in the JLab experiments is stable and known.”

P4, L1, “... the study of pion production over ...”

P4, L3, “... section 1.3, we provide a...”

P5, para 3, L3, “This kind of model is suitable...”

P6, L4, “... a suppression of hadron production ...and it can even reverse sign and increase at 
very low z.”

P6, bottom paragraph, line 3, “... excess in delta(pt)\^2.  It is notable that ... behavior in models 
... models do not yet treat baryon hadronization.”

P9, L6, “filled with liquid deuterium”

P9, para2, end of para, “... and detector properties cancel in the nuclear ratio.”

P10, L2, okay for a technical note but here the sentence should be rephrased to something like 
“For pions, we require a signal in the drift chambers (DC) and scintillator counters (SC) in 
addition to the successful reconstruction of the time-based tracking.”

P10, L10, “The derivation of these quantities is presented in section 2.3, while a list of 
corrections  is summarized in section 2.4.  The systematic uncertainty budget is detailed in 
section 2.5, and ...”

P10, just below equation 3, “ ... and the parameter b varies with momentum, as ...”

P13, L1 of section 2.2.2, sentence makes no sense as written. Do you mean something like, 
“Negatively charged pion candidates must not pass the electron selection criteria.”

P15, L2 of section 2.2.3 “... (see figure 11) due to a significant...”

P15 bottom, “These cuts minimize the kaon...”

P18, 6 lines from the bottom - “As Figure 14 ...”

P20, L1 of section 2.3.2 “... in figure 15 a few ...”

P21, L2, “... processed by CLAS software (GSIM, GPP and user\_ana) [what do these mean to a 
non-CLAS reader? supply references] to simulate the detector and the reconstruction process in 
a fashion similar to that done with the experimental data.”
Start of next paragraph, “The simulated data are processed like the experimental data by 
applying ...”  “ ... quite well the detector response, yet ...”

P22, bottom, “... space of our two-particle final state.  However, to evaluate the systematic 
errors associated with ...”

P33, 2 lines from bottom, “re-scattering on detector material”

P35, top of section 2.5.4, “... contributions from particle misidentification and acceptance ... 
effects, target misidentification and the isospin ...”

P36, second paragraph of section 3.1.1 -
 change conciliate to reconcile

P38, Para 3, L2, change signification to significance

P38, bottom, “However, our results (figure 32(left)) show no dependence besides ... and what is 
left will be washed ...”

P41, first paragraph, what does HERMES say about Q2 dependence?  Line 4, “... in figure 34, 
does not indicate ...”

P41, bottom paragraph, “... wide A coverage gives a outright indication ... found to be much 
smaller than that seen by HERMES [15], which ....from BDMPS [29] correlate pt\^2 with the 
nuclear radius.”

P42, top paragraph, last line, “colored parton does not interact with the whole nucleus which 
limits the nuclear effect.”

P42 second paragraph, L2, “they predict a rise of delta pt\^2 with Q\^2”
Same paragraph, L4, “... 38) gives a similar result.”
\end{document}

### 2017-01-03 1-Answers-Review.tex
Answer some comments!

@@
 
+{\it We are aware of this issue and we started regular meetings between the different 
+groups toward the objective of publishing as soon as possible results coherent with
+the different analysis performed on this topic (all three pions in particular). This
+will eventually translate into an addendum to this note with comparisons between Hayk's 
+and this analysis, which will be used to confirm the proper sizing of the systematic errors. 
+In a later stage an extra analysis note from Hayk will be submitted
+for the extraction of multi-dimensional results on pi+.} \\
+
 2.
@@
 
+{\it TODO when all questions are answered.} \\
+
 3.
 In the next version, line numbers need to be added to the document for easier reference.
+
+{\it Done.} \\
 
@@
 
+{\it Indeed the sentence about neutrino was a little too short. We moved it and added a 
+sentence to clarify the point.}\\
+
 2.
@@
 10 is from multiple optical photons (produced from a single electron).
+
+{\it The sentence was changed to clarify the statement.}\\
 
@@
 
+{\it The previous analysis from L. El Fassi et al. used $\pm 0.05$ ($\sim 3\sigma$), we decided
+to reduce this number to about $2\sigma$ because of the difference of observables. The 
+color transparency analysis was reconstructing the $\rho^0$ and implemented strong kinematical
+cut that reduced significantly possible contaminations. Our measurement uses all the 
+semi-inclusive production and is therefore more sensitive to contaminations. See next 
+question for profiles. (This paragraph is added to the note)}\\
+
 4.
 P16 - similarly, 1D fits for positive pion $\Delta\beta$?
+
+{\it As the positive particles show much more apparent contamination sources than negative 
+ones, we studied 
+the TOF profile much more thoroughly. You can see in figures~\ref{TOF-1}, \ref{TOF-2} and 
+\ref{TOF-3} the $\Delta \beta$ profiles for many momentum slices. In figure~\ref{TOF-1}
+one can see some contamination from lighter leptons ($e+$ and $\mu^+$). These represent
+a very small amount and one can see some justification for the choice of a $\pm 0.03$
+cut as these particles do not appear to be discernable beyond that level. Similarly
+in figure~\ref{TOF-2} one can see the contribution from kaons. The larger contribution
+of this contamination motivated the tightening of the TOF cut on this side, to the limit
+where kaons are a minority in the tail of the pion distribution. Finally a similar 
+method is applied for the even larger proton contamination as shown in figure \ref{TOF-3}.
+ (This paragraph and figures are added to the note)}\\
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
+\caption {$\Delta \beta$ of positively charged particles for low momentum slices 
+(GeV/c). The red lines shows the applied cuts to select positive pions. The bumps on the right
+correspond to muon and electron masses.}
+\label{TOF-1}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
+\caption {$\Delta \beta$ of positively charged particles for medium momentum slices 
+(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
+correspond to the kaon mass.}
+\label{TOF-2}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
+\caption {$\Delta \beta$ of positively charged particles for low momentum slices 
+(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
+correspond to the proton mass.}
+\label{TOF-3}
+\end{figure}
 

### 2017-01-03 chap5.tex
Answer some comments!

@@
 In the CC, the mean number of photo-electrons\footnote{Photo-electrons are 
-electrons produced in the front window of the Photo-Multiplier Tube (PMT) by a single photon.} from a high energy electron is expected to be around 10.
+electrons produced in the front window of the Photo-Multiplier Tube (PMT) by the Cerenkov photons.} from a high energy electron is expected to be around 10.
 However, hadrons can generate noise due to $\delta$ electrons produced in 
@@
 As we noticed there are not much negative kaons or anti-protons, we concluded that their contamination must be small (see section~\ref{SysId} for more detailed study).
+
+The previous analysis from L. El Fassi et al. used $\pm 0.05$ ($\sim 3\sigma$), we decided
+to reduce this number to about $2\sigma$ because of the difference of observables. The 
+color transparency analysis was reconstructing the $\rho^0$ and implemented strong kinematical
+cut that reduced significantly possible contaminations. Our measurement uses all the 
+semi-inclusive production and is therefore more sensitive to contaminations. See next 
+question for profiles.
 
@@
 \end{subequations}
+
+The much more apparent contamination sources than for negative pions, allow to study 
+the TOF profile much more thoroughly. You can see in figures~\ref{TOF-1}, \ref{TOF-2} and 
+\ref{TOF-3} the $\Delta \beta$ profiles for many momentum slices. In figure~\ref{TOF-1}
+one can see some contamination from lighter leptons ($e+$ and $\mu^+$). These represent
+a very small amount and one can see some justification for the choice of a $\pm 0.03$
+cut as these particles do not appear to be discernable beyond that level. Similarly
+in figure~\ref{TOF-2} one can see the contribution from kaons. The larger contribution
+of this contamination motivated the tightening of the TOF cut on this side, to the limit
+where kaons are a minority in the tail of the pion distribution. Finally a similar 
+method is applied for the even larger proton contamination as shown in figure \ref{TOF-3}.
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
+\caption {$\Delta \beta$ of positively charged particles for low momentum slices 
+(GeV/c). The red lines shows the applied cuts to select positive pions. The bumps on the right
+correspond to muon and electron masses.}
+\label{TOF-1}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
+\caption {$\Delta \beta$ of positively charged particles for medium momentum slices 
+(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
+correspond to the kaon mass.}
+\label{TOF-2}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
+\caption {$\Delta \beta$ of positively charged particles for low momentum slices 
+(GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left
+correspond to the proton mass.}
+\label{TOF-3}
+\end{figure}
 

### 2017-01-03 intro.tex
Answer some comments!

@@
 As the nuclear medium is hot and evolving in Relativistic Heavy Ion Collisions (RHIC), DIS experiments at JLab energies are well suited to test different theoretical models, including the RHIC's ones, because the size of cold nuclei is stable and known.
-A quantitative understanding of the hadronization process in nuclei is also an interesting theme for neutrino experiments that often use nuclei to maximize their cross sections.
-The hadronization can give an important information about nuclei through the quark energy loss, for example, Arleo's model~\cite{Arleo:2003yf} correlates the quark energy loss with a gluon density, and Kopeliovich et al.'s model~\cite{Kopeliovich:2010aa} correlates the $\Delta \langle P_T^2 \rangle$ with the saturation scale.
+The hadronization can give important information about nuclei through the quark energy loss, for example, Arleo's model~\cite{Arleo:2003yf} correlates the quark energy loss with a gluon density, and Kopeliovich et al.'s model~\cite{Kopeliovich:2010aa} correlates the $\Delta \langle P_T^2 \rangle$ with the saturation scale.
 Other models \cite{Gallmeister:2007an} utilize different assumptions to describe the pre-hadron evolution into a full hadron.
@@
 
-In order to constrain the existing models we extracted our results using a tight multi-dimensional binning.
-That was viable due to the high statistics of our EG2 data, which allowed the study of both pions production over a wide kinematic range.
+A quantitative understanding of the hadronization process in nuclei is also of importance for neutrino experiments.
+Indeed they use nuclear targets to maximize their cross sections and therefore have to account for the nuclear effects, including hadronization.
+
+In order to best constrain the models with our data, we extracted our results using tight multi-dimensional binning.
+That is possible because of the high statistics of our EG2 data, which allowed the study of both pions production over a wide kinematic range.
 

### 2017-01-04 1-Answers-Review.tex
More review answers

@@
 
+{\it We show in figures \ref{VertexSolid} and \ref{VertexLiquid} the evolution 
+of the position of the targets with run number. The data where the aluminum
+target is off by 1 cm has been excluded from the analysis. Other variations
+appear to be of a mm or less, while the gap between the solid and liquid target
+is about 5 cm. They should therefore have negligible contribution to the 
+error on acceptance corrections in regard to the error budget already associated
+to the procedure. (This paragraph and figures are added to the note)}\\
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7.5cm] {answer-fig/VertexC.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexAl.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexFe.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexSn.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexPb.png} 
+\caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
+number for the different solid targets.}
+\label{VertexSolid}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutC.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutFe.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutSn.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutPb.png} 
+\caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
+number for the deuterium target in different solid targets configurations.}
+\label{VertexLiquid}
+\end{figure}
+
 6.
 P17, Fig 12 - what solid target is shown?  Are the shifts the same for electrons and pions?
+
+{\it Sadly, this cannot be checked, the kumac used for this figure specify a file name that
+do not exist anymore (codes and files have been moved at some point and non essential files
+have been removed in the process). It is always possible to reproduce the figure with a root 
+file if the reviewer feel it is necessary.
+
+We provide here figure \ref{VertexEl} to better illustrate the result and figure 
+\ref{VertexPip} to show that the pions behave similarly.}\\
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7.5cm] {answer-fig/VertexElFe.png} 
+\caption {Vertex origin along $z$ (in cm) of electrons as a function of $\phi$ 
+for an iron run.}
+\label{VertexEl}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7.5cm] {answer-fig/VertexPipFe.png} 
+\caption {Vertex origin along $z$ (in cm) of positive pions as a function of $\phi$ 
+for an iron run.}
+\label{VertexPip}
+\end{figure}
 

### 2017-01-04 chap5.tex
More review answers

@@
 
-The position of our targets could also vary from a run to another, but this did not happen too often in this experiment.
+The position of our targets could also vary from a run to another, but this was not significant in this experiment.
 Indeed, except for aluminum, other targets remained in the same position within one or two millimeters.
 All targets' positions, in CLAS coordinates, are given in table \ref{tab:targets}.
+We show in figures \ref{VertexSolid} and \ref{VertexLiquid} the evolution 
+of the position of the targets with run number. The data where the aluminum
+target is off by 1 cm has been excluded from the analysis. Other variations
+appear to be of a mm or less, while the gap between the solid and liquid target
+is about 5 cm. They should therefore have negligible contribution to the 
+error on acceptance corrections in regard to the error budget already associated
+to the procedure.
 
@@
 
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7.5cm] {answer-fig/VertexC.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexAl.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexFe.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexSn.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexPb.png} 
+\caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
+number for the different solid targets.}
+\label{VertexSolid}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutC.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutFe.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutSn.png} 
+\includegraphics[width=7.5cm] {answer-fig/VertexDeutPb.png} 
+\caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
+number for the deuterium target in different solid targets configurations.}
+\label{VertexLiquid}
+\end{figure}
+
+The detected electrons are associated with the solid target if their vertex 
+position is less than 1.5~cm ($\sim$3~$\sigma$) from the values shown on table 
+\ref{tab:targets}.
+For the liquid target, the cut is a bit larger, 2 cm, in order to count for the cryogenic target's size (see figure \ref{vertex}).
+The pions' vertex was checked against the electron one and was imposed to satisfy this additional condition $| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).
+
 \begin{figure}[p]
@@
 \end{figure}
-
-The detected electrons are associated with the solid target if their vertex 
-position is less than 1.5~cm ($\sim$3~$\sigma$) from the values shown on table 
-\ref{tab:targets}.
-For the liquid target, the cut is a bit larger, 2 cm, in order to count for the cryogenic target's size (see figure \ref{vertex}).
-The pions' vertex was checked against the electron one and was imposed to satisfy this additional condition $| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).
 

### 2017-01-05 1-Answers-Review.tex
More questions answered...

@@
 have been removed in the process). It is always possible to reproduce the figure with a root 
-file if the reviewer feel it is necessary.
+routine if the reviewer feel it is necessary.
 
@@
 
+{\it You are right, the motivation for this cut is not stated properly. We are looking 
+at the ratio because it would affect our result, while ignoring issues that would not
+affect our observable. It is important to note that the initial run list was already
+cleaned from known detector failures. (The text is corrected in the note.) }
+
 8.
@@
 
+{\it The quantity of data removed is difficult to assess, since the problematic runs were
+not passed through the final analysis. We were unable to recover the orginal values of the
+fits for these specific figures and we 
+lack the problematic run which have been deleted. At this stage, we do not deem necessary
+to pull these old discarded data and reactivate the associated codes. If the reviewer
+think it is necessary, it is time consuming but of course possible.}
+
 9.
 P19 - If you use "c" constant in dimensions of Q2, then use it for W as well.
+
+{\it Corrected.} \\
 
@@
 
+{\it Figures \ref{DISKine} illustrates the request and have been added to the note.} \\
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=5cm] {answer-fig/DIS-Q2.png} 
+\includegraphics[width=5cm] {answer-fig/DIS-w.png} 
+\includegraphics[width=5cm] {answer-fig/DIS-y.png} 
+\caption {Inclusive distributions after DIS selection cuts for a sample of the iron
+data.}
+\label{DISKine}
+\end{figure}
+
 11.
@@
 weights?
+
+{\it They are indeed the counts multiplied by the weights, which is mathematically equivalent.
+The sum indicated runs over all the recorded events, it is not associated to the weights
+bins or anything like that. To be implemented!!!!} \\
 

### 2017-01-05 chap5.tex
More questions answered...

@@
 of data, but they were much smaller in case of problems.}, we monitored the ratio of scattered electrons yields obtained from solid and liquid targets.
-In case of the beam hitting other materials in the beam-line or any detector is not working
-properly, this ratio will be off and indicates problematic runs. A figure 
+In case of the beam hitting other materials in the beam-line or of ony other problem that would affect our final result,
+this ratio will be off and indicate the problematic runs. A figure 
 \ref{DataQ} shows electrons yields' ratios for different nuclear target; we fitted these ratios to extract the mean value for each target, then we discarded runs that were 5~$\sigma$ away from the appropriate mean.
@@
 Since we are interested in deep inelastic scattering, we use the following 
-cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV.
+cuts: $Q^2 > 1$~GeV$^2$/c$^2$ and $W > 2$~GeV/c$^2$, with the inclusive distributions
+after these cuts shown in figure \ref{DISKine}.
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=5cm] {answer-fig/DIS-Q2.png} 
+\includegraphics[width=5cm] {answer-fig/DIS-w.png} 
+\includegraphics[width=5cm] {answer-fig/DIS-y.png} 
+\caption {Inclusive distributions after DIS selection cuts for a sample of the iron
+data.}
+\label{DISKine}
+\end{figure}
+
 We also apply a cut on the energy transferred fraction, $y = \nu/E_{beam} < 0.85$.

### 2017-01-06 1-Answers-Review.tex
More questions answered!

@@
 
-{\it They are indeed the counts multiplied by the weights, which is mathematically equivalent.
-The sum indicated runs over all the recorded events, it is not associated to the weights
-bins or anything like that. To be implemented!!!!} \\
+{\it They are indeed the counts multiplied by the weights.
+The sum indicated runs over all the recorded events, it is not associated to the weight
+bins or anything like that. We tried to adapt the language in the note to make it clearer.} \\
 
@@
 right of the top right plot.
+
+{\it It is indeed an important issue. A related fact to keep in mind (while it is presented 
+later in the note in 2.5.1) is that the main issue there is the quantity of accidentals. Since
+the cross section get really small in this region, accidentals start to overcome
+the signal. We apply a cut
+$p_\perp^2 < 2.5$ GeV$^2$/c$^2$ to remove these regions. One could advocate to even lower this 
+cut, but it would affect significantly the outcome of the $\Delta P_\perp^2$, 
+because as often with averages the outliers have a strong impact.
+
+On the bright side, the slope and behavior appear to be rather well described by the MC
+simulation. We feel that a good reproduction of the data is an indication that the 
+acceptance correction will behave properly.} \\
 
@@
 
+{ \it The section has been reworked to clarify what we are doing. Few points you raised 
+are also answered here:
+
+The first set of variables is the one actually used for the
+analysis and the second set is only used to evaluate the systematic errors, so in the 
+note, the formulas are given only for the first set.
+
+The motivation for using such a weight cut based on the product of different unrelated
+values is actually directly linked to the inbent 
+particles being directed in the beam pipe. The $\pi^-$ acceptance drops very 
+strongly at low $p_\perp^2$ leading to very high weights, however there is no problem of 
+bin migration
+or low statistics because the generated yield is very high in this region. We found that 
+the best way
+to keep these bins while discarding bins where the weight might be slightly smaller but with 
+issues concerning bin migration and statistics was to apply this type of cut.
+
+In term of method, the two
+step acceptance correction is hopefully going to be clearer. It is the same as the method used 
+in the previous L. El Fassi et al. analysis note. The second step of the procedure is
+specifically used to take care of the holes in the acceptance (note, they are not really 
+holes because problematic bins are generally on the edges). You can see that the weights
+of the previously calculated acceptance are used in this step, ensuring that we do not
+double correct the data.
+
+The size of the bins is not constant and is indeed increased in region with small event yield.
+However, the multi dimensional binning cannot be fully adapted in a general maner. On this
+topic we added in annex tables indicating the bin limits that we used.} \\
+
 14.
 P26, bottom, if you have regions with very low acceptance, should they be cut out?
+
+{\it In the case of the $\Delta P_\perp^2$, we need to measure an average of the
+transverse momentum distribution. Completely cutting a part of the distribution
+would indeed solve the acceptance problem but would make the $\langle p_\perp^2 \rangle$
+measurement meaning less. We therefore have to live with it and do our best to
+reconstruct the whole distribution even if it means having larger error bars.} \\
 
@@
 your data points to show what you mean as consistent?
+
+{\it To look at } \\
 
@@
 
+{\it Sorry, we overlooked this for these intermediary plots. TO BE CORRECTED} \\
+
 17.
@@
 variables?
+
+{\it Sorry, it is a mistake on our part, there is absolutely no reason. TO BE CORRECTED} \\
 
@@
 P34, Fig. 28 - why is the resolution poorer than in Fig. 12?
+
+{\it Resolution is the same, it looks wider because on this figure, we show the integrated 
+result over the 6 sectors. } \\
 
@@
 29.
-P36 top of section 3.1.1, 5% versus 5% looks more like 1 sigma rather than the 1.5 sigma 
+P36 top of section 3.1.1, 5\% versus 5\% looks more like 1 sigma rather than the 1.5 sigma 
 you say in the text.

### 2017-01-06 chap5.tex
More questions answered!

@@
 
-However, the implementation of acceptance and radiative corrections is done through some given weights to each event based on its kinematics. The multiplicity ratio then becomes
+However, the implementation of acceptance and radiative corrections is done through weights associated to each event based on its kinematics. The multiplicity ratio then becomes
 \begin{equation}
@@
 \end{equation}
-where $\omega$ is the weight associated with the event, and the sums run over all measured particles. The expression of the transverse momentum broadening remains as
+where the sums run over all the events and $\omega$ is the weight associated with the event. The expression of the transverse momentum broadening remains as
 \begin{equation}
@@
 
-Thus, new expressions of the weighted statistical uncertainties are: 
+Thus, new expressions of the weighted statistical uncertainties are derived: 
 \begin{equation}
@@
 
-Experimental data were corrected using the weights defined as $\omega = 1/\text{Acc}$.
-These coefficients are calculated in many bins, in order to be independent of the imperfections of our event generator.
-However, an excess of bins could lead to a strong bin migration\footnote{Fraction of events not reconstructed in the bin they were produced in.}, which might introduce a bias in case it becomes quite large.
+Experimental data were corrected using the weights defined as $\omega = 1/\text{Acc}$. These 
+coefficients are calculated in many bins, in order to be independent of the imperfections of 
+our event generator. However, an excess of bins could lead to a large bin 
+migration\footnote{Fraction of events not reconstructed in the bin they were produced in.}, 
+which introduces a bias in the evaluation of acceptance. Bin sizes are therefore chosen to
+be larger than the resolution associated to each kinematic variable.
 
-We used a 4-dimensional binning to divide the large phase space of our two particles' final state.
-However, to evaluate the associated systematic errors with this correction, we used the two different binning presented in table~\ref{tab:AcceptBinning}.
-The total number of bins is constrained by the amount of generated data, and must be maintained reasonably low in order to keep a good statistical precision and a manageable bin migration.
+We used a 4-dimensional binning to divide the large phase space of our two particles' final 
+state. To evaluate systematic errors associated with this correction, we compared the
+method using two different sets of kinematic variables, as presented in 
+table~\ref{tab:AcceptBinning}. The first set of variables is the one actually used for the
+analysis and the second set is only used to evaluate the systematic errors, so in the 
+following, the formulas are given only for the first set. The total number of bins is 
+constrained by the amount of generated data and must be maintained reasonably low in order 
+to keep a good statistical precision and a small bin migration.
 
@@
 
-The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are then extracted from 
-the simulation using equation \ref{eq:acc}. However, it turned out that these coefficients should not be applied to data before resolving the issue of the problematic bins that have either
+The weights ($\omega_{\pi^\pm}(\nu,x_{Bj},p_h,t)$) are extracted from 
+the simulation using equation \ref{eq:acc}. However, these coefficients should not be applied to data before resolving the issues with bins that have either
 \begin{itemize}
  \item too large weight values, i.e., very small acceptance, or
- \item very few reconstructed events leading to large statistical errors, or
- \item a large fraction of events originally generated in an other bin (bin migration issue).
+ \item very few reconstructed events and very large statistical errors, or
+ \item a large fraction of events originally generated in another bin (bin migration issue).
 \end{itemize}
@@
 proportion of reconstructed events initially generated in an other kinematical bin. 
-Figure \ref{fig:AccCoef} shows $\omega$ distributions after applying these cuts.
-Around 900 bins remain for both targets, but we noticed that these weights are much larger for $\pi^-$ compared to $\pi^+$, as an indication of a larger correction for the inbent particles.
-In order to maximize the acceptance and reduce the sensitivity to our arbitrary weights' cuts, we corrected the data with an additional two dimensional reweighting factor as:
+Figure~\ref{fig:AccCoef} shows $\omega$ distributions after applying these cuts. Around 
+900 bins remain for both targets, but we noticed that these weights are much larger for 
+$\pi^-$ compared to $\pi^+$, as an indication of a larger correction for the inbent 
+particles. The motivation for using such a cut based on the product of different unrelated
+values is actually directly linked to this problem. The $\pi^-$ acceptance drops very 
+strongly at low \pt leading to very high weights, however there is no problem of bin migration
+or low statistics because the generated yield is very high in this region. We found that 
+the best way
+to keep these bins while discarding bins where the weight might be slightly smaller but which 
+have issues with bin migration and statistics was to apply this set of cuts.
+
+In order to correct for these droped bins and reduce the sensitivity to the arbitrary in
+the choice of the weights' cuts, we corrected the data with an additional two dimensional 
+reweighting factor as:
 \begin{equation}
@@
 \end{equation}
-where $\omega$ is the previously calculated weight of either one remaining bin or a bin that was excluded by the cuts. One of the criteria for setting the limits in equation \ref{eq:AccL1} and 
-\ref{eq:AccL2} is to keep reweighting factors, $\omega_2 = 1/\text{Acc}_2$, at the level of a few percents.
+where $\omega$ is the previously calculated weight or a 1 for a bin that was excluded by the 
+cuts of equation \ref{eq:AccL1} and \ref{eq:AccL2}. One of the criteria for setting the limits 
+in these equation is in fact to keep this reweighting factors, $\omega_2 = 1/\text{Acc}_2$, at 
+the level of a few percents. This indicates that the previous method only missed a small 
+fraction of the event in the first place and is a good indication of the sanity of the method.
 

### 2017-01-10 1-Answers-Review.tex
Two more answers

@@
 
+{\it We would like to thank you for the thorough review and hope you will be satisfied with
+our answers.} \\
+
 This report is organized in 3 sections: lager issues to resolve, questions from the reviewers, and 
@@
 is P\# for page \#.
+
+{\it The answers from the authors of the note are all presented in italic script 
+to allow a clear distinction.} \\
 
@@
 However, the multi dimensional binning cannot be fully adapted in a general maner. On this
-topic we added in annex tables indicating the bin limits that we used.} \\
+topic we added tables in the note indicating the bin limits that we used.} \\
 
@@
 
-{\it To look at } \\
+{\it This sentence states that similarly to HERMES, we find that both charged pions have similar
+transverse momentum. This can be seen in the Figure 4 of the note where we show the result from 
+HERMES. We did not want to mislead the reader into any claim about compatibility between 
+HERMES and CLAS data here, so we reworded the sentence. We want to point out that such claim 
+would be highly model dependent since it is expected that the effect varies with energy. } \\
 
@@
 
-{\it Sorry, it is a mistake on our part, there is absolutely no reason. TO BE CORRECTED} \\
+{\it Sorry, it is a mistake on our part, there is no reason. TO BE CORRECTED. And
+add figures after radiative correction!} \\
 
@@
 
+{\it The Coulomb correction is applied to incoming and outgoing electrons as well as
+produced charged pions. Indeed the effect is invisible in most of the phase space as
+it is comparable to the resolution of the detector (points overlap completely). The 
+effect is small but visible only for very low $z$ pions. It has been implemented 
+because it was suggested it might be big, but we now find that can be neglected 
+at our kinematics. ADD a FIGURE???} \\
+
 19.
@@
 fig.24 is missing X axis label. You also may consider 2D histogram for better display.
+
+{\it FIGURE TO BE REPLACED COMPLETELY} \\
 
@@
 
+{\it This correction is here to take care of the u/d quark imbalance in heavier nuclei.
+Indeed the production rate of positive pions on neutrons is significantly reduced and that
+should not be mistaken with absorbtion in the nuclear medium. We clarified the text in the
+note, hopefully it is now clear.} \\
+
 21.
 P33, Sec. 2.5.1 - list the negligible effects.
+
+{\it The sentence has been revised to list all effects tested. } \\
 
@@
 {\it Resolution is the same, it looks wider because on this figure, we show the integrated 
-result over the 6 sectors. } \\
+result over the 6 sectors.} \\
 
@@
 smaller than 1\%?
+
+{\it Multiplicity ratios are a double ratio. The claim is that the semi inclusive part 
+is not affected, but the inclusive electron ratio is affected. This is included
+as a normalisation error. We revisited slightly the paragraph to make it clearer.} \\
 

### 2017-01-10 chap5.tex
Two more answers

@@
 method using two different sets of kinematic variables, as presented in 
-table~\ref{tab:AcceptBinning}. The first set of variables is the one actually used for the
+table~\ref{tab:AcceptBinning} and \ref{tab:AcceptBins}. The first set of variables is the one actually used for the
 analysis and the second set is only used to evaluate the systematic errors, so in the 
@@
   \label{tab:AcceptBinning}
+\end{table}
+
+\begin{table}[htbp]
+\center
+\begin{tabular} {|l|c|c|c|c|}
+\hline
+ $\nu$ & \xb & $p_\pi$ & $-t$ \\ \hline
+ 2.20 & 0.12 & 0.25 &-3.50 \\ 
+ 3.00 & 0.18 & 0.60 &-2.10 \\ 
+ 3.40 & 0.22 & 1.00 &-1.75 \\ 
+ 3.75 & 0.27 & 1.45 &-1.50 \\ 
+ 4.00 & 0.33 & 1.70 &-1.30 \\ 
+ 4.25 & 0.60 & 2.15 &-1.10 \\ 
+      &      & 3.00 &-0.75 \\ 
+      &      & 4.25 &-0.00 \\ \hline
+\end{tabular}
+\quad
+\begin{tabular} {|l|c|c|c|c|}
+\hline
+ $Q^2$ & $\nu$ & $z$ & $-t$ \\ \hline
+ 1.00 & 2.20 & 0.00 & -3.50 \\
+ 1.20 & 3.00 & 0.20 & -2.10 \\
+ 1.40 & 3.40 & 0.40 & -1.75 \\
+ 1.65 & 3.75 & 0.45 & -1.50 \\
+ 2.10 & 4.00 & 0.52 & -1.30 \\
+ 4.00 & 4.25 & 0.62 & -1.10 \\
+      &      & 0.80 & -0.75 \\
+      &      & 1.00 & -0.00 \\ \hline
+\end{tabular}
+\caption{Bin limits used for the acceptance correction described in table \ref{tab:AcceptBinning}.}
+  \label{tab:AcceptBins}
 \end{table}
@@
 The large spread in weights makes the errors on \dpt very large, and the related results difficult to exploit.
-However, our transverse momentum broadening results of both pions matched each other after this correction, which is consistent
-with HERMES results.
+However, our transverse momentum broadening
+results of both pions matched each other after this correction, which is similar 
+to the HERMES results (see figure~\ref{fig:her3}).
 
@@
 
-The important excess of neutrons in heavy nuclei leads to a modification of both $\pi$ multiplicities on DIS events. Using Hall~C results 
-\cite{Asaturyan:2011mq}, shown in figure \ref{fig:IsoSpin}, we evaluated the correction factors for this effect. Our simple estimation is solely based on 
-proton and neutron numbers that gave $\pi^+$s results shown in table~\ref{tab:isospin}.
-As the effect on $\pi^-$s was found to be consistent with zero, no correction was applied to their multiplicity ratios.
-We attribute a 10\% normalization error to the effect of the isospin correction on our results.
-It is relatively chosen based on the precision of the Hall~C measurement, and the limited phase space coverage of Hall-C data compared to ours.
+The important excess of neutrons in heavy nuclei leads to a modification of 
+both $\pi$ multiplicities regardless of nuclear effects. Using Hall~C results 
+\cite{Asaturyan:2011mq}, shown in figure \ref{fig:IsoSpin}, we evaluated the 
+correction factors for the imbalance of u/d quarks in heavy nuclei compared
+to deuterium. Our simple estimation is solely based on proton and neutron 
+numbers and assumes that this isospin correction does not depend on any
+kinematic variable. We found that multiplicity ratios of $\pi^+$ need small
+corrections, shown in table~\ref{tab:isospin}. The effect on $\pi^-$s was 
+found to be consistent with zero, so no correction was applied to their 
+multiplicity ratios. We attribute a normalization error to the finale results
+equal to 10\% of the isospin correction. This is evaluated based on the 
+precision of the Hall~C measurement.
 
@@
 
-It is important to mention that the isospin correction is applied only to rates, which means applied only to $\pi^+$s multiplicity ratios.
-The transverse momentum broadening could, in principle, be affected, however, the results from \cite{Asaturyan:2011mq} showed no isospin effects in \ptp.
-Therefore, we are confident that our \dpt results should not be sensitive to any isospin effects.
+It is important to mention that the isospin correction is only relevant to 
+rate measurements. The transverse momentum broadening could, in principle, 
+be affected, however, the results from \cite{Asaturyan:2011mq} showed no 
+isospin effects in \ptp. Therefore, we are confident that our \dpt results 
+should not be sensitive to any isospin effects.
 
-We finally note that the $A$ dependence of multiplicity ratios of both charged pions became parallel after the isospin correction\footnote{Within 
+We finally note that the $A$ dependence of multiplicity ratios of both 
+charged pions became parallel after the isospin correction\footnote{Within 
 normalization errors presented in section \ref{sec:TotSys}} (see figure 
 \ref{fig:IsoPlot}). Considering previous measurements and existing models, 
-this result was expected and demonstrated the importance of this correction.
+this result was expected and demonstrates the importance of this correction.
 
@@
 \centering
-\includegraphics[width=8cm] {chap5-fig/c_RvA.png}
-\caption {Multiplicity ratios as a function of $A^{1/3}$ 
-with only the isospin correction applied.}
+\includegraphics[width=8.5cm] {chap5-fig/c_RvA.png}
+\caption {Multiplicity ratios as a function of $A^{1/3}$ with the isospin correction applied.}
 \label{fig:IsoPlot}
@@
 
-  - particles' re-scattering in different detectors,
+  - particles' scattering in different detectors,
 
@@
 
-To evaluate those errors, we are comparing the kinematics of reconstructed particles with the generated ones.
-Each reconstructed particle is associated with its generated parent if both particles have a similar momentum and angle coverage.
-However, the precision of the measured kinematical distribution $\Delta p$, $\Delta \theta$ and $\Delta \phi$ were determined as $\Delta x = {\sum_n |x_{gen} - x_{rec}| \over n}$, where $n$ is the kinematical bin number.
-Using the same simulation as for the acceptance, we found ${\delta p \over p } = 0.03$, $\delta \theta = 3$ mrad and $\delta \phi = 10$~mrad.
-Nevertheless of being much larger than the nominal CLAS resolutions published in \cite{Mecking:2003zu}, they are still reasonable for our measurement.
-Although, we evaluated the systematic errors associated with other variables\footnote{These values were evaluated for a typical kinematics range.
-However, the results can be much larger at extreme kinematics (large \pt or Q$^2$).}, such as $\delta Q^2 \sim 0.013$ GeV$^2$/c$^2$, $\delta z \sim 0.4 \%$, and $\delta P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$.
-These errors are overall negligible since they are several times smaller than our usual bin sizes (see figures in a section \ref{prelim}).
+To evaluate these errors, we are comparing the kinematics of reconstructed 
+particles with the generated ones. Each reconstructed particle is associated 
+with its generated parent if both particles have a similar momentum and 
+angle. The precision of the measured kinematical distribution 
+$\Delta p$, $\Delta \theta$ and $\Delta \phi$ were determined as $\Delta x = 
+{\sum_n |x_{gen} - x_{rec}| \over n}$. Using the same simulation as for 
+the acceptance, we found 
+${\delta p \over p } = 0.03$, $\delta \theta = 3$ mrad and $\delta \phi = 
+10$~mrad. While being larger than the nominal CLAS resolutions published in 
+\cite{Mecking:2003zu}, they are still reasonable for our measurement. We also 
+evaluated these errors in term of other variables, such as 
+$\delta Q^2 \sim 0.013$ GeV$^2$/c$^2$, $\delta z \sim 0.4 \%$ and $\delta 
+P_\perp^2 \sim 0.004$ GeV$^2$/c$^2$ (\footnote{These values are evaluated for 
+a typical kinematics range. The results can be larger at extreme kinematics 
+(large \pt or Q$^2$).}). These errors are overall negligible since they are 
+several times smaller than our usual bin sizes (see figures in a section 
+\ref{prelim}).
 
-We also evaluated the particles' misidentification and the re-scattering effect in different detectors or coils. The misidentification usually leads to a high 
-contamination on the kinematical distributions tails, which is manifested most in our case on the tail of the \pt distribution.
-This effect is due to a low probability to produce high \pt events, therefore the contribution from the accidental background is relatively increased.
-As a consequence, we used the following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which basically discarded only a very little amount of data (about one $\pi$ from 30000 pions).
-The misidentification of electrons was found to be too small in the order of $1\,e^-$ each 1000 events, hence does not contribute significantly to this uncertainty.
-For pions, the main contamination comes from kaons with momenta above 2~GeV/c ($\sim$ 3\% for $\pi^+$s and $\sim$ 0.5\% for $\pi^-$s).
-Protons also contaminates a $\pi^+$ sample at high momenta (up to a few \%).
-%TODO Justify the pt cut with a figure?
+We also evaluated the particles' misidentification and scattering on materials
+from the detectors or coils. For this study, we are looking at reconstructed 
+particles that do not have a clear parent (either because they are misidentified
+or because they scattered and their kinematic changed significantly). The 
+misidentification of electrons was found to be small, of the order of 1 in 
+1000 $e^-$ in all the kinematic space, hence this issue does not contribute 
+significantly to this uncertainty. We found however for pions
+a high proportion of accidental events on the kinematical distributions tails, 
+in particular of the \pt distribution. This effect is due to the low 
+probability to produce high \pt events, leading to an increased relative 
+contribution from the accidental background. As a consequence, we used the 
+following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which discards only a very 
+little amount of data (about 1 in 30000 $\pi$). On the contamination side,
+most events come from kaons with momenta above 2~GeV/c ($\sim$ 3\% for 
+$\pi^+$s and $\sim$ 0.5\% for $\pi^-$s). Protons also contaminate the 
+$\pi^+$ sample but only for the highest momenta (up to a few \%).
 
-In conclusion, the uncertainty related to particles' misidentification is taken into account in the point-to-point systematic errors by assuming a 100\% contamination level.
-Other effects were found negligible.
+In conclusion, the uncertainty related to particles' misidentification is 
+taken into account with the attribution of a point-to-point systematic 
+error equal to 100\% of the contamination level. The accidentals are taken 
+care of using a cut on the high \pt distribution. Finally, resolution effects
+were found to be negligible.
 
@@
 
-Because of some reconstruction errors or a re-scattering on detectors' materials, it 
+Because of reconstruction errors or scattering on detectors' material, it 
 is possible to associate a particle with the wrong target. To estimate this 
-effect, we looked, in the experimental data, at the number of reconstructed events upstream and downstream our targets, where nothing should be detected.
-Thus, we defined two test regions (see figure \ref{fig:targetleak}) to evaluate a targets' contamination.
-The upstream region, named as a test region 1, was given the size of the solid target's selection cut to evaluate the contamination from the liquid target.
-However, the downstream region, named as a test region 2, covered the same size of the liquid target's selection cut to estimate the leak from the solid target.
-The distance between detection and test regions is identical to the
-distance between the two targets' detection regions.
+effect, we looked, in the experimental data, at the number of reconstructed 
+events upstream and downstream of our targets, where nothing should be 
+detected. Thus, we defined two test regions (see figure \ref{fig:targetleak}) 
+to evaluate the associated contamination between the targets. The upstream 
+region, named test region 1, is of the size of the solid target's selection 
+cut to evaluate the contamination from the liquid target. The downstream region, 
+named test region 2, covers the same size of the liquid target's selection cut 
+to estimate the leak from the solid target. The distance between detection and 
+test regions is identical to the distance between the two targets' detection 
+regions.
 
 We found that the number of electrons in the test region 1 and 2 represents, 
-respectively, 1 and 2\% of the total number of events.
-However, in the case of semi-inclusive measurements, where we request two particles in the final state, this number drastically dropped, and became in the order of 0.01\%.
-In conclusion, only the number of electrons is significantly affected by a target's contamination issue, which leads to a normalization error of 1\% in all multiplicity ratios.
+respectively, 1 and 2\% of the total number of events. However, in the case 
+of semi-inclusive measurements, where we request two particles coming from the
+same spot in the final state, this number drastically dropped to $\sim$0.01\%. 
+Therefore, only the number of electrons is significantly affected by the 
+target's contamination issue, which is an issue only for multiplicity ratios.
+We associate a normalization error of 1\% to all multiplicity ratios to account
+with this issue.
 

### 2017-01-12 1-Answers-Review.tex
Continue review questions, start English corrections

@@
 
+{\it This is an interesting question and we might have overlooked this problem. WE
+NEED TO THINK ABOUT THAT. } \\
+
 25.
@@
 errors.
+
+{\it The point-to-point errors include only contributions from the bad particle 
+identifications and acceptance effects. It is also different for every bin, so
+we did not think a table would be useful to summarize only two contributions.} \\
 
@@
 
+{\it FIGURES NEED TO BE UPDATED WITH NEW ERROR BAR DISPLAY.} \\
+
 27.
@@
 
+{\it We decided to keep the normalization error, not the point to point. This was not
+said clearly in the text, it is now clarified. TO CLARIFY WHEN SORTED OUT.} \\
+
 28.
 P36, top paragraph, “that a factorization holds” means what??  Should explain.
+
+{\it This sentence has been reformulated with an additional reference.} \\
 
@@
 you say in the text.
+
+{\it The reson we quote 1.5, is that one need to move $\pi^+$ one sigma down and $\pi^-$ one
+sigma up. So for the overall normal deviation (sigma) we quadratically sum them,
+leading to 1.5.} \\
 
@@
 
+{\it This langage refers to figure 1, where we define a production time and a 
+formation time. We tried to rephrase for more clarity.}\\
+
 31.
@@
 two lines of this page.  I could not find whatever it is.  What should I be looking at?
+
+{\it The phrasing was incorrect, hopefully the new version is better. We will work with 
+the authors of the models to add some projections to our figures. This should eventually
+make all these physics comments much clearer.} \\
 
@@
 P10, just below equation 3, “ ... and the parameter b varies with momentum, as ...”
+
+{\it Done to this point. Need full reread after that!} \\
 

### 2017-01-12 chap5.tex
Continue review questions, start English corrections

@@
 collected in the beginning of 2004 during the third phase ({\it eg2c}), for 
-which the beam energy was 5.014~GeV\footnote{The other phases of the run gave only small amounts of data at beam energies of 4 and 4.7~GeV. Thus, we decided to not use them in this analysis.}.
-
-As the two married experiments aimed at comparing deuterium with heavy nuclei, it was decided to use a double target system~\cite{Hakobyan:2008zz}.
-The first target was filled with a liquid deuterium, and the second was a solid target.
-The latter was made of either carbon, aluminum, iron, tin or lead, and was changed remotely (see figure~\ref{fig:phototarget}).
-The two targets were separated by only 4~cm in order to minimize the difference on CLAS acceptance between them.
-The advantage of having two targets mounted simultaneously on the beam line is that several systematic effects related to the beam and detector's properties will cancel in the nuclear ratio.
+which the beam energy was 5.014~GeV\footnote{The other phases of the run 
+gave only small amounts of data at beam energies of 4 and 4.7~GeV. Thus, we 
+decided to not use them in this analysis.}.
+
+As the two experiments aimed at comparing deuterium with heavy nuclei, it was 
+decided to use a double target system~\cite{Hakobyan:2008zz}. The first target 
+was filled with liquid deuterium, and the second was a solid target. The 
+latter was made of either carbon, aluminum, iron, tin or lead, and was changed 
+remotely (see figure~\ref{fig:phototarget}). The two targets were separated by 
+only 4~cm in order to minimize the difference on CLAS acceptance between them. 
+The advantage of having two targets mounted simultaneously on the beam line is 
+that several systematic effects related to the beam and detector properties 
+cancel in the nuclear ratio.
 
@@
 target determination method. The pion identification cuts are, however, tightened
-in this analysis as we have less constraints on the kinematics to exclude any possible pions' contamination.
+in this analysis as we have less constraints on the kinematics to exclude any possible pion contamination.
 
 In the section \ref{sec:pid}, we identify the following particles, e$^-$, 
-$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs.
-For pions, we require a positive status of drift chambers (DC) and scintillator counters (SC) local signals, in addition to the global status reconstructed with the time-based tracking correction.
-For electron identification, we use good signals from
-all detectors, DC, Cherenkov Counters (CC), SC and the Electromagnetic 
+$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs. For pions, we require a signal in the drift chambers (DC) and scintillator counters (SC) in 
+addition to the successful reconstruction of the time-based tracking. For electron 
+identification, we use the same standards but requesting a good signal from 
+all detectors, DC, Cherenkov Counters (CC), SC and Electromagnetic 
 Calorimeter (EC).
 
-Once all particles are identified, we extract our two observables, multiplicity 
-ratios and the transverse momentum broadening.
-Their derivation method is presented in the section \ref{sec:obs}, while a list of our corrections is summarized in the section \ref{sec:corrections}.
-The budget of our systematical uncertainties is detailed in the section \ref{sec:TotSys}, and the final analysis results are presented and discussed in the next chapter.
+Once all particles are identified, we extract our two observables, 
+multiplicity ratios and the transverse momentum broadening. The derivation 
+of these quantities is presented in section \ref{sec:obs}, while a list of 
+corrections  is summarized in section \ref{sec:corrections}. The systematic 
+uncertainty budget is detailed in section \ref{sec:TotSys}, and the final 
+analysis results are presented and discussed in the next chapter.
 
@@
 where $\mu = 0.271$ is the mean of the total energy fraction deposited in the 
-calorimeter, the parameter $a$ is set to 0.5, and the parameter 
-$b$ varies with momenta, as shown in table \ref{tab:ecoutin-par}. The derivation of $b$ was motivated by the non-linear momentum dependence of the energy 
+calorimeter, the parameter $a$ is set to 0.5 and the parameter 
+$b$ varies with momentum, as shown in table \ref{tab:ecoutin-par}. The derivation of $b$ was motivated by the non-linear momentum dependence of the energy 
 deposited on both EC regions (see figure \ref{eleEC}). As pions are 
@@
 
-After testing several different acceptance correction methods, we finally converged with the one using the two different binning presented on a table \ref{tab:AcceptBinning}.
-The difference between these methods gave us an idea about the systematic error associated with this correction.
-Using our results on iron, we found the relative uncertainties presented in a table~\ref{tab:SysAcc}.
-We noticed the significantly large errors for $\pi^-$s, which were expected, due to their low acceptance and larger weights.
-Although, systematical errors are considerably large on \dpt measurements.
-This is mainly due to the nature of the \dpt observable; as a difference, it would indeed enhance relative errors significantly.
-As it was shown in figure~\ref{fig:AcceptPlots}, error bars became much larger for the corrected \dpt from the acceptance effect.
-This fact indicated an important statistical sensitivity introduced by our weighting methods.
-The errors on \dpt are of the same order, or smaller, than the differences observed between the two weighted data-sets.
-This is an indication that the uncertainties reported in table \ref{tab:SysAcc} are, in nature, similar to the statistical errors, in the sense that both originate from the large variation between event-by-event weights.
-For this reason, we decided to do not include this error in our systematic budget to avoid double counting this effect.
+After testing several different acceptance correction methods, we finally 
+converged with the one using four dimensions and a limited number of bins.
+The two different approaches to binning the data presented on a table 
+\ref{tab:AcceptBinning} are used to evaluate the systematic errors. The 
+difference between these two methods on iron data are used to evaluate 
+the relative uncertainties presented in a table~\ref{tab:SysAcc}. We noticed 
+the significantly large errors for $\pi^-$s, which were expected, due to their 
+lower acceptance and larger weights.
+
+Systematic errors are also
+considerably larger for \dpt measurements. This is mainly due to the nature of 
+the \dpt observable; as it is a difference, it enhances relative errors 
+significantly. Also, as shown in figure~\ref{fig:AcceptPlots}, error bars 
+became much larger for the corrected \dpt from the acceptance effect. This 
+result indicated an important statistical sensitivity introduced by our 
+weighting methods. The errors on \dpt are of the same order, or smaller, than 
+the differences observed between the two weighted data-sets. This is an 
+indication that the uncertainties reported in table \ref{tab:SysAcc} are, in 
+nature, similar to the statistical errors, in the sense that both originate 
+from the large variation between event-by-event weights. For this reason, we 
+decided not to include this error in our systematic budget to avoid double 
+counting this effect.
 
@@
   \end{tabular}
-  \caption{Relative errors on pions' observables using the two weighting methods described in the text.}
+  \caption{Relative errors on pions' observables using the two weighting 
+           methods described in the text.}
   \label{tab:SysAcc}
@@
 
-The point-to-point errors include contributions from a detection contamination and acceptance effects.
-However, the normalization errors, which are independent of kinematical variables and due to acceptance effects, a target's misidentification and the isospin correction, are summarized in a table~\ref{tab:sysid}.
+The point-to-point errors include contributions from the bad particle 
+identifications and acceptance effects. The normalization error, which is 
+independent of kinematic variables, are due to acceptance effects, target 
+misidentification and isospin correction; the constributions are summarized 
+in table~\ref{tab:sysid}.
 

### 2017-01-12 chap6.tex
Continue review questions, start English corrections

@@
 include results as function of all variables. All results were extracted with the following DIS selection cuts: 
-$Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$.
-To ensure that a factorization holds, we are selecting events with $0.4$~$<$~$z$~$<$~$0.7$~\footnote{This cut is not applied for plots with results as a function of $z$.} based on the previously published results from \cite{Asaturyan:2011mq}.
-Moreover, this cut also ensures that we are measuring the leading hadron, and avoiding the high $z$ region, which might be contaminated by
-the decay products of the diffractive production of $\rho^0$. Finally, we are applying a cut on $x_F > 0$ to select the forward fragmentation region.
+$Q^2$~$>$~$1$~GeV$^2$/c$^2$, $W$~$>$~$2$ GeV and $y<0.85$. To ensure that SIDIS 
+factorization applies~\cite{Mulders:2000jt}, we are selecting events with 
+$0.4$~$<$~$z$~$<$~$0.7$~\footnote{This cut is not applied for plots with results 
+as a function of $z$.} based on the previously published results from 
+\cite{Asaturyan:2011mq}. Moreover, this cut also ensures that we are measuring the 
+leading hadron, and avoiding the high $z$ region, which might be contaminated by 
+the decay products of the diffractive production of $\rho^0$. Finally, we are 
+applying a cut on $x_F > 0$ to select the forward fragmentation region.
 
@@
 
-The attenuation, presented in the figure \ref{fig:RA}, is not linear neither for $A^{1/3}$ nor $A^{2/3}$. The HERMES data have already showed some indication 
-of this feature~\cite{Airapetian:2007vu,Airapetian:2009jy}, but here, the non-linearity, which has important implication on models, is clear.
-Indeed, it seems difficult to conciliate the prehadron absorption models with this result.
-Prehadrons
+The attenuation, presented in the figure \ref{fig:RA}, is neither linear as a 
+function of $A^{1/3}$ nor as a function of $A^{2/3}$. The HERMES data had
+already showed some indication 
+of this feature~\cite{Airapetian:2007vu,Airapetian:2009jy}, but here the 
+non-linearity, which has important implication on models, is clear. Indeed, 
+it seems difficult to conciliate the prehadron absorption models with this result. Prehadrons 
 are expected to have their cross sections increasing with time and, therefore, 
-distance.
-On the parton energy loss side, the BDMPS calculation gives a parton energy loss proportional to $L^2 \propto A^{2/3}$, which is in contradiction with this result.
-However, this statement does not hold at low energy, and might be
-modified if the production time occurs inside the nuclei.
+distance. On the parton energy loss side, the BDMPS calculation gives a parton 
+energy loss proportional to $L^2 \propto A^{2/3}$, indicating that we are not
+in the region where this result applies. Morover, if the production 
+time\footnote{As defined in figure~\ref{fig:hadro}} occurs 
+inside the nuclei, the behavior of the multiplicity ratio can be more complicated
+as different processes intervene.
 
@@
 The $A$ dependence of the transverse momentum broadening, presented in 
-figure~\ref{fig:PA}, is a crucial result.
-The combination of our large statistics with a wide $A$ coverage gave an outright indication of $A^{1/3}$ dependence of \dpt.
-This \dptp~ effect is found much smaller compared to HERMES measurment\cite{Airapetian:2009jy}, which is consistent with theoretical models predicting larger effects at larger energies.
-However, calculations of the parton energy loss from BDMPS \cite{Baier:1996sk} correlated \pt with the nuclei radii.
-A feature that is not enhanced in our result.
-Although, by looking to the low energy of our CLAS experiment, one might argue the validity of a direct comparison with BDMPS calculations.
-Nonetheless, this result shows an unexpected pattern that remains to be explained.
-One interpretation might favor the occurrence of the production time inside nuclei, as we proposed for the $A^{1/3}$ dependence of multiplicity ratios.
-In this case, the colored parton would not interact with the whole nuclei which limit the nuclear effect.
+figure~\ref{fig:PA}, is a crucial result. The combination of our large 
+statistics with a wide $A$ coverage gave an outright indication of $A^{1/3}$ 
+dependence of \dpt. This \dptp~ effect is found much smaller compared to 
+HERMES measurment\cite{Airapetian:2009jy}, which is consistent with
+ theoretical models predicting larger effects at larger energies. However, 
+calculations of the parton energy loss from BDMPS \cite{Baier:1996sk} 
+correlated \pt with quadratically the nuclei radii. A feature that is not 
+observed in our result. Although, by looking to the low energy of our CLAS 
+experiment, one might argue the validity of a direct comparison with BDMPS 
+calculations. Nonetheless, this result shows an unexpected pattern that 
+remains to be explained. One possible interpretation is the occurrence of 
+the production time inside the nuclei, as we proposed for the $A^{1/3}$ 
+dependence of multiplicity ratios. In this case, the colored parton would 
+not interact with the whole nuclei, hence limiting the nuclear effect.
 
@@
 Finally, the $Q^2$ dependence of \dpt is an important result for the BDMPS based 
-calculation from \cite{Domdey:2008aq}.
-They have expected a raise of \dpt with $Q^2$, which is not observed in a figure \ref{fig:PQ2}.
-Even a tighter $\nu$ bin and a carbon normalization (see figure \ref{fig:PQ2-detailed}) gave a similar result.
-In conclusion, within error bars, no effect is observed for \dpt as a function of $Q^2$.
-However, as a theoretical input is missing, it is not clear if we have the needed resolution to observe the effect expected within BDMPS based models.
+calculation from \cite{Domdey:2008aq}. They have expected a raise of \dpt with $Q^2$, 
+which is not observed in figure \ref{fig:PQ2}. Using a tighter $\nu$ bin and a 
+carbon normalization should isolate this effect better, but figure \ref{fig:PQ2-detailed}
+gives a similar result. In conclusion, within error bars, no effect is observed for 
+\dpt as a function of $Q^2$. However, we would like to have a quantitative theoretical 
+input here, as it is not clear if we have the needed resolution to observe the effect 
+expected within BDMPS based models. We are going to work with the authors of the original 
+paper to add some projections on our figures.
 

### 2017-01-12 intro.tex
Continue review questions, start English corrections

@@
 
-The hadronization in nuclear matter is a key process of the Quantum Chromo-Dynamics theory (QCD) because it leads to major theoretical uncertainties in numerous measurements.
-As the nuclear medium is hot and evolving in Relativistic Heavy Ion Collisions (RHIC), DIS experiments at JLab energies are well suited to test different theoretical models, including the RHIC's ones, because the size of cold nuclei is stable and known.
-The hadronization can give important information about nuclei through the quark energy loss, for example, Arleo's model~\cite{Arleo:2003yf} correlates the quark energy loss with a gluon density, and Kopeliovich et al.'s model~\cite{Kopeliovich:2010aa} correlates the $\Delta \langle P_T^2 \rangle$ with the saturation scale.
+The hadronization in nuclear matter is a key process of the Quantum 
+Chromo-Dynamics theory (QCD) because it leads to major theoretical 
+uncertainties in numerous measurements. DIS experiments at JLab energies are 
+well suited to test different theoretical models of hadronization, including 
+the ones used for Relativistic Heavy Ion Collisions (RHIC). The main advantage 
+of testing models in lepton scattering is that the size of cold nuclei is 
+stable and known, while in RHIC the nuclear medium is hot and evolving 
+introducing many parameters and unknowns. The hadronization process can also 
+give important information about nuclei through the quark energy loss, for example, Arleo's model~\cite{Arleo:2003yf} correlates the quark energy loss with a gluon density, and Kopeliovich et al.'s model~\cite{Kopeliovich:2010aa} correlates the $\Delta \langle P_T^2 \rangle$ with the saturation scale.
 Other models \cite{Gallmeister:2007an} utilize different assumptions to describe the pre-hadron evolution into a full hadron.
@@
 In order to best constrain the models with our data, we extracted our results using tight multi-dimensional binning.
-That is possible because of the high statistics of our EG2 data, which allowed the study of both pions production over a wide kinematic range.
+That is possible because of the high statistics of our EG2 data, which allowed the study of both pion production on a wide kinematic range.
 
@@
 the parton energy loss, hence the observed suppression is due to the fact that a lower energy quark fragments into a low number of hadrons at a very low $z$.
-This kind of models is suitable for both RHIC and nDIS experiments since it permits a common interpretation of hadron suppression in the nuclear matter.
+This kind of model is suitable for both RHIC and nDIS experiments since it permits a common interpretation of hadron suppression in the nuclear matter.
 Moreover, various calculations have described the parton energy loss in the nuclear medium using the $\hat q$ (GeV$^2$ fm$^{-1}$) parameter, that is defined as the quark transverse momentum normalized by its propagation path length.
@@
 in nuclei by showing a suppression of hadrons' production in heavy nuclei.
-This suppression appears to be reduced at higher $\nu$ and lower $z$, and it 
-can even inverse sign and become an increased yield at very low $z$.
+This suppression appears to be reduced at higher $\nu$ and lower $z$, at very 
+low $z$ it can even change sign and become an increased yield.
 
@@
 
-The good precision of HERMES data shed light on new hadronization features, such as the behavior of K$^+$s, which have less attenuation than pions (see figure \ref{fig:her1}) but an excess on $\Delta \langle P_T^2 \rangle$.
-Must note that it is difficult to reproduce this behavior on models where only one hadronization stage is taken into account to explain all effects.
-Likewise, the different behavior of protons compared to anti-protons (see figure \ref{fig:her2}) is interesting and needs more precise analyses to unravel it since most of the existing models do not treat yet the baryons' hadronization.
+The good precision of HERMES data shed light on new hadronization features, 
+such as the behavior of K$^+$s, which have less attenuation than pions (see 
+figure \ref{fig:her1}) but an excess in $\Delta \langle P_T^2 \rangle$. It is 
+notable that it is difficult to reproduce this behavior in models where only 
+one hadronization stage is taken into account to explain all effects. Likewise, 
+the different behavior of protons compared to anti-protons (see figure 
+\ref{fig:her2}) is interesting but most existing models do not treat baryon 
+hadronization yet.

### 2017-01-13 1-Answers-Review.tex
Finished English corrections

@@
 
-{\it Done to this point. Need full reread after that!} \\
-
 P13, L1 of section 2.2.2, sentence makes no sense as written. Do you mean something like, 
@@
 Start of next paragraph, “The simulated data are processed like the experimental data by 
-applying ...”  “ ... quite well the detector response, yet ...”
+applying ...”  “ ... quite well the detector response, yet ...” \\
+
+{\it Not sure what reference we should add here. The analysis note is not only a technical document
+it is also an internal document.} \\
 
@@
 P41, first paragraph, what does HERMES say about Q2 dependence?  Line 4, “... in figure 34, 
-does not indicate ...”
+does not indicate ...” \\
+
+{\it HERMES do see an increase which is not statistically significant 
+(see figures 2 and 3 of the note).} \\
 
@@
 P42 second paragraph, L2, “they predict a rise of delta pt\^2 with Q\^2”
-Same paragraph, L4, “... 38) gives a similar result.”
+Same paragraph, L4, “... 38) gives a similar result.” \\
+
+{\it Sorry for the clumsy English in some parts. We have implemented all the 
+suggested changes and some more. This issue should now be solved.} \\
+
 \end{document}

### 2017-01-13 chap5.tex
Finished English corrections

@@
 
-To identify negatively charged pions, we select negative tracks which didn't verify electrons' identification cuts.
-Pions are detected in the angular range from $\sim$10 to $\sim$140 degrees using only DC and SC signals.
+Pions are detected in the angular range from $\sim$10 to $\sim$140 degrees 
+using only DC and SC signals. To identify negatively charged pions, we select 
+negative tracks which were not identified as electrons already.
 
@@
 pions. However, the time of flight plot is significantly more busy (see figure 
-\ref{PipTOF}), indicating a significant contamination from $K^+$s and protons at a
-higher momentum. As the CC is not efficient enough for a hadron separation, the 
+\ref{PipTOF}), due to an important contamination from $K^+$s and protons at a
+high momentum. As the CC is not efficient enough for a hadron separation, the 
 numerous kaons and protons should be removed by the following tighter TOF cuts:
@@
 
-These cuts permit to minimize the kaon contamination, below 2.5~GeV/c, and the 
+These cuts minimize the kaon contamination, below 2.5~GeV/c, and the 
 proton contamination for all momenta. The kaon contribution cannot be avoided, however, it should remain small ($\sim$ 3\% according to simulation) 
@@
 
-To check the quality of the runs\footnote{Runs were formed roughly from two hours
-of data, but they were much smaller in case of problems.}, we monitored the ratio of scattered electrons yields obtained from solid and liquid targets.
-In case of the beam hitting other materials in the beam-line or of ony other problem that would affect our final result,
-this ratio will be off and indicate the problematic runs. A figure 
-\ref{DataQ} shows electrons yields' ratios for different nuclear target; we fitted these ratios to extract the mean value for each target, then we discarded runs that were 5~$\sigma$ away from the appropriate mean.
-Must note that these ratios were consistent with our target's thicknesses given in \cite{Hakobyan:2008zz} except for a carbon target.
-For that reason, the density of the latter was recently remeasured, and its new value was finally matching our data\footnote{i.e.
-(1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.
+To check the quality of the runs\footnote{Runs are typically stopped every two hours
+of data taking, but they can be smaller when experimental problems arrise.}, we 
+monitored the ratio of scattered electrons yields obtained from solid and liquid 
+targets. In case of the beam hitting other materials in the beam-line or of any 
+other problems that would affect our final result, 
+this ratio will be off and indicate the problematic runs. In figure 
+\ref{DataQ}, we show the electron yield ratios for different nuclear target; we 
+fitted these ratios to determine the mean value for each target, then we discarded 
+runs that were 5~$\sigma$ away from the appropriate mean. Must note that these 
+ratios were consistent with our target's thicknesses given in \cite{Hakobyan:2008zz} 
+except for a carbon target. For that reason, the density of the latter was 
+recently remeasured, and its new value was finally matching our 
+data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.
 
@@
 
-To provide some insight into the quality of our data, we present in figure~\ref{fig:prelim} few preliminary results before the application of any corrections.
-These preliminary results will be used also to illustrate the effects of the corrections discussed below.
+To provide some insight into the quality of our data, we present in 
+figure~\ref{fig:prelim} a few preliminary results before the application of 
+any corrections. These preliminary results will be used also to illustrate 
+the effects of the corrections discussed below.
 
@@
 event by event to correct for any detection inefficiencies of used detectors.
-Incidentally, it also corrects for other small detection issues, such as misidentification and re-scattering on detectors' materials. The quality 
+Incidentally, it also corrects for other small detection issues, such as 
+misidentification and re-scattering on detector material. The quality 
 of the correction depends on the ability of the simulation to reproduce the 
@@
 generated events are processed by CLAS softwares (GSIM, GPP and user\_ana) 
-to simulate the detector and the reconstruction process similarly to the experimental data.
+to simulate the detector and the reconstruction process in a fashion similar 
+to that done with the experimental data.
 % TODO GPP factors
 
-Then the simulated data are processed in a similar way than the experimental data by 
+The simulated data are processed like the experimental data by 
 applying the cuts described in the section \ref{sec:pid}. Overall the 
-simulation reproduces quite well the detectors responses, yet two issues might 
+simulation reproduces quite well the detector response, yet two issues might 
 affect us and have to be understood. First, the efficiency of the CC is 
@@
 
-We used a 4-dimensional binning to divide the large phase space of our two particles' final 
-state. To evaluate systematic errors associated with this correction, we compared the
+We used a 4-dimensional binning to divide the large phase space of our two particle final 
+state. However, to evaluate systematic errors associated with this correction, we compared the
 method using two different sets of kinematic variables, as presented in 
@@
 
-Because of reconstruction errors or scattering on detectors' material, it 
+Because of reconstruction errors or scattering on detector material, it 
 is possible to associate a particle with the wrong target. To estimate this 
@@
 
-The point-to-point errors include contributions from the bad particle 
-identifications and acceptance effects. The normalization error, which is 
+The point-to-point errors include contributions from particle 
+misidentifications and acceptance effects. The normalization error, which is 
 independent of kinematic variables, are due to acceptance effects, target 
-misidentification and isospin correction; the constributions are summarized 
-in table~\ref{tab:sysid}.
+misidentification and the isospin correction. The various constributions 
+to the systematic normalization error are summarized in table~\ref{tab:sysid}.
 

### 2017-01-13 chap6.tex
Finished English corrections

@@
 non-linearity, which has important implication on models, is clear. Indeed, 
-it seems difficult to conciliate the prehadron absorption models with this result. Prehadrons 
+it seems difficult to reconcile the prehadron absorption models with this result. Prehadrons 
 are expected to have their cross sections increasing with time and, therefore, 
@@
 (right), has another interesting feature: the $\pi^+$s have a stronger Cronin 
-effect. However, the signification of this observation is not clear. This could be 
+effect. However, the significance of this observation is not clear. This could be 
 a contribution from target fragmentation, as we might expect more positive 
@@
 
-The HERMES collaboration clearly observed a rise of the multiplicity ratio with $\nu$ from 4 till 22~GeV.
-However, at first sight to our results (figure \ref{fig:RNu} (left)), no dependence is observed, besides a slight increase in lead.
-However, the Fermi motion could cancel most of this hadronization effect, and what left will be washed out with the acceptance correction systematic uncertainty.
-The normalized multiplicity ratio to carbon, however, offers a cleaner result with a slope consistent with what was observed on a much larger range of HERMES data.
+The HERMES collaboration clearly observed a rise of the multiplicity ratio 
+with $\nu$ from 6 to 22~GeV. However, our results (figure \ref{fig:RNu} (left))
+show no dependence, besides a slight increase in lead.
+However, the Fermi motion could cancel most of this hadronization effect, and 
+what is left will be washed out with the acceptance correction systematic 
+uncertainty. The normalized multiplicity ratio to carbon offers a 
+cleaner result, that is not affected by Fermi motion or acceptance. For this
+observable, we measure a slope consistent with what was observed by HERMES.
 
@@
 increase of the multiplicity ratio with $Q^2$. Our result, in figure 
-\ref{fig:RQ2}, did not indicate any significant $Q^2$ dependence, hence no conclusions can be made from our measurement.
+\ref{fig:RQ2}, does not indicate any $Q^2$ dependence, hence our 
+conclusion is that the multiplicity ratio has no significant $Q^2$ dependence.
 
@@
 figure~\ref{fig:PA}, is a crucial result. The combination of our large 
-statistics with a wide $A$ coverage gave an outright indication of $A^{1/3}$ 
-dependence of \dpt. This \dptp~ effect is found much smaller compared to 
-HERMES measurment\cite{Airapetian:2009jy}, which is consistent with
+statistics with a wide $A$ coverage gives an outright indication of $A^{1/3}$ 
+dependence of \dpt. This \dpt effect is found to be much smaller than that seen 
+by HERMES\cite{Airapetian:2009jy}, which is consistent with
  theoretical models predicting larger effects at larger energies. However, 
 calculations of the parton energy loss from BDMPS \cite{Baier:1996sk} 
-correlated \pt with quadratically the nuclei radii. A feature that is not 
+correlated \pt with the square of the nuclear radius. A feature that is not 
 observed in our result. Although, by looking to the low energy of our CLAS 
@@
 the production time inside the nuclei, as we proposed for the $A^{1/3}$ 
-dependence of multiplicity ratios. In this case, the colored parton would 
-not interact with the whole nuclei, hence limiting the nuclear effect.
+dependence of multiplicity ratios. In this case, the colored parton does 
+not interact with the whole nucleus which limits the nuclear effect.
 
@@
 Finally, the $Q^2$ dependence of \dpt is an important result for the BDMPS based 
-calculation from \cite{Domdey:2008aq}. They have expected a raise of \dpt with $Q^2$, 
+calculation from \cite{Domdey:2008aq}. They predict a raise of \dpt with $Q^2$, 
 which is not observed in figure \ref{fig:PQ2}. Using a tighter $\nu$ bin and a 

### 2017-02-22 1-Answers-Review.tex
Update the note on RC and Error bars calculations

@@
 In a later stage an extra analysis note from Hayk will be submitted
-for the extraction of multi-dimensional results on pi+.} \\
+for the extraction of multi-dimensional results on $\pi^+$.} \\
 
@@
 
-{\it TODO when all questions are answered.} \\
+{\it The text about acceptance has been reviewed in details to be clearer in this new 
+version. The section about radiative corrections has been updated with the new method.
+We maybe should meet during the next CLAS collaboration meeting (end of March) to clarify 
+some of the simpler issues.} \\
 
@@
 fits for these specific figures and we 
-lack the problematic run which have been deleted. At this stage, we do not deem necessary
-to pull these old discarded data and reactivate the associated codes. If the reviewer
-think it is necessary, it is time consuming but of course possible.}
+lack the problematic run which have been deleted. At this stage, it would be rather time
+consuming to recover all the data and update the softwares to run on the new machines, so 
+we did not produce this figure. If the reviewer think it is necessary to update this 
+figure and provide more information about the discarded data let us know, it is time 
+consuming but of course possible.}
 
@@
 
-The first set of variables is the one actually used for the
-analysis and the second set is only used to evaluate the systematic errors, so in the 
-note, the formulas are given only for the first set.
+The first set of variables is the one used for the acceptance correction used for results,
+while the second set is only used to evaluate the systematic errors. In the 
+note, the formulas are generally given only for the first set for simplicity.
 
-The motivation for using such a weight cut based on the product of different unrelated
-values is actually directly linked to the inbent 
-particles being directed in the beam pipe. The $\pi^-$ acceptance drops very 
+The motivation for using such a strange cut based on the product of different unrelated
+values is actually directly linked to the problem of inbent 
+particles being directed towards the beam pipe. The $\pi^-$ acceptance drops very 
 strongly at low $p_\perp^2$ leading to very high weights, however there is no problem of 
@@
 the best way
-to keep these bins while discarding bins where the weight might be slightly smaller but with 
-issues concerning bin migration and statistics was to apply this type of cut.
+to keep these bins while discarding bins where the sizze of the weight is less problematic 
+but with issues concerning bin migration and statistics was to apply this type of cut.
 
@@
 in the previous L. El Fassi et al. analysis note. The second step of the procedure is
-specifically used to take care of the holes in the acceptance (note, they are not really 
-holes because problematic bins are generally on the edges). You can see that the weights
+specifically used to take care of the bins that are removed by the cut on weights. You 
+can see in the formula that the weights
 of the previously calculated acceptance are used in this step, ensuring that we do not
@@
 effect is small but visible only for very low $z$ pions. It has been implemented 
-because it was suggested it might be big, but we now find that can be neglected 
-at our kinematics. ADD a FIGURE???} \\
+because it was suggested it might be big, but we now find that it could have been 
+neglected at our kinematics.} \\
 
@@
 
-{\it FIGURE TO BE REPLACED COMPLETELY} \\
+{\it This figure is replaced by others in the new radiative correction section.} \\
 
@@
 
-{\it Resolution is the same, it looks wider because on this figure, we show the integrated 
+{\it Resolution is the same, it looks wider because, on this figure, we show the integrated 
 result over the 6 sectors.} \\
@@
 
-{\it This is an interesting question and we might have overlooked this problem. WE
-NEED TO THINK ABOUT THAT. } \\
+{\it This is an interesting question and we might have overlooked this problem. We changed
+our method of calculating the statistical errors to avoid the double counting, see
+discussion in the 2.3.1. section about the method to calculate the error bars. } \\
 

### 2017-02-22 AnalysisNote.tex
Answer some comments!
Update the note on RC and Error bars calculations

@@
         \usepackage{epigraph}
+        \usepackage{lineno}
 
@@
 
+\linenumbers
+
 \makeatother
@@
   {\it Institut de Physique Nucl\'eaire, Orsay, France} \\
+  Kawtar \textsc{Hafidi} \\ 
+  {\it Physics Division, Argonne National Laboratory,} \\ 
+  {\it Argonne, Illinois 60439, USA} \\
   Lamiaa \textsc{El Fassi} \\ 
@@
   {\it Mississippi 39762, USA} \\
-  Kawtar \textsc{Hafidi} \\ 
-  {\it Physics Division, Argonne National Laboratory,} \\ 
-  {\it Argonne, Illinois 60439, USA} \\
-  William \textsc{Brooks} \\
+  William \textsc{Brooks}, Ahmed \textsc{El Alaoui}, Hayk \textsc{Hakobyan}, \\
+  Taisiya \textsc{Mineeva} \\
   {\it Universidad T\'ecnica Federico Santa Mar\'ia,} \\ 
@@
 \begin{abstract}
-Hadronization is the process by which energetic quarks transform into colorless hadrons.
-The process is non-perturbative, therefore, only a qualitative understanding based on phenomenological models can be achieved.
-By comparing hadron production on different nuclei, one can measure the most sensitive variables to the hadronization phases, the transverse momentum broadening, that is believed to be tightly connected to the quark energy loss, and the multiplicity ratio, which is a measure of the hadron attenuation in the nuclear medium.
+Hadronization is the process by which energetic quarks transform into colorless 
+hadrons. The process is non-perturbative, therefore, only a qualitative 
+understanding based on phenomenological models can be achieved. By comparing 
+hadron production on different nuclei, one can measure the most sensitive variables 
+to the hadronization phases, the transverse momentum broadening, that is believed 
+to be tightly connected to the quark energy loss, and the multiplicity ratio, 
+which is a measure of the hadron attenuation in the nuclear medium.
 
-The goal of the experiment E-02-104 was the study of the quark propagation and hadronization dynamics using various nuclear targets.
-In this note, we focus on the production of two charged particles, positive and negative pions, to constrain theoretical models using a precise multidimensional analysis.
+The goal of the experiment E-02-104 was the study of the quark propagation and 
+hadronization dynamics using various nuclear targets. In this note, we focus 
+on the production of two charged particles, positive and negative pions, to 
+constrain theoretical models using a precise multidimensional analysis.
 

### 2017-02-22 chap5.tex
Update the note on RC and Error bars calculations

@@
 \caption {Picture of the {\it eg2} target system. The cryogenic target is 
-in the back wrapped with aluminum foils, while solid targets are held by mechanical arms that were controlled remotely. In the picture, the top solid target is in the beam line.}
+in the back wrapped with aluminum foils, while solid targets are held by 
+mechanical arms that were controlled remotely. In the picture, the top 
+solid target is in the beam line.}
 \label{fig:phototarget}
@@
 transparency effects, has been approved and published~\cite{ElFassi:2008}. As this 
-analysis went through a careful review by the CLAS collaboration, we have adapted similar analysis methods as much as possible. In particular, the electron selection 
+analysis went through a careful review by the CLAS collaboration, we have 
+adapted similar analysis methods as much as possible. In particular, the electron selection 
 presented here is very similar to theirs; the main difference being a new 
@@
 In the section \ref{sec:pid}, we identify the following particles, e$^-$, 
-$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs. For pions, we require a signal in the drift chambers (DC) and scintillator counters (SC) in 
+$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs. For 
+pions, we require a signal in the drift chambers (DC) and scintillator counters (SC) in 
 addition to the successful reconstruction of the time-based tracking. For electron 
@@
 \begin{equation}
+\label{eq:MRError}
 {\delta \left ( R_A^h \right ) \over R_A^h} = \sqrt{ 1 /N_A^h + 1/ N_A^e +1/N_D^h + 1/N_D^e}
@@
 \begin{equation}
+\label{eq:DPtError}
 \left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
@@
 \left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
-   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
-         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
- + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
-	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
+   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} 
+ - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
+         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over 
+                \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
+ + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} 
+ - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
+	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) 
+          \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
 \end{split}
 \end{equation}
+
+Following the first round of questions from the analysis review committee, we
+reflected about this implementation of error bars and possible overlap with the 
+systematic errors
+evaluated below. We found first that the correlation between the weights should reduce
+the statistical errors. In a given bin the weights associated with each 
+targets are always of similar sizes, this correlation will reduce the size of 
+error bars. However, we do not see a method to properly take this 
+effect fully into account in term of purely statistical error bars. In order
+to solve this issue we came back to a point by the committee on the topic of 
+systematic error bars (Q 24). There it was noted that some of these effects are
+double counted once in the statistical error and once in the systematic. As these
+errors are solely due to the acceptance correction, we decided to account them 
+only in the systematic error budget. So we reverted statistical errors to equations
+\ref{eq:MRError} and \ref{eq:DPtError} and keep the full systematic errors as they
+were evaluated before.
 
@@
 
-\paragraph{Simulation}
-\label{sec:simul}
-
+\paragraph{Simulation} ~\\
 To correct for acceptance effects, we simulated a total of 100 million events 
@@
 
-\paragraph{Correction of the Data}
-
+\paragraph{Correction of the Data} ~\\
 The acceptance correction coefficients are defined as the ratio of reconstructed and generated events,
@@
 \center
-\begin{tabular} {|l|c|c|c|c|}
+\begin{tabular} {|c|c|c|c|c|}
 \hline
@@
 \quad
-\begin{tabular} {|l|c|c|c|c|}
+\begin{tabular} {|c|c|c|c|c|}
 \hline
@@
 
-The large electric charge of our nuclear targets create an electric field that should be taken into account at our energies.
-Besides the fact that the nuclear electric field accelerates or decelerates the incoming and outgoing charged particles, it has some non trivial effects such as the focusing of low energy particles.
-Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb effects could be corrected for by using an effective momentum approximation at large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$).
-As our kinematics coverage is beyond this limit, we decided to use this approximation on the coulomb correction of our data-sets.
-According to Aste {\it et al.}, the best effective potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the electrostatic potential at the center of nuclei.
-The latter is evaluated as $V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure constant, Z is the proton number, and R is the radius of nuclei.
-Table 5 contains the used values of $V_0$ and $\bar V$ on different nuclear target's analysis.
-We must note that this Coulomb correction has been applied to both electrons and charged pions before calculating any kinematical variables.
+The large electric charge of our nuclear targets create an electric field that 
+should be taken into account at our energies. Besides the fact that the nuclear 
+electric field accelerates or decelerates the incoming and outgoing charged 
+particles, it has some non trivial effects such as the focusing of low energy 
+particles. Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb 
+effects could be corrected for by using an effective momentum approximation at 
+large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$). As our kinematics coverage is 
+beyond this limit, we decided to use this approximation on the Coulomb 
+correction of our data-sets. According to Aste {\it et al.}, the best effective 
+potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the 
+electrostatic potential at the center of nuclei. The latter is evaluated as 
+$V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure 
+constant, $Z$ is the proton number, and R is the radius of nuclei. Table 
+\ref{tab:Coulomb} contains the used values of $V_0$ and $\bar V$ on different 
+nuclear target's analysis. The Coulomb correction is applied to both electrons 
+and charged pions before calculating the plotted kinematical variables.
 
@@
 
-Despite its lower magnitude compared to the strong force, the 
-electromagnetic force may have a non negligible impact on our results. The 
-reason is that even a moderate energy photon emission can modify significantly the measured kinematical variables.
-To correct this effect, several simulation codes exist \cite{Akushevich:2001yp}, however, none of them treat directly the SIDIS production on nuclei.
-For that reason, a dedicated Monte-Carlo simulation based on existing codes was developed.
-
-\paragraph{Simulation}
-
-The inclusive radiative effects are generated using the RADGEN code 
-\cite{Akushevich:1998ft}, which includes Feynman diagrams shown in 
-figure~\ref{fig:FDRadCorr}. Using this code one can evaluate the correction 
-factors for inclusive measurements as $\delta = \sigma_{obs} / \sigma_{Born}$, where $\sigma_{obs}$ is the measured inclusive cross section, and $\sigma_{Born}$ is the Born cross section.
-As RADGEN is also a Monte-Carlo generator for photon emissions, it could be used to modify the virtual photon kinematics before the
-hadron production in any DIS generator. This allows the evaluation of the radiative 
-effects on semi-inclusive measurements by implementing RADGEN inside the main 
-Monte-Carlo event generator.
+The QED diagrams shown in figure \ref{fig:FDRadCorr} contribute to the measurement
+of the leptoproduction of hadrons. The diagram (a) is the Born cross section, the
+others are radiative contributions that we would like to subtract in order to 
+have results more easily interpretable in term of hadronic physics.
+This substraction is what we call the radiative correction, as can be seen 
+this correction should take care of real photon productions (diagrams b and c)
+but also virtual photon exchange (diagram d) and photon self energy (diagram e).
+We neglect exchanges of photons with hadrons as they are suppressed due to the 
+large mass of hadrons in comparison to electrons. For practical reasons, we also 
+limit this correction to leading order as can be seen from the presented diagrams.
 
@@
 \includegraphics[width=12cm] {chap5-fig/RadDiag.png}
-\caption {Diagrams taken into account in RADGEN \cite{Akushevich:1998ft}. The 
-diagrams b) to e) contribute to the first order calculation of the radiative 
-effects on Born cross section (diagram a)).}
+\caption {Diagrams taken into account in the HAPRAD 2 code \cite{Akushevich:2007jc}. The 
+diagrams b to e contribute to the first order calculation of the radiative 
+effects of the Born cross section represented in diagram a.}
 \label{fig:FDRadCorr}
@@
 
-The Monte-Carlo simulation was done using the event generator, GENIE~\cite{Andreopoulos:2009rq}, that describes well electron-nucleus interactions.
-Indeed, GENIE contains the quasi-elastic scattering\footnote{Elastic
-scattering off a single nucleon on nuclei.}, which is considered as the main channel generating radiative events in the DIS region \cite{Akushevich:2007jc}.
-This generator includes also hadronic cascades in nuclei, at which pions might be generated in quasi-elastic events.
-This is an important feature because the quasi-elastic production can not contribute directly to semi-inclusive measurements.
-
-\paragraph{Correction of the Data}
-
-We generated 100 million events with and without radiative effects for each target.
-The RADGEN code gave us the magnitude of inclusive correction coefficients, however, the comparison between the two data sets allows the extraction of semi-inclusive correction factors.
-
-The ratio of inclusive correction factors, as depicted in figure \ref{fig:RadCorrFac}, is relatively small (couple of percents at most) except for low \xb and high $\nu$.
-Similarly for the semi-inclusive factors' ratio shown in figure \ref{fig:RadCorrFacSIDIS} as a function of $z$ and \ptp.
-However, the associated statistical errors are quite large because only a small fraction of the events involved a photon radiation.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=9cm] {chap5-fig/ElecRadWei_Lead.png}
-\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
-\delta_{^2\text{H}}$, as a function of \xb in various $\nu$ bins.}
-\label{fig:RadCorrFac}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics[width=9cm] {chap5-fig/RadGenFactors.png}
-\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
-\delta_{^2\text{H}}$, as a function of $z$ (top) and \ptp (bottom).}
-\label{fig:RadCorrFacSIDIS}
-\end{figure}
-
-The semi-inclusive part of the radiative correction turned out to be limited 
-in amplitude for the most kinematics, except for high $z$ and \ptp. Thus, we decided to not apply this correction before further studies.
-
-{\color{red} We found a better way to implement the radiative correction,
-that is not limited by the used MC technique. We will implement it in
-the second version of the note as we do not want to delay the review process because this correction that we already found to be small. Sorry about that.}
+The radiative correction is not expected to be important in the multiplicity 
+ratios due to the double cancellation between the different contributions of 
+the ratio. However, its impact on the transverse momentum brodening is more 
+difficult to anticipate. We therefore decided to calculate the correction using 
+the recent Haprad 2 code \cite{Akushevich:2007jc} with adaptations to include
+nuclear effects such as Fermi motion \cite{Osipenko:PC}. This calculation is
+using modeled semi-inclusive structure functions (based on former CLAS
+data \cite{Akushevich:2007jc}) and modeled exclusive channels from MAID 2003
+\cite{Drechsel:1998hk}. This calculation is the state of the art in the matter
+as it is an exact calculation in the complete five dimension cross section
+and do not use the peaking approximation generally used in previous method.
+
+To apply the radiative correction, we apply a weight to each events in a fashion
+similar to the acceptance correction. The HAPRAD 2 code provides 
+$\delta = \sigma_{obs} / \sigma_B$ at given kinematics. Table \ref{tab:RCBins} 
+shows the binning used to calculate the radiative correction weights.
+We chose to make a finer 
+binning for the radiative corrections than for acceptance as the computing time 
+to calculate weights is more reasonnable (around 1000 days of cpu time).
+
+\begin{table}[htbp]
+\center
+\begin{tabular} {|c|c|c|c|c|c|c|}
+\hline
+Bin Nb & $\nu$ & \xb & $p_\pi$ & $-t$ & $\phi$ \\ \hline
+
+ 0     & 2.25 & 0.12 & 0.20 & -3.50 &   0.0 \\ 
+ 1     & 2.45 & 0.15 & 0.35 & -2.10 &  18.0 \\ 
+ 2     & 2.66 & 0.17 & 0.50 & -1.75 &  36.0 \\ 
+ 3     & 2.82 & 0.18 & 0.75 & -1.50 &  54.0 \\ 
+ 4     & 2.96 & 0.19 & 1.00 & -1.30 &  72.0 \\ 
+ 5     & 3.07 & 0.20 & 1.60 & -1.10 &  90.0 \\ 
+ 6     & 3.17 & 0.21 & 2.20 & -0.75 & 108.0 \\ 
+ 7     & 3.27 & 0.22 & 4.25 &  0.00 & 126.0 \\ 
+ 8     & 3.37 & 0.23 &      &       & 144.0 \\ 
+ 9     & 3.46 & 0.24 &      &       & 162.0 \\ 
+10     & 3.55 & 0.25 &      &       & 180.0 \\ 
+11     & 3.64 & 0.26 &      &       &       \\ 
+12     & 3.72 & 0.27 &      &       &       \\ 
+13     & 3.80 & 0.28 &      &       &       \\ 
+14     & 3.87 & 0.30 &      &       &       \\ 
+15     & 3.94 & 0.33 &      &       &       \\ 
+16     & 4.01 & 0.36 &      &       &       \\ 
+17     & 4.07 & 0.39 &      &       &       \\ 
+18     & 4.12 & 0.43 &      &       &       \\ 
+19     & 4.18 & 0.48 &      &       &       \\ 
+20     & 4.25 & 0.56 &      &       &       \\
+
+\hline
+\end{tabular}
+\caption{Bin limits used for the radiative correction described in section \ref{RadCor}.}
+  \label{tab:RCBins}
+\end{table}
+
+We show in figure \ref{fig:RCexample} a selected sample of radiative correction factors
+($= \delta_{Fe} / \delta_D$) in order to illustrate the expected effect on observables.
+In the large majority of the cases the factors are within 5\% of 1, so we do not expect to
+see a strong effect on the final results where these will be integrated. This is confirmed 
+in figure \ref{} ... In the case of the transverse momentum braodening, the variations
+appear to ...
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_2356.png}
+\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_3756.png}
+\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_7756.png}
+\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_10756.png}
+\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_11556.png}
+\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_18956.png}
+\caption {RC factors ($= \delta_{Fe} / \delta_D$) as a function of $\phi$ and 
+$-t$ for a selection of bins specified above each figure.}
+\label{fig:IsoSpin}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\caption {Preliminary results ..., 
+for multiplicity ratios (top) and transverse momentum broadening 
+(bottom). Only statistical errors are shown.}
+\label{fig:RCPlots}
+\end{figure}
 
@@
 \includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
-\caption {Ratios of deuteron over proton for $\pi^+$s (top) and $\pi^-$s (bottom)
-as a function of \xb at $z=0.55$ \cite{Asaturyan:2011mq}.}
-\label{fig:IsoSpin}
+\caption {}
+\label{fig:RCexample}
 \end{figure}

### 2017-02-28 chap5.tex
Fixed figure link problems and add 120Sn statement

@@
 was filled with liquid deuterium, and the second was a solid target. The 
-latter was made of either carbon, aluminum, iron, tin or lead, and was changed 
+latter was made of either carbon, aluminum, iron, tin\footnote{The tin was 
+enriched and composed of more than 99\% $^{120}$Sn.} or lead, and was changed 
 remotely (see figure~\ref{fig:phototarget}). The two targets were separated by 
@@
 \centering
-\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
+\includegraphics[width=8cm] {answer-fig/TofProfile2.png} 
 \caption {$\Delta \beta$ of positively charged particles for medium momentum slices 
@@
 \centering
-\includegraphics[width=8cm] {answer-fig/TofProfile1.png} 
-\caption {$\Delta \beta$ of positively charged particles for low momentum slices 
+\includegraphics[width=8cm] {answer-fig/TofProfile3.png} 
+\caption {$\Delta \beta$ of positively charged particles for high momentum slices 
 (GeV/c). The red lines shows the applied cuts to select positive pions. The bump on the left

### 2017-03-01 chap5.tex
Few corrections

@@
 reflected about this implementation of error bars and possible overlap with the 
-systematic errors
-evaluated below. We found first that the correlation between the weights should reduce
+systematic errors evaluated below. First we found an error with how the formula
+above was implemented and corrected it. This reduces the size of statistical 
+error bars of the transverse momentum broadening by roughly a factor 2 to 3.
+
+TODO See new results and re evaluate statement below.
+We found first that the correlation between the weights should reduce
 the statistical errors. In a given bin the weights associated with each 
@@
 $V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure 
-constant, $Z$ is the proton number, and R is the radius of nuclei. Table 
+constant, $Z$ is the proton number, and $R$ is the radius of the nuclei. Table 
 \ref{tab:Coulomb} contains the used values of $V_0$ and $\bar V$ on different 
@@
 \end{table}
+
+TODO Add figures of the effect and comment from review answers!
 
@@
 \includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
-\caption {}
+\caption {Ratios of deuteron over proton for $\pi^+$s and $\pi^-$s 
+as a function of \xb at $z=0.55$ \cite{Asaturyan:2011mq}.}
 \label{fig:RCexample}

### 2017-03-23 chap5.tex
Small fixes (pt max = 1.5 GeV2)

--- 2017-02-22 chap5.tex
@@
 \caption {Picture of the {\it eg2} target system. The cryogenic target is 
-in the back wrapped with aluminum foils, while solid targets are held by 
-mechanical arms that were controlled remotely. In the picture, the top 
-solid target is in the beam line.}
+in the back wrapped with aluminum foils, while solid targets are held by mechanical arms that were controlled remotely. In the picture, the top solid target is in the beam line.}
 \label{fig:phototarget}
@@
 transparency effects, has been approved and published~\cite{ElFassi:2008}. As this 
-analysis went through a careful review by the CLAS collaboration, we have 
-adapted similar analysis methods as much as possible. In particular, the electron selection 
+analysis went through a careful review by the CLAS collaboration, we have adapted similar analysis methods as much as possible. In particular, the electron selection 
 presented here is very similar to theirs; the main difference being a new 
@@
 In the section \ref{sec:pid}, we identify the following particles, e$^-$, 
-$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs. For 
-pions, we require a signal in the drift chambers (DC) and scintillator counters (SC) in 
+$\pi^-$ and $\pi^+$ using a series of cuts on various detector outputs. For pions, we require a signal in the drift chambers (DC) and scintillator counters (SC) in 
 addition to the successful reconstruction of the time-based tracking. For electron 
@@
 \begin{equation}
-\label{eq:MRError}
 {\delta \left ( R_A^h \right ) \over R_A^h} = \sqrt{ 1 /N_A^h + 1/ N_A^e +1/N_D^h + 1/N_D^e}
@@
 \begin{equation}
-\label{eq:DPtError}
 \left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
@@
 \left ( \delta \left ( \Delta \langle P_\perp^2 \rangle \right ) \right )^2 = 
-   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} 
- - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
-         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over 
-                \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
- + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} 
- - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
-	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) 
-          \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
+   \left ({{\sum \omega^h_A P_\perp^4 }\over{\sum \omega^h_A}} - \left ({\sum \omega^h_A P_\perp^2 }\over{\sum \omega^h_A}\right )^2 \right ) 
+         \times \left ( {\sum \left ( {\omega^h_A}^2 \right ) \over \left ( \sum \omega^h_A \right ) ^2 }\right ) \\
+ + \left ({{\sum \omega^h_D P_\perp^4 }\over{\sum \omega^h_D}} - \left ({\sum \omega^h_D P_\perp^2 }\over{\sum \omega^h_D}\right )^2 \right ) 
+	 \times \left ( {\sum \left ( {\omega^h_D}^2 \right ) \over \left ( \sum \omega^h_D \right ) ^2 }\right ).
 \end{split}
 \end{equation}
-
-Following the first round of questions from the analysis review committee, we
-reflected about this implementation of error bars and possible overlap with the 
-systematic errors
-evaluated below. We found first that the correlation between the weights should reduce
-the statistical errors. In a given bin the weights associated with each 
-targets are always of similar sizes, this correlation will reduce the size of 
-error bars. However, we do not see a method to properly take this 
-effect fully into account in term of purely statistical error bars. In order
-to solve this issue we came back to a point by the committee on the topic of 
-systematic error bars (Q 24). There it was noted that some of these effects are
-double counted once in the statistical error and once in the systematic. As these
-errors are solely due to the acceptance correction, we decided to account them 
-only in the systematic error budget. So we reverted statistical errors to equations
-\ref{eq:MRError} and \ref{eq:DPtError} and keep the full systematic errors as they
-were evaluated before.
 
@@
 
-\paragraph{Simulation} ~\\
+\paragraph{Simulation}
+\label{sec:simul}
+
 To correct for acceptance effects, we simulated a total of 100 million events 
@@
 
-\paragraph{Correction of the Data} ~\\
+\paragraph{Correction of the Data}
+
 The acceptance correction coefficients are defined as the ratio of reconstructed and generated events,
@@
 \center
-\begin{tabular} {|c|c|c|c|c|}
+\begin{tabular} {|l|c|c|c|c|}
 \hline
@@
 \quad
-\begin{tabular} {|c|c|c|c|c|}
+\begin{tabular} {|l|c|c|c|c|}
 \hline
@@
 
-The large electric charge of our nuclear targets create an electric field that 
-should be taken into account at our energies. Besides the fact that the nuclear 
-electric field accelerates or decelerates the incoming and outgoing charged 
-particles, it has some non trivial effects such as the focusing of low energy 
-particles. Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb 
-effects could be corrected for by using an effective momentum approximation at 
-large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$). As our kinematics coverage is 
-beyond this limit, we decided to use this approximation on the Coulomb 
-correction of our data-sets. According to Aste {\it et al.}, the best effective 
-potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the 
-electrostatic potential at the center of nuclei. The latter is evaluated as 
-$V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure 
-constant, $Z$ is the proton number, and R is the radius of nuclei. Table 
-\ref{tab:Coulomb} contains the used values of $V_0$ and $\bar V$ on different 
-nuclear target's analysis. The Coulomb correction is applied to both electrons 
-and charged pions before calculating the plotted kinematical variables.
+The large electric charge of our nuclear targets create an electric field that should be taken into account at our energies.
+Besides the fact that the nuclear electric field accelerates or decelerates the incoming and outgoing charged particles, it has some non trivial effects such as the focusing of low energy particles.
+Aste {\it et al.}~\cite{Aste:2005wc} showed that these Coulomb effects could be corrected for by using an effective momentum approximation at large momenta ({\it i.e.}, $Q^2>.5$ GeV$^2$).
+As our kinematics coverage is beyond this limit, we decided to use this approximation on the coulomb correction of our data-sets.
+According to Aste {\it et al.}, the best effective potential approximation is given by $\bar V= 0.8 V_0$, where $V_0$ is the electrostatic potential at the center of nuclei.
+The latter is evaluated as $V_0= -3 \alpha_{EM} Z / (2 R)$, where $\alpha_{EM}$ is the fine-structure constant, Z is the proton number, and R is the radius of nuclei.
+Table 5 contains the used values of $V_0$ and $\bar V$ on different nuclear target's analysis.
+We must note that this Coulomb correction has been applied to both electrons and charged pions before calculating any kinematical variables.
 
@@
 
-The QED diagrams shown in figure \ref{fig:FDRadCorr} contribute to the measurement
-of the leptoproduction of hadrons. The diagram (a) is the Born cross section, the
-others are radiative contributions that we would like to subtract in order to 
-have results more easily interpretable in term of hadronic physics.
-This substraction is what we call the radiative correction, as can be seen 
-this correction should take care of real photon productions (diagrams b and c)
-but also virtual photon exchange (diagram d) and photon self energy (diagram e).
-We neglect exchanges of photons with hadrons as they are suppressed due to the 
-large mass of hadrons in comparison to electrons. For practical reasons, we also 
-limit this correction to leading order as can be seen from the presented diagrams.
+Despite its lower magnitude compared to the strong force, the 
+electromagnetic force may have a non negligible impact on our results. The 
+reason is that even a moderate energy photon emission can modify significantly the measured kinematical variables.
+To correct this effect, several simulation codes exist \cite{Akushevich:2001yp}, however, none of them treat directly the SIDIS production on nuclei.
+For that reason, a dedicated Monte-Carlo simulation based on existing codes was developed.
+
+\paragraph{Simulation}
+
+The inclusive radiative effects are generated using the RADGEN code 
+\cite{Akushevich:1998ft}, which includes Feynman diagrams shown in 
+figure~\ref{fig:FDRadCorr}. Using this code one can evaluate the correction 
+factors for inclusive measurements as $\delta = \sigma_{obs} / \sigma_{Born}$, where $\sigma_{obs}$ is the measured inclusive cross section, and $\sigma_{Born}$ is the Born cross section.
+As RADGEN is also a Monte-Carlo generator for photon emissions, it could be used to modify the virtual photon kinematics before the
+hadron production in any DIS generator. This allows the evaluation of the radiative 
+effects on semi-inclusive measurements by implementing RADGEN inside the main 
+Monte-Carlo event generator.
 
@@
 \includegraphics[width=12cm] {chap5-fig/RadDiag.png}
-\caption {Diagrams taken into account in the HAPRAD 2 code \cite{Akushevich:2007jc}. The 
-diagrams b to e contribute to the first order calculation of the radiative 
-effects of the Born cross section represented in diagram a.}
+\caption {Diagrams taken into account in RADGEN \cite{Akushevich:1998ft}. The 
+diagrams b) to e) contribute to the first order calculation of the radiative 
+effects on Born cross section (diagram a)).}
 \label{fig:FDRadCorr}
@@
 
-The radiative correction is not expected to be important in the multiplicity 
-ratios due to the double cancellation between the different contributions of 
-the ratio. However, its impact on the transverse momentum brodening is more 
-difficult to anticipate. We therefore decided to calculate the correction using 
-the recent Haprad 2 code \cite{Akushevich:2007jc} with adaptations to include
-nuclear effects such as Fermi motion \cite{Osipenko:PC}. This calculation is
-using modeled semi-inclusive structure functions (based on former CLAS
-data \cite{Akushevich:2007jc}) and modeled exclusive channels from MAID 2003
-\cite{Drechsel:1998hk}. This calculation is the state of the art in the matter
-as it is an exact calculation in the complete five dimension cross section
-and do not use the peaking approximation generally used in previous method.
-
-To apply the radiative correction, we apply a weight to each events in a fashion
-similar to the acceptance correction. The HAPRAD 2 code provides 
-$\delta = \sigma_{obs} / \sigma_B$ at given kinematics. Table \ref{tab:RCBins} 
-shows the binning used to calculate the radiative correction weights.
-We chose to make a finer 
-binning for the radiative corrections than for acceptance as the computing time 
-to calculate weights is more reasonnable (around 1000 days of cpu time).
-
-\begin{table}[htbp]
-\center
-\begin{tabular} {|c|c|c|c|c|c|c|}
-\hline
-Bin Nb & $\nu$ & \xb & $p_\pi$ & $-t$ & $\phi$ \\ \hline
-
- 0     & 2.25 & 0.12 & 0.20 & -3.50 &   0.0 \\ 
- 1     & 2.45 & 0.15 & 0.35 & -2.10 &  18.0 \\ 
- 2     & 2.66 & 0.17 & 0.50 & -1.75 &  36.0 \\ 
- 3     & 2.82 & 0.18 & 0.75 & -1.50 &  54.0 \\ 
- 4     & 2.96 & 0.19 & 1.00 & -1.30 &  72.0 \\ 
- 5     & 3.07 & 0.20 & 1.60 & -1.10 &  90.0 \\ 
- 6     & 3.17 & 0.21 & 2.20 & -0.75 & 108.0 \\ 
- 7     & 3.27 & 0.22 & 4.25 &  0.00 & 126.0 \\ 
- 8     & 3.37 & 0.23 &      &       & 144.0 \\ 
- 9     & 3.46 & 0.24 &      &       & 162.0 \\ 
-10     & 3.55 & 0.25 &      &       & 180.0 \\ 
-11     & 3.64 & 0.26 &      &       &       \\ 
-12     & 3.72 & 0.27 &      &       &       \\ 
-13     & 3.80 & 0.28 &      &       &       \\ 
-14     & 3.87 & 0.30 &      &       &       \\ 
-15     & 3.94 & 0.33 &      &       &       \\ 
-16     & 4.01 & 0.36 &      &       &       \\ 
-17     & 4.07 & 0.39 &      &       &       \\ 
-18     & 4.12 & 0.43 &      &       &       \\ 
-19     & 4.18 & 0.48 &      &       &       \\ 
-20     & 4.25 & 0.56 &      &       &       \\
-
-\hline
-\end{tabular}
-\caption{Bin limits used for the radiative correction described in section \ref{RadCor}.}
-  \label{tab:RCBins}
-\end{table}
-
-We show in figure \ref{fig:RCexample} a selected sample of radiative correction factors
-($= \delta_{Fe} / \delta_D$) in order to illustrate the expected effect on observables.
-In the large majority of the cases the factors are within 5\% of 1, so we do not expect to
-see a strong effect on the final results where these will be integrated. This is confirmed 
-in figure \ref{} ... In the case of the transverse momentum braodening, the variations
-appear to ...
-
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_2356.png}
-\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_3756.png}
-\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_7756.png}
-\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_10756.png}
-\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_11556.png}
-\includegraphics[width=7cm] {chap5-fig/ElecRadWei_Iron_18956.png}
-\caption {RC factors ($= \delta_{Fe} / \delta_D$) as a function of $\phi$ and 
-$-t$ for a selection of bins specified above each figure.}
-\label{fig:IsoSpin}
-\end{figure}
-
-\begin{figure}[tbp]
-\centering
-\caption {Preliminary results ..., 
-for multiplicity ratios (top) and transverse momentum broadening 
-(bottom). Only statistical errors are shown.}
-\label{fig:RCPlots}
-\end{figure}
+The Monte-Carlo simulation was done using the event generator, GENIE~\cite{Andreopoulos:2009rq}, that describes well electron-nucleus interactions.
+Indeed, GENIE contains the quasi-elastic scattering\footnote{Elastic
+scattering off a single nucleon on nuclei.}, which is considered as the main channel generating radiative events in the DIS region \cite{Akushevich:2007jc}.
+This generator includes also hadronic cascades in nuclei, at which pions might be generated in quasi-elastic events.
+This is an important feature because the quasi-elastic production can not contribute directly to semi-inclusive measurements.
+
+\paragraph{Correction of the Data}
+
+We generated 100 million events with and without radiative effects for each target.
+The RADGEN code gave us the magnitude of inclusive correction coefficients, however, the comparison between the two data sets allows the extraction of semi-inclusive correction factors.
+
+The ratio of inclusive correction factors, as depicted in figure \ref{fig:RadCorrFac}, is relatively small (couple of percents at most) except for low \xb and high $\nu$.
+Similarly for the semi-inclusive factors' ratio shown in figure \ref{fig:RadCorrFacSIDIS} as a function of $z$ and \ptp.
+However, the associated statistical errors are quite large because only a small fraction of the events involved a photon radiation.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=9cm] {chap5-fig/ElecRadWei_Lead.png}
+\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
+\delta_{^2\text{H}}$, as a function of \xb in various $\nu$ bins.}
+\label{fig:RadCorrFac}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics[width=9cm] {chap5-fig/RadGenFactors.png}
+\caption {Ratios of radiative correction factors, $\delta_\text{Pb}/
+\delta_{^2\text{H}}$, as a function of $z$ (top) and \ptp (bottom).}
+\label{fig:RadCorrFacSIDIS}
+\end{figure}
+
+The semi-inclusive part of the radiative correction turned out to be limited 
+in amplitude for the most kinematics, except for high $z$ and \ptp. Thus, we decided to not apply this correction before further studies.
+
+{\color{red} We found a better way to implement the radiative correction,
+that is not limited by the used MC technique. We will implement it in
+the second version of the note as we do not want to delay the review process because this correction that we already found to be small. Sorry about that.}
 
@@
 \includegraphics[width=10cm] {chap5-fig/HallC-Isospin.png}
-\caption {}
-\label{fig:RCexample}
+\caption {Ratios of deuteron over proton for $\pi^+$s (top) and $\pi^-$s (bottom)
+as a function of \xb at $z=0.55$ \cite{Asaturyan:2011mq}.}
+\label{fig:IsoSpin}
 \end{figure}
@@
 contribution from the accidental background. As a consequence, we used the 
-following cut $p_\perp^2 < 2.5$~GeV$^2$/c$^2$, which discards only a very 
+following cut $p_\perp^2 < 1.5$~GeV$^2$/c$^2$, which discards only a very 
 little amount of data (about 1 in 30000 $\pi$). On the contamination side,

### 2017-03-23 1-Answers-Review.tex
Fixed figure link problems and add 120Sn statement

@@
 the signal. We apply a cut
-$p_\perp^2 < 2.5$ GeV$^2$/c$^2$ to remove these regions. One could advocate to even lower this 
-cut, but it would affect significantly the outcome of the $\Delta P_\perp^2$, 
+$p_\perp^2 < 2.5$ GeV$^2$/c$^2$ to remove these regions. One could advocate to lower this 
+cut, but it would affect the outcome of the $\Delta P_\perp^2$, 
 because as often with averages the outliers have a strong impact.
@@
 {\it The Coulomb correction is applied to incoming and outgoing electrons as well as
-produced charged pions. Indeed the effect is invisible in most of the phase space as
-it is comparable to the resolution of the detector (points overlap completely). The 
-effect is small but visible only for very low $z$ pions. It has been implemented 
-because it was suggested it might be big, but we now find that it could have been 
-neglected at our kinematics.} \\
+produced charged pions. Indeed the effect is small in most of the phase space, but 
+by slightly shifting the $z$ distribution it slightly changes the normalization. A
+point to point effect is also visible for low $z$ pions.
+
+TODO Add figure as a function of A1/3 and z.} \\
 
@@
 
-{\it This is an interesting question and we might have overlooked this problem. We changed
-our method of calculating the statistical errors to avoid the double counting, see
-discussion in the 2.3.1. section about the method to calculate the error bars. } \\
+{\it This is an interesting question and we might have overlooked this problem. We noted an error
+in our function calculating the statistical errors. This change in size somewhat
+modifies our initial statement,
+
+TODO Complete the answer when full results are there.} \\
 
@@
 
-{\it The point-to-point errors include only contributions from the bad particle 
+{\it The point-to-point errors include only contributions from the particle 
 identifications and acceptance effects. It is also different for every bin, so

### 2018-02-23 chap5.tex
Add notes on possible checks

@@
 \end{table}
+
+\subsection{Cross Checks}
+\label{sec:XChecks}
+
+The goal here is to check known results in order to make sure we have normalization right. This is 
+especially important since discrepencies with Hayk's analysis have been found and demonstrated the 
+normalization to be a tricky problem.
+
+\subsubsection{Inclusive electron normalization}
+
+We expect the EMC ratio to cross unity around 0.3 - 0.35 and we know precisely the target thickesses.
+From these we check our inclusive normalization...
+
+\subsubsection{Pion ratio from Hall-C}
+
+In paper from Hall-C they present results shown in fig 20 (to reproduce here). The bin corresponds to 
+1.5 < Q2 < 4 GeV2, 0.35 < xb < 0.45, 0.5 < z < 0.6 and Pt2 < 0.2. They find ratios of 0.556+-0.011 for pi+
+and 0.520+-0.011 for pi-. Note that it is not a double ratio and should be affected by the EMC effect,
+moreover they do not make an isospin correction which is 1.5\%.
+
+Put my result here

### 2019-01-23 1-Answers-Review.tex
Finalized the answers

@@
 version. The section about radiative corrections has been updated with the new method.
-We maybe should meet during the next CLAS collaboration meeting (end of March) to clarify 
-some of the simpler issues.} \\
+We can have a meeting to clarify some of the simpler issues more rapidly.} \\
 
@@
 have been removed in the process). It is always possible to reproduce the figure with a root 
-routine if the reviewer feel it is necessary.
+routine if the reviewer feel it is necessary to know the specific run used.
 
@@
 lack the problematic run which have been deleted. At this stage, it would be rather time
-consuming to recover all the data and update the softwares to run on the new machines, so 
+consuming to recover the raw data and update all the softwares to run on the new machines, so 
 we did not produce this figure. If the reviewer think it is necessary to update this 
@@
 The sum indicated runs over all the recorded events, it is not associated to the weight
-bins or anything like that. We tried to adapt the language in the note to make it clearer.} \\
+bins or anything like that. We adapted the language in the note to make it clearer.} \\
 
@@
 
-{\it It is indeed an important issue. A related fact to keep in mind (while it is presented 
-later in the note in 2.5.1) is that the main issue there is the quantity of accidentals. Since
-the cross section get really small in this region, accidentals start to overcome
-the signal. We apply a cut
-$p_\perp^2 < 2.5$ GeV$^2$/c$^2$ to remove these regions. One could advocate to lower this 
-cut, but it would affect the outcome of the $\Delta P_\perp^2$, 
-because as often with averages the outliers have a strong impact.
-
-On the bright side, the slope and behavior appear to be rather well described by the MC
-simulation. We feel that a good reproduction of the data is an indication that the 
-acceptance correction will behave properly.} \\
+{\it It is indeed a problematic issue, linked to the abscence of radiative effects in the 
+simulation. At the time that it was generated, no better simulation was available. This
+discrepency in $\nu$ motivates to also use it for the binning of the acceptance. This way,
+it limits the impact of this difference.} \\
 
@@
 
-The first set of variables is the one used for the acceptance correction used for results,
-while the second set is only used to evaluate the systematic errors. In the 
+The first set of variables is the one used for the acceptance correction presented in the results,
+while the second set is only used to evaluate the systematic errors associated with the correction. In the 
 note, the formulas are generally given only for the first set for simplicity.
@@
 the best way
-to keep these bins while discarding bins where the sizze of the weight is less problematic 
+to keep these bins while discarding bins where the size of the weight is less problematic 
 but with issues concerning bin migration and statistics was to apply this type of cut.
@@
 step acceptance correction is hopefully going to be clearer. It is the same as the method used 
-in the previous L. El Fassi et al. analysis note. The second step of the procedure is
+in the previous L. El Fassi et al. analysis note of eg2 data. The second step of the procedure is
 specifically used to take care of the bins that are removed by the cut on weights. You 
 can see in the formula that the weights
-of the previously calculated acceptance are used in this step, ensuring that we do not
+of the previously calculated acceptance are used in this second step, ensuring that we do not
 double correct the data.
@@
 transverse momentum distribution. Completely cutting a part of the distribution
-would indeed solve the acceptance problem but would make the $\langle p_\perp^2 \rangle$
-measurement meaning less. We therefore have to live with it and do our best to
+would indeed solve the acceptance problems for $\pi^-$ but would make the $\langle p_\perp^2 \rangle$
+measurement meaningless. We therefore have to live with it and do our best to
 reconstruct the whole distribution even if it means having larger error bars.} \\
@@
 
-{\it Sorry, we overlooked this for these intermediary plots. TO BE CORRECTED} \\
+{\it Sorry, we overlooked this for these intermediary plots.} \\
 
@@
 
-{\it Sorry, it is a mistake on our part, there is no reason. TO BE CORRECTED. And
-add figures after radiative correction!} \\
+{\it Sorry, it is a mistake on our part, there is no reason.} \\
 
@@
 by slightly shifting the $z$ distribution it slightly changes the normalization. A
-point to point effect is also visible for low $z$ pions.
-
-TODO Add figure as a function of A1/3 and z.} \\
+point to point effect is also visible for low $z$ pions. Note that in general, there
+is also a focussing factor in Coulomb corrections, but they happen to cancel out in
+our specific observables.} \\
 
@@
 {\it This correction is here to take care of the u/d quark imbalance in heavier nuclei.
-Indeed the production rate of positive pions on neutrons is significantly reduced and that
+Indeed the multiplicity of positive pions on neutrons is significantly smaller than on protons and that
 should not be mistaken with absorbtion in the nuclear medium. We clarified the text in the
-note, hopefully it is now clear.} \\
+note.} \\
 
@@
 
-{\it The sentence has been revised to list all effects tested. } \\
+{\it The sentence has been revised to list all effects tested.} \\
 
@@
 {\it Resolution is the same, it looks wider because, on this figure, we show the integrated 
-result over the 6 sectors.} \\
+result over the 6 sectors, which are slightly shifted between each other.} \\
 
@@
 
-{\it Multiplicity ratios are a double ratio. The claim is that the semi inclusive part 
+{\it Multiplicity ratios are a double ratio. The claim is that the semi-inclusive part 
 is not affected, but the inclusive electron ratio is affected. This is included
-as a normalisation error. We revisited slightly the paragraph to make it clearer.} \\
+as a normalisation error. We revisited the paragraph to make this point clearer.} \\
 
@@
 
-{\it This is an interesting question and we might have overlooked this problem. We noted an error
-in our function calculating the statistical errors. This change in size somewhat
-modifies our initial statement,
-
-TODO Complete the answer when full results are there.} \\
+{\it This is an interesting question and we might have overlooked this problem. Looking into the
+issue we noticed an error in our function calculating the statistical errors. This change 
+would modify our initial statement. Altogether, after reviewing the question, we believe that 
+because the different acceptance are calculated from the same simulated data and applied to 
+the same experimental data, our systematic error calculation should not include the effect 
+of statistical errors. In conclusion, we removed the previous statement and now fully include 
+the systematic errors for the transverse momentum broadening.} \\
 
@@
 
-{\it FIGURES NEED TO BE UPDATED WITH NEW ERROR BAR DISPLAY.} \\
+{\it We add this on the figures intended to be published.} \\
 
@@
 {\it We decided to keep the normalization error, not the point to point. This was not
-said clearly in the text, it is now clarified. TO CLARIFY WHEN SORTED OUT.} \\
+said clearly in the text, it is now changed as mentioned above.} \\
 
@@
 sigma up. So for the overall normal deviation (sigma) we quadratically sum them,
-leading to 1.5.} \\
+leading to 1.5, you think it should say 2?} \\
 
@@
 {\it This langage refers to figure 1, where we define a production time and a 
-formation time. We tried to rephrase for more clarity.}\\
+formation time. We rephrased for more clarity.}\\
 

### 2019-01-23 chap5.tex
Correct the Delta beta formula
Finalized the answers

@@
 cut that reduced significantly possible contaminations. Our measurement uses all the 
-semi-inclusive production and is therefore more sensitive to contaminations. See next 
-question for profiles.
+semi-inclusive production and is therefore more sensitive to contaminations.
 
@@
 \begin{align}
-    p_\pi &\leq 3.375 \text{ GeV/c : }
-  & \Delta \beta &> \max\left(-0.03,{p \over\sqrt{p^2+0.4^2}}\right), \\ 
-    p_\pi &> 3.375    \text{ GeV/c : }
-  & \Delta \beta &> \max\left(-0.02,{p \over\sqrt{p^2+0.7^2}}\right).
+    p_\pi &\leq 1.838 \text{ GeV/c : }
+  & \Delta \beta &> \max\left(-0.03,{p \over\sqrt{p^2+0.4^2}}- {p \over \sqrt{p^2 + m_\pi^2}}\right), \\ 
+    p_\pi &> 1.838    \text{ GeV/c : }
+  & \Delta \beta &> \max\left(-0.02,{p \over\sqrt{p^2+0.7^2}}- {p \over \sqrt{p^2 + m_\pi^2}}\right).
 \end{align}
@@
 
-The much more apparent contamination sources than for negative pions, allow to study 
-the TOF profile much more thoroughly. You can see in figures~\ref{TOF-1}, \ref{TOF-2} and 
+The much more apparent contamination sources than for negative pions, motivates us to study 
+the TOF profile much more thoroughly. One can see in figures~\ref{TOF-1}, \ref{TOF-2} and 
 \ref{TOF-3} the $\Delta \beta$ profiles for many momentum slices. In figure~\ref{TOF-1}
@@
 
+\subsubsection{Endcap correction}
+
+TO BE IMPLEMENTED IN THE ANALYSIS
+
+The goal of this work is to correct the measured multiplicity ratio:
+\begin{equation}
+  R_h^A |_{corr} = {N_h^A / N_e^A \over (N_h^D-N_h^{EC}) / (N_e^D-N_e^{EC})},
+\end{equation}
+with the $EC$ target being the endcaps of the liquid target. Using a Taylor expension at first order for small $N^{EC}$, we find that:
+\begin{equation}
+  {N_h^D-N_h^{EC} \over N_e^D-N_e^{EC}} = {N_h^D \over N_e^D} - {N_h^{EC} \over N_e^D} + {N_e^{EC} N_h^D \over {N_e^D}^2}.
+\end{equation}
+After few straightforward transformation, we get
+\begin{equation}
+  R_h^A |_{corr} = R_h^A \left( 1 - {N_e^{EC} \over N_e^D} \left( 1-R_h^{Al} \right) \right).
+\end{equation}
+Based on target thickness ${N_e^{EC} \over N_e^D} \sim 0.03$ and $R_h^{Al} \sim 0.65$, the correction is on average a 1\% decrease of the measured multiplicity ratio.
+
+With the same method, the transverse momentum broadening can be corrected with:
+\begin{equation}
+  \Delta P_T^2 |_{corr} = \Delta P_T^2 + R_h^{Al} {N_e^{EC} \over N_e^D} \Delta P_T^2|_{Al}
+\end{equation}
+
 \subsection{Systematic Uncertainties}
@@
 the significantly large errors for $\pi^-$s, which were expected, due to their 
-lower acceptance and larger weights.
-
-Systematic errors are also
+larger acceptance weights. Systematic errors are also
 considerably larger for \dpt measurements. This is mainly due to the nature of 
 the \dpt observable; as it is a difference, it enhances relative errors 
-significantly. Also, as shown in figure~\ref{fig:AcceptPlots}, error bars 
-became much larger for the corrected \dpt from the acceptance effect. This 
-result indicated an important statistical sensitivity introduced by our 
-weighting methods. The errors on \dpt are of the same order, or smaller, than 
-the differences observed between the two weighted data-sets. This is an 
-indication that the uncertainties reported in table \ref{tab:SysAcc} are, in 
-nature, similar to the statistical errors, in the sense that both originate 
-from the large variation between event-by-event weights. For this reason, we 
-decided not to include this error in our systematic budget to avoid double 
-counting this effect.
+rather than cancelling them.
 

### 2019-03-13 intro.tex
Small fixes (pt max = 1.5 GeV2)
Minor text edits in introductory chapter

@@
 
-The hadronization in nuclear matter is a key process of the Quantum 
+The hadronization in nuclear matter is also a key process for the study of the Quantum 
 Chromo-Dynamics theory (QCD) because it leads to major theoretical 
@@
 A quantitative understanding of the hadronization process in nuclei is also of importance for neutrino experiments.
-Indeed they use nuclear targets to maximize their cross sections and therefore have to account for the nuclear effects, including hadronization.
+Indeed, these use nuclear targets to maximize their cross sections and therefore have to account for the nuclear effects, including hadronization.
 
@@
 
-In this analysis we use the following Semi-Inclusive Deep Inelastic Scattering (SIDIS) variables:
+In this analysis, we use the following Semi-Inclusive Deep Inelastic Scattering (SIDIS) variables:
 \begin{itemize}
  \item $\nu = E_i - E_f$ is the energy transferred by the lepton probe in the laboratory frame, where $E_i$ is the beam energy and $E_f$ is the scattered electron energy,
- \item $Q^2 = 4 E_i E_f \sin ^2(\theta_e / 2)$ is the 4-momentum transferred, with $\theta_e$ is the polar angle of a scattered electron,
- \item $x_{Bj} = {{Q^2} \over {2 M_n \nu}}$ is the proton momentum fraction carried by the struck quark, with $M_n$ is the nucleon mass,
+ \item $Q^2 = 4 E_i E_f \sin ^2(\theta_e / 2)$ is the 4-momentum transferred, where $\theta_e$ is the polar angle of a scattered electron,
+ \item $x_{Bj} = {{Q^2} \over {2 M_n \nu}}$ is the proton momentum fraction carried by the struck quark, with $M_n$ the nucleon mass,
  \item $W^2 = M_n^2 - Q^2 + 2 M_n \nu$ is the mass squared of the hadronic final state,
- \item $z_h = E_h / \nu$ is the virtual photon energy fraction carried by the measured hadron, with $E_h$ is the hadron energy,
+ \item $z_h = E_h / \nu$ is the virtual photon energy fraction carried by the measured hadron, with $E_h$ the hadron energy,
  \item $P_T^2$ is the hadron transverse momentum measured with regard to the virtual photon direction,
@@
  \item $x_F = P_L/P_L^{max}$ is the longitudinal momentum fraction carried by the hadron, and calculated with respect to the virtual photon direction in the laboratory frame.
+ Effectively this translate into: $$ x_F = 2 {z M_n \nu^2 - z Q^2 \nu - (M_n+\nu)(\boldsymbol{P_h \cdotp q}) \over (W^2-M_h^2) \sqrt{\nu^2+Q^2} } .$$
 \end{itemize}
@@
 $N^e_A$ and $N_A^h$ are the number of electrons and semi-inclusive hadrons $h$ measured simultaneously on a target $A$.
-The multiplicity ratio represents the attenuation of the hadron $h$ in a nuclear target~$A$.
+The multiplicity ratio represents the relative production rate of the hadron $h$ in a nuclear target~$A$.
 \newline
@@
 interactions.
-For illustration, we will give an example of each case, but for more detailed information, we refer the readers again to our reference~\cite{Accardi:2009qv}, which is more exhaustive and highlights also models describing RHIC's experiments.
+For illustration, we will give an example of each case, but for more detailed information, we refer the readers again to the Accardi {\it et al.} review~\cite{Accardi:2009qv}, which is more exhaustive and highlights also models describing RHIC's experiments.
 
@@
 Moreover, various calculations have described the parton energy loss in the nuclear medium using the $\hat q$ (GeV$^2$ fm$^{-1}$) parameter, that is defined as the quark transverse momentum normalized by its propagation path length.
-In these models, $\hat q$ is mainly related to the $P_T$ broadening observable.
+In these models, $\hat q$ can also be related to the $\Delta \langle P_T^2 \rangle$ observable.
 The main difficulty of quark energy loss models is the lack of a coherent description for both multiplicity ratios and $P_T$ broadening behaviors.
@@
 
-The other transport model, GiBUU~\cite{Gallmeister:2007an}, is based on the 
+The transport model, GiBUU~\cite{Gallmeister:2007an}, is based on the 
 Boltzmann equation that employs hadronic and pre-hadronic interactions in the nuclear matter without involving any quark energy loss.
@@
 
-Furthermore, B.Z.~Kopeliovich et al.
+Finally, B.Z.~Kopeliovich et al.
 \cite{Kopeliovich:2008uy} described the process by neither neglecting the quark energy loss nor the hadron absorption, but used both $\Delta \langle P_T^2 \rangle$ and $R_A^h$ observables to differentiate between these effects.
@@
 
-Hadron multiplicity ratios in nuclei were measured in numerous lepton 
+Hadron multiplicity ratios in nuclei were originaly measured in numerous lepton 
 facilities: L.S.~Osborne {\it et al.} \cite{Osborne:1978ai} at SLAC,
@@
 Figures \ref{fig:her1}, \ref{fig:her2} and \ref{fig:her3} show a sample of 
-the most recent HERMES data~\cite{Airapetian:2007vu}, where numerous hadrons were individually studied, and new variables linked with the transverse momentum were used in addition to the usual multiplicity ratio.
+the most recent HERMES data~\cite{Airapetian:2007vu} from DESY, where numerous hadrons were individually studied, and new variables linked with the transverse momentum were used in addition to the traditional multiplicity ratio.
 

### 2019-03-14 chap5.tex
Edits of first part of chap5

@@
 
-Pions are detected in the angular range from $\sim$10 to $\sim$140 degrees 
+Pions are detected starting at a momentum of 250 MeV in the angular range 
+from $\sim$10 to $\sim$140 degrees 
 using only DC and SC signals. To identify negatively charged pions, we select 
@@
 high momentum. As the CC is not efficient enough for a hadron separation, the 
-numerous kaons and protons should be removed by the following tighter TOF cuts:
+kaons and protons contributions are reduced by the following tighter TOF cuts:
 
@@
 
-The much more apparent contamination sources than for negative pions, motivates us to study 
-the TOF profile much more thoroughly. One can see in figures~\ref{TOF-1}, \ref{TOF-2} and 
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {chap5-fig/pip_data.png} 
+\caption {$\Delta \beta$ of positively charged particles as a function of momentum (GeV/c).
+The red lines shows the applied cuts to select positive pions.
+The blue lines indicate other particles' theoretical positions, and present from top to
+bottom positrons, muons, kaons and protons.}
+\label{PipTOF}
+\end{figure}
+
+In opposition with negative pions, contamination sources are apparent and motivate a careful 
+study of the TOF profile. One can see in figures~\ref{TOF-1}, \ref{TOF-2} and 
 \ref{TOF-3} the $\Delta \beta$ profiles for many momentum slices. In figure~\ref{TOF-1}
-one can see some contamination from lighter leptons ($e+$ and $\mu^+$). These represent
+one can see some contamination from lighter leptons ($e^+$ and $\mu^+$). These represent
 a very small amount and one can see some justification for the choice of a $\pm 0.03$
@@
 These cuts minimize the kaon contamination, below 2.5~GeV/c, and the 
-proton contamination for all momenta. The kaon contribution cannot be avoided, however, it should remain small ($\sim$ 3\% according to simulation) 
+proton contamination for all momenta. The kaon contribution cannot be avoided, however, it should remain small (peaking $\sim$ 3\% according to our simulation) 
 with only a small effect on our final results (see section \ref{SysId} 
@@
 
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=8cm] {chap5-fig/pip_data.png} 
-\caption {$\Delta \beta$ of positively charged particles as a function of momentum (GeV/c).
-The red lines shows the applied cuts to select positive pions.
-The blue lines indicate other particles' theoretical positions, and present from top to
-bottom positrons, muons, kaons and protons.}
-\label{PipTOF}
-\end{figure}
-
 \subsubsection{Target Determination}
@@
 To differentiate between the two targets and remove the background, we need to 
-determine the origin of our final-state particles.
+determine the point of origin of our final-state particles.
 As illustrated in figure~\ref{vertex}, the small misalignment of the beam with the CLAS detector led to an artificial shift on different sectors' z-vertex positions.
@@
 Those values were obtained from the fit of the solid target distribution on each sector.
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=10cm] {chap5-fig/Vertex_el_data.png}
+\caption {Sector-by-sector electrons' vertex distributions.
+The latter are reconstructed along the beam direction and relative to the center of CLAS located at 0~cm.
+The red lines show the applied cuts to select the two targets.}
+\label{vertex}
+\end{figure}
 
@@
 \end{table}
+
+The detected electrons are associated with the solid target if their vertex 
+position is less than 1.5~cm ($\sim$3~$\sigma$) from the values shown on table 
+\ref{tab:targets}.
+For the liquid target, the cut is a bit larger, 2 cm, in order to count for the cryogenic target's size (see figure \ref{vertex}).
+The pions' vertex was checked against the electron one and was imposed to satisfy this additional condition $| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=8cm] {chap5-fig/Vertex_pi_data.png}
+\caption {The difference between electrons and pions z-vertex positions.
+$\pi^+$s and $\pi^-$ are plotted, respectively, in the top and bottom panels.
+The red lines show the applied cuts to select both pions.}
+\label{fig:dvzpi}
+\end{figure}
 
@@
 error on acceptance corrections in regard to the error budget already associated
-to the procedure.
+to the measurements.
 
@@
 \caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
-number for the different solid targets.}
+number for the different solid targets. Top left is for carbon, top right
+aluminum, middle left iron, middle right tin and bottom is for lead.}
 \label{VertexSolid}
@@
 \caption {Vertex origin along $z$ (in cm) of electrons as a function of run 
-number for the deuterium target in different solid targets configurations.}
+number for the deuterium target in different solid targets configurations.
+Top left is for carbon, top right iron, bottom left tin and bottom right is for lead.}
 \label{VertexLiquid}
-\end{figure}
-
-The detected electrons are associated with the solid target if their vertex 
-position is less than 1.5~cm ($\sim$3~$\sigma$) from the values shown on table 
-\ref{tab:targets}.
-For the liquid target, the cut is a bit larger, 2 cm, in order to count for the cryogenic target's size (see figure \ref{vertex}).
-The pions' vertex was checked against the electron one and was imposed to satisfy this additional condition $| Vz^{e^-} - Vz^{\pi} | < 3$ cm (see figure \ref{fig:dvzpi}).
-
-\begin{figure}[p]
-\centering
-\includegraphics[width=10cm] {chap5-fig/Vertex_el_data.png}
-\caption {Sector-by-sector electrons' vertex distributions.
-The latter are reconstructed along the beam direction and relative to the center of CLAS located at 0~cm.
-The red lines show the applied cuts to select the two targets.}
-\label{vertex}
-\end{figure}
-
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=8cm] {chap5-fig/Vertex_pi_data.png}
-\caption {The difference between electrons and pions z-vertex positions.
-$\pi^+$s and $\pi^-$ are plotted, respectively, in the top and bottom panels.
-The red lines show the applied cuts to select both pions.}
-\label{fig:dvzpi}
 \end{figure}
@@
 ratios were consistent with our target's thicknesses given in \cite{Hakobyan:2008zz} 
-except for a carbon target. For that reason, the density of the latter was 
-recently remeasured, and its new value was finally matching our 
+except for the carbon target. For that reason, the density of the latter was 
+remeasured, and its new value was finally matching our 
 data\footnote{i.e. (1.747+/-0.0007)g/cm$^3$ instead of 2.235 g/cm$^3$}.
@@
 \end{figure}
+
+%TODO provide an updated target table
 
@@
 We also apply a cut on the energy transferred fraction, $y = \nu/E_{beam} < 0.85$.
-This cut aims to remove the low energy electrons that are significantly affected by radiative effects and sat at the limit of our trigger threshold.
+This cut aims to remove the low energy electrons that are significantly affected by radiative effects and are at the limit of our trigger threshold.
 
@@
 systematic errors evaluated below. First we found an error with how the formula
-above was implemented and corrected it. This reduces the size of statistical 
+for transverse momentum broadening was implemented and corrected it. This 
+reduces the size of statistical 
 error bars of the transverse momentum broadening by roughly a factor 2 to 3. 
-
-TODO See new results and re evaluate statement below.
-We found first that the correlation between the weights should reduce
+We also reflected that the correlation between the weights should reduce
 the statistical errors. In a given bin the weights associated with each 
@@
 error bars. However, we do not see a method to properly take this 
-effect fully into account in term of purely statistical error bars. In order
-to solve this issue we came back to a point by the committee on the topic of 
-systematic error bars (Q 24). There it was noted that some of these effects are
-double counted once in the statistical error and once in the systematic. As these
-errors are solely due to the acceptance correction, we decided to account them 
-only in the systematic error budget. So we reverted statistical errors to equations
-\ref{eq:MRError} and \ref{eq:DPtError} and keep the full systematic errors as they
-were evaluated before.
+effect fully into account in term of purely statistical error bars, and
+remains as is. Finally, 
+it was noted that some of the effects were double counted once through the 
+statistical error on the acceptance correction and the systematics associated
+with the correction. So, we decided to account only the systematic error budget
+and use purely statistical errors of equations
+\ref{eq:MRError} and \ref{eq:DPtError}. In summary, we concluded that the 
+systematic error contribution associated to the statistics of the 
+simulation sample were indeed a double counting and are not used anymore
+in any error bars.
 

### 2019-03-22 chap5.tex
minor edits

@@
 The acceptance correction consists of applying weights to the experimental data
-event by event to correct for any detection inefficiencies of used detectors.
+event by event to correct for the detection inefficiencies of the detectors.
 Incidentally, it also corrects for other small detection issues, such as 
-misidentification and re-scattering on detector material. The quality 
+misidentification and scatterings on detector material. The quality 
 of the correction depends on the ability of the simulation to reproduce the 
 experiment, the accumulated statistics, and the size of interfering effects, such 
-as the bin migration. For this correction, we applied the method from the 
-approved and published analysis from the same eg2 data~\cite{ElFassi:2008}.
+as bin migration. For this correction, we applied the method from the 
+approved analysis from the same eg2 data~\cite{ElFassi:2008}.
 
@@
 to that done with the experimental data.
-% TODO GPP factors
+% TODO GPP factors: -a1.7 -b1.9 -c2. -f1. -R41147 (likely the one used)
 
@@
 feature should not affect us too much, because we are cutting only the tail of the 
-distribution in both cases.
-Second, since in the simulation the beam is perfectly aligned with CLAS, the vertex cuts do not need to be shifted from one sector to an other.
-Therefore, we do not apply the shift from table \ref{tab:vertex} to the simulated data; the resulting cuts are shown in figure~\ref{simvertex}.
+distribution in both cases. Second, since in the simulation the beam is perfectly 
+aligned with CLAS, the vertex cuts do not need to be shifted from one sector to 
+another. Therefore, we do not apply the shift from table \ref{tab:vertex} to the 
+simulated data; the resulting cuts are shown in figure~\ref{simvertex}.
 
@@
 \includegraphics[width=9cm] {chap5-fig/Vertex_el_sim.png}
-\caption {Sector by sector electrons' vertex distributions from the {\bf simulated data}.
-The latter are reconstructed along the beam direction, and relative to the CLAS center.
-The red lines show the used cuts to select both targets.}
+\caption {Sector by sector electrons' vertex distributions from the 
+{\bf simulated data}. The latter are reconstructed along the beam direction, 
+and relative to the CLAS center. The red lines show the used cuts to select 
+both targets.}
 \label{simvertex}
@@
 perfect. The differences are due to the PYTHIA simulation, which is not including some 
-physical effects, such as radiative and diffractive processes.
+physical effects, such as radiative effects and diffractive processes.
 
@@
 where $\delta \omega / \omega$ is the relative error on the weight, and $R_c$ is the 
-proportion of reconstructed events initially generated in an other kinematical bin. 
+proportion of reconstructed events initially generated in another kinematical bin. 
 Figure~\ref{fig:AccCoef} shows $\omega$ distributions after applying these cuts. Around 
@@
 to keep these bins while discarding bins where the weight might be slightly smaller but which 
-have issues with bin migration and statistics was to apply this set of cuts.
-
-In order to correct for these droped bins and reduce the sensitivity to the arbitrary in
-the choice of the weights' cuts, we corrected the data with an additional two dimensional 
-reweighting factor as:
+have issues with bin migration and statistics was to apply the cuts presented above.
+
+This process can create a bias, if for instance low $Q^2$ bins are more often dropped.
+So, in order to correct for these bins and reduce the sensitivity to the arbitrary in
+the choice of the cuts, we corrected the data with an second two dimensional 
+acceptance correction as:
 \begin{equation}
@@
 
-In order to correct the number of electrons in multiplicity ratios, we followed the semi-inclusive acceptance correction method by using only the two first dimensions ($\nu$ and $Q^2$).
-However, the reweighting was not used for electrons as all non-empty bins pass the two cuts, \ref{eq:AccL1} and \ref{eq:AccL2}.
+In order to correct the number of electrons in multiplicity ratios, we followed the 
+semi-inclusive acceptance correction method by using only the two first dimensions 
+($\nu$ and $Q^2$). However, the reweighting was not used for electrons as all 
+non-empty bins pass the two cuts, \ref{eq:AccL1} and \ref{eq:AccL2}.
 
@@
 represented, shows the new results after applying the acceptance correction.
-The acceptance correction effects appear to be in the order of $10$\% for 
-multiplicity ratios and $30$\% for the transverse momentum broadening.
-This is a surprisingly significant correction with regard to a few centimeters separating the two targets.
-The reason for such a large correction is that the small shift in the $z$-vertex position changes slightly the minimum angle of the detector in the region where most hadron production is concentrated, {\it i.e.} at low \pt close to the beam line.
-The $\pi^-$s were more affected due to the inbending magnetic field.
-Indeed, the low \pt $\pi^-$s had very low acceptance which led to large correction factors.
-The large spread in weights makes the errors on \dpt very large, and the related results difficult to exploit.
-However, our transverse momentum broadening
-results of both pions matched each other after this correction, which is similar 
+The acceptance correction effects appear to be of the order of $10$\% for 
+multiplicity ratios and $30$\% for the transverse momentum broadening. This 
+is a surprisingly significant correction with regard to a few centimeters 
+separating the two targets. The reason for such a large correction is that 
+the small shift in the $z$-vertex position changes slightly the minimum 
+angle of the detector in the region where most hadron production is 
+concentrated, {\it i.e.} at low \pt close to the beam line. The 
+$\pi^-$s were more affected due to the inbending magnetic field. Indeed, 
+the low \pt $\pi^-$s had very low acceptance which led to large correction 
+factors. The large spread in weights makes the errors on \dpt rather large. 
+However, the transverse momentum broadening 
+results of both pions matched each other better after this correction, which is similar 
 to the HERMES results (see figure~\ref{fig:her3}).
@@
 \ref{tab:Coulomb} contains the used values of $V_0$ and $\bar V$ on different 
-nuclear target's analysis. The Coulomb correction is applied to both electrons 
-and charged pions before calculating the plotted kinematical variables.
+nuclear target's analysis.
 
@@
 
-TODO Add figures of the effect and comment from review answers!
+The Coulomb correction is applied to incoming and outgoing electrons as well as
+produced charged pions. The effect of the correction is shown in figure \ref{fig:CCPlots},
+we observe that it is small in most of the phase space, but by slightly shifting 
+the $z$ distribution it affects the normalization at a couple of percent level. A
+point to point effect is also visible for low $z$ pions. Note that in general, there
+is also a focussing factor in Coulomb corrections, but they happen to cancel out in
+our specific observables.
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
+\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
+\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
+\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
+\caption {Preliminary results are compared with the acceptance corrected ones, 
+for multiplicity ratios (top) and transverse momentum broadening 
+(bottom). Only statistical errors are shown.}
+\label{fig:CCPlots}
+\end{figure}
 
@@
 binning for the radiative corrections than for acceptance as the computing time 
-to calculate weights is more reasonnable (around 1000 days of cpu time).
+to calculate weights is more reasonnable ("only" around 1000 days of CPU time).
 
@@
 ($= \delta_{Fe} / \delta_D$) in order to illustrate the expected effect on observables.
-In the large majority of the cases the factors are within 5\% of 1, so we do not expect to
+In the large majority of the cases the factors are within 5\% of 1. Therefore, we do not expect to
 see a strong effect on the final results where these will be integrated. This is confirmed 
-in figure \ref{} ... In the case of the transverse momentum braodening, the variations
-appear to ...
+in figure \ref{fig:RCPlots}, where the radiative correction appears limited to a few percents. 
+In the case of the transverse momentum braodening, the variations appear to be similar in size 
+and not too worrisome.
 
@@
 \centering
-\caption {Preliminary results ..., 
+\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
+\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
+\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
+\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
+\caption {Preliminary results including radiative corrections
+compared to the ones without, 
 for multiplicity ratios (top) and transverse momentum broadening 
@@
 Put my result here
+
+\subsubsection{Pion ratio from HERMES}

### 2019-04-16 chap5.tex
Small progress on reread

@@
 numbers and assumes that this isospin correction does not depend on any
-kinematic variable. We found that multiplicity ratios of $\pi^+$ need small
+kinematic variable. We decide to apply such a simple correction to make it easy
+to remove it for comparison with models or other data in the future.
+
+We found that multiplicity ratios of $\pi^+$ need small
 corrections, shown in table~\ref{tab:isospin}. The effect on $\pi^-$s was 
@@
 this result was expected and demonstrates the importance of this correction.
+%TODO Check if that is still true
 
@@
 
-\subsubsection{Endcap correction}
-
-TO BE IMPLEMENTED IN THE ANALYSIS
-
-The goal of this work is to correct the measured multiplicity ratio:
-\begin{equation}
-  R_h^A |_{corr} = {N_h^A / N_e^A \over (N_h^D-N_h^{EC}) / (N_e^D-N_e^{EC})},
-\end{equation}
-with the $EC$ target being the endcaps of the liquid target. Using a Taylor expension at first order for small $N^{EC}$, we find that:
-\begin{equation}
-  {N_h^D-N_h^{EC} \over N_e^D-N_e^{EC}} = {N_h^D \over N_e^D} - {N_h^{EC} \over N_e^D} + {N_e^{EC} N_h^D \over {N_e^D}^2}.
-\end{equation}
-After few straightforward transformation, we get
-\begin{equation}
-  R_h^A |_{corr} = R_h^A \left( 1 - {N_e^{EC} \over N_e^D} \left( 1-R_h^{Al} \right) \right).
-\end{equation}
-Based on target thickness ${N_e^{EC} \over N_e^D} \sim 0.03$ and $R_h^{Al} \sim 0.65$, the correction is on average a 1\% decrease of the measured multiplicity ratio.
-
-With the same method, the transverse momentum broadening can be corrected with:
-\begin{equation}
-  \Delta P_T^2 |_{corr} = \Delta P_T^2 + R_h^{Al} {N_e^{EC} \over N_e^D} \Delta P_T^2|_{Al}
-\end{equation}
+%\subsubsection{Endcap correction}
+
+%TO BE IMPLEMENTED IN THE ANALYSIS
+
+%The goal of this work is to correct the measured multiplicity ratio:
+%\begin{equation}
+%  R_h^A |_{corr} = {N_h^A / N_e^A \over (N_h^D-N_h^{EC}) / (N_e^D-N_e^{EC})},
+%\end{equation}
+%with the $EC$ target being the endcaps of the liquid target. Using a Taylor expension at first order for small $N^{EC}$, we find that:
+%\begin{equation}
+%  {N_h^D-N_h^{EC} \over N_e^D-N_e^{EC}} = {N_h^D \over N_e^D} - {N_h^{EC} \over N_e^D} + {N_e^{EC} N_h^D \over {N_e^D}^2}.
+%\end{equation}
+%After few straightforward transformation, we get
+%\begin{equation}
+%  R_h^A |_{corr} = R_h^A \left( 1 - {N_e^{EC} \over N_e^D} \left( 1-R_h^{Al} \right) \right).
+%\end{equation}
+%Based on target thickness ${N_e^{EC} \over N_e^D} \sim 0.03$ and $R_h^{Al} \sim 0.65$, the correction is on average a 1\% decrease of the measured multiplicity ratio.
+%
+%With the same method, the transverse momentum broadening can be corrected with:
+%\begin{equation}
+%  \Delta P_T^2 |_{corr} = \Delta P_T^2 + R_h^{Al} {N_e^{EC} \over N_e^D} \Delta P_T^2|_{Al}
+%\end{equation}
+%
 
@@
 
-In this section, we are presenting details of our two types of systematic uncertainties.
-The point-to-point systematic errors, that vary with kinematical variables, were calculated bin by bin for each result.
-They are caused by uncertainties on the particles' identification cuts and the CLAS acceptance.
-The normalization errors are attributed globally since they don't depend on kinematics.
-They are due to acceptance effects, target's misidentification, and the isospin correction.
+In this section, we are presenting details the systematic uncertainties. The 
+point-to-point systematic errors, that vary with kinematical variables, were 
+calculated bin by bin for each result. They are caused by uncertainties on the 
+particles' identification cuts and the CLAS acceptance. The normalization 
+errors are attributed globally since they don't depend on kinematics. They 
+are due to acceptance effects, target's misidentification, and the isospin 
+correction.
 

### 2019-04-16 chap5.tex
Update all analysis figures

@@
 
-\begin{figure}[htb]
-\centering
-\includegraphics[width=7.4cm] {chap5-fig/a_RvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/a_RvZ.png} 
-\includegraphics[width=7.4cm] {chap5-fig/a_PvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/a_PvNu.png} 
-\caption {Results for multiplicity ratios (top) and the transverse momentum 
-broadening (bottom) before applying any corrections.}
+\begin{figure}[p]
+\centering
+\includegraphics[width=7.4cm] {new-fig/40_Adep_Ratio_A13_0.png} 
+\includegraphics[width=7.4cm] {new-fig/44_Adep_DePts_A13_0.png} 
+\includegraphics[width=7.4cm] {new-fig/41_Ndep_Ratio_Nu_0.png} 
+\includegraphics[width=7.4cm] {new-fig/46_Qdep_DePts_Q2_0.png} 
+\includegraphics[width=7.4cm] {new-fig/42_zdep_Ratio_Zz_0.png} 
+\includegraphics[width=7.4cm] {new-fig/47_zdep_DePts_Zz_0.png} 
+\caption {Results for multiplicity ratios (left) and the transverse momentum 
+broadening (right) before applying any corrections.}
 \label{fig:prelim}
@@
 
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=14cm] {chap5-fig/pawpipdeut.png}
+\caption {The extracted acceptance correction weights for pions on a deuterium target (not re-weighted).}
+\label{fig:AccCoef}
+\end{figure}
+
 This process can create a bias, if for instance low $Q^2$ bins are more often dropped.
@@
 
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=14cm] {chap5-fig/pawpipdeut.png}
-\caption {The extracted acceptance correction weights for pions on a deuterium target (not re-weighted).}
-\label{fig:AccCoef}
-\end{figure}
-
 In order to correct the number of electrons in multiplicity ratios, we followed the 
@@
 
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
-\caption {Preliminary results are compared with the acceptance corrected ones, 
-for multiplicity ratios (top) and transverse momentum broadening 
-(bottom). Only statistical errors are shown.}
+\begin{figure}[p]
+\centering
+\includegraphics[width=7.4cm] {new-fig/50_Adep_Ratio_A13_1.png} 
+\includegraphics[width=7.4cm] {new-fig/54_Adep_DePts_A13_1.png} 
+\includegraphics[width=7.4cm] {new-fig/51_Ndep_Ratio_Nu_1.png} 
+\includegraphics[width=7.4cm] {new-fig/56_Qdep_DePts_Q2_1.png} 
+\includegraphics[width=7.4cm] {new-fig/52_zdep_Ratio_Zz_1.png} 
+\includegraphics[width=7.4cm] {new-fig/57_zdep_DePts_Zz_1.png} 
+\caption {Preliminary raw results are compared with the acceptance corrected ones, 
+for multiplicity ratios (left) and transverse momentum broadening 
+(right). Only statistical errors are shown.}
 \label{fig:AcceptPlots}
@@
 \centering
-\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
-\caption {Preliminary results are compared with the acceptance corrected ones, 
-for multiplicity ratios (top) and transverse momentum broadening 
-(bottom). Only statistical errors are shown.}
+\includegraphics[width=7.4cm] {new-fig/50_Adep_Ratio_A13_2.png} 
+\includegraphics[width=7.4cm] {new-fig/54_Adep_DePts_A13_2.png} 
+\includegraphics[width=7.4cm] {new-fig/51_Ndep_Ratio_Nu_2.png} 
+\includegraphics[width=7.4cm] {new-fig/56_Qdep_DePts_Q2_2.png} 
+\includegraphics[width=7.4cm] {new-fig/52_zdep_Ratio_Zz_2.png} 
+\includegraphics[width=7.4cm] {new-fig/57_zdep_DePts_Zz_2.png} 
+\caption {Preliminary results are compared with with and without Coulomb correction,
+the acceptance remains applied for both. The multiplicity ratios are presented on the left 
+and the transverse momentum broadening on the right. Only statistical errors are shown.}
 \label{fig:CCPlots}
@@
 
-\begin{figure}[tbp]
-\centering
-\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
-\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
+\begin{figure}[p]
+\centering
+\includegraphics[width=7.4cm] {new-fig/60_Adep_Ratio_A13_3.png} 
+\includegraphics[width=7.4cm] {new-fig/64_Adep_DePts_A13_3.png} 
+\includegraphics[width=7.4cm] {new-fig/61_Ndep_Ratio_Nu_3.png} 
+\includegraphics[width=7.4cm] {new-fig/66_Qdep_DePts_Q2_3.png} 
+\includegraphics[width=7.4cm] {new-fig/62_zdep_Ratio_Zz_3.png} 
+\includegraphics[width=7.4cm] {new-fig/67_zdep_DePts_Zz_3.png} 
 \caption {Preliminary results including radiative corrections
-compared to the ones without, 
-for multiplicity ratios (top) and transverse momentum broadening 
-(bottom). Only statistical errors are shown.}
+compared to the ones without (acceptance and Coulomb corrections remain applied in both), 
+for multiplicity ratios (left) and transverse momentum broadening 
+(right). Only statistical errors are shown.}
 \label{fig:RCPlots}
@@
 \centering
-\includegraphics[width=8.5cm] {chap5-fig/c_RvA.png}
-\caption {Multiplicity ratios as a function of $A^{1/3}$ with the isospin correction applied.}
+\includegraphics[width=8.5cm] {new-fig/IsospinCorrection.png}
+\caption {Multiplicity ratios as a function of $A^{1/3}$ with and without the isospin correction applied.}
 \label{fig:IsoPlot}

### 2019-04-16 new-fig/50_Adep_Ratio_A13_2.C

@@ -1,0 +1,212 @@
+{
+//=========Macro generated from canvas: Plot_49/Multiplicity Ratio as a function of A
+//=========  (Fri Mar 29 18:04:36 2019) by ROOT version 6.14/00
+   TCanvas *Plot_49 = new TCanvas("Plot_49", "Multiplicity Ratio as a function of A",0,0,600,500);
+   Plot_49->Range(0,0,1,1);
+   Plot_49->SetFillColor(0);
+   Plot_49->SetBorderMode(0);
+   Plot_49->SetBorderSize(2);
+   Plot_49->SetFrameBorderMode(0);
+   
+   TH2D *CanmI124__50 = new TH2D("CanmI124__50","Multiplicity Ratio as a function of A",100,2,6,100,0,1);
+   CanmI124__50->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI124__50->SetLineColor(ci);
+   CanmI124__50->GetXaxis()->SetTitle("A^{1/3}");
+   CanmI124__50->GetXaxis()->CenterTitle(true);
+   CanmI124__50->GetXaxis()->SetLabelFont(42);
+   CanmI124__50->GetXaxis()->SetLabelSize(0.035);
+   CanmI124__50->GetXaxis()->SetTitleSize(0.035);
+   CanmI124__50->GetXaxis()->SetTitleFont(42);
+   CanmI124__50->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI124__50->GetYaxis()->CenterTitle(true);
+   CanmI124__50->GetYaxis()->SetLabelFont(42);
+   CanmI124__50->GetYaxis()->SetLabelSize(0.035);
+   CanmI124__50->GetYaxis()->SetTitleSize(0.035);
+   CanmI124__50->GetYaxis()->SetTitleOffset(0);
+   CanmI124__50->GetYaxis()->SetTitleFont(42);
+   CanmI124__50->GetZaxis()->SetLabelFont(42);
+   CanmI124__50->GetZaxis()->SetLabelSize(0.035);
+   CanmI124__50->GetZaxis()->SetTitleSize(0.035);
+   CanmI124__50->GetZaxis()->SetTitleFont(42);
+   CanmI124__50->Draw("");
+   
[…]

### 2019-04-16 new-fig/51_Ndep_Ratio_Nu_2.C

@@ -1,0 +1,292 @@
+{
+//=========Macro generated from canvas: Plot_50/Multiplicity Ratio as a function of #nu
+//=========  (Fri Mar 29 18:04:36 2019) by ROOT version 6.14/00
+   TCanvas *Plot_50 = new TCanvas("Plot_50", "Multiplicity Ratio as a function of #nu",0,0,600,500);
+   Plot_50->Range(0,0,1,1);
+   Plot_50->SetFillColor(0);
+   Plot_50->SetBorderMode(0);
+   Plot_50->SetBorderSize(2);
+   Plot_50->SetFrameBorderMode(0);
+   
+   TH2D *CanmI125__51 = new TH2D("CanmI125__51","Multiplicity Ratio as a function of #nu",100,2.25,4.25,100,0,1);
+   CanmI125__51->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI125__51->SetLineColor(ci);
+   CanmI125__51->GetXaxis()->SetTitle("#nu (GeV)");
+   CanmI125__51->GetXaxis()->CenterTitle(true);
+   CanmI125__51->GetXaxis()->SetLabelFont(42);
+   CanmI125__51->GetXaxis()->SetLabelSize(0.035);
+   CanmI125__51->GetXaxis()->SetTitleSize(0.035);
+   CanmI125__51->GetXaxis()->SetTitleFont(42);
+   CanmI125__51->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI125__51->GetYaxis()->CenterTitle(true);
+   CanmI125__51->GetYaxis()->SetLabelFont(42);
+   CanmI125__51->GetYaxis()->SetLabelSize(0.035);
+   CanmI125__51->GetYaxis()->SetTitleSize(0.035);
+   CanmI125__51->GetYaxis()->SetTitleOffset(0);
+   CanmI125__51->GetYaxis()->SetTitleFont(42);
+   CanmI125__51->GetZaxis()->SetLabelFont(42);
+   CanmI125__51->GetZaxis()->SetLabelSize(0.035);
+   CanmI125__51->GetZaxis()->SetTitleSize(0.035);
+   CanmI125__51->GetZaxis()->SetTitleFont(42);
+   CanmI125__51->Draw("");
+   
[…]

### 2019-04-16 new-fig/52_zdep_Ratio_Zz_2.C

@@ -1,0 +1,292 @@
+{
+//=========Macro generated from canvas: Plot_51/Multiplicity Ratio as a function of z
+//=========  (Fri Mar 29 18:04:36 2019) by ROOT version 6.14/00
+   TCanvas *Plot_51 = new TCanvas("Plot_51", "Multiplicity Ratio as a function of z",0,0,600,500);
+   Plot_51->Range(0,0,1,1);
+   Plot_51->SetFillColor(0);
+   Plot_51->SetBorderMode(0);
+   Plot_51->SetBorderSize(2);
+   Plot_51->SetFrameBorderMode(0);
+   
+   TH2D *CanmI126__52 = new TH2D("CanmI126__52","Multiplicity Ratio as a function of z",100,0,1,100,0,1.2);
+   CanmI126__52->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI126__52->SetLineColor(ci);
+   CanmI126__52->GetXaxis()->SetTitle("z");
+   CanmI126__52->GetXaxis()->CenterTitle(true);
+   CanmI126__52->GetXaxis()->SetLabelFont(42);
+   CanmI126__52->GetXaxis()->SetLabelSize(0.035);
+   CanmI126__52->GetXaxis()->SetTitleSize(0.035);
+   CanmI126__52->GetXaxis()->SetTitleFont(42);
+   CanmI126__52->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI126__52->GetYaxis()->CenterTitle(true);
+   CanmI126__52->GetYaxis()->SetLabelFont(42);
+   CanmI126__52->GetYaxis()->SetLabelSize(0.035);
+   CanmI126__52->GetYaxis()->SetTitleSize(0.035);
+   CanmI126__52->GetYaxis()->SetTitleOffset(0);
+   CanmI126__52->GetYaxis()->SetTitleFont(42);
+   CanmI126__52->GetZaxis()->SetLabelFont(42);
+   CanmI126__52->GetZaxis()->SetLabelSize(0.035);
+   CanmI126__52->GetZaxis()->SetTitleSize(0.035);
+   CanmI126__52->GetZaxis()->SetTitleFont(42);
+   CanmI126__52->Draw("");
+   
[…]

### 2019-04-16 new-fig/54_Adep_DePts_A13_2.C

@@ -1,0 +1,212 @@
+{
+//=========Macro generated from canvas: Plot_53/#DeltaP_{T}^{2} as a function of A
+//=========  (Fri Mar 29 18:04:36 2019) by ROOT version 6.14/00
+   TCanvas *Plot_53 = new TCanvas("Plot_53", "#DeltaP_{T}^{2} as a function of A",0,0,600,500);
+   Plot_53->Range(0,0,1,1);
+   Plot_53->SetFillColor(0);
+   Plot_53->SetBorderMode(0);
+   Plot_53->SetBorderSize(2);
+   Plot_53->SetFrameBorderMode(0);
+   
+   TH2D *CanmI128__54 = new TH2D("CanmI128__54","#DeltaP_{T}^{2} as a function of A",100,2,6,100,0,0.05);
+   CanmI128__54->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI128__54->SetLineColor(ci);
+   CanmI128__54->GetXaxis()->SetTitle("A^{1/3}");
+   CanmI128__54->GetXaxis()->CenterTitle(true);
+   CanmI128__54->GetXaxis()->SetLabelFont(42);
+   CanmI128__54->GetXaxis()->SetLabelSize(0.035);
+   CanmI128__54->GetXaxis()->SetTitleSize(0.035);
+   CanmI128__54->GetXaxis()->SetTitleFont(42);
+   CanmI128__54->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI128__54->GetYaxis()->CenterTitle(true);
+   CanmI128__54->GetYaxis()->SetLabelFont(42);
+   CanmI128__54->GetYaxis()->SetLabelSize(0.035);
+   CanmI128__54->GetYaxis()->SetTitleSize(0.035);
+   CanmI128__54->GetYaxis()->SetTitleOffset(0);
+   CanmI128__54->GetYaxis()->SetTitleFont(42);
+   CanmI128__54->GetZaxis()->SetLabelFont(42);
+   CanmI128__54->GetZaxis()->SetLabelSize(0.035);
+   CanmI128__54->GetZaxis()->SetTitleSize(0.035);
+   CanmI128__54->GetZaxis()->SetTitleFont(42);
+   CanmI128__54->Draw("");
+   
[…]

### 2019-04-16 new-fig/56_Qdep_DePts_Q2_2.C

@@ -1,0 +1,292 @@
+{
+//=========Macro generated from canvas: Plot_55/#DeltaP_{T}^{2} as a function of Q^{2}
+//=========  (Fri Mar 29 18:04:36 2019) by ROOT version 6.14/00
+   TCanvas *Plot_55 = new TCanvas("Plot_55", "#DeltaP_{T}^{2} as a function of Q^{2}",0,0,600,500);
+   Plot_55->Range(0,0,1,1);
+   Plot_55->SetFillColor(0);
+   Plot_55->SetBorderMode(0);
+   Plot_55->SetBorderSize(2);
+   Plot_55->SetFrameBorderMode(0);
+   
+   TH2D *CanmI130__56 = new TH2D("CanmI130__56","#DeltaP_{T}^{2} as a function of Q^{2}",100,1,4,100,0,0.05);
+   CanmI130__56->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI130__56->SetLineColor(ci);
+   CanmI130__56->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   CanmI130__56->GetXaxis()->CenterTitle(true);
+   CanmI130__56->GetXaxis()->SetLabelFont(42);
+   CanmI130__56->GetXaxis()->SetLabelSize(0.035);
+   CanmI130__56->GetXaxis()->SetTitleSize(0.035);
+   CanmI130__56->GetXaxis()->SetTitleFont(42);
+   CanmI130__56->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI130__56->GetYaxis()->CenterTitle(true);
+   CanmI130__56->GetYaxis()->SetLabelFont(42);
+   CanmI130__56->GetYaxis()->SetLabelSize(0.035);
+   CanmI130__56->GetYaxis()->SetTitleSize(0.035);
+   CanmI130__56->GetYaxis()->SetTitleOffset(0);
+   CanmI130__56->GetYaxis()->SetTitleFont(42);
+   CanmI130__56->GetZaxis()->SetLabelFont(42);
+   CanmI130__56->GetZaxis()->SetLabelSize(0.035);
+   CanmI130__56->GetZaxis()->SetTitleSize(0.035);
+   CanmI130__56->GetZaxis()->SetTitleFont(42);
+   CanmI130__56->Draw("");
+   
[…]

### 2019-04-16 new-fig/57_zdep_DePts_Zz_2.C

@@ -1,0 +1,292 @@
+{
+//=========Macro generated from canvas: Plot_56/#DeltaP_{T}^{2} as a function of z
+//=========  (Fri Mar 29 18:04:36 2019) by ROOT version 6.14/00
+   TCanvas *Plot_56 = new TCanvas("Plot_56", "#DeltaP_{T}^{2} as a function of z",0,0,600,500);
+   Plot_56->Range(0,0,1,1);
+   Plot_56->SetFillColor(0);
+   Plot_56->SetBorderMode(0);
+   Plot_56->SetBorderSize(2);
+   Plot_56->SetFrameBorderMode(0);
+   
+   TH2D *CanmI131__57 = new TH2D("CanmI131__57","#DeltaP_{T}^{2} as a function of z",100,0,1,100,0,0.05);
+   CanmI131__57->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI131__57->SetLineColor(ci);
+   CanmI131__57->GetXaxis()->SetTitle("z");
+   CanmI131__57->GetXaxis()->CenterTitle(true);
+   CanmI131__57->GetXaxis()->SetLabelFont(42);
+   CanmI131__57->GetXaxis()->SetLabelSize(0.035);
+   CanmI131__57->GetXaxis()->SetTitleSize(0.035);
+   CanmI131__57->GetXaxis()->SetTitleFont(42);
+   CanmI131__57->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI131__57->GetYaxis()->CenterTitle(true);
+   CanmI131__57->GetYaxis()->SetLabelFont(42);
+   CanmI131__57->GetYaxis()->SetLabelSize(0.035);
+   CanmI131__57->GetYaxis()->SetTitleSize(0.035);
+   CanmI131__57->GetYaxis()->SetTitleOffset(0);
+   CanmI131__57->GetYaxis()->SetTitleFont(42);
+   CanmI131__57->GetZaxis()->SetLabelFont(42);
+   CanmI131__57->GetZaxis()->SetLabelSize(0.035);
+   CanmI131__57->GetZaxis()->SetTitleSize(0.035);
+   CanmI131__57->GetZaxis()->SetTitleFont(42);
+   CanmI131__57->Draw("");
+   
[…]

### 2019-04-16 new-fig/IsospinCorrection.C

@@ -1,0 +1,212 @@
+{
+//=========Macro generated from canvas: Plot_49/Multiplicity Ratio as a function of A
+//=========  (Fri Mar 29 18:04:36 2019) by ROOT version 6.14/00
+   TCanvas *Plot_49 = new TCanvas("Plot_49", "Multiplicity Ratio as a function of A",0,0,600,500);
+   Plot_49->Range(0,0,1,1);
+   Plot_49->SetFillColor(0);
+   Plot_49->SetBorderMode(0);
+   Plot_49->SetBorderSize(2);
+   Plot_49->SetFrameBorderMode(0);
+   
+   TH2D *CanmI124__50 = new TH2D("CanmI124__50","Multiplicity Ratio as a function of A",100,2,6,100,0,1);
+   CanmI124__50->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI124__50->SetLineColor(ci);
+   CanmI124__50->GetXaxis()->SetTitle("A^{1/3}");
+   CanmI124__50->GetXaxis()->CenterTitle(true);
+   CanmI124__50->GetXaxis()->SetLabelFont(42);
+   CanmI124__50->GetXaxis()->SetLabelSize(0.035);
+   CanmI124__50->GetXaxis()->SetTitleSize(0.035);
+   CanmI124__50->GetXaxis()->SetTitleFont(42);
+   CanmI124__50->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI124__50->GetYaxis()->CenterTitle(true);
+   CanmI124__50->GetYaxis()->SetLabelFont(42);
+   CanmI124__50->GetYaxis()->SetLabelSize(0.035);
+   CanmI124__50->GetYaxis()->SetTitleSize(0.035);
+   CanmI124__50->GetYaxis()->SetTitleOffset(0);
+   CanmI124__50->GetYaxis()->SetTitleFont(42);
+   CanmI124__50->GetZaxis()->SetLabelFont(42);
+   CanmI124__50->GetZaxis()->SetLabelSize(0.035);
+   CanmI124__50->GetZaxis()->SetTitleSize(0.035);
+   CanmI124__50->GetZaxis()->SetTitleFont(42);
+   CanmI124__50->Draw("");
+   
[…]

### 2019-04-16 chap5.tex
Comment some unfinished stuff

@@
 
-\subsection{Cross Checks}
-\label{sec:XChecks}
-
-The goal here is to check known results in order to make sure we have normalization right. This is 
-especially important since discrepencies with Hayk's analysis have been found and demonstrated the 
-normalization to be a tricky problem.
-
-\subsubsection{Inclusive electron normalization}
-
-We expect the EMC ratio to cross unity around 0.3 - 0.35 and we know precisely the target thickesses.
-From these we check our inclusive normalization...
-
-\subsubsection{Pion ratio from Hall-C}
-
-In paper from Hall-C they present results shown in fig 20 (to reproduce here). The bin corresponds to 
-1.5 < Q2 < 4 GeV2, 0.35 < xb < 0.45, 0.5 < z < 0.6 and Pt2 < 0.2. They find ratios of 0.556+-0.011 for pi+
-and 0.520+-0.011 for pi-. Note that it is not a double ratio and should be affected by the EMC effect,
-moreover they do not make an isospin correction which is 1.5\%.
-
-Put my result here
-
-\subsubsection{Pion ratio from HERMES}
+%\subsection{Cross Checks}
+%\label{sec:XChecks}
+
+%The goal here is to check known results in order to make sure we have normalization right. This is 
+%especially important since discrepencies with Hayk's analysis have been found and demonstrated the 
+%normalization to be a tricky problem.
+
+%\subsubsection{Inclusive electron normalization}
+
+%We expect the EMC ratio to cross unity around 0.3 - 0.35 and we know precisely the target thickesses.
+%From these we check our inclusive normalization...
+
+%\subsubsection{Pion ratio from Hall-C}
+
+%In paper from Hall-C they present results shown in fig 20 (to reproduce here). The bin corresponds to 
+%1.5 < Q2 < 4 GeV2, 0.35 < xb < 0.45, 0.5 < z < 0.6 and Pt2 < 0.2. They find ratios of 0.556+-0.011 for pi+
+%and 0.520+-0.011 for pi-. Note that it is not a double ratio and should be affected by the EMC effect,
+%moreover they do not make an isospin correction which is 1.5\%.
+
+%Put my result here
+
+%\subsubsection{Pion ratio from HERMES}

### 2019-04-17 chap6-fig/F_PvA.C
Update all final results with up to date figures

@@ -1,0 +1,194 @@
+{
+//=========Macro generated from canvas: Plot_16/#DeltaP_{T}^{2} as a function of A
+//=========  (Thu Mar 21 18:22:27 2019) by ROOT version 6.14/00
+   TCanvas *Plot_16 = new TCanvas("Plot_16", "#DeltaP_{T}^{2} as a function of A",0,0,600,500);
+   Plot_16->Range(0,0,1,1);
+   Plot_16->SetFillColor(0);
+   Plot_16->SetBorderMode(0);
+   Plot_16->SetBorderSize(2);
+   Plot_16->SetFrameBorderMode(0);
+   
+   TH2D *CanmI91__17 = new TH2D("CanmI91__17","#DeltaP_{T}^{2} as a function of A",100,2,6.25,100,0,0.035);
+   CanmI91__17->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI91__17->SetLineColor(ci);
+   CanmI91__17->GetXaxis()->SetTitle("A^{1/3}");
+   CanmI91__17->GetXaxis()->CenterTitle(true);
+   CanmI91__17->GetXaxis()->SetLabelFont(42);
+   CanmI91__17->GetXaxis()->SetLabelSize(0.035);
+   CanmI91__17->GetXaxis()->SetTitleSize(0.035);
+   CanmI91__17->GetXaxis()->SetTitleFont(42);
+   CanmI91__17->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI91__17->GetYaxis()->CenterTitle(true);
+   CanmI91__17->GetYaxis()->SetLabelFont(42);
+   CanmI91__17->GetYaxis()->SetLabelSize(0.035);
+   CanmI91__17->GetYaxis()->SetTitleSize(0.035);
+   CanmI91__17->GetYaxis()->SetTitleOffset(1.5);
+   CanmI91__17->GetYaxis()->SetTitleFont(42);
+   CanmI91__17->GetZaxis()->SetLabelFont(42);
+   CanmI91__17->GetZaxis()->SetLabelSize(0.035);
+   CanmI91__17->GetZaxis()->SetTitleSize(0.035);
+   CanmI91__17->GetZaxis()->SetTitleFont(42);
+   CanmI91__17->Draw("");
+   
[…]

### 2019-04-17 chap6-fig/F_PvNu.C

@@ -1,0 +1,384 @@
+{
+//=========Macro generated from canvas: Plot_17/#DeltaP_{T}^{2} as a function of #nu
+//=========  (Thu Mar 21 18:22:27 2019) by ROOT version 6.14/00
+   TCanvas *Plot_17 = new TCanvas("Plot_17", "#DeltaP_{T}^{2} as a function of #nu",0,0,600,500);
+   Plot_17->Range(0,0,1,1);
+   Plot_17->SetFillColor(0);
+   Plot_17->SetBorderMode(0);
+   Plot_17->SetBorderSize(2);
+   Plot_17->SetFrameBorderMode(0);
+   
+   TH2D *CanmI92__18 = new TH2D("CanmI92__18","#DeltaP_{T}^{2} as a function of #nu",100,2.25,4.25,100,0,0.04);
+   CanmI92__18->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI92__18->SetLineColor(ci);
+   CanmI92__18->GetXaxis()->SetTitle("#nu (GeV)");
+   CanmI92__18->GetXaxis()->CenterTitle(true);
+   CanmI92__18->GetXaxis()->SetLabelFont(42);
+   CanmI92__18->GetXaxis()->SetLabelSize(0.035);
+   CanmI92__18->GetXaxis()->SetTitleSize(0.035);
+   CanmI92__18->GetXaxis()->SetTitleFont(42);
+   CanmI92__18->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI92__18->GetYaxis()->CenterTitle(true);
+   CanmI92__18->GetYaxis()->SetLabelFont(42);
+   CanmI92__18->GetYaxis()->SetLabelSize(0.035);
+   CanmI92__18->GetYaxis()->SetTitleSize(0.035);
+   CanmI92__18->GetYaxis()->SetTitleOffset(1.5);
+   CanmI92__18->GetYaxis()->SetTitleFont(42);
+   CanmI92__18->GetZaxis()->SetLabelFont(42);
+   CanmI92__18->GetZaxis()->SetLabelSize(0.035);
+   CanmI92__18->GetZaxis()->SetTitleSize(0.035);
+   CanmI92__18->GetZaxis()->SetTitleFont(42);
+   CanmI92__18->Draw("");
+   
+   
+   Double_t Graph3_fx1160[10] = {
[…]

### 2019-04-17 chap6-fig/F_PvNu_PbC.C

@@ -1,0 +1,167 @@
+{
+//=========Macro generated from canvas: Plot_34/#DeltaP_{T}^{2} as a function of #nu
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_34 = new TCanvas("Plot_34", "#DeltaP_{T}^{2} as a function of #nu",0,0,600,500);
+   Plot_34->Range(0,0,1,1);
+   Plot_34->SetFillColor(0);
+   Plot_34->SetBorderMode(0);
+   Plot_34->SetBorderSize(2);
+   Plot_34->SetFrameBorderMode(0);
+   
+   TH2D *CanmI109__35 = new TH2D("CanmI109__35","#DeltaP_{T}^{2} as a function of #nu",100,2.25,4.25,100,0,0.03);
+   CanmI109__35->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI109__35->SetLineColor(ci);
+   CanmI109__35->GetXaxis()->SetTitle("#nu (GeV)");
+   CanmI109__35->GetXaxis()->CenterTitle(true);
+   CanmI109__35->GetXaxis()->SetLabelFont(42);
+   CanmI109__35->GetXaxis()->SetLabelSize(0.035);
+   CanmI109__35->GetXaxis()->SetTitleSize(0.035);
+   CanmI109__35->GetXaxis()->SetTitleFont(42);
+   CanmI109__35->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI109__35->GetYaxis()->CenterTitle(true);
+   CanmI109__35->GetYaxis()->SetLabelFont(42);
+   CanmI109__35->GetYaxis()->SetLabelSize(0.035);
+   CanmI109__35->GetYaxis()->SetTitleSize(0.035);
+   CanmI109__35->GetYaxis()->SetTitleOffset(1.5);
+   CanmI109__35->GetYaxis()->SetTitleFont(42);
+   CanmI109__35->GetZaxis()->SetLabelFont(42);
+   CanmI109__35->GetZaxis()->SetLabelSize(0.035);
+   CanmI109__35->GetZaxis()->SetTitleSize(0.035);
+   CanmI109__35->GetZaxis()->SetTitleFont(42);
+   CanmI109__35->Draw("");
+   
+   
[…]

### 2019-04-17 chap6-fig/F_PvQ2.C

@@ -1,0 +1,167 @@
+{
+//=========Macro generated from canvas: Plot_18/#DeltaP_{T}^{2} as a function of Q^{2}
+//=========  (Thu Mar 21 18:22:27 2019) by ROOT version 6.14/00
+   TCanvas *Plot_18 = new TCanvas("Plot_18", "#DeltaP_{T}^{2} as a function of Q^{2}",0,0,600,500);
+   Plot_18->Range(0,0,1,1);
+   Plot_18->SetFillColor(0);
+   Plot_18->SetBorderMode(0);
+   Plot_18->SetBorderSize(2);
+   Plot_18->SetFrameBorderMode(0);
+   
+   TH2D *CanmI93__19 = new TH2D("CanmI93__19","#DeltaP_{T}^{2} as a function of Q^{2}",100,1,4,100,0,0.03);
+   CanmI93__19->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI93__19->SetLineColor(ci);
+   CanmI93__19->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   CanmI93__19->GetXaxis()->CenterTitle(true);
+   CanmI93__19->GetXaxis()->SetLabelFont(42);
+   CanmI93__19->GetXaxis()->SetLabelSize(0.035);
+   CanmI93__19->GetXaxis()->SetTitleSize(0.035);
+   CanmI93__19->GetXaxis()->SetTitleFont(42);
+   CanmI93__19->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI93__19->GetYaxis()->CenterTitle(true);
+   CanmI93__19->GetYaxis()->SetLabelFont(42);
+   CanmI93__19->GetYaxis()->SetLabelSize(0.035);
+   CanmI93__19->GetYaxis()->SetTitleSize(0.035);
+   CanmI93__19->GetYaxis()->SetTitleOffset(1.5);
+   CanmI93__19->GetYaxis()->SetTitleFont(42);
+   CanmI93__19->GetZaxis()->SetLabelFont(42);
+   CanmI93__19->GetZaxis()->SetLabelSize(0.035);
+   CanmI93__19->GetZaxis()->SetTitleSize(0.035);
+   CanmI93__19->GetZaxis()->SetTitleFont(42);
+   CanmI93__19->Draw("");
+   
[…]

### 2019-04-17 chap6-fig/F_PvQ2_PbC.C

@@ -1,0 +1,165 @@
+{
+//=========Macro generated from canvas: Plot_35/#DeltaP_{T}^{2} as a function of Q^{2}
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_35 = new TCanvas("Plot_35", "#DeltaP_{T}^{2} as a function of Q^{2}",0,0,600,500);
+   Plot_35->Range(0,0,1,1);
+   Plot_35->SetFillColor(0);
+   Plot_35->SetBorderMode(0);
+   Plot_35->SetBorderSize(2);
+   Plot_35->SetFrameBorderMode(0);
+   
+   TH2D *CanmI110__36 = new TH2D("CanmI110__36","#DeltaP_{T}^{2} as a function of Q^{2}",100,1,4,100,0,0.03);
+   CanmI110__36->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI110__36->SetLineColor(ci);
+   CanmI110__36->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   CanmI110__36->GetXaxis()->CenterTitle(true);
+   CanmI110__36->GetXaxis()->SetLabelFont(42);
+   CanmI110__36->GetXaxis()->SetLabelSize(0.035);
+   CanmI110__36->GetXaxis()->SetTitleSize(0.035);
+   CanmI110__36->GetXaxis()->SetTitleFont(42);
+   CanmI110__36->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI110__36->GetYaxis()->CenterTitle(true);
+   CanmI110__36->GetYaxis()->SetLabelFont(42);
+   CanmI110__36->GetYaxis()->SetLabelSize(0.035);
+   CanmI110__36->GetYaxis()->SetTitleSize(0.035);
+   CanmI110__36->GetYaxis()->SetTitleOffset(1.5);
+   CanmI110__36->GetYaxis()->SetTitleFont(42);
+   CanmI110__36->GetZaxis()->SetLabelFont(42);
+   CanmI110__36->GetZaxis()->SetLabelSize(0.035);
+   CanmI110__36->GetZaxis()->SetTitleSize(0.035);
+   CanmI110__36->GetZaxis()->SetTitleFont(42);
[…]

### 2019-04-17 chap6-fig/F_PvQ2inNu.C

@@ -1,0 +1,384 @@
+{
+//=========Macro generated from canvas: Plot_27/#DeltaP_{T}^{2} as a function of Q^{2} in a #nu bin
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_27 = new TCanvas("Plot_27", "#DeltaP_{T}^{2} as a function of Q^{2} in a #nu bin",0,0,600,500);
+   Plot_27->Range(0,0,1,1);
+   Plot_27->SetFillColor(0);
+   Plot_27->SetBorderMode(0);
+   Plot_27->SetBorderSize(2);
+   Plot_27->SetFrameBorderMode(0);
+   
+   TH2D *CanmI102__28 = new TH2D("CanmI102__28","#DeltaP_{T}^{2} as a function of Q^{2} in a #nu bin",100,1,4,100,0,0.05);
+   CanmI102__28->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI102__28->SetLineColor(ci);
+   CanmI102__28->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   CanmI102__28->GetXaxis()->CenterTitle(true);
+   CanmI102__28->GetXaxis()->SetLabelFont(42);
+   CanmI102__28->GetXaxis()->SetLabelSize(0.035);
+   CanmI102__28->GetXaxis()->SetTitleSize(0.035);
+   CanmI102__28->GetXaxis()->SetTitleFont(42);
+   CanmI102__28->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI102__28->GetYaxis()->CenterTitle(true);
+   CanmI102__28->GetYaxis()->SetLabelFont(42);
+   CanmI102__28->GetYaxis()->SetLabelSize(0.035);
+   CanmI102__28->GetYaxis()->SetTitleSize(0.035);
+   CanmI102__28->GetYaxis()->SetTitleOffset(1.5);
+   CanmI102__28->GetYaxis()->SetTitleFont(42);
+   CanmI102__28->GetZaxis()->SetLabelFont(42);
+   CanmI102__28->GetZaxis()->SetLabelSize(0.035);
+   CanmI102__28->GetZaxis()->SetTitleSize(0.035);
+   CanmI102__28->GetZaxis()->SetTitleFont(42);
[…]

### 2019-04-17 chap6-fig/F_PvZ.C

@@ -1,0 +1,383 @@
+{
+//=========Macro generated from canvas: Plot_19/#DeltaP_{T}^{2} as a function of z
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_19 = new TCanvas("Plot_19", "#DeltaP_{T}^{2} as a function of z",0,0,600,500);
+   Plot_19->Range(0,0,1,1);
+   Plot_19->SetFillColor(0);
+   Plot_19->SetBorderMode(0);
+   Plot_19->SetBorderSize(2);
+   Plot_19->SetFrameBorderMode(0);
+   
+   TH2D *CanmI94__20 = new TH2D("CanmI94__20","#DeltaP_{T}^{2} as a function of z",100,0,1,100,0,0.04);
+   CanmI94__20->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI94__20->SetLineColor(ci);
+   CanmI94__20->GetXaxis()->SetTitle("z");
+   CanmI94__20->GetXaxis()->CenterTitle(true);
+   CanmI94__20->GetXaxis()->SetLabelFont(42);
+   CanmI94__20->GetXaxis()->SetLabelSize(0.035);
+   CanmI94__20->GetXaxis()->SetTitleSize(0.035);
+   CanmI94__20->GetXaxis()->SetTitleFont(42);
+   CanmI94__20->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI94__20->GetYaxis()->CenterTitle(true);
+   CanmI94__20->GetYaxis()->SetLabelFont(42);
+   CanmI94__20->GetYaxis()->SetLabelSize(0.035);
+   CanmI94__20->GetYaxis()->SetTitleSize(0.035);
+   CanmI94__20->GetYaxis()->SetTitleOffset(1.5);
+   CanmI94__20->GetYaxis()->SetTitleFont(42);
+   CanmI94__20->GetZaxis()->SetLabelFont(42);
+   CanmI94__20->GetZaxis()->SetLabelSize(0.035);
+   CanmI94__20->GetZaxis()->SetTitleSize(0.035);
+   CanmI94__20->GetZaxis()->SetTitleFont(42);
+   CanmI94__20->Draw("");
+   
+   Double_t Graph3_fx1184[10] = {
+   0.09148271,
[…]

### 2019-04-17 chap6-fig/F_PvZ_PbC.C

@@ -1,0 +1,274 @@
+{
+//=========Macro generated from canvas: Plot_36/#DeltaP_{T}^{2} as a function of z
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_36 = new TCanvas("Plot_36", "#DeltaP_{T}^{2} as a function of z",0,0,600,500);
+   Plot_36->Range(0,0,1,1);
+   Plot_36->SetFillColor(0);
+   Plot_36->SetBorderMode(0);
+   Plot_36->SetBorderSize(2);
+   Plot_36->SetFrameBorderMode(0);
+   
+   TH2D *CanmI111__37 = new TH2D("CanmI111__37","#DeltaP_{T}^{2} as a function of z",100,0,1,100,0,0.035);
+   CanmI111__37->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI111__37->SetLineColor(ci);
+   CanmI111__37->GetXaxis()->SetTitle("z");
+   CanmI111__37->GetXaxis()->CenterTitle(true);
+   CanmI111__37->GetXaxis()->SetLabelFont(42);
+   CanmI111__37->GetXaxis()->SetLabelSize(0.035);
+   CanmI111__37->GetXaxis()->SetTitleSize(0.035);
+   CanmI111__37->GetXaxis()->SetTitleFont(42);
+   CanmI111__37->GetYaxis()->SetTitle("#DeltaP_{T}^{2}");
+   CanmI111__37->GetYaxis()->CenterTitle(true);
+   CanmI111__37->GetYaxis()->SetLabelFont(42);
+   CanmI111__37->GetYaxis()->SetLabelSize(0.035);
+   CanmI111__37->GetYaxis()->SetTitleSize(0.035);
+   CanmI111__37->GetYaxis()->SetTitleOffset(1.5);
+   CanmI111__37->GetYaxis()->SetTitleFont(42);
+   CanmI111__37->GetZaxis()->SetLabelFont(42);
+   CanmI111__37->GetZaxis()->SetLabelSize(0.035);
+   CanmI111__37->GetZaxis()->SetTitleSize(0.035);
+   CanmI111__37->GetZaxis()->SetTitleFont(42);
+   CanmI111__37->Draw("");
+   
[…]

### 2019-04-17 chap6-fig/F_RvA.C

@@ -1,0 +1,194 @@
+{
+//=========Macro generated from canvas: Plot_0/Multiplicity Ratio as a function of A
+//=========  (Thu Mar 21 18:22:26 2019) by ROOT version 6.14/00
+   TCanvas *Plot_0 = new TCanvas("Plot_0", "Multiplicity Ratio as a function of A",0,0,600,500);
+   Plot_0->Range(0,0,1,1);
+   Plot_0->SetFillColor(0);
+   Plot_0->SetBorderMode(0);
+   Plot_0->SetBorderSize(2);
+   Plot_0->SetFrameBorderMode(0);
+   
+   TH2D *CanmI75__1 = new TH2D("CanmI75__1","Multiplicity Ratio as a function of A",100,2,6.25,100,0.3,0.85);
+   CanmI75__1->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI75__1->SetLineColor(ci);
+   CanmI75__1->GetXaxis()->SetTitle("A^{1/3}");
+   CanmI75__1->GetXaxis()->CenterTitle(true);
+   CanmI75__1->GetXaxis()->SetLabelFont(42);
+   CanmI75__1->GetXaxis()->SetLabelSize(0.035);
+   CanmI75__1->GetXaxis()->SetTitleSize(0.035);
+   CanmI75__1->GetXaxis()->SetTitleFont(42);
+   CanmI75__1->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI75__1->GetYaxis()->CenterTitle(true);
+   CanmI75__1->GetYaxis()->SetLabelFont(42);
+   CanmI75__1->GetYaxis()->SetLabelSize(0.035);
+   CanmI75__1->GetYaxis()->SetTitleSize(0.035);
+   CanmI75__1->GetYaxis()->SetTitleOffset(1.5);
+   CanmI75__1->GetYaxis()->SetTitleFont(42);
+   CanmI75__1->GetZaxis()->SetLabelFont(42);
+   CanmI75__1->GetZaxis()->SetLabelSize(0.035);
+   CanmI75__1->GetZaxis()->SetTitleSize(0.035);
+   CanmI75__1->GetZaxis()->SetTitleFont(42);
+   CanmI75__1->Draw("");
+   
+   Double_t Graph0_fx1001[5] = {
[…]

### 2019-04-17 chap6-fig/F_RvNu.C

@@ -1,0 +1,710 @@
+{
+//=========Macro generated from canvas: Plot_1/Multiplicity Ratio as a function of #nu
+//=========  (Thu Mar 21 18:22:26 2019) by ROOT version 6.14/00
+   TCanvas *Plot_1 = new TCanvas("Plot_1", "Multiplicity Ratio as a function of #nu",0,0,600,500);
+   Plot_1->Range(0,0,1,1);
+   Plot_1->SetFillColor(0);
+   Plot_1->SetBorderMode(0);
+   Plot_1->SetBorderSize(2);
+   Plot_1->SetFrameBorderMode(0);
+   
+   TH2D *CanmI76__2 = new TH2D("CanmI76__2","Multiplicity Ratio as a function of #nu",100,2.25,4.25,100,0,.9);
+   CanmI76__2->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI76__2->SetLineColor(ci);
+   CanmI76__2->GetXaxis()->SetTitle("#nu (GeV)");
+   CanmI76__2->GetXaxis()->CenterTitle(true);
+   CanmI76__2->GetXaxis()->SetLabelFont(42);
+   CanmI76__2->GetXaxis()->SetLabelSize(0.035);
+   CanmI76__2->GetXaxis()->SetTitleSize(0.035);
+   CanmI76__2->GetXaxis()->SetTitleFont(42);
+   CanmI76__2->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI76__2->GetYaxis()->CenterTitle(true);
+   CanmI76__2->GetYaxis()->SetLabelFont(42);
+   CanmI76__2->GetYaxis()->SetLabelSize(0.035);
+   CanmI76__2->GetYaxis()->SetTitleSize(0.035);
+   CanmI76__2->GetYaxis()->SetTitleOffset(1.5);
+   CanmI76__2->GetYaxis()->SetTitleFont(42);
+   CanmI76__2->GetZaxis()->SetLabelFont(42);
+   CanmI76__2->GetZaxis()->SetLabelSize(0.035);
+   CanmI76__2->GetZaxis()->SetTitleSize(0.035);
+   CanmI76__2->GetZaxis()->SetTitleFont(42);
+   CanmI76__2->Draw("");
+   
+   Double_t Graph0_fx1005[10] = {
[…]

### 2019-04-17 chap6-fig/F_RvNu_PbC.C

@@ -1,0 +1,274 @@
+{
+//=========Macro generated from canvas: Plot_28/Multiplicity Ratio as a function of #nu
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_28 = new TCanvas("Plot_28", "Multiplicity Ratio as a function of #nu",0,0,600,500);
+   Plot_28->Range(0,0,1,1);
+   Plot_28->SetFillColor(0);
+   Plot_28->SetBorderMode(0);
+   Plot_28->SetBorderSize(2);
+   Plot_28->SetFrameBorderMode(0);
+   
+   TH2D *CanmI103__29 = new TH2D("CanmI103__29","Multiplicity Ratio as a function of #nu",100,2.25,4.25,100,0.45,0.7);
+   CanmI103__29->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI103__29->SetLineColor(ci);
+   CanmI103__29->GetXaxis()->SetTitle("Nu (GeV)");
+   CanmI103__29->GetXaxis()->CenterTitle(true);
+   CanmI103__29->GetXaxis()->SetLabelFont(42);
+   CanmI103__29->GetXaxis()->SetLabelSize(0.035);
+   CanmI103__29->GetXaxis()->SetTitleSize(0.035);
+   CanmI103__29->GetXaxis()->SetTitleFont(42);
+   CanmI103__29->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI103__29->GetYaxis()->CenterTitle(true);
+   CanmI103__29->GetYaxis()->SetLabelFont(42);
+   CanmI103__29->GetYaxis()->SetLabelSize(0.035);
+   CanmI103__29->GetYaxis()->SetTitleSize(0.035);
+   CanmI103__29->GetYaxis()->SetTitleOffset(1.5);
+   CanmI103__29->GetYaxis()->SetTitleFont(42);
+   CanmI103__29->GetZaxis()->SetLabelFont(42);
+   CanmI103__29->GetZaxis()->SetLabelSize(0.035);
+   CanmI103__29->GetZaxis()->SetTitleSize(0.035);
+   CanmI103__29->GetZaxis()->SetTitleFont(42);
+   CanmI103__29->Draw("");
+   
[…]

### 2019-04-17 chap6-fig/F_RvPh.C

@@ -1,0 +1,710 @@
+{
+//=========Macro generated from canvas: Plot_6/Multiplicity Ratio as a function of #phi_{h}
+//=========  (Thu Mar 21 18:22:26 2019) by ROOT version 6.14/00
+   TCanvas *Plot_6 = new TCanvas("Plot_6", "Multiplicity Ratio as a function of #phi_{h}",0,0,600,500);
+   Plot_6->Range(0,0,1,1);
+   Plot_6->SetFillColor(0);
+   Plot_6->SetBorderMode(0);
+   Plot_6->SetBorderSize(2);
+   Plot_6->SetFrameBorderMode(0);
+   
+   TH2D *CanmI81__7 = new TH2D("CanmI81__7","Multiplicity Ratio as a function of #phi_{h}",100,0,180,100,0,.9);
+   CanmI81__7->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI81__7->SetLineColor(ci);
+   CanmI81__7->GetXaxis()->SetTitle("#phi_{h}");
+   CanmI81__7->GetXaxis()->CenterTitle(true);
+   CanmI81__7->GetXaxis()->SetLabelFont(42);
+   CanmI81__7->GetXaxis()->SetLabelSize(0.035);
+   CanmI81__7->GetXaxis()->SetTitleSize(0.035);
+   CanmI81__7->GetXaxis()->SetTitleFont(42);
+   CanmI81__7->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI81__7->GetYaxis()->CenterTitle(true);
+   CanmI81__7->GetYaxis()->SetLabelFont(42);
+   CanmI81__7->GetYaxis()->SetLabelSize(0.035);
+   CanmI81__7->GetYaxis()->SetTitleSize(0.035);
+   CanmI81__7->GetYaxis()->SetTitleOffset(1.5);
+   CanmI81__7->GetYaxis()->SetTitleFont(42);
+   CanmI81__7->GetZaxis()->SetLabelFont(42);
+   CanmI81__7->GetZaxis()->SetLabelSize(0.035);
+   CanmI81__7->GetZaxis()->SetTitleSize(0.035);
+   CanmI81__7->GetZaxis()->SetTitleFont(42);
+   CanmI81__7->Draw("");
+   
+   Double_t Graph0_fx1065[10] = {
[…]

### 2019-04-17 chap6-fig/F_RvPh_PbC.C

@@ -1,0 +1,274 @@
+{
+//=========Macro generated from canvas: Plot_33/Multiplicity Ratio as a function of #phi_{h}
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_33 = new TCanvas("Plot_33", "Multiplicity Ratio as a function of #phi_{h}",0,0,600,500);
+   Plot_33->Range(0,0,1,1);
+   Plot_33->SetFillColor(0);
+   Plot_33->SetBorderMode(0);
+   Plot_33->SetBorderSize(2);
+   Plot_33->SetFrameBorderMode(0);
+   
+   TH2D *CanmI108__34 = new TH2D("CanmI108__34","Multiplicity Ratio as a function of #phi_{h}",100,0,180,100,0.45,0.8);
+   CanmI108__34->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI108__34->SetLineColor(ci);
+   CanmI108__34->GetXaxis()->SetTitle("#phi_{h}");
+   CanmI108__34->GetXaxis()->CenterTitle(true);
+   CanmI108__34->GetXaxis()->SetLabelFont(42);
+   CanmI108__34->GetXaxis()->SetLabelSize(0.035);
+   CanmI108__34->GetXaxis()->SetTitleSize(0.035);
+   CanmI108__34->GetXaxis()->SetTitleFont(42);
+   CanmI108__34->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI108__34->GetYaxis()->CenterTitle(true);
+   CanmI108__34->GetYaxis()->SetLabelFont(42);
+   CanmI108__34->GetYaxis()->SetLabelSize(0.035);
+   CanmI108__34->GetYaxis()->SetTitleSize(0.035);
+   CanmI108__34->GetYaxis()->SetTitleOffset(1.5);
+   CanmI108__34->GetYaxis()->SetTitleFont(42);
+   CanmI108__34->GetZaxis()->SetLabelFont(42);
+   CanmI108__34->GetZaxis()->SetLabelSize(0.035);
+   CanmI108__34->GetZaxis()->SetTitleSize(0.035);
+   CanmI108__34->GetZaxis()->SetTitleFont(42);
[…]

### 2019-04-17 chap6-fig/F_RvPt.C

@@ -1,0 +1,710 @@
+{
+//=========Macro generated from canvas: Plot_4/Multiplicity Ratio as a function of P_{T}^{2}
+//=========  (Thu Mar 21 18:22:26 2019) by ROOT version 6.14/00
+   TCanvas *Plot_4 = new TCanvas("Plot_4", "Multiplicity Ratio as a function of P_{T}^{2}",0,0,600,500);
+   Plot_4->Range(0,0,1,1);
+   Plot_4->SetFillColor(0);
+   Plot_4->SetBorderMode(0);
+   Plot_4->SetBorderSize(2);
+   Plot_4->SetFrameBorderMode(0);
+   
+   TH2D *CanmI79__5 = new TH2D("CanmI79__5","Multiplicity Ratio as a function of P_{T}^{2}",100,0,1.3,100,0,4);
+   CanmI79__5->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI79__5->SetLineColor(ci);
+   CanmI79__5->GetXaxis()->SetTitle("P_{T}^{2} (GeV^{2}/c^{2})");
+   CanmI79__5->GetXaxis()->CenterTitle(true);
+   CanmI79__5->GetXaxis()->SetLabelFont(42);
+   CanmI79__5->GetXaxis()->SetLabelSize(0.035);
+   CanmI79__5->GetXaxis()->SetTitleSize(0.035);
+   CanmI79__5->GetXaxis()->SetTitleFont(42);
+   CanmI79__5->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI79__5->GetYaxis()->CenterTitle(true);
+   CanmI79__5->GetYaxis()->SetLabelFont(42);
+   CanmI79__5->GetYaxis()->SetLabelSize(0.035);
+   CanmI79__5->GetYaxis()->SetTitleSize(0.035);
+   CanmI79__5->GetYaxis()->SetTitleOffset(1.5);
+   CanmI79__5->GetYaxis()->SetTitleFont(42);
+   CanmI79__5->GetZaxis()->SetLabelFont(42);
+   CanmI79__5->GetZaxis()->SetLabelSize(0.035);
+   CanmI79__5->GetZaxis()->SetTitleSize(0.035);
+   CanmI79__5->GetZaxis()->SetTitleFont(42);
+   CanmI79__5->Draw("");
+   
[…]

### 2019-04-17 chap6-fig/F_RvPt_PbC.C

@@ -1,0 +1,274 @@
+{
+//=========Macro generated from canvas: Plot_31/Multiplicity Ratio as a function of P_{T}^{2}
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_31 = new TCanvas("Plot_31", "Multiplicity Ratio as a function of P_{T}^{2}",0,0,600,500);
+   Plot_31->Range(0,0,1,1);
+   Plot_31->SetFillColor(0);
+   Plot_31->SetBorderMode(0);
+   Plot_31->SetBorderSize(2);
+   Plot_31->SetFrameBorderMode(0);
+   
+   TH2D *CanmI106__32 = new TH2D("CanmI106__32","Multiplicity Ratio as a function of P_{T}^{2}",100,0,1.5,100,0,2);
+   CanmI106__32->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI106__32->SetLineColor(ci);
+   CanmI106__32->GetXaxis()->SetTitle("P_{T}^{2} (GeV^{2}/c^{2})");
+   CanmI106__32->GetXaxis()->CenterTitle(true);
+   CanmI106__32->GetXaxis()->SetLabelFont(42);
+   CanmI106__32->GetXaxis()->SetLabelSize(0.035);
+   CanmI106__32->GetXaxis()->SetTitleSize(0.035);
+   CanmI106__32->GetXaxis()->SetTitleFont(42);
+   CanmI106__32->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI106__32->GetYaxis()->CenterTitle(true);
+   CanmI106__32->GetYaxis()->SetLabelFont(42);
+   CanmI106__32->GetYaxis()->SetLabelSize(0.035);
+   CanmI106__32->GetYaxis()->SetTitleSize(0.035);
+   CanmI106__32->GetYaxis()->SetTitleOffset(1.3);
+   CanmI106__32->GetYaxis()->SetTitleFont(42);
+   CanmI106__32->GetZaxis()->SetLabelFont(42);
+   CanmI106__32->GetZaxis()->SetLabelSize(0.035);
+   CanmI106__32->GetZaxis()->SetTitleSize(0.035);
+   CanmI106__32->GetZaxis()->SetTitleFont(42);
[…]

### 2019-04-17 chap6-fig/F_RvPtinNu.C

@@ -1,0 +1,492 @@
+{
+//=========Macro generated from canvas: Plot_11/Multiplicity Ratio as a function of P_{T}^{2} in various #nu bins
+//=========  (Thu Mar 21 18:22:27 2019) by ROOT version 6.14/00
+   TCanvas *Plot_11 = new TCanvas("Plot_11", "Multiplicity Ratio as a function of P_{T}^{2} in various #nu bins",0,0,600,500);
+   Plot_11->Range(0,0,1,1);
+   Plot_11->SetFillColor(0);
+   Plot_11->SetBorderMode(0);
+   Plot_11->SetBorderSize(2);
+   Plot_11->SetFrameBorderMode(0);
+   
+   TH2D *CanmI86__12 = new TH2D("CanmI86__12","Multiplicity Ratio as a function of P_{T}^{2} in various #nu bins",100,0,1.3,100,0.2,4);
+   CanmI86__12->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI86__12->SetLineColor(ci);
+   CanmI86__12->GetXaxis()->SetTitle("P_{T}^{2} (GeV^{2}/c^{2})");
+   CanmI86__12->GetXaxis()->CenterTitle(true);
+   CanmI86__12->GetXaxis()->SetLabelFont(42);
+   CanmI86__12->GetXaxis()->SetLabelSize(0.035);
+   CanmI86__12->GetXaxis()->SetTitleSize(0.035);
+   CanmI86__12->GetXaxis()->SetTitleFont(42);
+   CanmI86__12->GetYaxis()->SetTitle("R_{Fe}^{#pi^{+}}");
+   CanmI86__12->GetYaxis()->CenterTitle(true);
+   CanmI86__12->GetYaxis()->SetLabelFont(42);
+   CanmI86__12->GetYaxis()->SetLabelSize(0.035);
+   CanmI86__12->GetYaxis()->SetTitleSize(0.035);
+   CanmI86__12->GetYaxis()->SetTitleOffset(1.3);
+   CanmI86__12->GetYaxis()->SetTitleFont(42);
+   CanmI86__12->GetZaxis()->SetLabelFont(42);
+   CanmI86__12->GetZaxis()->SetLabelSize(0.035);
[…]

### 2019-04-17 chap6-fig/F_RvPtinZ.C

@@ -1,0 +1,492 @@
+{
+//=========Macro generated from canvas: Plot_13/Multiplicity Ratio as a function of P_{T}^{2} in various z bins
+//=========  (Thu Mar 21 18:22:27 2019) by ROOT version 6.14/00
+   TCanvas *Plot_13 = new TCanvas("Plot_13", "Multiplicity Ratio as a function of P_{T}^{2} in various z bins",0,0,600,500);
+   Plot_13->Range(0,0,1,1);
+   Plot_13->SetFillColor(0);
+   Plot_13->SetBorderMode(0);
+   Plot_13->SetBorderSize(2);
+   Plot_13->SetFrameBorderMode(0);
+   
+   TH2D *CanmI88__14 = new TH2D("CanmI88__14","Multiplicity Ratio as a function of P_{T}^{2} in various z bins",100,0,1.3,100,0,4);
+   CanmI88__14->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI88__14->SetLineColor(ci);
+   CanmI88__14->GetXaxis()->SetTitle("P_{T}^{2} (GeV^{2}/c^{2})");
+   CanmI88__14->GetXaxis()->CenterTitle(true);
+   CanmI88__14->GetXaxis()->SetLabelFont(42);
+   CanmI88__14->GetXaxis()->SetLabelSize(0.035);
+   CanmI88__14->GetXaxis()->SetTitleSize(0.035);
+   CanmI88__14->GetXaxis()->SetTitleFont(42);
+   CanmI88__14->GetYaxis()->SetTitle("R_{Fe}^{#pi^{+}}");
+   CanmI88__14->GetYaxis()->CenterTitle(true);
+   CanmI88__14->GetYaxis()->SetLabelFont(42);
+   CanmI88__14->GetYaxis()->SetLabelSize(0.035);
+   CanmI88__14->GetYaxis()->SetTitleSize(0.035);
+   CanmI88__14->GetYaxis()->SetTitleOffset(1.3);
+   CanmI88__14->GetYaxis()->SetTitleFont(42);
+   CanmI88__14->GetZaxis()->SetLabelFont(42);
+   CanmI88__14->GetZaxis()->SetLabelSize(0.035);
+   CanmI88__14->GetZaxis()->SetTitleSize(0.035);
[…]

### 2019-04-17 chap6-fig/F_RvQ2.C

@@ -1,0 +1,710 @@
+{
+//=========Macro generated from canvas: Plot_2/Multiplicity Ratio as a function of Q^{2}
+//=========  (Thu Mar 21 18:22:26 2019) by ROOT version 6.14/00
+   TCanvas *Plot_2 = new TCanvas("Plot_2", "Multiplicity Ratio as a function of Q^{2}",0,0,600,500);
+   Plot_2->Range(0,0,1,1);
+   Plot_2->SetFillColor(0);
+   Plot_2->SetBorderMode(0);
+   Plot_2->SetBorderSize(2);
+   Plot_2->SetFrameBorderMode(0);
+   
+   TH2D *CanmI77__3 = new TH2D("CanmI77__3","Multiplicity Ratio as a function of Q^{2}",100,1,4,100,0,0.9);
+   CanmI77__3->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI77__3->SetLineColor(ci);
+   CanmI77__3->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   CanmI77__3->GetXaxis()->CenterTitle(true);
+   CanmI77__3->GetXaxis()->SetLabelFont(42);
+   CanmI77__3->GetXaxis()->SetLabelSize(0.035);
+   CanmI77__3->GetXaxis()->SetTitleSize(0.035);
+   CanmI77__3->GetXaxis()->SetTitleFont(42);
+   CanmI77__3->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI77__3->GetYaxis()->CenterTitle(true);
+   CanmI77__3->GetYaxis()->SetLabelFont(42);
+   CanmI77__3->GetYaxis()->SetLabelSize(0.035);
+   CanmI77__3->GetYaxis()->SetTitleSize(0.035);
+   CanmI77__3->GetYaxis()->SetTitleOffset(1.3);
+   CanmI77__3->GetYaxis()->SetTitleFont(42);
+   CanmI77__3->GetZaxis()->SetLabelFont(42);
+   CanmI77__3->GetZaxis()->SetLabelSize(0.035);
+   CanmI77__3->GetZaxis()->SetTitleSize(0.035);
+   CanmI77__3->GetZaxis()->SetTitleFont(42);
+   CanmI77__3->Draw("");
+   
[…]

### 2019-04-17 chap6-fig/F_RvQ2_PbC.C

@@ -1,0 +1,274 @@
+{
+//=========Macro generated from canvas: Plot_29/Multiplicity Ratio as a function of Q^{2}
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_29 = new TCanvas("Plot_29", "Multiplicity Ratio as a function of Q^{2}",0,0,600,500);
+   Plot_29->Range(0,0,1,1);
+   Plot_29->SetFillColor(0);
+   Plot_29->SetBorderMode(0);
+   Plot_29->SetBorderSize(2);
+   Plot_29->SetFrameBorderMode(0);
+   
+   TH2D *CanmI104__30 = new TH2D("CanmI104__30","Multiplicity Ratio as a function of Q^{2}",100,1,4,100,0.4,.95);
+   CanmI104__30->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI104__30->SetLineColor(ci);
+   CanmI104__30->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   CanmI104__30->GetXaxis()->CenterTitle(true);
+   CanmI104__30->GetXaxis()->SetLabelFont(42);
+   CanmI104__30->GetXaxis()->SetLabelSize(0.035);
+   CanmI104__30->GetXaxis()->SetTitleSize(0.035);
+   CanmI104__30->GetXaxis()->SetTitleFont(42);
+   CanmI104__30->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI104__30->GetYaxis()->CenterTitle(true);
+   CanmI104__30->GetYaxis()->SetLabelFont(42);
+   CanmI104__30->GetYaxis()->SetLabelSize(0.035);
+   CanmI104__30->GetYaxis()->SetTitleSize(0.035);
+   CanmI104__30->GetYaxis()->SetTitleOffset(1.3);
+   CanmI104__30->GetYaxis()->SetTitleFont(42);
+   CanmI104__30->GetZaxis()->SetLabelFont(42);
+   CanmI104__30->GetZaxis()->SetLabelSize(0.035);
+   CanmI104__30->GetZaxis()->SetTitleSize(0.035);
+   CanmI104__30->GetZaxis()->SetTitleFont(42);
[…]

### 2019-04-17 chap6-fig/F_RvQ2inNu.C

@@ -1,0 +1,710 @@
+{
+//=========Macro generated from canvas: Plot_15/Multiplicity Ratio as a function of Q^{2} in a #nu bin
+//=========  (Thu Mar 21 18:22:27 2019) by ROOT version 6.14/00
+   TCanvas *Plot_15 = new TCanvas("Plot_15", "Multiplicity Ratio as a function of Q^{2} in a #nu bin",0,0,600,500);
+   Plot_15->Range(0,0,1,1);
+   Plot_15->SetFillColor(0);
+   Plot_15->SetBorderMode(0);
+   Plot_15->SetBorderSize(2);
+   Plot_15->SetFrameBorderMode(0);
+   
+   TH2D *CanmI90__16 = new TH2D("CanmI90__16","Multiplicity Ratio as a function of Q^{2} in a #nu bin",100,1,4,100,0,.9);
+   CanmI90__16->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI90__16->SetLineColor(ci);
+   CanmI90__16->GetXaxis()->SetTitle("Q^{2} (GeV^{2}/c^{2})");
+   CanmI90__16->GetXaxis()->CenterTitle(true);
+   CanmI90__16->GetXaxis()->SetLabelFont(42);
+   CanmI90__16->GetXaxis()->SetLabelSize(0.035);
+   CanmI90__16->GetXaxis()->SetTitleSize(0.035);
+   CanmI90__16->GetXaxis()->SetTitleFont(42);
+   CanmI90__16->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI90__16->GetYaxis()->CenterTitle(true);
+   CanmI90__16->GetYaxis()->SetLabelFont(42);
+   CanmI90__16->GetYaxis()->SetLabelSize(0.035);
+   CanmI90__16->GetYaxis()->SetTitleSize(0.035);
+   CanmI90__16->GetYaxis()->SetTitleOffset(1.3);
+   CanmI90__16->GetYaxis()->SetTitleFont(42);
+   CanmI90__16->GetZaxis()->SetLabelFont(42);
+   CanmI90__16->GetZaxis()->SetLabelSize(0.035);
+   CanmI90__16->GetZaxis()->SetTitleSize(0.035);
[…]

### 2019-04-17 chap6-fig/F_RvZ.C

@@ -1,0 +1,710 @@
+{
+//=========Macro generated from canvas: Plot_3/Multiplicity Ratio as a function of z
+//=========  (Thu Mar 21 18:22:26 2019) by ROOT version 6.14/00
+   TCanvas *Plot_3 = new TCanvas("Plot_3", "Multiplicity Ratio as a function of z",0,0,600,500);
+   Plot_3->Range(0,0,1,1);
+   Plot_3->SetFillColor(0);
+   Plot_3->SetBorderMode(0);
+   Plot_3->SetBorderSize(2);
+   Plot_3->SetFrameBorderMode(0);
+   
+   TH2D *CanmI78__4 = new TH2D("CanmI78__4","Multiplicity Ratio as a function of z",100,0,1,100,0.2,1.2);
+   CanmI78__4->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI78__4->SetLineColor(ci);
+   CanmI78__4->GetXaxis()->SetTitle("z");
+   CanmI78__4->GetXaxis()->CenterTitle(true);
+   CanmI78__4->GetXaxis()->SetLabelFont(42);
+   CanmI78__4->GetXaxis()->SetLabelSize(0.035);
+   CanmI78__4->GetXaxis()->SetTitleSize(0.035);
+   CanmI78__4->GetXaxis()->SetTitleFont(42);
+   CanmI78__4->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI78__4->GetYaxis()->CenterTitle(true);
+   CanmI78__4->GetYaxis()->SetLabelFont(42);
+   CanmI78__4->GetYaxis()->SetLabelSize(0.035);
+   CanmI78__4->GetYaxis()->SetTitleSize(0.035);
+   CanmI78__4->GetYaxis()->SetTitleOffset(1.3);
+   CanmI78__4->GetYaxis()->SetTitleFont(42);
+   CanmI78__4->GetZaxis()->SetLabelFont(42);
+   CanmI78__4->GetZaxis()->SetLabelSize(0.035);
+   CanmI78__4->GetZaxis()->SetTitleSize(0.035);
+   CanmI78__4->GetZaxis()->SetTitleFont(42);
+   CanmI78__4->Draw("");
+   
+   Double_t Graph0_fx1029[10] = {
+   0,
[…]

### 2019-04-17 chap6-fig/F_RvZ_PbC.C

@@ -1,0 +1,274 @@
+{
+//=========Macro generated from canvas: Plot_30/Multiplicity Ratio as a function of z
+//=========  (Thu Mar 21 18:22:28 2019) by ROOT version 6.14/00
+   TCanvas *Plot_30 = new TCanvas("Plot_30", "Multiplicity Ratio as a function of z",0,0,600,500);
+   Plot_30->Range(0,0,1,1);
+   Plot_30->SetFillColor(0);
+   Plot_30->SetBorderMode(0);
+   Plot_30->SetBorderSize(2);
+   Plot_30->SetFrameBorderMode(0);
+   
+   TH2D *CanmI105__31 = new TH2D("CanmI105__31","Multiplicity Ratio as a function of z",100,0,1,100,0.35,0.75);
+   CanmI105__31->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   CanmI105__31->SetLineColor(ci);
+   CanmI105__31->GetXaxis()->SetTitle("z");
+   CanmI105__31->GetXaxis()->CenterTitle(true);
+   CanmI105__31->GetXaxis()->SetLabelFont(42);
+   CanmI105__31->GetXaxis()->SetLabelSize(0.035);
+   CanmI105__31->GetXaxis()->SetTitleSize(0.035);
+   CanmI105__31->GetXaxis()->SetTitleFont(42);
+   CanmI105__31->GetYaxis()->SetTitle("R_{A}^{#pi}");
+   CanmI105__31->GetYaxis()->CenterTitle(true);
+   CanmI105__31->GetYaxis()->SetLabelFont(42);
+   CanmI105__31->GetYaxis()->SetLabelSize(0.035);
+   CanmI105__31->GetYaxis()->SetTitleSize(0.035);
+   CanmI105__31->GetYaxis()->SetTitleOffset(1.3);
+   CanmI105__31->GetYaxis()->SetTitleFont(42);
+   CanmI105__31->GetZaxis()->SetLabelFont(42);
+   CanmI105__31->GetZaxis()->SetLabelSize(0.035);
+   CanmI105__31->GetZaxis()->SetTitleSize(0.035);
+   CanmI105__31->GetZaxis()->SetTitleFont(42);
+   CanmI105__31->Draw("");
+   
[…]
